### 2016-08-03 WinterResearch/Report.Rmd
Updated Report, Scenes and Faces

---
title: "Report"
author: "Stephanie Kobakian, Mitchell O'Hara Wild"
date: "26 July 2016"
output: pdf_document
geometry: margin=.75in
---

(1) Background: 2-3 paragraphs describing the mental side of tennis, need for direct measurement, tools for other applications with unknown performance in high-performance sport

As many Tennis Professionals believe that tennis is a game heavily affected by the mental states of the players, the opportunity for researching this concept presents itself with the hope of improving the playing and coaching of Tennis players. By measuring and analysing the faces and expressions of players during a match there is a hope that insight may be gained into the affects of the mental state on the outcome of a match.

In this paper, we investigate the performance of several popular facial recognition algorithms and evaluate their performance when applied to the broadcasts of elite tennis matches. While it is impossibe to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through recognition softwares.

Make use of the recognition softwares currently available presents a challenge as high performance sports are not the intended uses of such softwares.
Their capabilities are often limited to their intended uses. This report aims to analyse the application of these softwares to a broadcast to find a suitable software for use on a pre recorded tennis broadcast file.

(2) Materials: Paragraph describing the sample and sampling approach; processing of selecting the software, which we ended up with and anything we know about their methodology/limitations

The sample consisted of a set of 6404 still images. These images were taken at every three seconds, from 5 minute segments of the 105 Broadcast video files.
All 105 Broadcast video files were the live broadcast of the tennis match shown on the 7 Network during th Australian Open 2016.
To test the softwares the diversity of the players had to be considered, therefore the sample included singles tennis matches played between females and males. The rounds of the competition vary as to not limit the pool of players to only those who progressed, though there was a higher chance of these players appearing.

- Gender, either Male or Female
- Court, one of 7 possible courts

We then took:

- 
- Of these segments, a still was taken at every 3 seconds

##

(3) Methodology: Describe the annotation tool developed and procedure; describe collection of algorithm results; describe the validation analysis

(4) Results: Table 1 = Describe the characteristics of the images - how many? what are the typical situations? how many have faces? etc. Table 2 = Describe the images/boxes identified by the algorithms--what are they typically like? what is the area represented? Table 3= Evaluate the performance: what is the overall accuracy of each algorithm (sample should be annotated faces + all boxed identified by algorithms) How often is type I error made (a face detached incorrectly)? How often type II error (a face is incorrectly NOT detected)? How often are duplicates? Table 4 = Identify possible explanatory factors to performance; Does accuracy vary by lighting conditions? face size? obscuring factors? angle? etc.

(5) Conclusions

(6) Future Work

### 2016-08-11 analysis.R
Finished merging all face data

@@ -5,14 +5,13 @@ library(imager)
 library(dplyr)
 library(tidyr)
 library(purrr)
-library(rgeos)
 
 #Load Data
-MicrosoftClassifiedFaces <- read.csv("MicrosoftClassifiedFaces.csv")
-AnimetricsClassifiedFaces <- read.csv("AnimetricsClassifiedFaces.csv")
-SkybiometryClassifiedFaces <- read.csv("SkybiometryClassifiedFaces.csv")
-ManualClassifiedFaces <- read.csv("ManualClassifiedFaces.csv")
-ManualClassifiedScenes <- read.csv("ManualClassifiedScenes.csv")
+MicrosoftClassifiedFaces <- read.csv("~/github/face-recognition/MicrosoftClassifiedFaces.csv")
+AnimetricsClassifiedFaces <- read.csv("~/github/face-recognition/AnimetricsClassifiedFaces.csv")
+SkybiometryClassifiedFaces <- read.csv("~/github/face-recognition/SkybiometryClassifiedFaces.csv")
+ManualClassifiedFaces <- read.csv("~/github/face-recognition/ManualClassifiedFaces.csv")
+ManualClassifiedScenes <- read.csv("~/github/face-recognition/ManualClassifiedScenes.csv")
 
 #Check all equal length
 length(unique(MicrosoftClassifiedFaces$file))
@@ -25,7 +24,9 @@ AnimetricsClassifiedFaces <- AnimetricsClassifiedFaces[!is.na(AnimetricsClassifi
 SkybiometryClassifiedFaces <- SkybiometryClassifiedFaces[!is.na(SkybiometryClassifiedFaces$width),]
 
 #Manual Classified Faces minimum size set
-ManualClassifiedFaces <- ManualClassifiedFaces[ManualClassifiedFaces$xmax - ManualClassifiedFaces$xmin > 36,]
+ManualClassifiedFaces <- ManualClassifiedFaces %>%
+  mutate(type = "Manual", time.user.self=NA, time.sys.self=NA, time.elapsed=NA, ID=1:NROW(ManualClassifiedFaces)) %>%
+  filter(xmax - xmin > 36)
 
 #Merge data
 MicrosoftMerge <- MicrosoftClassifiedFaces %>% 
@@ -44,7 +45,6 @@ SkyBiometryMerge <- SkybiometryClassifiedFaces %>%
          minY = (center.y - height/2)*4.5, maxY = (center.y + height/2)*4.5) %>%
[…]

### 2016-11-13 presentation.Rmd
added presentation

---
title: "Facial Recognition"
author: 
  - Stephanie Kobakian
  - Mitchell O'Hara-Wild
date: "26 September 2016"
output: 
  revealjs::revealjs_presentation:
    theme: black
    highlight: pygments
    transition: slide
    center: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Winter research project {data-background="img/intro_bg.png"}

## Project goals

- Find the best facial recognition software for tennis matches
- Build manually classified dataset of faces
- Compare software performance under varied conditions
- Determine ideal camera feeds for facial recognition

## Challenges

- Access to usable images and videos
- Availability of software
- Using the software
- Time constraints

# Applications of facial detection software

## Camera auto-focus
![Camera auto-focus](img/Face_detection.jpg)

## Facebook's image tagging
![Facebook's tagging feature for quick classification of friends](img/FacebookTag.png)

## Snapchat filters
![snap](img/snapchat.jpg)

## Surveillance and security
![security](img/security.png)

## Google's Mobile Vision

![Google Mobile Vision](img/googleMobile.png)

# Applying facial recognition to tennis

## Emotion in tennis

Serena Williams

> "Tennis is mostly mental. You win or lose the match before you even go out there."

![Serena GIF](img/serenaWilliams.gif)

## Long-term goals

- Better understand emotion's effect on player performance
- Automatic collection of player emotion data from video

# Manual classification

## Dataset

- 6406 Australian Open images (2.8GB)
- 800x450px size frames from 105 match broadcast videos
- Video frames taken every 3 seconds over a 5 minute segment

## So how do we classify these?
- Do it in Excel
- Write a website
- Write a program

## Shiny Application
![ShinyApp](img/shiny.png)

# Facial recognition software

## Evaluated software (APIs)

- Animetrics
- Skybiometry
- Microsoft
- Google

## Comparison of features

| Feature        | Google | Microsoft | Skybiometry | Animetrics |
|----------------|--------|-----------|-------------|------------|
| Face features  | ✔      | ✔         | ✔           | ✔          |
| Head angle     | ✔      | ✔         | ✔           | ✔          |
| Basic emotion  | ✔      | ✔         |             |            |
| Face landmarks | ✔      | ✔         |             | ✔          |
| Scene labels   | ✔      |           |             |            |
| 3D points      | ✔      |           |             |            |

## Using the software

> API: Application programming interface

APIs are built to be part of a larger program.

(for example, a camera app)

In order to use them, we need to write scripts to use the API.

## Running the scripts

Detecting faces in each image typically took 3-4 seconds.

To complete all 6406 images, it would take 5-7 hours, per API.

Some APIs had usage limits, and took several days to run.

## Raspberry Pie
![RaspPie](img/raspberry-pie-4.jpg)

## Raspberry Pi
![RPi](img/rasp.png)

## Raspberry Pi
![RaspPi](img/RP.png)

## Several days later...

We have all our data!  
(toward the end of the original project window)

# Preparing the data

## Overlaying face boxes
Check if the software is producing sensible output.
```{r,echo=FALSE, message=FALSE}
ALLmetaIMG <- read.csv("~/github/face-recognition/ALLmetaIMG.csv")

ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))

ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:3, labels = c("Player", "Other staff on court", "Fan", "None"))
ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 0:2, labels = c("Direct sunlight", "Shaded", "Partially shaded"))
ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))

library(imager)
library(dplyr)
library(tidyr)

prepareFaceBox <- function(data){
  boxX <- c(data$minX, data$minX, data$maxX, data$maxX, data$minX)
  boxY <- c(data$maxY, data$minY, data$minY, data$maxY, data$maxY)
  data.frame(x = boxX, y = boxY)
}

library(ggplot2)
getManualCount <- function(type, nTotal) {
  return(nTotal[type == "Manual"])
}
ggplotProportion <- function(dataset, factorVar){
  factorVar <- deparse(substitute(factorVar))
  dataset <- dataset %>% filter(matchesManual) %>% group_by_(factorVar, "type") %>% summarise(nTotal=n()) %>% group_by_(factorVar) %>% mutate(ManualCount = getManualCount(type, nTotal)) %>%
    mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
  ggplot(dataset, aes(x=factor(xvar), y=proportion, group = type, fill=type)) + geom_bar(stat = "identity", position = "dodge") +
    ylab("Proportion of faces matched") + xlab(factorVar)
}

overlayFaceBox <- function(imgList, mergeData, matchBox=TRUE){
  for(i in imgList){
    img <- load.image(paste0("images/", i))
    plot(img)
    faceData <- mergeData %>% filter(file == i)
    if(NROW(faceData) > 0){
      for(face in 1:NROW(faceData)){
        faceBox <- faceData[face,] %>% prepareFaceBox()
        if(matchBox){
          lines(faceBox$x, faceBox$y, col=as.numeric(faceData[face,"boxID"])+1)
        }
        else{
          lines(faceBox$x, faceBox$y, col=as.numeric(faceData[face,"type"])+1)
        }
      }
      if(!matchBox){
        legend("topright", legend = unique(faceData$type), col = unique(as.numeric(faceData$type) + 1), lty = 1)
      }
    }
  }
}
```

## Data is reasonable!

```{r, }
overlayFaceBox("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png", ALLmetaIMG, FALSE)
```

## Most of the time.

```{r}
overlayFaceBox("2016_HSA_R01_PKohlschreiber_GER_vs_KNishikori_JPN_MS116_clip.0057.png", ALLmetaIMG, FALSE)
```

## Merging the data

Collected data was spread across 6 files, to analyse it, we need to merge it all together.

![Data structure](img/DataLayout.png)

## Matching face boxes

We also need to determine if the boxes from each API match the same face.

This is also important for importing the extra face information from the manual classification.

Comparing every box generated, if the intersection of the box was >10%, they matched.

![box intersection](img/sharedBox.png)

## Matching face boxes
```{r}
overlayFaceBox("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0020.png", ALLmetaIMG, TRUE)
```

# Analysing the data

## Shot angles
```{r}
ggplotProportion(ALLmetaIMG, shotangle)
```

## Best shot angle
Player close-up
![closeup](img/closeup.png)

## Worst shot angle
Birds-eye view
![birdseye](img/birdseye.png)

## Hats and visors
As expected, they reduce the detection.
```{r, echo=FALSE}
ggplotProportion(ALLmetaIMG, visorhat)
```

## Classification time
![time](img/recognitionTime.png)

## Face size
![size](img/size.png)

# Conclusions

## The best facial recognition software

Google

- Provided the most accurate face detection
- Provided lots of meta information
- Includes basic emotion recognition
- Well priced

## Room for improvement

Facial recognition software needs work to improve detection of faces, let alone emotion.

Some basic emotion is possible, however the precision is questionable, especially with players expressions during a game.

## Further research

- Use higher definition images
- Obtain and use only best camera angles
- Analyse player microphone audio for emotion
- Use videos for facial recognition

# Q & A

### 2016-12-13 Report06-12.Rmd
Rearranging Repo

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: Stephanie Kobakian, Mitchell O'Hara Wild. Supervised by Dianne Cook, Stephanie
  Kovalcik
date: "November 19 2016"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
fontsize: 11pt
bibliography: references.bib
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
require(pander)
require(ggplot2)
require(imager)
require(devtools)
require(knitcitations)
require(RefManageR)
require(readr)
require(knitr)
require(grid)
require(tidyverse)
require(magick)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,cache=TRUE)

options("citation_format" = "pandoc")

BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')

setwd("C:/Users/steff/Github/face-recognition-presentation")

#csv files:
ALLmetaIMG<-read_csv("ALLmetaIMG.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
FaceAttributes<-read_csv("TableCSVs/FaceAttributes.csv")
SolutionSpecs<-read_csv("TableCSVs/SolutionSpecifications.csv")

#plot images with overlaid boxes
overlayGgplot <- function(imgList, mergeData, matchBox=TRUE){
  for(i in imgList){

    img <- image_read(paste0("images/", i))

    p <- ggplot(data.frame(x=c(0,800), y=c(0,450)), aes(x,y)) +
      theme_void()+ coord_fixed()+
      annotation_custom(rasterGrob(img)) +
      scale_x_continuous(expand = c(0,0), limits = c(0,800)) +
      scale_y_continuous(expand = c(0,0), limits = c(0,450))

    faceData <- ALLmetaIMG %>% filter(file == i)

      if(nrow(faceData) == 0){
      return(p)
    } else{

      faceData <- faceData %>%
        mutate(x1 = minX, x2 = minX, x3 = maxX, x4 = maxX, x5 = minX,
               y1 = minY, y2 = maxY, y3 = maxY, y4 = minY, y5 = minY) %>%
        gather(corner, boxPos, x1:y5) %>%
        mutate(posCoord = substr(corner, 1, 1), posID = substr(corner, 2, 2)) %>%
        select(-corner) %>% spread(posCoord, boxPos)

    }
    if(matchBox){
      p <- p + geom_path(aes(x=x, y=450-y, group = faceID, colour=faceID), faceData) + guides(colour="none")
    }
    else{
      p <- p + geom_path(aes(x=x, y=450-y, group = faceID, colour=type), faceData)
 }
  }
  return(p)
}

# Create graphs of factors in manual proportions
getManualCount <- function(type, count) {
  return(count[type == "Manual"])
}
ggplotProportion <- function(dataset, factorVar){
  factorVar <- deparse(substitute(factorVar))
  dataset <- dataset %>% filter(matchesManual) %>% group_by_(factorVar, "type") %>% summarise(nTotal=n()) %>% group_by_(factorVar) %>% mutate(ManualCount = getManualCount(type, nTotal)) %>%
    mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
  ggplot(dataset, aes(x=factor(xvar), y=proportion, group = type, fill=type)) + geom_bar(stat = "identity", position = "dodge") +
    ylab("Proportion of faces matched") + xlab(factorVar)
}

#Factor Names 
ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))

ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:3, labels = c("Player", "Other staff on court", "Fan", "None"))
ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 0:2, labels = c("Direct sunlight", "Shaded", "Partially shaded"))
ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))

ALLmetaIMG$headangle <- as.character(ALLmetaIMG$headangle)
ALLmetaIMG$headangle[ALLmetaIMG$headangle == "Back of head"] <- "Other"
ALLmetaIMG$headangle <- as.factor(ALLmetaIMG$headangle)

ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")

```

##Introduction##

Many Tennis professionals believe that tennis is a game heavily affected by the mental states of the players. The opportunity for researching this concept presents itself with the hope of improving the playing and coaching of Tennis players. 
By statistically analysing the faces and expressions of players during a match there is a hope that insight may be gained into the effects of the mental state on the outcome of a match.
Facial expressions during competition provide the most direct insight into a player's thoughts. The aim of this project is to begin to develop methods to collect accurate information about the facial expressions of elite tennis athletes during matchplay.

In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcasted videos of elite tennis matches. While it is impossible to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through results produced by a recognition software.

Making use of the recognition software's currently available presents a challenge as high performance sports are not the intended uses of such software's.
Their capabilities are often limited to their intended security and surveillance uses. This report aims to analyse the application of these software's to a broadcast to find a suitable software and API to use to analyse a pre-recorded tennis broadcast file.

####Project Aim
- Find the best facial recognition software for tennis matches
- Build manually classified dataset of faces
- Compare software performance under varied conditions

####Sample and sampling approach#### 
The goal of the sample was to be representative of the video files that will be used for future facial recognition analysis.

- 6406 Australian Open images (2.8GB)
- 800x450px size frames from 105 match broadcast videos
- Video frames taken every 3 seconds over a 5 minute segment

The sample consisted of a set of 6404 still images. To produce these images, a still shot of the frame was taken at every three seconds, for the length of each 5 minute segment. The stills were provided by Tennis Australia for use in this research, these segments were taken from 105 video files, which were the broadcast of the Tennis Matches shown on the Seven Network during the Australian Open 2016. The sample included an equal amount of singles tennis matches played between females and males. The rounds of the competition vary as to not limit the pool of players to only those who progressed, though there was a higher chance of advancing players reappearing.

There are many matches played during the Australian Open, and they are played on the range of courts available at Melbourne Olympic Park. Therefore the sample was selected to be representative of the seven courts that have the Hawk Eye technology enabled.

####Selecting the software####
The choice of the initial softwares considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'

The process of software selection to determine which we would compare was based on several criteria. Firstly, we based our choices on the results of the report as it considered processing speed and feature selction techniques, as well as the ability to perform both still-to-video and video-to-video recognition.

From the software's analysed we considered availability for use within the timeframe of the report. This led us to choose Animetrics FaceR. The report outlines that for Animetrics, 'one requirement is that image/face proportion
should be at least 1:8 and that at least 64 pixels between eyes are required'. We realise this could present challenges given our dataset.
It will also allow for an extension from detecting to recognising people in the dataset.

After considering several other off-the-shelf products, we did not choose any other software's from those analysed as they were not as readily available as other products on the market.

This led to SkyBiometry, an API that also allows for both detection and recognition. The cloud-based software as a service, is a 'spin-off of Neurotechnology', a software considered by the report.

We then chose to consider company's who are expanding their API ranges. This resulted in the choice of Microsoft API, provided by Microsoft Cognitive Services. This detects faces and return a square area where the face was located, and predicts facial features. It also allows the possibility of video stream detection.

The final software we chose to analyse was Google Vision API. Due to Google's expansion in many web based solutions we researched for a facial recognition software. While it was somewhat difficult to access

We were able to try the online demos to see whether these softwares were viable, we used the following image:
```{r Trial Image, results=FALSE}
imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
overlayGgplot(imagesList0, ALLmetaIMG, matchBox = FALSE)
```

## Methodology ##
An annotation tool was constructed to create a base for comparative analysis, we refer to this as Manual Classifications.
These manual Classifications involved describing the features of the Scenes. For this we considered the following attributes of the scenes:

#####**Table 1.** Scene Attributes
```{r T1 Scene Attributes Table}
kable(SceneAttributes, format = "pandoc", booktabs = TRUE)
```

The aim was to collect specific information on each different face within the scene. To determine which of the sometimes many faces in the scene it would be reasonable for softwares to detect a standard was created for reasonable detection. This was based on the attributes provided in the table below:

#####**Table 2.** Solution Specifications
```{r T2 Solution Specifications Table, results='asis'}
kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)

```

It was decided that it would be reasonable for a software to detect was decided to be a face size larger than 20 by 20 pixels, as it was specified that the software had minimum distances between the eyes on a face for recognition. (reference table with values)
If it was the face of a player it was always recorded if it captured their face. The back of the head was not able to be picked up by any software, so after a demo trial these faces were not classified manually.
Crowd shots provided difficultly in determining which faces were reasonable to classify. As these faces were not the intended targets of the recognition these faces were contributing to our understanding of the softwares. 
The same face size standard applied to crowd memebers, but focus was placed on the most prominent faces. For each of these faces, we collected information on the following attributes:

#####**Table 3.** Face Attributes
```{r T3 Face Attribute Tables, results='asis'}
kable(FaceAttributes, format = "pandoc", booktabs = TRUE)

```

####Manual Annotation
To record these questions a Shiny App was created. We called this Application our ManualClassificationProgram. This helped to provide information for all attributes readily and consistently. This worked by presenting an image, using the imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene table as shown above. If there was a face in the image we were able to highlight the square 'Face Box'. This recorded the x and y coordinates of the box drawn, and when the save button was hit it saved all the radio button selections and the 'Face Box' coordinates to a CSV file.

Following the saving of each face, and the Scene radio button selections, the save button would then save the Scene selections to a separate CSV file. This data can be seen in the ManualClassifiedFaces.csv file located in the appendix.

If there were issues, the CSV files were able to be edited, this was reserved for extreme circumstances. And a lot of care was taken to ensure the first selections were correctly submitted and applied to the correct Faces and Scenes.

The results in the CSV files showed the file name, and the attributes relating to the Scene being considered. 
This can be seen in the ManualClassifiedScenes.csv file located in the appendix.

####Software Recognition
The software choices allowed for POST requests to be sent via the internet. To access the APIs through R we enlisted the httr package, using functions from this package a script was written for each software API, it would loop through the images, individually posting a request for each image to be analysed. These scripts included retrieving the information provided and converting it into a usable format.
One interesting anomoly was found when using the Skybiometry software as it limited the amount of requests per minute. We accounted for this by stalling the posts for the amount of waiting time the software notified, and checking until the time lapsed and the script could continue looping.

####Data Manipulation
The collected data was spread across 6 files. See Appendices.
For each software we had the classified faces csv file, these are located in the appendix.
The collation of the results from the Manual Recognition Program created the files ManualClassifiedFaces and ManualClassifiedScenes.

A single data set was created to combine all necessary information in the previously mentioned files for our analysis. The information in the dataset,(cite ALLmetaIMG.csv,) was carefully considered. It considers the identify of each face, and all relative face attributes, as well as the image file the face was found in, from this information each face was able to be uniquely identified. Also included was information on the software that found it, and the time it took the software to identify the face. It also has a record of how many faces had been indentified in the image by counting each additional recognised face.

To find whether the softwares were recongising the same faces a function was created. As the location and size of the boxes around the faces were recorded, these values were used to see if a particular identified face box matched a manually identified face.
 This function uses the information of each face and compares the intersecting regions of the polygons created by the x,y coordinates of Manual Faces and other software's faces, to determine if the same face was recognised. We determined the ratio of intersecting area to total area must be greater than 0.1 to be considered the same face. This allowed us to compare the identification areas, as well as contrast the identified faces of each software.

####Analysis
The statistical analysis conducted to summarise and assess the validity of the method.
This method allowed all the softwares and the faces they found to be compared.

## Results
Using the database of the combined results, we were able to compare the performance of the softwares.
Firstly, we considered how many individual faces the softwares were able to detect.

#####**Graph 1.** Face Bounding Box Data: Bar Chart
```{r G1 Face Bounding Box Data, results='hide'}
ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge")  +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE) 
```

The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognised almost 1000 more faces than the next best software, Microsoft.

#####**Graph 4.** Face Bounding Box Data: Box Plot 
```{r G4 Face Bounding Box Data}
ggplot(ALLmetaIMG, aes(x = factor(x = factor(type)), fill=type, y = size)) + geom_boxplot() + scale_y_continuous(trans='log') +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Google","Animetrics","Manual","Microsoft","Skybiometry"))+ylab("Size of Face Bounding Boxes")+guides(fill=FALSE)

```

This box and whisker plot shows the differences between the sizes of the 'Face Bounding Boxes' produced by each software. Where a 'Face Bounding Box' refers to the size of the square the software provided as a location in the image of a face that was detected. On average, Google maps the largest boxes around faces, however Animetrics has the largest box recognised in the set. On average, the smallest faces are recognised by Skybiometry.

Skybiometry results accounted for the 255 smallest recognised faces. However this is not necessarily a benefit to this research, as these are not all faces.

Note: Skybiometry boxes are pink, Microsoft are blue, Google are Green and Animetrics are Red.

##### Image 2.2016_CT6_R02_JSousa_POR_vs_SGiraldo_COL_MS231_clip.0017.png
```{r I2, results=TRUE}
imagesList2<-as.list("2016_CT6_R02_JSousa_POR_vs_SGiraldo_COL_MS231_clip.0017.png")
overlayGgplot(imagesList2, ALLmetaIMG, matchBox = FALSE)
```

This image shows the smallest Face Bounding Box recognised. However visual inspection shows it only captures the player's eye and nose, not their whole face.

##### Image 3.2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png
```{r I3, results=TRUE}
imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
overlayGgplot(imagesList3, ALLmetaIMG, matchBox = FALSE)
```

As before, the 'face' is not as we would hope it would be classified. Just right of the centre, the smaller box actaully captures a fist, not a face.

##### Image 4.2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png
```{r I4,results=TRUE}
imagesList4<-as.list("2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png")
overlayGgplot(imagesList4, ALLmetaIMG, matchBox = FALSE)
```

This is almost usable, however this shows the sensitivity of the software. We may consider this too sensitive as it recognised the eye and nose of the ballboy on the court.

##### Image 5.2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png
```{r I5, results=TRUE}
imagesList5<-("2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png") 
overlayGgplot(imagesList5, ALLmetaIMG, matchBox = FALSE)
```

As seen in this image of the crowd, the software is performing reasonably well. It does recognise the faces, yet only one not recognised by the other softwares, this may be due to the sunglasses.

This image demonstrates that the it is not necessarily the smaller faces that Skybiometry recognises, but it puts smaller bounds on the facial features than other softwares.

#####**Table 4.** Type Matches Manual
```{r T4 Type Matches Manual}
library(descr, quietly = TRUE)
NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
NoManual<-NoManual %>% droplevels(NoManual$type)
Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
pander(CrossTable(Accuracy, prop.chisq = FALSE) , digits = 2)
```

To evaluate the performance in terms of the overall accuracy of each algorithm we considered the amount of faces they classified that matched faces that were selected manually.

The sample used contains all the manually annotated faces and all the faces recognised by the four softwares.

To consider how many Type I errors occured, where a face was detected incorrectly, we look at the Bounding Boxes that do not match manually annotated faces.

Table 4 shows whether the potential Face Bounding Boxes match faces that were annotated during the manual classifications. Where the FALSE row denotes where software's Face Bounding Boxes do not coincide with manually annotated faces. The tables shows that Google found 38.70% of the 90.34% of the Faces found that matched Faces also identified manually.

A potential face detected that does not match a face manually annotated occurs for 9.66% of all the Faces detected by the softwares. This is especially high for Google with 289 faces identified.

All the Face Bounding Boxes that Google found which do not match manually annotated faces were correctly identifying faces. This exhibits the occurences of errors.

We then considered the characteristics of the images that the softwares found Potential Face Bounding Boxes^[These boxes represent an area of pixels that are a potentially recognised face.] in.

#####**Table 5.** Image Characteristics
```{r T5 Image Characteristics Table}
ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))

kable(ImageCharacteristics[1:10,], format = "pandoc", booktabs = TRUE)
```

This table displays the feature combinations that produced the most potential face Bounding Boxes recognitions by all four softwares. The most common shot is a crowd shot.
The second row in the table with 830 faces recognised is more interesting than the first result. This useful scene is an image of a Court Player Close-Up in front of a Logo Wall, taken at Player Shoulder Height.

These attributes typically represent an image similar to the following:

##### **Image 1.Typically Recognised Image**

```{r I1 Typical Best Recognised, results=FALSE}
imagesList1<-as.list("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png") 
overlayGgplot(imagesList1, ALLmetaIMG, matchBox = FALSE)
```

#####**Table 6.** Google Errors Characteristics
```{r T6 Google Errors Characteristics Table}
library(dplyr)

GoogleNoMatch <- ALLmetaIMG %>%
  filter(type=="Google") %>%
  filter(matchesManual==FALSE) %>%
  group_by(person, situation, bg, shotangle) %>% dplyr::summarise(count=n())

#use this list in the overlay function to view the images where Google found faces not annotated manually
#GoogleImages<-GoogleNoMatch$file
#GoogleImages<-as.list(GoogleImages)

GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
pander(GoogleNoMatch[1:10,], type = 'table')

#overlayGgplot(GoogleImages, GoogleNoMatch, matchBox = TRUE)
```

This Table shows that the potential Face Bounding Boxes Google returned were found in images that had the same characteristics of those that were manually annotated for faces.
This is shown by the same combinations of characteristics occuring in both Table 5 and Table 6. 
Without looking at each individual image this Table confirms that the potential Face Bounding Boxes Google located will likely be reasonable, and actually contain faces.

The best scenes for facial recongition have been found, given this information the following table considers the Characteristics of the individual faces found within those scenes. For this section we chose to consider only the faces that were manually annotated as players, with the intention of not basing results on recognitions of undesirable faces.

#####**Table 7.** Face Characteristics
```{r T7 Face Characteristics Table}
FaceCharacteristics <- ALLmetaIMGPlayers %>%   filter(type=="Google")%>% filter(matchesManual==TRUE)%>% group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())
FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
pander(FaceCharacteristics[1:10,], type = 'table')
```

Table 7 utilises a set of faces that were Manually annotated and also found by Google. 
Nine of the top ten facial characteristic combinations contained faces that were not wearing glasses.
The head angle describing the face angle was 'Other'^[Definition for headangle factor level 'Other' found in..]
for nine of the top ten facial characteristic combinations.

#####**Table 8.** Glasses on Recognised Faces
```{r T8 Glasses}
GlassesGoogle <- ALLmetaIMGPlayers %>% filter(type=="Google") %>%
filter(matchesManual==TRUE)

pander(table(GlassesGoogle$glasses))
```
The extreme disparity between the amount of faces with glasses to without them means that the occurence of these attributes across the softwares must be considered proportionally.

#####**Graph 2.** Glasses
```{r G2 Glasses}
ggplotProportion(ALLmetaIMGPlayers, glasses)
```
Graph 2 above shows that Google outperforms the other softwares, with or without glasses. When there are no glasses worn Google finds over 60% of the manually annotated faces.

#####**Table 9.** Head Angles
```{r T9 HeadAngles}
HeadangleGoogle <- ALLmetaIMGPlayers %>%   filter(type=="Google") %>%
filter(matchesManual==TRUE)

pander(table(HeadangleGoogle$headangle))
```
The amount of faces found by Google with the headangle "Other", is much larger than the amount of faces with the headangle "Profile" or "Front On". Therefor this should also be considered propotionately.

#####**Graph 3.** Glasses
```{r G3 Glasses}
ggplotProportion(ALLmetaIMGPlayers, headangle)
```
Graph 3 diplays that Google performs much better in comparison to the other softwares when the headangle is Profile. This is outperforming unusually well, however this could also be due to the poor performance of the softwares in this circumstance.

Table 2 = Describe the images/boxes identified by the algorithms--what are they typically like? what is the area represented?

Table 3= Evaluate the performance: what is the overall accuracy of each algorithm (sample should be annotated faces + all boxed identified by algorithms) 
  How often is type I error made (a face detected incorrectly)?

##### **Table 10.**
```{r T10}
library(tables, quietly = TRUE)
Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
pander(Accuracy)
```

  How often type II error (a face is incorrectly NOT detected)?   
  3 of the four software's

It should be noted that there were results where a single face was recognised twice within the same image. This was a very unusual result and is notable as a point of interest but given it only occured for Animetrics, it is not worth basing decisions on this unusual result.

Table 4 = Identify possible explanatory factors to performance; Does accuracy vary by lighting conditions? face size? obscuring factors? angle? etc.

#####**Table 11.** Google Characteristics
```{r T11 Google Characteristics Table}
GoogleCharacteristics <- ALLmetaIMG %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
GoogleCharacteristics<-arrange(GoogleCharacteristics, desc(count))

kable(GoogleCharacteristics, format = "pandoc", booktabs = TRUE)
```
This table shows how many images with potential player's faces Google recognised. This diplays a vast gap between the amount of potential faces found given the different shot angles. Shoulder height is an optimum angle for a Face Bounding Box.

Considering only the Shoulder Height Angle, the following Graph looks at how accessories affected Google's recognition.

#####**Graph 4.** Google Face Bounding Boxes: Mosaic Plot
```{r G4 Google Characteristics Mosaic Plot}
GoogleAccessories <- ALLmetaIMG %>% filter(type=="Google") %>% filter(shotangle=="Player Shoulder Height") %>% filter(detect=="Player") %>% filter(lighting!="Direct sunlight")

GoogleAccessories<-droplevels(GoogleAccessories)
#lighting headangle glasses visorhat

mosaicplot(~ headangle + visorhat, data = GoogleAccessories, color = TRUE)

mosaicplot(~ lighting + visorhat, data = GoogleAccessories, color = TRUE)

mosaicplot(~ lighting +headangle +visorhat, data = GoogleAccessories, color = TRUE)

mosaicplot(~ glasses + lighting, data = GoogleAccessories, color = TRUE)

```

### Discussion
Graph 1, the Bar Chart of the Face Bounding Boxes promotes Google as the best possible software for a facial recognition application in tennis. According to Table 4 Google had 38.23% of the 9.66% potential face boxes not annotated manually.
It was considered that this may have shown Google's API may have been finding more unwanted faces than the other softwares. However, visual inspection showed that these were actually faces. This is considered in Table 6, which showed that some of the faces were found in a crowd setting. Therefore some of these could be considered irrelevant, possibly being crowd faces. These were deemed unlikely to be detected and neglected during manual annotation. 
Interestingly, Animetrics had the least amount of matches to Manually annotated faces. Looking into this further showed that Animetrics results contained potential Face Bounding Boxes that did not contain faces.

The images were all considered manually. The scene information was recorded and the combinations were shown to find how many potential face Bounding Boxes were found with the combination of scene attributes.
This showed that crowd members faces were often recognised, this is both helpful and unhelpful as it shows a strong ability of Google's algorithm to recognise faces, even when these faces are not the goal of the research.

Image 1 shows the images preferable for future research. Where the faces will be recognised and allow both the identity and emotion of the players to be recognised.

Google gave the optimum results in this image as it found the face of the player, but did not locate the face of the staff memeber behind him on the court.

While Google's recognitions mostly matched the Manually annotated set of faces, there were some that did not. These were all actually faces and were missed during manual annotations.

Table 6 shows that 190 of the faces that were not found manually occured in the scene of a Court player close-up, with a background of a logo wall, where the shot was taken at player shoulder height.

This shows it was performing extremely well and not resulting in unexplainable face Bounding Boxes as some of the other softwares were. This is a strong indicator that applying Google's software for further research would result in the recognition of desired faces.

These results have contributed to the choice of Google given the optimum scene as described above. Implementing a filtering process, either using current or alternative footage^[See future research for further information on these options] would allow Google to provide Tennis Australia with the most applicable results.

We moved to considering the characteristics of the faces. This helped to distinguish where Google performed well in comparison to the other software options.

Table 7 showed the combinations of attributes that were found for each face[Given that information was not recorded where Google provided facial recognitions for faces not Manually annotated thesse could not be considered.].
The use of accessories, Glasses and Visors or Hats, was considered as the Australian Open takes place on both indoor and outdoor courts. To apply this research all courts that elite Tennis players compete on had to be included.
It was assumed that outdoor courts would led to the use of these accessories and these accessories may contribute to the performance of a recongition software.
It may be implied by the table that Glasses prohibits recognition as all but one of the combinations have 'No' for the Glasses variable. However, we are cautious of validating this as Table 8 tells that there are many more faces recognised, by both the Google recnogitions and manual annotations, that do not have Glasses. This disproportionate sample of faces with Glasses means that we considered it proportionally rather than as a total.

Graph 2 demonstrates that the prescence of Glasses on faces annotated manually did affect recognition by Google's alrgorithm, while it outperformed the other softwares in both instances, faces were identified more often if the person did not wear glasses.

Moving to looking at the characteristics that were considered manually shows that the use of glasses by players coincided with less faces being annotated.

The boxplot in graph encourages our comparisons to not consider the size of face bounding box as a measure of how the software performs on small faces.

#### Challenges

 it is understandable that there would be many more faces to recognise in these shots than in shots where there is only a player, and therefore many more faces recognised. However in this research

- Access to usable images and videos
- Availability of software
- Using the software
- Time constraints

Long Term Goals
- Better understand emotion's effect on player performance
- Automatic collection of player emotion data from video

Method, automated the process to reduce datacleaning and help group characterstics

Pricing

(5) Conclusions 
Employ the Google Vision API, which would allow the use of still images, or video (TEST VIDEO) files, reducing the need for stills.
This product - cost in relation
Ease of access - API calling

(6) Future Work
Considering the images used during our study were stills derived from Broadcast video files,
it would be useful to extend further research to deal with the video files directly. 
These companies have the potential to allow for video recognition......

It should also be considered that there are softwares focussed on providing recognition in certain controlled scenarios.
If the study was controlled to focus on certain camera angles that align with the facial angles these security minded programs
are intended for it may be helpful to extend the research to softwares currently available but were deemed impractical for this study.

To check for manual errors, create another app that shows the 'faces' identified by each program, confirm manually whether or not these are faces.
We feel this would be necessary when expanding on the use

We also feel that incorporating audio information from the microphones worn by players may assist in sentiment analysis.

Getting specific camera angle access from the seven network to reduce the work of computers

To undertake sentiment analysis, we would take the boxes of faces found in this set of images. Allowing each face a border we would crop the images and produce an individual face image that would form the data set for emotion recognition. igh enough quality?

Write a program to create images of only that faces

(7)
Appendix
```{r}

```

## References

citation @Automated

```{r}
#Survey of commercial technologies for face recognition in video

#Report number: DRDC-RDDC-2014-C245

#Affiliation: Department of National Defence of Canada.

```

### 2016-12-13 SoftwareRequestScripts/animetrics.R

@@ -1,5 +1,5 @@
 # Starting script for Animetrics FaceR API
-a.api_key <- "b94ed4dde06aca433a90af1a88c731b2"
+a.api_key <- ""
 a.selection <- "FULL"
 
 image_urls <- c("mitchelloharawild.com/tennis/2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0003.png")

### 2016-12-13 SoftwareRequestScripts/microsoftAPI.R

@@ -1,6 +1,6 @@
 library(httr)
 a <- POST(url="https://api.projectoxford.ai/face/v1.0/detect?returnFaceId=false&returnFaceLandmarks=true",
-     add_headers(`Ocp-Apim-Subscription-Key` = "1f5f1bdb8e7d4a9abf25daea59ce79bc",
+     add_headers(`Ocp-Apim-Subscription-Key` = "",
                  `Content-Type` = "application/json"),
      body = list(`url` = "http://mitchelloharawild.com/tennis/2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0003.png"))
 
@@ -16,7 +16,7 @@ mybody = list(url = img.url)
 
 MicrosoftAPI <- function(img.url){
   POST(url = "https://api.projectoxford.ai/face/v1.0/detect?returnFaceId=false&returnFaceLandmarks=true", 
-    content_type('application/json'), add_headers(.headers = c('Ocp-Apim-Subscription-Key' = "1f5f1bdb8e7d4a9abf25daea59ce79bc")),
+    content_type('application/json'), add_headers(.headers = c('Ocp-Apim-Subscription-Key' = "")),
     body = list(url = img.url),
     encode = 'json'
   )

### 2016-12-14 Report06-12.Rmd
report
Updates

@@
     toc_depth: 2
+    fig_caption: yes
   word_document:
@@
 require(magick)
+require(kfigr)
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,cache=TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,
+                      cache=TRUE, fig.align = 'center')
 
@@
 
-setwd("C:/Users/steff/Github/face-recognition-presentation")
+setwd("C:/Users/steff/Github/face-recognition")
 
@@
 #####**Table 1.** Scene Attributes
-```{r T1 Scene Attributes Table}
-kable(SceneAttributes, format = "pandoc", booktabs = TRUE)
+```{r Scene-Attributes-Table, anchor="table"}
+kable(SceneAttributes, format = "pandoc", booktabs = TRUE, caption = figr("Scene-Attributes-Table", TRUE, type="Table"))
 ```
+
+`r figr("Scene-Attributes-Table", TRUE, type="Table")`   Yayyy
 
@@
 #####**Table 2.** Solution Specifications
-```{r T2 Solution Specifications Table, results='asis'}
+```{r Solution-Specifications-Table, results='asis', anchor="table"}
 kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)
@@
 
-#####**Table 3.** Face Attributes
+#####**Table \label{tab:FAT}.** Face Attributes
 ```{r T3 Face Attribute Tables, results='asis'}
 kable(FaceAttributes, format = "pandoc", booktabs = TRUE)
+```
 
-```
+Table \ref{tab:FAT} above
 
@@
 
-####Data Manipulation
-The collected data was spread across 6 files. See Appendices.
-For each software we had the classified faces csv file, these are located in the appendix.
+####Data Processing
+The data was spread across 6 files. For each software we had the classified faces csv file, these are located in the appendix.
 The collation of the results from the Manual Recognition Program created the files ManualClassifiedFaces and ManualClassifiedScenes.

### 2016-12-14 trial.Rmd
Updates

---
title: "Untitled"
author: "Stepahnie Kobakian"
date: "14 December 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(readr)
require(knitr)

require(kfigr)

SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")

```

```{r Scene-Attributes-Table, anchor="table"}
kable(SceneAttributes, format = "pandoc", booktabs = TRUE)
```

Table `r figr("Scene-Attributes-Table", TRUE, type="Table")`   Yayyy

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2016-12-16 Report06-12.Rmd
Refining Analysis script

@@
 title: "Detecting Facial Expressions in Professional Tennis Matches"
-author: Stephanie Kobakian, Mitchell O'Hara Wild. Supervised by Dianne Cook, Stephanie
+author: Stephanie Kobakian, Mitchell O'Hara-Wild. Supervised by Dianne Cook, Stephanie
   Kovalcik
@@
   pdf_document:
+    fig_caption: yes
     toc: yes
     toc_depth: 2
-    fig_caption: yes
-  word_document:
-    toc: yes
-fontsize: 11pt
+fontsize: 10pt
 bibliography: references.bib
@@
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,
-                      cache=TRUE, fig.align = 'center')
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE)
 
@@
 #plot images with overlaid boxes
-overlayGgplot <- function(imgList, mergeData, matchBox=TRUE){
+overlayGgplot <- function(imgList, mergeData, matchBox=FALSE){
   for(i in imgList){
@@
 
-    faceData <- ALLmetaIMG %>% filter(file == i)
+    faceData <- ALLmetaIMGFaces %>% filter(file == i)
 
@@
     if(matchBox){
-      p <- p + geom_path(aes(x=x, y=450-y, group = faceID, colour=faceID), faceData) + guides(colour="none")
+      p <- p + geom_path(aes(x=x, y=450-y, group = type, colour=boxID), faceData) + guides(colour="none")
     }
     else{
-      p <- p + geom_path(aes(x=x, y=450-y, group = faceID, colour=type), faceData)
- }
+      p <- p + geom_path(aes(x=x, y=450-y, group = type, colour=type), faceData)
     }
   return(p)
+  }
 }
@@
 ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")
+
+#change this to facesVenn with binary information
+ALLmetaIMGFaces<-ALLmetaIMG%>%
+  filter(!is.na(boxID)) %>% 
+  select(-ID, -facecounter)%>%
+  mutate(fileID = as.numeric(factor(file))) %>%
+  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
+  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))
 
@@
 
-We were able to try the online demos to see whether these softwares were viable, we used the following image:
-```{r Trial Image, results=FALSE}
+We were able to try the online demos to see whether these softwares were viable, we used the following  `r figr("Trial-Image", TRUE, type="Figure")`:
+
+```{r Trial-Image, fig.cap="This is a player", anchor="figure"}
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
@@
 An annotation tool was constructed to create a base for comparative analysis, we refer to this as Manual Classifications.
-These manual Classifications involved describing the features of the Scenes. For this we considered the following attributes of the scenes:
+These manual Classifications involved describing the features of the Scenes.
 
-#####**Table 1.** Scene Attributes
-```{r Scene-Attributes-Table, anchor="table"}
-kable(SceneAttributes, format = "pandoc", booktabs = TRUE, caption = figr("Scene-Attributes-Table", TRUE, type="Table"))
+```{r Scene-Attributes-Table, anchor="table", fig.cap="Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute."}
+kable(SceneAttributes, format = "pandoc", booktabs = TRUE)
 ```
-
-`r figr("Scene-Attributes-Table", TRUE, type="Table")`   Yayyy
 
@@
 To determine which of the sometimes many faces in the scene it would be reasonable for softwares to detect a standard was created for reasonable detection.
-This was based on the attributes provided in the table below:
+This was based on the attributes provided in `r figr("Solution-Specifications-Table", TRUE, type="Table")`, below:
 
-#####**Table 2.** Solution Specifications
 ```{r Solution-Specifications-Table, results='asis', anchor="table"}
-kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)
+kable(SolutionSpecs, format = "pandoc", booktabs = TRUE, caption = "Software solutions specifications.")
 
@@
 
-#####**Table \label{tab:FAT}.** Face Attributes
-```{r T3 Face Attribute Tables, results='asis'}
-kable(FaceAttributes, format = "pandoc", booktabs = TRUE)
+```{r Face-Attribute-Tables, results='asis', anchor="table"}
+kable(FaceAttributes, format = "pandoc", booktabs = TRUE, caption = "Attributes of an individual face within an image. The most appropriate option from the list was selected for each attribute.")
 ```
-
-Table \ref{tab:FAT} above
 
@@
 This helped to provide information for all attributes readily and consistently.
-This worked by presenting an image, using the imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene table as shown above.
+This worked by presenting an image, using the imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attibutes in `r figr("Scene-Attributes-Table", TRUE, type="Table")` as shown above.
 If there was a face in the image we were able to highlight the square 'Face Box'.
@@
 
-#####**Graph 1.** Face Bounding Box Data: Bar Chart
-```{r G1 Face Bounding Box Data, results='hide'}
+```{r Face-Bounding-Box-Data, results='hide', type="figure", fig.cap='..', anchor="figure"}
 ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE)
@@
 #####**Graph 4.** Face Bounding Box Data: Box Plot 
-```{r G4 Face Bounding Box Data}
+```{r G4 Face Bounding Box Data, anchor="figure"}
 ggplot(ALLmetaIMG, aes(x = factor(x = factor(type)), fill=type, y = size)) + geom_boxplot() + scale_y_continuous(trans='log') +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Google","Animetrics","Manual","Microsoft","Skybiometry"))+ylab("Size of Face Bounding Boxes")+guides(fill=FALSE)
@@
 
-##### Image 2.2016_CT6_R02_JSousa_POR_vs_SGiraldo_COL_MS231_clip.0017.png
-```{r I2, results=TRUE}
+```{r I2, results=TRUE, fig.cap="2016_CT6_R02_JSousa_POR_vs_SGiraldo_COL_MS231_clip.0017.png", anchor="figure"}
 imagesList2<-as.list("2016_CT6_R02_JSousa_POR_vs_SGiraldo_COL_MS231_clip.0017.png")
@@
 
-##### Image 3.2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png
-```{r I3, results=TRUE}
+```{r I3, results=TRUE, fig.cap="2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png", anchor="figure"}
 imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
@@
 
-##### Image 4.2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png
-```{r I4,results=TRUE}
+```{r I4,results=TRUE, fig.cap="2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png", anchor="figure"}
 imagesList4<-as.list("2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png")
@@
 
-This is almost usable, however this shows the sensitivity of the software. We may consider this too sensitive as it recognised the eye and nose of the ballboy on the court.
+I4 shows the sensitivity of the software. We may consider this too sensitive as it recognised the eye and nose of the ballboy on the court.
 
 ##### Image 5.2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png
-```{r I5, results=TRUE}
+```{r I5, results=TRUE, fig.cap="2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png", anchor="figure"}
 imagesList5<-("2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png") 
@@
 
-#####**Table 4.** Type Matches Manual
-```{r T4 Type Matches Manual}
+```{r Type-Matches-Manual, anchor="table"}
 library(descr, quietly = TRUE)
@@
 Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
-pander(CrossTable(Accuracy, prop.chisq = FALSE) , digits = 2)
+kable((Accuracy))
 ```
@@
 
-#####**Table 5.** Image Characteristics
-```{r T5 Image Characteristics Table}
-ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
+```{r Image-Characteristics-Table, anchor="table"}
+ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
 ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
-
-kable(ImageCharacteristics[1:10,], format = "pandoc", booktabs = TRUE)
+ImageCharacteristics<-ImageCharacteristics[1:10,]
+kable(ImageCharacteristics, booktabs = TRUE)
 ```
 
-This table displays the feature combinations that produced the most potential face Bounding Boxes recognitions by all four softwares. The most common shot is a crowd shot.
+`r figr("Image-Characteristics-Table", TRUE, type="Figure")`
+ displays the feature combinations that produced the most potential face Bounding Boxes recognitions by all four softwares. The most common shot is a crowd shot.
 The second row in the table with 830 faces recognised is more interesting than the first result.
@@
 
-##### **Image 1.Typically Recognised Image**
-
-```{r I1 Typical Best Recognised, results=FALSE}
+```{r Typical-Best-Recognised, results=FALSE, anchor="figure"}
 imagesList1<-as.list("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png") 
@@
 
-#####**Table 6.** Google Errors Characteristics
-```{r T6 Google Errors Characteristics Table}
+```{r Google-Errors-Characteristics-Table, anchor="Table"}
 library(dplyr)
@@
 GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
-pander(GoogleNoMatch[1:10,], type = 'table')
+kable(GoogleNoMatch[1:10,], type = 'table')
 
@@
 
-This Table shows that the potential Face Bounding Boxes Google returned were found in images that had the same characteristics of those that were manually annotated for faces.
-This is shown by the same combinations of characteristics occuring in both Table 5 and Table 6. 
+`r figr("Google-Errors-Characteristics-Table", TRUE, type="table")`
+ shows that the potential Face Bounding Boxes Google returned were found in images that had the same characteristics of those that were manually annotated for faces.
+<!-- This is shown by the same combinations of characteristics occuring in both Table 5 and Table 6.  keep as tables?-->
 Without looking at each individual image this Table confirms that the potential Face Bounding Boxes Google located will likely be reasonable, and actually contain faces.
 
-The best scenes for facial recongition have been found, given this information the following table considers the Characteristics of the individual faces found within those scenes.
+The best scenes for facial recongition have been found, given this information the following `r figr("Face-Characteristics-Table", TRUE, type="table")`
+ considers the Characteristics of the individual faces found within those scenes.
 For this section we chose to consider only the faces that were manually annotated as players, with the intention of not basing results on recognitions of undesirable faces.
 
-#####**Table 7.** Face Characteristics
-```{r T7 Face Characteristics Table}
+```{r Face-Characteristics-Table, anchor="Table"}
 FaceCharacteristics <- ALLmetaIMGPlayers %>%   filter(type=="Google")%>% filter(matchesManual==TRUE)%>% group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())
 FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
-pander(FaceCharacteristics[1:10,], type = 'table')
+FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
+kable(FaceCharacteristics, type = 'table')
 ```
 
-Table 7 utilises a set of faces that were Manually annotated and also found by Google. 
+`r figr("Face-Characteristics-Table", TRUE, type="table")`
+utilises a set of faces that were Manually annotated and also found by Google. 
 Nine of the top ten facial characteristic combinations contained faces that were not wearing glasses.
@@
 
-#####**Table 8.** Glasses on Recognised Faces
-```{r T8 Glasses}
+```{r Glasses, anchor="Figure"}
 GlassesGoogle <- ALLmetaIMGPlayers %>% filter(type=="Google") %>%
@@
 
-#####**Graph 2.** Glasses
-```{r G2 Glasses}
+```{r Glasses-Figure, anchor="Figure"}
 ggplotProportion(ALLmetaIMGPlayers, glasses)
@@
 
-#####**Table 9.** Head Angles
-```{r T9 HeadAngles}
+```{r HeadAngles, anchor="Table"}
 HeadangleGoogle <- ALLmetaIMGPlayers %>%   filter(type=="Google") %>%
@@
 The amount of faces found by Google with the headangle "Other", is much larger than the amount of faces with the headangle "Profile" or "Front On".
-Therefor this should also be considered propotionately.
+Therefore this should also be considered propotionately.
 
-#####**Graph 3.** Glasses
-```{r G3 Glasses}
+```{r Headangle-Figure, anchor="Figure"}
 ggplotProportion(ALLmetaIMGPlayers, headangle)
@@
 
-##### **Table 10.**
-```{r T10}
-library(tables, quietly = TRUE)
+```{r Accuracy}
 Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
-pander(Accuracy)
+kable(Accuracy)
+# make this a proportional table, would this be necessary if we have the UpSetR
 ```
@@
 
-#####**Table 11.** Google Characteristics
-```{r T11 Google Characteristics Table}
+```{r Google-Characteristics-Table, anchor="table"}
 GoogleCharacteristics <- ALLmetaIMG %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
@@
 ```
-This table shows how many images with potential player's faces Google recognised.
+
+`r figr("Google-Characteristics-Table", TRUE, type="table")`
+shows how many images with potential player's faces Google recognised.
 This diplays a vast gap between the amount of potential faces found given the different shot angles.
@@
 Considering only the Shoulder Height Angle, the following Graph looks at how accessories affected Google's recognition.
-
-#####**Graph 4.** Google Face Bounding Boxes: Mosaic Plot
-```{r G4 Google Characteristics Mosaic Plot}
-GoogleAccessories <- ALLmetaIMG %>% filter(type=="Google") %>% filter(shotangle=="Player Shoulder Height") %>% filter(detect=="Player") %>% filter(lighting!="Direct sunlight")
-
-GoogleAccessories<-droplevels(GoogleAccessories)
-#lighting headangle glasses visorhat
-
-mosaicplot(~ headangle + visorhat, data = GoogleAccessories, color = TRUE)
-
-mosaicplot(~ lighting + visorhat, data = GoogleAccessories, color = TRUE)
-
-mosaicplot(~ lighting +headangle +visorhat, data = GoogleAccessories, color = TRUE)
-
-mosaicplot(~ glasses + lighting, data = GoogleAccessories, color = TRUE)
-
-```
 

### 2016-12-16 analysis.R

@@ -7,15 +7,15 @@ library(tidyr)
 library(purrr)
 
 #Load Data
-MicrosoftClassifiedFaces <- read.csv("~/github/face-recognition/MicrosoftClassifiedFaces.csv")
-AnimetricsClassifiedFaces <- read.csv("~/github/face-recognition/AnimetricsClassifiedFaces.csv")
-SkybiometryClassifiedFaces <- read.csv("~/github/face-recognition/SkybiometryClassifiedFaces.csv")
-GoogleClassifiedFaces <- read.csv("~/github/face-recognition/GoogleClassifiedFaces.csv")
-ManualClassifiedFaces <- read.csv("~/github/face-recognition/ManualClassifiedFaces.csv")
-ManualClassifiedScenes <- read.csv("~/github/face-recognition/ManualClassifiedScenes.csv")
+MicrosoftClassifiedFaces <- read.csv("SoftwareRequestScripts/MicrosoftClassifiedFaces.csv")
+AnimetricsClassifiedFaces <- read.csv("SoftwareRequestScripts/AnimetricsClassifiedFaces.csv")
+SkybiometryClassifiedFaces <- read.csv("SoftwareRequestScripts/SkybiometryClassifiedFaces.csv")
+GoogleClassifiedFaces <- read.csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
+ManualClassifiedFaces <- read.csv("ManualClassifiedFaces.csv")
+ManualClassifiedScenes <- read.csv("ManualClassifiedScenes.csv")
 
 #Check all equal length
-length(unique(MicrosoftClassifiedFaces$file))
+length(unique(ManualClassifiedScenes$file))
 length(unique(AnimetricsClassifiedFaces$file))
 length(unique(SkybiometryClassifiedFaces$file))
 length(unique(GoogleClassifiedFaces$file))
@@ -26,7 +26,7 @@ AnimetricsClassifiedFaces <- AnimetricsClassifiedFaces[!is.na(AnimetricsClassifi
 SkybiometryClassifiedFaces <- SkybiometryClassifiedFaces[!is.na(SkybiometryClassifiedFaces$width),]
 GoogleClassifiedFaces <- GoogleClassifiedFaces[!is.na(GoogleClassifiedFaces$rollAngle),]
 
-#Manual Classified Faces minimum size set
+#Manual Classified Faces
 ManualClassifiedFaces <- ManualClassifiedFaces %>%
[…]

### 2016-12-20 Report06-12.Rmd
removed hard link, changed authorship

--- 2016-12-14 Report06-12.Rmd
@@
 title: "Detecting Facial Expressions in Professional Tennis Matches"
-author: Stephanie Kobakian, Mitchell O'Hara Wild. Supervised by Dianne Cook, Stephanie
-  Kovalcik
+author: Stephanie Kobakian, Mitchell O'Hara Wild, Stephanie
+  Kovalcik, Dianne Cook
 date: "November 19 2016"
@@
 
-setwd("C:/Users/steff/Github/face-recognition")
+#setwd("C:/Users/steff/Github/face-recognition")
 

### 2016-12-21 Report06-12.Rmd
title

@@
 ---
-title: "Detecting Facial Expressions in Professional Tennis Matches"
+title: "Detecting Faces in Tennis Match Videos"
 author: Stephanie Kobakian, Mitchell O'Hara Wild, Stephanie

### 2017-01-09 Report06-12.Rmd
Updates
Additional reference

--- 2016-12-16 Report06-12.Rmd
@@
 #packages:
-require(pander)
-require(ggplot2)
-require(imager)
-require(devtools)
-require(knitcitations)
-require(RefManageR)
-require(readr)
-require(knitr)
-require(grid)
-require(tidyverse)
-require(magick)
-require(kfigr)
+library(pander)
+library(ggplot2)
+library(imager)
+library(devtools)
+library(knitcitations)
+library(RefManageR)
+library(readr)
+library(knitr)
+library(grid)
+library(tidyverse)
+library(magick)
+library(kfigr)
+library(UpSetR)
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE)
 
@@
     if(matchBox){
-      p <- p + geom_path(aes(x=x, y=450-y, group = type, colour=boxID), faceData) + guides(colour="none")
+      p <- p + geom_path(aes(x=x, y=450-y, group = c(type, boxID), colour=boxID), faceData) + guides(colour="none")
     }
@@
 
-#change this to facesVenn with binary information
+# change this to facesVenn with binary information
 ALLmetaIMGFaces<-ALLmetaIMG%>%
   filter(!is.na(boxID)) %>% 
-  select(-ID, -facecounter)%>%
+  dplyr::select(-ID, -facecounter)%>%
   mutate(fileID = as.numeric(factor(file))) %>%
@@
   mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))
+
+# Create Venn Diagrams
+VennLists<-ALLmetaIMGFaces %>%
+  split(.$type) %>% 
+  map(~ .$FaceKey)%>% 
+  fromList() %>%
+  upset(order.by="freq", nsets=100)
 
@@
 
-Many Tennis professionals believe that tennis is a game heavily affected by the mental states of the players.
-The opportunity for researching this concept presents itself with the hope of improving the playing and coaching of Tennis players.
+Many tennis professionals believe that tennis is a game heavily affected by the mental states of the players.
+The opportunity for researching this "inner game" presents itself with the hope of improving the playing and coaching of tennis players by improving their "mental game".
 By statistically analysing the faces and expressions of players during a match there is a hope that insight may be gained into the effects of the mental state on the outcome of a match.
@@
 Their capabilities are often limited to their intended security and surveillance uses.
+@Boston addresses the 'lack of robustness of current tools in unstructured environments' that this paper faces and applies to a sports environment.
 This report aims to analyse the application of these software's to a broadcast to find a suitable software and API to use to analyse a pre-recorded tennis broadcast file.
@@
 ####Project Aim
-- Find the best facial recognition software for tennis matches
-- Build manually classified dataset of faces
-- Compare software performance under varied conditions
+The major aim of the present study were to determine the feasibility of using currently available facial recognition algorithms for extracting facial information from players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
+The performance of the evaluated software was compared against manual classification obtained notational tool developed by the authors.
+In addition to looking at the overall performance, we also evaluated image factors that influences the performance of each service.
 
@@
 To produce these images, a still shot of the frame was taken at every three seconds, for the length of each 5 minute segment.
-The stills were provided by Tennis Australia for use in this research, these segments were taken from 105 video files, which were the broadcast of the Tennis Matches shown on the Seven Network during the Australian Open 2016.
+The stills were provided by Tennis Australia for use in this research, these segments were taken from 105 video files, which were the broadcast of the tennis Matches shown on the Seven Network during the Australian Open 2016.
 The sample included an equal amount of singles tennis matches played between females and males.
 The rounds of the competition vary as to not limit the pool of players to only those who progressed, though there was a higher chance of advancing players reappearing.
+
+The sample included images that contained the faces of many people, this included players, staff on the court and fans in the crowd.
+These faces were included in the manual annontations as they were likely to be found by the softwares selected.
+To be able to contrast the abilities of the softwares and provide information on how to differentiate between players and other people for further research the sample was not filtered at this stage.
 
@@
 
-The final software we chose to analyse was Google Vision API.
-Due to Google's expansion in many web based solutions we researched for a facial recognition software.
-While it was somewhat difficult to access
+The final software we chose to analyse was Google Vision API. Due to Google's expansion in many web based solutions we searched for a facial recognition software.
 
@@
 (reference table with values)
-If it was the face of a player it was always recorded if it captured their face.
-The back of the head was not able to be picked up by any software, so after a demo trial these faces were not classified manually.
+If it was the face of a player it was recorded if it obviously showed their face.
+The back of the head was not able to be picked up by any software, so after a demo trial these faces were classified manually  but reclassified as other.
 Crowd shots provided difficultly in determining which faces were reasonable to classify.
 As these faces were not the intended targets of the recognition these faces were contributing to our understanding of the softwares.
-The same face size standard applied to crowd memebers, but focus was placed on the most prominent faces. For each of these faces, we collected information on the following attributes:
+The same face size standard applied to crowd members, but focus was placed on the most prominent faces. For each of these faces, we collected information on the following attributes:
 
@@
 ####Manual Annotation
-To record these questions a Shiny App was created.
+To record the selections of attribute values for each face and scene a Shiny @shiny App was created.
 We called this Application our ManualClassificationProgram.
-This helped to provide information for all attributes readily and consistently.
-This worked by presenting an image, using the imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attibutes in `r figr("Scene-Attributes-Table", TRUE, type="Table")` as shown above.
-If there was a face in the image we were able to highlight the square 'Face Box'.
-This recorded the x and y coordinates of the box drawn, and when the save button was hit it saved all the radio button selections and the 'Face Box' coordinates to a CSV file.
+This helped to provide information for all attributes quickly and consistently.
+The program worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attibutes in `r figr("Scene-Attributes-Table", TRUE, type="Table")` as shown above.
 
-Following the saving of each face, and the Scene radio button selections, the save button would then save the Scene selections to a separate CSV file.
-This data can be seen in the ManualClassifiedFaces.csv file located in the appendix.
+If there was a face in the image the annotator was able to highlight the square 'Face Box'.
+This changed the display and presented a set of Attributes with radio buttons, this allowed information to be recorded for the specific face.
+This recorded the x and y coordinates of the corner points of a box drawn by the mouse, and when the save button was hit it saved all the radio button selections and the 'Face Box' coordinates to a CSV file^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedFaces.csv].
+
+When a face was not selected, the radio buttons showed the Scene attributes and the radio buttons with the possible selections the annotated was able to choose from.
+When in this display, selecting the save button would then save the Scene selections to a specific CSV file^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedScenes.csv].
 
 If there were issues, the CSV files were able to be edited, this was reserved for extreme circumstances.
-And a lot of care was taken to ensure the first selections were correctly submitted and applied to the correct Faces and Scenes.
-
-The results in the CSV files showed the file name, and the attributes relating to the Scene being considered. 
-This can be seen in the ManualClassifiedScenes.csv file located in the appendix.
+As a lot of care was taken to ensure the first selections were correctly submitted and applied to the correct Faces and Scenes.
 
@@
 The software choices allowed for POST requests to be sent via the internet.
-To access the APIs through R we enlisted the httr package, using functions from this package a script was written for each software API, it would loop through the images, individually posting a request for each image to be analysed.
-These scripts included retrieving the information provided and converting it into a usable format.
+To access the APIs through R we enlisted the httr package, using functions from this package a script was written for Google, Animetrics^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/animetrics.R], Microsoft^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/microsoftAPI.R] and Skybiometry^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/autoSkybiometry.R].
+These scripts contained loops that would move through the images, individually posting a request for each image to be analysed.
+These scripts included retrieving the information provided and converting it into a usable format for our analysis.
 One interesting anomoly was found when using the Skybiometry software as it limited the amount of requests per minute.
@@
 ####Data Processing
-The data was spread across 6 files. For each software we had the classified faces csv file, these are located in the appendix.
-The collation of the results from the Manual Recognition Program created the files ManualClassifiedFaces and ManualClassifiedScenes.
+The data needed for our analysis was spread across six files.
+For each software we had the information on the location of the Facial Bounding Boxes, as well as the time taken for the software to find the information.
+Some of the softwares also provided a more detailed level of information.
+
+The collation of the results from the Manual Recognition Program created
+two CSVs, ManualClassifiedFaces^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedFaces.csv] and ManualClassifiedScenes^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedScenes.csv].
 
 A single data set was created to combine all necessary information in the previously mentioned files for our analysis.
-The information in the dataset,(cite ALLmetaIMG.csv,) was carefully considered.
+The information in the data set^[https://github.com/mvparrot/face-recognition/blob/master/ALLmetIMG.csv], was carefully considered.
 It considers the identify of each face, and all relative face attributes, as well as the image file the face was found in, from this information each face was able to be uniquely identified.
@@
 It also has a record of how many faces had been indentified in the image by counting each additional recognised face.
+To do so, we gathered the name of the file the face was found in and the software Type the Face Bounding Box was determined by.
+The automatically determined time values were also included.
+The minimum and maximum x and y values were drawn from different values in each software's CSV files.
+This required some processing to align the differing values to be comparable.
 
-To find whether the softwares were recongising the same faces a function was created.
-As the location and size of the boxes around the faces were recorded, these values were used to see if a particular identified face box matched a manually identified face.
+To find whether the softwares were recognising the same faces a function was created.
+As the location and size of the boxes around the faces were recorded, these values were used to see if a particular identified face box matched a manually identified face, or a region found by another software.
 This function uses the information of each face and compares the intersecting regions of the polygons created by the x,y coordinates of Manual Faces and other software's faces, to determine if the same face was recognised.
@@
 This allowed us to compare the identification areas, as well as contrast the identified faces of each software.
+This contributed another variable, boxID, to the data set^[https://github.com/mvparrot/face-recognition/blob/master/ALLmetIMG.csv].
 
@@
 
+Using the data set^[ALLmetaIMG] of the combined results, we were able to compare the performance of the softwares.
+Firstly, we considered how many individual faces the softwares were able to detect in 
+`r figr("Face-Bounding-Box-Data", TRUE, type="Figure")` .
+
 ## Results
-Using the database of the combined results, we were able to compare the performance of the softwares.
-Firstly, we considered how many individual faces the softwares were able to detect.
 
-```{r Face-Bounding-Box-Data, results='hide', type="figure", fig.cap='..', anchor="figure"}
+```{r Face-Bounding-Box-Data, results='hide', type="figure", fig.cap="Face Bounding Box Data:", anchor="figure"}
 ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE)
@@
 
-The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognised almost 1000 more faces than the next best software, Microsoft.
+The bar chart in 
+`r figr("Face-Bounding-Box-Data", TRUE, type="Figure")` above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognised almost 1000 more faces than the next best software, Microsoft.
 
-#####**Graph 4.** Face Bounding Box Data: Box Plot 
-```{r G4 Face Bounding Box Data, anchor="figure"}
+```{r Face-Bounding-Box-Data-Box, anchor="figure"}
 ggplot(ALLmetaIMG, aes(x = factor(x = factor(type)), fill=type, y = size)) + geom_boxplot() + scale_y_continuous(trans='log') +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Google","Animetrics","Manual","Microsoft","Skybiometry"))+ylab("Size of Face Bounding Boxes")+guides(fill=FALSE)
@@
 
-This box and whisker plot shows the differences between the sizes of the 'Face Bounding Boxes' produced by each software.
+The box and whisker plot in 
+`r figr("Face-Bounding-Box-Data-Box", TRUE, type="Figure")` shows the differences between the sizes of the 'Face Bounding Boxes' produced by each software.
 Where a 'Face Bounding Box' refers to the size of the square the software provided as a location in the image of a face that was detected.
@@
 Skybiometry results accounted for the 255 smallest recognised faces. However this is not necessarily a benefit to this research, as these are not all faces.
-
-Note: Skybiometry boxes are pink, Microsoft are blue, Google are Green and Animetrics are Red.
 
@@
 #### Challenges
+It is understandable that there would be many more faces to recognise in these shots than in shots where there is only a player, and therefore many more faces recognised.
+This provides many faces to sort through to find emotions of a player.
 
- it is understandable that there would be many more faces to recognise in these shots than in shots where there is only a player, and therefore many more faces recognised. However in this research
-
-- Access to usable images and videos
+We faced the challenge of accessing usable images of players, and specifically their faces.
 - Availability of software
@@
 - Time constraints
-
-Long Term Goals
-- Better understand emotion's effect on player performance
-- Automatic collection of player emotion data from video
 
@@
 
-(5) Conclusions 
+## Conclusions 
 Employ the Google Vision API, which would allow the use of still images, or video (TEST VIDEO) files, reducing the need for stills.
@@
 
-(6) Future Work
-Considering the images used during our study were stills derived from Broadcast video files,
-it would be useful to extend further research to deal with the video files directly. 
-These companies have the potential to allow for video recognition......
+## Future Work
+The Long Term goal of this research is to better understand how the emotion's felt by a player during a match affect player performance.
+Ultimately we would aim to create a program that automated the collection of player emotion data from throughout a match.
+This information would be presented in a timeline that allowed match performance, in the form of points won, to be aligned with the emotions felt at certain times throughout.
 
-It should also be considered that there are softwares focussed on providing recognition in certain controlled scenarios.
-If the study was controlled to focus on certain camera angles that align with the facial angles these security minded programs
-are intended for it may be helpful to extend the research to softwares currently available but were deemed impractical for this study.
+Considering the images used during our study were stills derived from Broadcast video files, it would be useful to extend further research to deal with the video files directly.
+The Google Vision API used in this research which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.
 
-To check for manual errors, create another app that shows the 'faces' identified by each program, confirm manually whether or not these are faces.
-We feel this would be necessary when expanding on the use
+It should also be considered that these are softwares focussed on providing recognition in certain controlled scenarios.
+If the study was controlled to focus on certain camera angles that align with the facial angles these security programs are intended to recognise faces in.
 
-We also feel that incorporating audio information from the microphones worn by players may assist in sentiment analysis.
+Given that Google found many faces that did not match manually annotated face, we considered that we should check for manual errors.
+There is the possibility that we could create another app that shows the Facical Bounding Boxes identified by each program, this would allow the annotator to confirm manually whether or not these are faces.
 
-Getting specific camera angle access from the seven network to reduce the work of computers
+Given that certain Scene attribute combinations produced more facial recognitions than other combinations we should consider limiting the sample of images sent to Google Vision API.
+This would not only reduce cost but also provide a greater level of detail of the emotions felt by a player during a match.
+To provide a greater level of information at all points in a match it would be beneficial to derive images from a single camera feed.
+This feed should match the Scene attributes that provided the most Google faces.
 
 To undertake sentiment analysis, we would take the boxes of faces found in this set of images.
-Allowing each face a border we would crop the images and produce an individual face image that would form the data set for emotion recognition.
-igh enough quality?
-
-Write a program to create images of only that faces
-
-(7)
-Appendix
-```{r}
-
-```
+Allowing each face a border of pixels, we would crop the images and produce an individual face image that would form the data set for emotion recognition.
+We also feel that incorporating audio information from the microphones worn by players may assist in sentiment analysis.
+By including this information we would be able to define differences between certain emotions that may not be able to be found by facial features only.
 
 ## References
-
-citation @Automated
-
-```{r}
-#Survey of commercial technologies for face recognition in video
-
-#Report number: DRDC-RDDC-2014-C245
-
-#Affiliation: Department of National Defence of Canada.
-
-```

### 2017-01-18 Report06-12.Rmd
Analysis Updates

@@
 title: "Detecting Facial Expressions in Professional Tennis Matches"
-author: Stephanie Kobakian, Mitchell O'Hara-Wild. Supervised by Dianne Cook, Stephanie
-  Kovalcik
-date: "November 19 2016"
+author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
+date: '2017'
 output:
   pdf_document:
+    citation_package: natbib
     fig_caption: yes
+    fig_crop: yes
     toc: yes
     toc_depth: 2
-fontsize: 10pt
+  html_notebook: null
+fontsize: 11pt
+documentclass: article
 bibliography: references.bib
@@
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE)
 
@@
     else{
-      p <- p + geom_path(aes(x=x, y=450-y, group = type, colour=type), faceData)
+      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData)
     }
@@
 
-# Create Venn Diagrams
-VennLists<-ALLmetaIMGFaces %>%
+# Create UpSetR graph
+createUpSet <- function(data) {
+VennLists<-data %>%
   split(.$type) %>% 
@@
   upset(order.by="freq", nsets=100)
+}
 
@@
 
-##Introduction##
+##Introduction
 
@@
 The opportunity for researching this "inner game" presents itself with the hope of improving the playing and coaching of tennis players by improving their "mental game".
-By statistically analysing the faces and expressions of players during a match there is a hope that insight may be gained into the effects of the mental state on the outcome of a match.
+By statistically analyzing the faces and expressions of players during a match there is a hope that insight may be gained into the effects of the mental state on the outcome of a match.
 Facial expressions during competition provide the most direct insight into a player's thoughts.
-The aim of this project is to begin to develop methods to collect accurate information about the facial expressions of elite tennis athletes during matchplay.
+The aim of this project is to begin to develop methods to collect accurate information about the facial expressions of elite tennis athletes during match play.
 
 In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcasted videos of elite tennis matches.
+Using the broadcasted videos gives an objective insight to emotions as the player progresses through a match.
 While it is impossible to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through results produced by a recognition software.
+As opposed to the approach of previous studies that have used Player's recollections after a game to determine their emotions.
 
@@
 ####Project Aim
-The major aim of the present study were to determine the feasibility of using currently available facial recognition algorithms for extracting facial information from players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
-The performance of the evaluated software was compared against manual classification obtained notational tool developed by the authors.
+The aims of the present study were to determine the feasibility of using currently available facial recognition algorithms for extracting facial information from players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
+This limited selection was based on accessible APIs that we believed would produce appropriate and useful facial recognition.
+The performance of the evaluated software was compared against manual classification obtained notation tool developed by the authors.
 In addition to looking at the overall performance, we also evaluated image factors that influences the performance of each service.
 
-####Sample and sampling approach#### 
+####Sample and sampling approach
 The goal of the sample was to be representative of the video files that will be used for future facial recognition analysis.
@@
 The sample included images that contained the faces of many people, this included players, staff on the court and fans in the crowd.
-These faces were included in the manual annontations as they were likely to be found by the softwares selected.
-To be able to contrast the abilities of the softwares and provide information on how to differentiate between players and other people for further research the sample was not filtered at this stage.
+These faces were included in the manual annotations as they were likely to be found by the software selected.
+We felt including these additional faces would not only increase the sample by which to judge the software's capabilities but also allow provision of information on how to differentiate between players and other people for further research.
+Therefore the sample was not filtered at this initial stage.
 
@@
 
-####Selecting the software####
-The choice of the initial softwares considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'
+####Selecting the software
+The choice of the initial software considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'
 
 The process of software selection to determine which we would compare was based on several criteria.
-Firstly, we based our choices on the results of the report as it considered processing speed and feature selction techniques, as well as the ability to perform both still-to-video and video-to-video recognition.
+Firstly, we based our choices on the results of the report as it considered processing speed and feature selection techniques, as well as the ability to perform both still-to-video and video-to-video recognition.
 
-From the software's analysed we considered availability for use within the timeframe of the report.
+From the software's analysed we considered availability for use within the time frame of the report.
 This led us to choose Animetrics FaceR.
 The report outlines that for Animetrics, 'one requirement is that image/face proportion
-should be at least 1:8 and that at least 64 pixels between eyes are required'. We realise this could present challenges given our dataset.
-It will also allow for an extension from detecting to recognising people in the dataset.
+should be at least 1:8 and that at least 64 pixels between eyes are required'. We realize this could present challenges given our data set.
+It will also allow for an extension from detecting to recognizing people in the data set.
 
@@
 
-We then chose to consider company's who are expanding their API ranges.
+We then chose to consider companies who are expanding their API ranges.
 This resulted in the choice of Microsoft API, provided by Microsoft Cognitive Services.
@@
 
-We were able to try the online demos to see whether these softwares were viable, we used the following  `r figr("Trial-Image", TRUE, type="Figure")`:
+We were able to try the online demos to see whether these software were viable, we used the following Image displayed below in `r figr("Trial-Image", TRUE, type="Figure")`:
 
-```{r Trial-Image, fig.cap="This is a player", anchor="figure"}
+```{r Trial-Image, caption="This is a player", message=TRUE, warning=TRUE, anchor="figure"}
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
@@
 
-## Methodology ##
+## Methodology
 An annotation tool was constructed to create a base for comparative analysis, we refer to this as Manual Classifications.
@@
 
-```{r Scene-Attributes-Table, anchor="table", fig.cap="Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute."}
+```{r Scene-Attributes-Table, anchor="table", caption="Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute."}
 kable(SceneAttributes, format = "pandoc", booktabs = TRUE)
@@
 The aim was to collect specific information on each different face within the scene.
-To determine which of the sometimes many faces in the scene it would be reasonable for softwares to detect a standard was created for reasonable detection.
+To determine which of the sometimes many faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
 This was based on the attributes provided in `r figr("Solution-Specifications-Table", TRUE, type="Table")`, below:
@@
 Crowd shots provided difficultly in determining which faces were reasonable to classify.
-As these faces were not the intended targets of the recognition these faces were contributing to our understanding of the softwares.
+As these faces were not the intended targets of the recognition these faces were contributing to our understanding of the software.
 The same face size standard applied to crowd members, but focus was placed on the most prominent faces. For each of these faces, we collected information on the following attributes:
@@
 ####Manual Annotation
-To record the selections of attribute values for each face and scene a Shiny @shiny App was created.
-We called this Application our ManualClassificationProgram.
+To record the details of attributes for each face and scene a Shiny [-@shiny] App was created.
+We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassificationProgram.R].
 This helped to provide information for all attributes quickly and consistently.
-The program worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attibutes in `r figr("Scene-Attributes-Table", TRUE, type="Table")` as shown above.
+The Shiny [@shinyw] package provides a 'framework for building web applications using R'.
+It allows for the creation of web applications using R rather than 'requiring HTML, CSS, or JavaScript knowledge.'
 
-If there was a face in the image the annotator was able to highlight the square 'Face Box'.
-This changed the display and presented a set of Attributes with radio buttons, this allowed information to be recorded for the specific face.
+The program we created was an interactive application that worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attributes in `r figr("Scene-Attributes-Table", TRUE, type="Table")` as shown above.
+
+If there was a face in the image the annotator was able to highlight a section of the image to create a square 'Face Box'.
+This changed the display and presented a set of Attributes with radio buttons, this allowed information to be recorded for the face in the specific 'Face Box'.
 This recorded the x and y coordinates of the corner points of a box drawn by the mouse, and when the save button was hit it saved all the radio button selections and the 'Face Box' coordinates to a CSV file^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedFaces.csv].
@@
 
+All the annotations for this sample were completed by one author.
+This was chosen to provide consistency across the sample of faces annotated manually.
+However the initial choices of what would be reasonably detected were made by several of the authors.
+
 ####Software Recognition
@@
 These scripts included retrieving the information provided and converting it into a usable format for our analysis.
-One interesting anomoly was found when using the Skybiometry software as it limited the amount of requests per minute.
+One interesting anomaly was found when using the Skybiometry software as it limited the amount of requests per minute.
 We accounted for this by stalling the posts for the amount of waiting time the software notified, and checking until the time lapsed and the script could continue looping.
@@
 For each software we had the information on the location of the Facial Bounding Boxes, as well as the time taken for the software to find the information.
-Some of the softwares also provided a more detailed level of information.
+Some of the software also provided a more detailed level of information.
 
@@
 Also included was information on the software that found it, and the time it took the software to identify the face.
-It also has a record of how many faces had been indentified in the image by counting each additional recognised face.
+It also has a record of how many faces had been identified in the image by counting each additional recognized face.
 To do so, we gathered the name of the file the face was found in and the software Type the Face Bounding Box was determined by.
@@
 
-To find whether the softwares were recognising the same faces a function was created.
+To find whether the software were recognizing the same faces a function was created.
 As the location and size of the boxes around the faces were recorded, these values were used to see if a particular identified face box matched a manually identified face, or a region found by another software.
-This function uses the information of each face and compares the intersecting regions of the polygons created by the x,y coordinates of Manual Faces and other software's faces, to determine if the same face was recognised.
+This function uses the information of each face and compares the intersecting regions of the polygons created by the x,y coordinates of Manual Faces and other software's faces, to determine if the same face was recognized.
 We determined the ratio of intersecting area to total area must be greater than 0.1 to be considered the same face.
@@
 ####Analysis
-The statistical analysis conducted to summarise and assess the validity of the method.
-This method allowed all the softwares and the faces they found to be compared.
+The statistical analysis conducted to summarize and assess the validity of the method.
+This method allowed all the software and the faces they found to be compared.
 
-Using the data set^[ALLmetaIMG] of the combined results, we were able to compare the performance of the softwares.
-Firstly, we considered how many individual faces the softwares were able to detect in 
-`r figr("Face-Bounding-Box-Data", TRUE, type="Figure")` .
+Using the data set^[ALLmetaIMG] of the combined API and manual results, we were able to compare the performance of the software.
+Firstly, we considered how many individual faces the software were able to detect in `r figr("Face-Bounding-Box-Data", TRUE, type="Figure")` .
+
+However, individual faces are not beneficial if they do not correspond to the faces manually annotated.
+`r figr("Face-Bounding-Box-UpSet", TRUE, type="Figure")` was created by defining groups depending on the softwares
+that recognized each particular face.
+The UpSetR [-@UpSetR] package helps visualise set intersections.
+Where in this circumstance Face Bounding Boxes may overlap on the same face, each bar shows the number of individual faces that have Face Bounding Boxes resulting from each of the softwares highlighted below the bar.
+
+Following, we considered the sizes of the Boxes created in `r figr("Face-Bounding-Box-Data-Box", TRUE, type="Figure")`, this was an attempt to determine how the software performed when presented with smaller faces.
+The boxplot uses the size of the Face Bounding Boxes, and contrasts based on the software the Boxes were found from.
+
+To determine how each software reacted to the same face we looked at an image that contained only
+
+finding faces that were recognized and grouping them by the softwares
+
+Skybiometry results accounted for the 255 smallest recognized faces. However this is not necessarily a benefit to this research, as these are not all faces.
 
@@
 
-```{r Face-Bounding-Box-Data, results='hide', type="figure", fig.cap="Face Bounding Box Data:", anchor="figure"}
+```{r Face-Bounding-Box-Data, results='hide', type="figure", caption="Face Bounding Box Data:", anchor="figure"}
 ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE)
@@
 The bar chart in 
-`r figr("Face-Bounding-Box-Data", TRUE, type="Figure")` above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognised almost 1000 more faces than the next best software, Microsoft.
+`r figr("Face-Bounding-Box-Data", TRUE, type="Figure")` above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft.
+
+```{r Face-Bounding-Box-UpSet, results='hide', type="figure", caption="Face Bounding Box Data:", anchor="figure"}
+createUpSet(ALLmetaIMGFaces)
+```
+
+`r figr("Face-Bounding-Box-Upset", TRUE, type="Figure")` Bar Chart shows the Face Bounding Boxes that were recognized by multiple software.
+The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations. The following groups were Boxes recognized by both Manual annotations and the Google API.
 
 ```{r Face-Bounding-Box-Data-Box, anchor="figure"}
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(type)), fill=type, y = size)) + geom_boxplot() + scale_y_continuous(trans='log') +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Google","Animetrics","Manual","Microsoft","Skybiometry"))+ylab("Size of Face Bounding Boxes")+guides(fill=FALSE)
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(type)), fill=type, y = size)) + geom_boxplot() + scale_y_continuous() +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Google","Animetrics","Manual","Microsoft","Skybiometry"))+ylab("Size of Face Bounding Boxes")+guides(fill=FALSE)
 
@@
 Where a 'Face Bounding Box' refers to the size of the square the software provided as a location in the image of a face that was detected.
-On average, Google maps the largest boxes around faces, however Animetrics has the largest box recognised in the set.
-On average, the smallest faces are recognised by Skybiometry.
+On average, Google maps the largest boxes around faces, and has the largest box recognized in the set.
+On average, the smallest Face Boxes are created by Skybiometry.
 
-Skybiometry results accounted for the 255 smallest recognised faces. However this is not necessarily a benefit to this research, as these are not all faces.
-
-```{r I2, results=TRUE, fig.cap="2016_CT6_R02_JSousa_POR_vs_SGiraldo_COL_MS231_clip.0017.png", anchor="figure"}
-imagesList2<-as.list("2016_CT6_R02_JSousa_POR_vs_SGiraldo_COL_MS231_clip.0017.png")
+```{r I2, results=TRUE, caption="2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0014.png", anchor="figure"}
+imagesList2<-as.list("2016_CT6_R02_FLopez_ESP_vs_GPella_ARG_MS227_clip.0009.png")
 overlayGgplot(imagesList2, ALLmetaIMG, matchBox = FALSE)
@@
 
-This image shows the smallest Face Bounding Box recognised. However visual inspection shows it only captures the player's eye and nose, not their whole face.
+The image above shows the smallest Face Bounding Box recognized. However visual inspection shows it only captures the player's eye and nose, not their whole face.
 
-```{r I3, results=TRUE, fig.cap="2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png", anchor="figure"}
+```{r I3, results=TRUE, caption="2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png", anchor="figure"}
 imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
@@
 
-As before, the 'face' is not as we would hope it would be classified. Just right of the centre, the smaller box actaully captures a fist, not a face.
+As before, the 'face' is not as we would hope it would be classified. Just right of the center, the smaller box actually captures a fist, not a face.
 
-```{r I4,results=TRUE, fig.cap="2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png", anchor="figure"}
+```{r I4,results=TRUE, caption="2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png", anchor="figure"}
 imagesList4<-as.list("2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png")
@@
 
-I4 shows the sensitivity of the software. We may consider this too sensitive as it recognised the eye and nose of the ballboy on the court.
+I4 shows the sensitivity of the software. We may consider this too sensitive as it recognized the eye and nose of the ball boy on the court.
 
-##### Image 5.2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png
-```{r I5, results=TRUE, fig.cap="2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png", anchor="figure"}
+```{r I5, results=TRUE, caption="2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png", anchor="figure"}
 imagesList5<-("2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png") 
@@
 
-As seen in this image of the crowd, the software is performing reasonably well. It does recognise the faces, yet only one not recognised by the other softwares, this may be due to the sunglasses.
+As seen in this image of the crowd, the software is performing reasonably well. It does recognize the faces, yet only one not recognized by the other software, this may be due to the sunglasses.
 
-This image demonstrates that the it is not necessarily the smaller faces that Skybiometry recognises, but it puts smaller bounds on the facial features than other softwares.
+This image demonstrates that the it is not necessarily the smaller faces that Skybiometry recognizes, but it puts smaller bounds on the facial features than other software.
 
@@
 
-The sample used contains all the manually annotated faces and all the faces recognised by the four softwares.
+The sample used contains all the manually annotated faces and all the faces recognized by the four software.
 
-To consider how many Type I errors occured, where a face was detected incorrectly, we look at the Bounding Boxes that do not match manually annotated faces.
+To consider how many Type I errors occurred, where a face was detected incorrectly, we look at the Bounding Boxes that do not match manually annotated faces.
 
@@
 
-A potential face detected that does not match a face manually annotated occurs for 9.66% of all the Faces detected by the softwares. This is especially high for Google with 289 faces identified.
+A potential face detected that does not match a face manually annotated occurs for 9.66% of all the Faces detected by the software. This is especially high for Google with 289 faces identified.
 
-All the Face Bounding Boxes that Google found which do not match manually annotated faces were correctly identifying faces. This exhibits the occurences of errors.
+All the Face Bounding Boxes that Google found which do not match manually annotated faces were correctly identifying faces. This exhibits the occurrences of errors.
 
-We then considered the characteristics of the images that the softwares found Potential Face Bounding Boxes^[These boxes represent an area of pixels that are a potentially recognised face.] in.
+We then considered the characteristics of the images that the software found Potential Face Bounding Boxes^[These boxes represent an area of pixels that are a potentially recognized face.] in.
 
@@
 `r figr("Image-Characteristics-Table", TRUE, type="Figure")`
- displays the feature combinations that produced the most potential face Bounding Boxes recognitions by all four softwares. The most common shot is a crowd shot.
-The second row in the table with 830 faces recognised is more interesting than the first result.
+ displays the feature combinations that produced the most potential face Bounding Boxes recognition by all four software. The most common shot is a crowd shot.
+The second row in the table with 830 faces recognized is more interesting than the first result.
 This useful scene is an image of a Court Player Close-Up in front of a Logo Wall, taken at Player Shoulder Height.
@@
 
-The best scenes for facial recongition have been found, given this information the following `r figr("Face-Characteristics-Table", TRUE, type="table")`
+The best scenes for facial recognition have been found, given this information the following `r figr("Face-Characteristics-Table", TRUE, type="table")`
  considers the Characteristics of the individual faces found within those scenes.
-For this section we chose to consider only the faces that were manually annotated as players, with the intention of not basing results on recognitions of undesirable faces.
+For this section we chose to consider only the faces that were manually annotated as players, with the intention of not basing results on recognition of undesirable faces.
 
@@
 `r figr("Face-Characteristics-Table", TRUE, type="table")`
-utilises a set of faces that were Manually annotated and also found by Google. 
+utilizes a set of faces that were Manually annotated and also found by Google. 
 Nine of the top ten facial characteristic combinations contained faces that were not wearing glasses.
-The head angle describing the face angle was 'Other'^[Definition for headangle factor level 'Other' found in..]
+The head angle describing the face angle was 'Other'^[Definition for head-angle factor level 'Other' found in..]
 for nine of the top ten facial characteristic combinations.
@@
 ```
-The extreme disparity between the amount of faces with glasses to without them means that the occurence of these attributes across the softwares must be considered proportionally.
+
+The extreme disparity between the amount of faces with glasses to without them means that the occurrence of these attributes across the software must be considered proportionally.
 
@@
 ```
-Graph 2 above shows that Google outperforms the other softwares, with or without glasses. When there are no glasses worn Google finds over 60% of the manually annotated faces.
+
+Graph 2 above shows that Google outperforms the other software, with or without glasses. When there are no glasses worn Google finds over 60% of the manually annotated faces.
 
@@
 ```
-The amount of faces found by Google with the headangle "Other", is much larger than the amount of faces with the headangle "Profile" or "Front On".
-Therefore this should also be considered propotionately.
+
+The amount of faces found by Google with the head-angle "Other", is much larger than the amount of faces with the head-angle "Profile" or "Front On".
+Therefore this should also be considered proportionately.
 
@@
 ```
-Graph 3 diplays that Google performs much better in comparison to the other softwares when the headangle is Profile.
-This is outperforming unusually well, however this could also be due to the poor performance of the softwares in this circumstance.
+
+Graph 3 displays that Google performs much better in comparison to the other software when the head-angle is Profile.
+This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance.
 
@@
 
-It should be noted that there were results where a single face was recognised twice within the same image.
-This was a very unusual result and is notable as a point of interest but given it only occured for Animetrics, it is not worth basing decisions on this unusual result.
+It should be noted that there were results where a single face was recognized twice within the same image.
+This was a very unusual result and is notable as a point of interest but given it only occurred for Animetrics, it is not worth basing decisions on this unusual result.
 
@@
 `r figr("Google-Characteristics-Table", TRUE, type="table")`
-shows how many images with potential player's faces Google recognised.
-This diplays a vast gap between the amount of potential faces found given the different shot angles.
+shows how many images with potential player's faces Google recognized.
+This displays a vast gap between the amount of potential faces found given the different shot angles.
 Shoulder height is an optimum angle for a Face Bounding Box.
@@
 According to Table 4 Google had 38.23% of the 9.66% potential face boxes not annotated manually.
-It was considered that this may have shown Google's API may have been finding more unwanted faces than the other softwares.
+It was considered that this may have shown Google's API may have been finding more unwanted faces than the other software.
 However, visual inspection showed that these were actually faces.
@@
 The scene information was recorded and the combinations were shown to find how many potential face Bounding Boxes were found with the combination of scene attributes.
-This showed that crowd members faces were often recognised, this is both helpful and unhelpful as it shows a strong ability of Google's algorithm to recognise faces, even when these faces are not the goal of the research.
+This showed that crowd members faces were often recognized, this is both helpful and unhelpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
 
-Image 1 shows the images preferable for future research. Where the faces will be recognised and allow both the identity and emotion of the players to be recognised.
+Image 1 shows the images preferable for future research. Where the faces will be recognized and allow both the identity and emotion of the players to be recognized.
 
-Google gave the optimum results in this image as it found the face of the player, but did not locate the face of the staff memeber behind him on the court.
+Google gave the optimum results in this image as it found the face of the player, but did not locate the face of the staff member behind him on the court.
 
-While Google's recognitions mostly matched the Manually annotated set of faces, there were some that did not. These were all actually faces and were missed during manual annotations.
+While Google's recognition's mostly matched the Manually annotated set of faces, there were some that did not. These were all actually faces and were missed during manual annotations.
 
-Table 6 shows that 190 of the faces that were not found manually occured in the scene of a Court player close-up, with a background of a logo wall, where the shot was taken at player shoulder height.
+Table 6 shows that 190 of the faces that were not found manually occurred in the scene of a Court player close-up, with a background of a logo wall, where the shot was taken at player shoulder height.
 
-This shows it was performing extremely well and not resulting in unexplainable face Bounding Boxes as some of the other softwares were.
+This shows it was performing extremely well and not resulting in unexplained face Bounding Boxes as some of the other software were.
 This is a strong indicator that applying Google's software for further research would result in the recognition of desired faces.
@@
 
-Table 7 showed the combinations of attributes that were found for each face[Given that information was not recorded where Google provided facial recognitions for faces not Manually annotated thesse could not be considered.].
+Table 7 showed the combinations of attributes that were found for each face[Given that information was not recorded where Google provided facial recognition for faces not Manually annotated these could not be considered.].
 The use of accessories, Glasses and Visors or Hats, was considered as the Australian Open takes place on both indoor and outdoor courts.
 To apply this research all courts that elite Tennis players compete on had to be included.
-It was assumed that outdoor courts would led to the use of these accessories and these accessories may contribute to the performance of a recongition software.
+It was assumed that outdoor courts would led to the use of these accessories and these accessories may contribute to the performance of a recognition software.
 It may be implied by the table that Glasses prohibits recognition as all but one of the combinations have 'No' for the Glasses variable.
-However, we are cautious of validating this as Table 8 tells that there are many more faces recognised, by both the Google recnogitions and manual annotations, that do not have Glasses.
+However, we are cautious of validating this as Table 8 tells that there are many more faces recognized, by both the Google recognition's and manual annotations, that do not have Glasses.
 This disproportionate sample of faces with Glasses means that we considered it proportionally rather than as a total.
 
-Graph 2 demonstrates that the prescence of Glasses on faces annotated manually did affect recognition by Google's alrgorithm, while it outperformed the other softwares in both instances, faces were identified more often if the person did not wear glasses.
+Graph 2 demonstrates that the presence of Glasses on faces annotated manually did affect recognition by Google's algorithm, while it outperformed the other software in both instances, faces were identified more often if the person did not wear glasses.
 
@@
 
-The boxplot in graph encourages our comparisons to not consider the size of face bounding box as a measure of how the software performs on small faces.
+The box-plot in graph encourages our comparisons to not consider the size of face bounding box as a measure of how the software performs on small faces.
 
 #### Challenges
-It is understandable that there would be many more faces to recognise in these shots than in shots where there is only a player, and therefore many more faces recognised.
+It is understandable that there would be many more faces to recognize in these shots than in shots where there is only a player, and therefore many more faces recognized.
 This provides many faces to sort through to find emotions of a player.
@@
 
-Method, automated the process to reduce datacleaning and help group characterstics
+Method, automated the process to reduce data cleaning and help group characteristics
 
@@
 
-It should also be considered that these are softwares focussed on providing recognition in certain controlled scenarios.
-If the study was controlled to focus on certain camera angles that align with the facial angles these security programs are intended to recognise faces in.
+It should also be considered that these are software focused on providing recognition in certain controlled scenarios.
+If the study was controlled to focus on certain camera angles that align with the facial angles these security programs are intended to recognize faces in.
 
 Given that Google found many faces that did not match manually annotated face, we considered that we should check for manual errors.
-There is the possibility that we could create another app that shows the Facical Bounding Boxes identified by each program, this would allow the annotator to confirm manually whether or not these are faces.
+There is the possibility that we could create another app that shows the Facial Bounding Boxes identified by each program, this would allow the annotator to confirm manually whether or not these are faces.
 
-Given that certain Scene attribute combinations produced more facial recognitions than other combinations we should consider limiting the sample of images sent to Google Vision API.
+Given that certain Scene attribute combinations produced more facial recognition than other combinations we should consider limiting the sample of images sent to Google Vision API.
 This would not only reduce cost but also provide a greater level of detail of the emotions felt by a player during a match.

### 2017-01-18 analysis.R
Removed system specific directories

@@ -1,5 +1,3 @@
-setwd("~/github/face-recognition/")
-
 #Load Packages
 library(imager)
 library(dplyr)
@@ -7,12 +5,12 @@ library(tidyr)
 library(purrr)
 
 #Load Data
-MicrosoftClassifiedFaces <- read.csv("~/github/face-recognition/MicrosoftClassifiedFaces.csv")
-AnimetricsClassifiedFaces <- read.csv("~/github/face-recognition/AnimetricsClassifiedFaces.csv")
-SkybiometryClassifiedFaces <- read.csv("~/github/face-recognition/SkybiometryClassifiedFaces.csv")
-GoogleClassifiedFaces <- read.csv("~/github/face-recognition/GoogleClassifiedFaces.csv")
-ManualClassifiedFaces <- read.csv("~/github/face-recognition/ManualClassifiedFaces.csv")
-ManualClassifiedScenes <- read.csv("~/github/face-recognition/ManualClassifiedScenes.csv")
+MicrosoftClassifiedFaces <- read.csv("MicrosoftClassifiedFaces.csv")
+AnimetricsClassifiedFaces <- read.csv("AnimetricsClassifiedFaces.csv")
+SkybiometryClassifiedFaces <- read.csv("SkybiometryClassifiedFaces.csv")
+GoogleClassifiedFaces <- read.csv("GoogleClassifiedFaces.csv")
+ManualClassifiedFaces <- read.csv("ManualClassifiedFaces.csv")
+ManualClassifiedScenes <- read.csv("ManualClassifiedScenes.csv")
 
 #Check all equal length
 length(unique(MicrosoftClassifiedFaces$file))

### 2017-01-18 mergeData.R
Repo organisation

@@ -124,6 +124,7 @@ metaManualClassifiedFaces <- merge(dplyr::select(ManualClassifiedFaces, file, fa
 
 metaFaces <- merge(metaManualClassifiedFaces, classifiedIMG, by=c("file", "boxID")) %>% dplyr::select(-ID.y) %>% rename(ID = ID.x)
 
+## THIS CAUSES boxID NAs
 ALLmetaIMG <- merge(ManualClassifiedScenes, metaFaces, by="file", all=TRUE)
 
 #Extract file name info

### 2017-01-18 mergeData.R
Tweaked boxOverlap sensitivity

@@ -83,7 +83,7 @@ boxOverlap <- function(boxes){
           if(!is.null(intersectPoly)){ #If they actually intersect
             intersectArea <- area(intersectPoly)
             totalArea <- area(newPoly) + area(comparePoly) - intersectArea
-            if(intersectArea/totalArea > 0.1){
+            if(intersectArea/totalArea > 1/3){
               boxes[compareBox,"boxID"] <- boxes[newBox,"boxID"]
             }
           }

### 2017-01-18 regressionWIP.R
Added initial GLM variable analysis

@@ -1,0 +1,33 @@
+hitmiss <- function(x){
+  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
+  hit <- allType %in% x$type
+  x[1,] %>%
+    dplyr::select(file:visorhat) %>%
+    cbind(type = allType, hit = hit)
+}
+
+glmFits <- ALLmetaIMGFaces %>%
+  split(.$FaceKey) %>%
+  map_df(~ hitmiss(.)) %>%
+  split(.$type) %>%
+  map(~ select(., -type, -file, -boxID)) %>%
+  map(~ glm(hit ~ ., data=.))
+
+glmSummary <- glmFits %>%
+  map(~ cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.))))))) %>%
+  map(~ rename(., variable = rowname))
+
+glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary)))
+
+## Coefficient of variables by software
+glmPlot %>%
+  ggplot(aes(x=type, y=Estimate)) +
+  geom_col() + 
+  facet_wrap(~ variable)
+
+## Significance of variables by software
+glmPlot %>%
+  mutate(significant = `Pr(>|t|)` < 0.05) %>%
+  ggplot(aes(x=type, y=`Pr(>|t|)`)) +
+  geom_col(aes(fill=significant)) + 
+  facet_wrap(~ variable)

### 2017-01-18 regressionWIP.R
Removed unnecessary maps

@@ -1,3 +1,4 @@
+# Prepare data
 hitmiss <- function(x){
   allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
   hit <- allType %in% x$type
@@ -10,15 +11,14 @@ glmFits <- ALLmetaIMGFaces %>%
   split(.$FaceKey) %>%
   map_df(~ hitmiss(.)) %>%
   split(.$type) %>%
-  map(~ select(., -type, -file, -boxID)) %>%
-  map(~ glm(hit ~ ., data=.))
+  map(~ glm(hit ~ ., data = select(., -type, -file, -boxID)))
 
 glmSummary <- glmFits %>%
-  map(~ cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.))))))) %>%
-  map(~ rename(., variable = rowname))
+  map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname))
 
 glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary)))
 
+# Graphs
 ## Coefficient of variables by software
 glmPlot %>%
   ggplot(aes(x=type, y=Estimate)) +

### 2017-01-19 Report06-12.Rmd
Manual full versions
Report Changes,
overlay plot colouring

@@
 
-setwd("C:/Users/steff/Github/face-recognition")
-
 #csv files:
@@
         mutate(posCoord = substr(corner, 1, 1), posID = substr(corner, 2, 2)) %>%
-        select(-corner) %>% spread(posCoord, boxPos)
+        dplyr::select(-corner) %>% spread(posCoord, boxPos)
 
@@
     else{
-      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData)
+      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData) + scale_color_manual(values = c(Skybiometry="#ffe093", Microsoft="#5cc3f6", Google="#5cba82", Animetrics="#FF959c", Manual="#db70ff"))
     }
@@
 ALLmetaIMGFaces<-ALLmetaIMG%>%
-  filter(!is.na(boxID)) %>% 
+  filter(matchesManual) %>% 
   dplyr::select(-ID, -facecounter)%>%
@@
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
-overlayGgplot(imagesList0, ALLmetaIMG, matchBox = FALSE)
+overlayGgplot(imagesList0, ALLmetaIMGFaces, matchBox = FALSE)
 ```
@@
 However, individual faces are not beneficial if they do not correspond to the faces manually annotated.
-`r figr("Face-Bounding-Box-UpSet", TRUE, type="Figure")` was created by defining groups depending on the softwares
-that recognized each particular face.
+`r figr("Face-Bounding-Box-UpSet", TRUE, type="Figure")` was created by defining groups depending on the softwares that recognized each particular face.
 The UpSetR [-@UpSetR] package helps visualise set intersections.
@@
 
+## Regression
+
+```{r}
+ALLmetaIMGFaces
+#for each face there
+```
+
 ## Results
@@
 
+-Google more than others
+
 ```{r Face-Bounding-Box-UpSet, results='hide', type="figure", caption="Face Bounding Box Data:", anchor="figure"}
@@
 `r figr("Face-Bounding-Box-Upset", TRUE, type="Figure")` Bar Chart shows the Face Bounding Boxes that were recognized by multiple software.
-The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations. The following groups were Boxes recognized by both Manual annotations and the Google API.
+The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations.
+The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API.
 
-```{r Face-Bounding-Box-Data-Box, anchor="figure"}
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(type)), fill=type, y = size)) + geom_boxplot() + scale_y_continuous() +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Google","Animetrics","Manual","Microsoft","Skybiometry"))+ylab("Size of Face Bounding Boxes")+guides(fill=FALSE)
-
-```
-
-The box and whisker plot in 
-`r figr("Face-Bounding-Box-Data-Box", TRUE, type="Figure")` shows the differences between the sizes of the 'Face Bounding Boxes' produced by each software.
-Where a 'Face Bounding Box' refers to the size of the square the software provided as a location in the image of a face that was detected.
-On average, Google maps the largest boxes around faces, and has the largest box recognized in the set.
-On average, the smallest Face Boxes are created by Skybiometry.
-
-```{r I2, results=TRUE, caption="2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0014.png", anchor="figure"}
-imagesList2<-as.list("2016_CT6_R02_FLopez_ESP_vs_GPella_ARG_MS227_clip.0009.png")
-overlayGgplot(imagesList2, ALLmetaIMG, matchBox = FALSE)
-```
-
-The image above shows the smallest Face Bounding Box recognized. However visual inspection shows it only captures the player's eye and nose, not their whole face.
+On average, Google maps the largest boxes around faces, and has the largest box recognized in the set. On average, the smallest Face Boxes are created by Skybiometry.
 
@@
 imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
-overlayGgplot(imagesList3, ALLmetaIMG, matchBox = FALSE)
+overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
 ```

### 2017-01-21 Report06-12.Rmd
Report Alterations
referencing in bookdown form

@@
 date: '2017'
-output:
-  pdf_document:
-    citation_package: natbib
-    fig_caption: yes
-    fig_crop: yes
-    toc: yes
-    toc_depth: 2
-  html_notebook: null
+output: bookdown::pdf_document2
 fontsize: 11pt
@@
 #packages:
+library(bookdown)
 library(pander)
@@
 library(UpSetR)
+library(descr)
+library(tables)
 
@@
 #csv files:
-ALLmetaIMG<-read_csv("ALLmetaIMG.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+ALLmetaIMG<-read_csv("ALLmetaIMG1.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
 SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
@@
 
-We were able to try the online demos to see whether these software were viable, we used the following Image displayed below in `r figr("Trial-Image", TRUE, type="Figure")`:
+We were able to try the online demos to see whether these software were viable, we used the following Image displayed below in Figure \@ref(Trial-Image):
 
-```{r Trial-Image, caption="This is a player", message=TRUE, warning=TRUE, anchor="figure"}
+```{r Trial-Image, fig.cap = "Initial Image Used For Testing\\label{Trial-Image}", message=TRUE, warning=TRUE}
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
@@
 
-```{r Scene-Attributes-Table, anchor="table", caption="Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute."}
-kable(SceneAttributes, format = "pandoc", booktabs = TRUE)
+```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
+kable(SceneAttributes, format = "pandoc", booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
 ```
@@
 To determine which of the sometimes many faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
-This was based on the attributes provided in `r figr("Solution-Specifications-Table", TRUE, type="Table")`, below:
+This was based on the attributes provided in Table  \@ref(tab:Solution-Specifications-Table), below:
 
-```{r Solution-Specifications-Table, results='asis', anchor="table"}
-kable(SolutionSpecs, format = "pandoc", booktabs = TRUE, caption = "Software solutions specifications.")
+```{r Solution-Specifications-Table, results='asis', fig.cap = "\\label{tab:Solution-Specifications-Table}"}
+kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)
 
@@
 
-```{r Face-Attribute-Tables, results='asis', anchor="table"}
-kable(FaceAttributes, format = "pandoc", booktabs = TRUE, caption = "Attributes of an individual face within an image. The most appropriate option from the list was selected for each attribute.")
+```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image.
+The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
+kable(FaceAttributes, format = "pandoc", booktabs = TRUE)
 ```
@@
 
-The program we created was an interactive application that worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attributes in `r figr("Scene-Attributes-Table", TRUE, type="Table")` as shown above.
+The program we created was an interactive application that worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attributes in \@ref(tab:Scene-Attributes-Table) as shown above.
 
@@
 Using the data set^[ALLmetaIMG] of the combined API and manual results, we were able to compare the performance of the software.
-Firstly, we considered how many individual faces the software were able to detect in `r figr("Face-Bounding-Box-Data", TRUE, type="Figure")` .
+Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(Face-Bounding-Box-Data).
 
 However, individual faces are not beneficial if they do not correspond to the faces manually annotated.
-`r figr("Face-Bounding-Box-UpSet", TRUE, type="Figure")` was created by defining groups depending on the softwares that recognized each particular face.
+Figure \@ref(Face-Bounding-Box-Upset) was created by defining groups depending on the softwares that recognized each particular face.
 The UpSetR [-@UpSetR] package helps visualise set intersections.
@@
 
-Following, we considered the sizes of the Boxes created in `r figr("Face-Bounding-Box-Data-Box", TRUE, type="Figure")`, this was an attempt to determine how the software performed when presented with smaller faces.
-The boxplot uses the size of the Face Bounding Boxes, and contrasts based on the software the Boxes were found from.
-
-To determine how each software reacted to the same face we looked at an image that contained only
-
-finding faces that were recognized and grouping them by the softwares
-
-Skybiometry results accounted for the 255 smallest recognized faces. However this is not necessarily a benefit to this research, as these are not all faces.
-
 ## Regression
-
-```{r}
-ALLmetaIMGFaces
-#for each face there
-```
 
@@
 
-```{r Face-Bounding-Box-Data, results='hide', type="figure", caption="Face Bounding Box Data:", anchor="figure"}
+```{r Face-Bounding-Box-Data, results='hide', fig.cap = "Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft.\\label{Face-Bounding-Box-Data}"}
 ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE)
-```
-
-The bar chart in 
-`r figr("Face-Bounding-Box-Data", TRUE, type="Figure")` above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft.
-
--Google more than others
-
-```{r Face-Bounding-Box-UpSet, results='hide', type="figure", caption="Face Bounding Box Data:", anchor="figure"}
-createUpSet(ALLmetaIMGFaces)
-```
-
-`r figr("Face-Bounding-Box-Upset", TRUE, type="Figure")` Bar Chart shows the Face Bounding Boxes that were recognized by multiple software.
-The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations.
-The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API.
-
-On average, Google maps the largest boxes around faces, and has the largest box recognized in the set. On average, the smallest Face Boxes are created by Skybiometry.
-
-```{r I3, results=TRUE, caption="2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png", anchor="figure"}
-imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
-overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
-```
-
-As before, the 'face' is not as we would hope it would be classified. Just right of the center, the smaller box actually captures a fist, not a face.
-
-```{r I4,results=TRUE, caption="2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png", anchor="figure"}
-imagesList4<-as.list("2016_RLA_R04_NDjokovic_SRB_vs_GSimon_FRA_MS401_clip.0003.png")
-overlayGgplot(imagesList4, ALLmetaIMG, matchBox = FALSE)
-```
-
-I4 shows the sensitivity of the software. We may consider this too sensitive as it recognized the eye and nose of the ball boy on the court.
-
-```{r I5, results=TRUE, caption="2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png", anchor="figure"}
-imagesList5<-("2016_SC2_R01_AKerber_GER_vs_MDoi_JPN_WS1332_clip.0083.png") 
-overlayGgplot(imagesList5, ALLmetaIMG, matchBox = FALSE)
-```
-
-As seen in this image of the crowd, the software is performing reasonably well. It does recognize the faces, yet only one not recognized by the other software, this may be due to the sunglasses.
-
-This image demonstrates that the it is not necessarily the smaller faces that Skybiometry recognizes, but it puts smaller bounds on the facial features than other software.
-
-```{r Type-Matches-Manual, anchor="table"}
-library(descr, quietly = TRUE)
-NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
-NoManual<-NoManual %>% droplevels(NoManual$type)
-Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
-kable((Accuracy))
 ```
@@
 
+```{r Face-Bounding-Box-UpSet, fig.cap = "Face Bounding Boxes Per Software Combination.
+The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software.
+The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations.
+The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API.\\label{Face-Bounding-Box-Upset}"}
+createUpSet(ALLmetaIMGFaces)
+```
+
+```{r I3, results=TRUE, fig.cap = "There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face.\\label{fig:I3}"}
+imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
+overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
+```
+
 To consider how many Type I errors occurred, where a face was detected incorrectly, we look at the Bounding Boxes that do not match manually annotated faces.
 
-Table 4 shows whether the potential Face Bounding Boxes match faces that were annotated during the manual classifications.
+```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}
+
+NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
+NoManual<-NoManual %>% droplevels(NoManual$type) 
+Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
+CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
+```
+
+Table \@ref(Type-Matches-Manual) shows whether the potential Face Bounding Boxes match faces that were annotated during the manual classifications.
 Where the FALSE row denotes where software's Face Bounding Boxes do not coincide with manually annotated faces.
@@
 
-```{r Image-Characteristics-Table, anchor="table"}
+```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
 ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
@@
 
-`r figr("Image-Characteristics-Table", TRUE, type="Figure")`
- displays the feature combinations that produced the most potential face Bounding Boxes recognition by all four software. The most common shot is a crowd shot.
+\@ref(Image-Characteristics-Table) displays the feature combinations that produced the most potential face Bounding Boxes recognition by all four software. The most common shot is a crowd shot.
 The second row in the table with 830 faces recognized is more interesting than the first result.
@@
 
-```{r Typical-Best-Recognised, results=FALSE, anchor="figure"}
+```{r Typical-Best-Recognised, results=FALSE, fig.cap = "\\label{fig:Typical-Best-Recognised}"}
 imagesList1<-as.list("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png")
@@
 
-```{r Google-Errors-Characteristics-Table, anchor="Table"}
+```{r Google-Errors-Characteristics-Table, fig.cap = "\\label{tab:Google-Errors-Characteristics-Table}"}
 library(dplyr)
@@
 
-`r figr("Google-Errors-Characteristics-Table", TRUE, type="table")`
+Table \@ref(Google-Errors-Characteristics-Table)
  shows that the potential Face Bounding Boxes Google returned were found in images that had the same characteristics of those that were manually annotated for faces.
@@
 
-The best scenes for facial recognition have been found, given this information the following `r figr("Face-Characteristics-Table", TRUE, type="table")`
- considers the Characteristics of the individual faces found within those scenes.
+The best scenes for facial recognition have been found, given this information the following \@ref(Face-Characteristics-Table) considers the Characteristics of the individual faces found within those scenes.
 For this section we chose to consider only the faces that were manually annotated as players, with the intention of not basing results on recognition of undesirable faces.
 
-```{r Face-Characteristics-Table, anchor="Table"}
+```{r Face-Characteristics-Table, fig.cap = "\\label{tab:Face-Characteristics-Table}"}
 FaceCharacteristics <- ALLmetaIMGPlayers %>%   filter(type=="Google")%>% filter(matchesManual==TRUE)%>% group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())
@@
 
-`r figr("Face-Characteristics-Table", TRUE, type="table")`
+Table \@ref(Face-Characteristics-Table)
 utilizes a set of faces that were Manually annotated and also found by Google. 
@@
 
-```{r Glasses, anchor="Figure"}
-GlassesGoogle <- ALLmetaIMGPlayers %>% filter(type=="Google") %>%
+```{r Glasses, fig.cap = "This table shows the amount of faces recognised by google wearing glasses.
+The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally.\\label{tab:Glasses}"}
+GlassesGoogle <- ALLmetaIMGFaces %>% filter(type=="Google") %>%
 filter(matchesManual==TRUE)
-
 pander(table(GlassesGoogle$glasses))
@@
 
-The extreme disparity between the amount of faces with glasses to without them means that the occurrence of these attributes across the software must be considered proportionally.
-
-```{r Glasses-Figure, anchor="Figure"}
-ggplotProportion(ALLmetaIMGPlayers, glasses)
+```{r Glasses-Figure, fig.cap = "The figure above shows that Google outperforms the other software, with or without glasses.
+When there are no glasses worn Google finds over 60% of the manually annotated faces.\\label{fig:Glasses-Figure}"}
+ggplotProportion(ALLmetaIMGPlayers, glasses)+xlab("Glasses on Face")
 ```
 
-Graph 2 above shows that Google outperforms the other software, with or without glasses. When there are no glasses worn Google finds over 60% of the manually annotated faces.
-
-```{r HeadAngles, anchor="Table"}
+```{r HeadAngles, fig.cap = "\\label{tab:HeadAngles}"}
 HeadangleGoogle <- ALLmetaIMGPlayers %>%   filter(type=="Google") %>%
@@
 
-The amount of faces found by Google with the head-angle "Other", is much larger than the amount of faces with the head-angle "Profile" or "Front On".
+In Table \@ref(HeadAngles), the amount of faces found by Google with the head-angle "Other", is much larger than the amount of faces with the head-angle "Profile" or "Front On".
 Therefore this should also be considered proportionately.
 
-```{r Headangle-Figure, anchor="Figure"}
-ggplotProportion(ALLmetaIMGPlayers, headangle)
+```{r Headangle-Figure, fig.cap = "Google performs much better in comparison to the other software when the head-angle is Profile.
+This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance.\\label{fig:Headangle-Figure}"}
+ggplotProportion(ALLmetaIMGPlayers, headangle)+xlab("Head Angle of Face")
 ```
-
-Graph 3 displays that Google performs much better in comparison to the other software when the head-angle is Profile.
-This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance.
 
@@
 
-```{r Google-Characteristics-Table, anchor="table"}
+```{r Google-Characteristics-Table, fig.cap = "\\label{tab:Google-Characteristics-Table}"}
 GoogleCharacteristics <- ALLmetaIMG %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
@@
 
-`r figr("Google-Characteristics-Table", TRUE, type="table")`
+Table \@ref(Google-Characteristics-Table)
 shows how many images with potential player's faces Google recognized.

### 2017-01-21 regressionWIP.R

@@ -1,4 +1,7 @@
 # Prepare data
+library(purrr)
+library(dplyr)
+library(ggplot2)
 hitmiss <- function(x){
   allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
   hit <- allType %in% x$type

### 2017-02-13 Report06-12.Rmd
Table formatting

@@
 author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
-date: '2017'
+date: "13 February 2017"
 output: bookdown::pdf_document2
@@
 library(tables)
+library(xtable)
 
@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-kable(SceneAttributes, format = "pandoc", booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
+kable(SceneAttributes, format = "markdown", booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
 ```
@@
 To determine which of the sometimes many faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
-This was based on the attributes provided in Table  \@ref(tab:Solution-Specifications-Table), below:
+This was based on the attributes provided in Table
+\@ref(tab:Solution-Specifications-Table), below:
 
-```{r Solution-Specifications-Table, results='asis', fig.cap = "\\label{tab:Solution-Specifications-Table}"}
-kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)
-
+```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis',}
+kable(SolutionSpecs, format = "markdown", booktabs = TRUE, caption="")
 ```
@@
 The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
-kable(FaceAttributes, format = "pandoc", booktabs = TRUE)
+kable(FaceAttributes, format = "markdown", booktabs = TRUE)
 ```
@@
 This helped to provide information for all attributes quickly and consistently.
-The Shiny [@shinyw] package provides a 'framework for building web applications using R'.
-It allows for the creation of web applications using R rather than 'requiring HTML, CSS, or JavaScript knowledge.'
-
-The program we created was an interactive application that worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attributes in \@ref(tab:Scene-Attributes-Table) as shown above.
 
@@
 
+```{r Regression, fig.cap = "\\label{Regression}"}
+hitmiss <- function(x){
+  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
+  hit <- allType %in% x$type
+  x[1,] %>%
+    dplyr::select(file:visorhat) %>%
+    cbind(type = allType, hit = hit)
+}
+
+glmFits <- ALLmetaIMGFaces %>%
+  split(.$FaceKey) %>%
+  map_df(~ hitmiss(.)) %>%
+  split(.$type) %>%
+  map(~ glm(hit ~ ., data = select(., -type, -file), family=binomial(link='logit')))
+
+glmSummary <- glmFits %>%
+  map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname))
+
+glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary)))
+
+## Significance of variables by software
+#glmPlot %>%
+#  mutate(significant = `Pr(>|t|)` < 0.05) %>%
+#  filter(significant==TRUE) %>% 
+#  droplevels(glmPlot$variable) %>% 
+#  ggplot(aes(x=type, y=`Pr(>|t|)`)) + 
+#  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
+#  geom_col(aes(fill=significant))
+
+glmx <- glmPlot %>%
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  filter(significant==TRUE) %>% 
+  droplevels(glmPlot$variable) %>% 
+  ggplot(aes(x=variable, y=`Pr(>|z|)`)) + 
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
+  geom_col(aes(fill=type)) 
+glmx
+
+```
+
+This shows how influential certain attributes are in determining whether a face will be detected or not.
+
+Regression analysis showed
+
 ## Results
@@
 ```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}
-
 NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
@@
 Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
-CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
+ct<-CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
+print(ct)
 ```
@@
 ImageCharacteristics<-ImageCharacteristics[1:10,]
-kable(ImageCharacteristics, booktabs = TRUE)
+kable(ImageCharacteristics, booktabs = TRUE, caption="", format = "markdown")
 ```
@@
 GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
-kable(GoogleNoMatch[1:10,], type = 'table')
+kable(GoogleNoMatch[1:10,], caption="", format = "markdown")
 
@@
 ```{r Face-Characteristics-Table, fig.cap = "\\label{tab:Face-Characteristics-Table}"}
-FaceCharacteristics <- ALLmetaIMGPlayers %>%   filter(type=="Google")%>% filter(matchesManual==TRUE)%>% group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())
+FaceCharacteristics <- ALLmetaIMGPlayers %>%
+  filter(type=="Google") %>%
+  filter(matchesManual==TRUE) %>%
+  group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())
+
 FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
 FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
-kable(FaceCharacteristics, type = 'table')
+kable(FaceCharacteristics, caption="", format = "markdown")
 ```
@@
 Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
-kable(Accuracy)
+kable(Accuracy, caption="", format = "markdown")
 # make this a proportional table, would this be necessary if we have the UpSetR
@@
 
-kable(GoogleCharacteristics, format = "pandoc", booktabs = TRUE)
+kable(GoogleCharacteristics, format = "markdown", booktabs = TRUE, caption="")
 ```

### 2017-02-14 Report06-12.Rmd
glm modelling

@@
 ####Analysis
-The statistical analysis conducted to summarize and assess the validity of the method.
-This method allowed all the software and the faces they found to be compared.
 
@@
 
-```{r Regression, fig.cap = "\\label{Regression}"}
+This shows how influential certain attributes are in determining whether a face will be detected or not.
+
+Regression analysis showed that the situation attribute of an image was most influential in increasing the likelihood of a hit.
+And head angle was most influential in decreasing.
+
+```{r}
+# Prepare data
+library(purrr)
+library(dplyr)
+library(ggplot2)
 hitmiss <- function(x){
@@
   split(.$type) %>%
-  map(~ glm(hit ~ ., data = select(., -type, -file), family=binomial(link='logit')))
+  map(~ glm(hit ~ . + visorhat*glasses, data = select(., -type, -file), binomial(link = "logit")))
 
@@
 
-## Significance of variables by software
-#glmPlot %>%
-#  mutate(significant = `Pr(>|t|)` < 0.05) %>%
-#  filter(significant==TRUE) %>% 
-#  droplevels(glmPlot$variable) %>% 
-#  ggplot(aes(x=type, y=`Pr(>|t|)`)) + 
-#  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
-#  geom_col(aes(fill=significant))
-
-glmx <- glmPlot %>%
-  mutate(significant = `Pr(>|z|)` < 0.05) %>%
-  filter(significant==TRUE) %>% 
-  droplevels(glmPlot$variable) %>% 
-  ggplot(aes(x=variable, y=`Pr(>|z|)`)) + 
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
-  geom_col(aes(fill=type)) 
-glmx
-
 ```
 
-This shows how influential certain attributes are in determining whether a face will be detected or not.
+```{r, Regression-Significance-Plot, fig.cap = "\\label{Regression--Significance-Plot}"}
+## Significance of variables by software
+glmPlot %>%
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
+  ggplot(aes(x=type, y=`Pr(<|z|)`)) + 
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
+  geom_col(aes(fill=significant)) + 
+  facet_wrap(~ variable)
+```
 
-Regression analysis showed
+The bar chart of the interaction of Glasses and Visors in \@ref(Regression--Significance-Plot) or Hats shows that when the face is accessorised with both, Google has a significantly increased chance of finding the face
+
+```{r, Regression-Estimates-Plot, fig.cap = "\\label{Regression--Estimates-Plot}"}
+## Significance of Estimated variable influences by software
+glmPlot %>%
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  ggplot(aes(x=type, y=Estimate)) + 
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
+  geom_col(aes(fill=significant)) + 
+  facet_wrap(~ variable, scales = "free_y")
+
+#parallel coordinate plot, vars on x????
+#unpack intercept
+#don't force to zero
+#convert into full model decription - every single level combination
+#have every level and cross level - order combinations by p value
+#function for estimates for each treatment
+#multinomail 
+```
+
+```{r Regression-Situation-Table, fig.cap = "\\label{Regression-Situation-Table}"}
+
+RegSituation<-glmPlot %>% subset(grepl("situation*", variable)) %>% select(variable, Estimate, type)
+
+#RegSituation
+
+data_wide <- spread(RegSituation, variable, Estimate)
+
+names(data_wide)[names(data_wide)=="situationCourt player close-up"] <- "Court player close-up"
+names(data_wide)[names(data_wide)=="situationCrowd"] <- "Crowd"
+names(data_wide)[names(data_wide)=="situationOff court close up of player"] <- "Off court close up of player"
+names(data_wide)[names(data_wide)=="situationCourt close-up not player"] <- "Court close-up not player"
+
+kable(data_wide, format = "markdown", booktabs = TRUE, caption = "")
+```
+
+```{r Regression-Angle-Table, fig.cap = "\\label{Regression-Angle-Table}"}
+
+RegHeadAngle<-glmPlot %>% subset(grepl("headangle*", variable)) %>% select(variable, Estimate, type)
+
+#RegSituation
+
+data_wideHead <- spread(RegHeadAngle, variable, Estimate)
+
+names(data_wideHead)[names(data_wideHead)=="headangleOther"] <- "Other"
+names(data_wideHead)[names(data_wideHead)=="headangleProfile"] <- "Profile"
+
+kable(data_wideHead, format = "markdown", booktabs = TRUE, caption = "")
+```
 
@@
 
-```{r Face-Bounding-Box-Data, results='hide', fig.cap = "Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft.\\label{Face-Bounding-Box-Data}"}
-ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE)
+```{r Face-Bounding-Box-Data, results='hide', fig.cap = "\\label{Face-Bounding-Box-Data} Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft."}
+ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE) + labs(caption="")
 ```
@@
 
-```{r Face-Bounding-Box-UpSet, fig.cap = "Face Bounding Boxes Per Software Combination.
+```{r Face-Bounding-Box-UpSet, fig.cap = "\\label{Face-Bounding-Box-Upset} Face Bounding Boxes Per Software Combination.
 The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software.
 The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations.
-The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API.\\label{Face-Bounding-Box-Upset}"}
+The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API."}
 createUpSet(ALLmetaIMGFaces)
@@
 
-```{r I3, results=TRUE, fig.cap = "There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face.\\label{fig:I3}"}
+```{r I3, results=TRUE, fig.cap = "\\label{fig:I3} There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face."}
 imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
@@
 
-```{r Glasses, fig.cap = "This table shows the amount of faces recognised by google wearing glasses.
-The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally.\\label{tab:Glasses}"}
+```{r Glasses, fig.cap = "\\label{tab:Glasses} This table shows the amount of faces recognised by google wearing glasses.
+The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally."}
 GlassesGoogle <- ALLmetaIMGFaces %>% filter(type=="Google") %>%
@@
 
-```{r Glasses-Figure, fig.cap = "The figure above shows that Google outperforms the other software, with or without glasses.
-When there are no glasses worn Google finds over 60% of the manually annotated faces.\\label{fig:Glasses-Figure}"}
+```{r Glasses-Figure, fig.cap = "\\label{fig:Glasses-Figure} The figure above shows that Google outperforms the other software, with or without glasses.
+When there are no glasses worn Google finds over 60% of the manually annotated faces."}
 ggplotProportion(ALLmetaIMGPlayers, glasses)+xlab("Glasses on Face")
@@
 
-```{r Headangle-Figure, fig.cap = "Google performs much better in comparison to the other software when the head-angle is Profile.
-This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance.\\label{fig:Headangle-Figure}"}
+```{r Headangle-Figure, fig.cap = "\\label{fig:Headangle-Figure} Google performs much better in comparison to the other software when the head-angle is Profile.
+This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance."}
 ggplotProportion(ALLmetaIMGPlayers, headangle)+xlab("Head Angle of Face")

### 2017-02-14 Supplementary Materials.Rmd
glm modelling

--- 2017-01-21 Report06-12.Rmd
@@
 ---
-title: "Detecting Facial Expressions in Professional Tennis Matches"
+title: "Supplementary Materials"
 author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
-date: '2017'
+date: "13 February 2017"
 output: bookdown::pdf_document2
@@
 ```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#packages:
+
 library(bookdown)
@@
 library(kfigr)
+library(tables)
 library(UpSetR)
 library(descr)
-library(tables)
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE)
-
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.env = TRUE)
 options("citation_format" = "pandoc")
@@
 
-# Create UpSetR graph
-createUpSet <- function(data) {
-VennLists<-data %>%
+```
+
+Talk about how sample was created?
+
+The Shiny [@shinyw] package provides a 'framework for building web applications using R'.
+It allows for the creation of web applications using R rather than 'requiring HTML, CSS, or JavaScript knowledge.'
+
+The program we created was an interactive application that worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attributes in Scene-Attributes-Table.
+
+Describe a hit in regression
+
+```{r Regression, results='hide', fig.cap = "\\label{Regression}"}
+library(purrr)
+
+hitmiss <- function(x){
+  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
+  hit <- allType %in% x$type
+  x[1,] %>%
+    dplyr::select(file:visorhat) %>%
+    cbind(type = allType, hit = hit)
+}
+
+glmFits <- ALLmetaIMGFaces %>%
+  split(.$FaceKey) %>%
+  map_df(~ hitmiss(.)) %>%
   split(.$type) %>%
-  map(~ .$FaceKey)%>% 
-  fromList() %>%
-  upset(order.by="freq", nsets=100)
-}
+  map(~ glm(hit ~ ., data = select(., -type, -file)))
+
+glmSummary <- glmFits %>%
+  map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname))
+
+glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary)))
+
+# Graphs
+## Coefficient of variables by software
+#glmPlot %>%
+#  ggplot(aes(x=type, y=Estimate)) +
+#  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
+#  geom_col() + 
+#  facet_wrap(~ variable)
+
+## Significance of variables by software
+glmPlot %>%
+  mutate(significant = `Pr(>|t|)` < 0.05) %>%
+  mutate(`Pr(<|t|)` = 1 - `Pr(>|t|)`) %>%
+  ggplot(aes(x=type, y=`Pr(<|t|)`)) + 
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
+  geom_col(aes(fill=significant)) + 
+  facet_wrap(~ variable)
+
+## Significance of Estimated variable influences by software
+glmPlot %>%
+  mutate(significant = `Pr(>|t|)` < 0.05) %>%
+  ggplot(aes(x=type, y=Estimate)) + 
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
+  geom_col(aes(fill=significant)) + 
+  facet_wrap(~ variable)
 
@@
 
-##Introduction
+```{r Regression-Table, fig.cap = "\\label{Regression-Table}"}
 
-Many tennis professionals believe that tennis is a game heavily affected by the mental states of the players.
-The opportunity for researching this "inner game" presents itself with the hope of improving the playing and coaching of tennis players by improving their "mental game".
-By statistically analyzing the faces and expressions of players during a match there is a hope that insight may be gained into the effects of the mental state on the outcome of a match.
-Facial expressions during competition provide the most direct insight into a player's thoughts.
-The aim of this project is to begin to develop methods to collect accurate information about the facial expressions of elite tennis athletes during match play.
+RegSituation<-glmPlot %>% subset(grepl("situation*", variable)) %>% select(variable, Estimate, type)
 
-In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcasted videos of elite tennis matches.
-Using the broadcasted videos gives an objective insight to emotions as the player progresses through a match.
-While it is impossible to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through results produced by a recognition software.
-As opposed to the approach of previous studies that have used Player's recollections after a game to determine their emotions.
+#RegSituation
 
-Making use of the recognition software's currently available presents a challenge as high performance sports are not the intended uses of such software's.
-Their capabilities are often limited to their intended security and surveillance uses.
-@Boston addresses the 'lack of robustness of current tools in unstructured environments' that this paper faces and applies to a sports environment.
-This report aims to analyse the application of these software's to a broadcast to find a suitable software and API to use to analyse a pre-recorded tennis broadcast file.
+data_wide <- spread(RegSituation, variable, Estimate)
 
-####Project Aim
-The aims of the present study were to determine the feasibility of using currently available facial recognition algorithms for extracting facial information from players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
-This limited selection was based on accessible APIs that we believed would produce appropriate and useful facial recognition.
-The performance of the evaluated software was compared against manual classification obtained notation tool developed by the authors.
-In addition to looking at the overall performance, we also evaluated image factors that influences the performance of each service.
+names(data_wide)[names(data_wide)=="situationCourt player close-up"] <- "Court player close-up"
+names(data_wide)[names(data_wide)=="situationCrowd"] <- "Crowd"
+names(data_wide)[names(data_wide)=="situationOff court close up of player"] <- "Off court close up of player"
+names(data_wide)[names(data_wide)=="situationCourt close-up not player"] <- "Court close-up not player"
 
-####Sample and sampling approach
-The goal of the sample was to be representative of the video files that will be used for future facial recognition analysis.
-
-- 6406 Australian Open images (2.8GB)
-- 800x450px size frames from 105 match broadcast videos
-- Video frames taken every 3 seconds over a 5 minute segment
-
-The sample consisted of a set of 6404 still images.
-To produce these images, a still shot of the frame was taken at every three seconds, for the length of each 5 minute segment.
-The stills were provided by Tennis Australia for use in this research, these segments were taken from 105 video files, which were the broadcast of the tennis Matches shown on the Seven Network during the Australian Open 2016.
-The sample included an equal amount of singles tennis matches played between females and males.
-The rounds of the competition vary as to not limit the pool of players to only those who progressed, though there was a higher chance of advancing players reappearing.
-
-The sample included images that contained the faces of many people, this included players, staff on the court and fans in the crowd.
-These faces were included in the manual annotations as they were likely to be found by the software selected.
-We felt including these additional faces would not only increase the sample by which to judge the software's capabilities but also allow provision of information on how to differentiate between players and other people for further research.
-Therefore the sample was not filtered at this initial stage.
-
-There are many matches played during the Australian Open, and they are played on the range of courts available at Melbourne Olympic Park.
-Therefore the sample was selected to be representative of the seven courts that have the Hawk Eye technology enabled.
-
-####Selecting the software
-The choice of the initial software considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'
-
-The process of software selection to determine which we would compare was based on several criteria.
-Firstly, we based our choices on the results of the report as it considered processing speed and feature selection techniques, as well as the ability to perform both still-to-video and video-to-video recognition.
-
-From the software's analysed we considered availability for use within the time frame of the report.
-This led us to choose Animetrics FaceR.
-The report outlines that for Animetrics, 'one requirement is that image/face proportion
-should be at least 1:8 and that at least 64 pixels between eyes are required'. We realize this could present challenges given our data set.
-It will also allow for an extension from detecting to recognizing people in the data set.
-
-After considering several other off-the-shelf products, we did not choose any other software's from those analysed as they were not as readily available as other products on the market.
-
-This led to SkyBiometry, an API that also allows for both detection and recognition. The cloud-based software as a service, is a 'spin-off of Neurotechnology', a software considered by the report.
-
-We then chose to consider companies who are expanding their API ranges.
-This resulted in the choice of Microsoft API, provided by Microsoft Cognitive Services.
-This detects faces and return a square area where the face was located, and predicts facial features.
-It also allows the possibility of video stream detection.
-
-The final software we chose to analyse was Google Vision API. Due to Google's expansion in many web based solutions we searched for a facial recognition software.
-
-We were able to try the online demos to see whether these software were viable, we used the following Image displayed below in Figure \@ref(Trial-Image):
-
-```{r Trial-Image, fig.cap = "Initial Image Used For Testing\\label{Trial-Image}", message=TRUE, warning=TRUE}
-imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
-overlayGgplot(imagesList0, ALLmetaIMGFaces, matchBox = FALSE)
+kable(data_wide, format = "markdown", booktabs = TRUE, caption = "")
 ```
 
-## Methodology
-An annotation tool was constructed to create a base for comparative analysis, we refer to this as Manual Classifications.
-These manual Classifications involved describing the features of the Scenes.
+```{r Regression-Table, fig.cap = "\\label{Regression-Table}"}
 
-```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-kable(SceneAttributes, format = "pandoc", booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
+RegHeadAngle<-glmPlot %>% subset(grepl("headangle*", variable)) %>% select(variable, Estimate, type)
+
+#RegSituation
+
+data_wideHead <- spread(RegHeadAngle, variable, Estimate)
+
+names(data_wideHead)[names(data_wideHead)=="headangleOther"] <- "Other"
+names(data_wideHead)[names(data_wideHead)=="headangleProfile"] <- "Profile"
+
+kable(data_wideHead, format = "markdown", booktabs = TRUE, caption = "")
 ```
-
-The aim was to collect specific information on each different face within the scene.
-To determine which of the sometimes many faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
-This was based on the attributes provided in Table  \@ref(tab:Solution-Specifications-Table), below:
-
-```{r Solution-Specifications-Table, results='asis', fig.cap = "\\label{tab:Solution-Specifications-Table}"}
-kable(SolutionSpecs, format = "pandoc", booktabs = TRUE)
-
-```
-
-It was decided that it would be reasonable for a software to detect was decided to be a face size larger than 20 by 20 pixels, as it was specified that the software had minimum distances between the eyes on a face for recognition.
-(reference table with values)
-If it was the face of a player it was recorded if it obviously showed their face.
-The back of the head was not able to be picked up by any software, so after a demo trial these faces were classified manually  but reclassified as other.
-Crowd shots provided difficultly in determining which faces were reasonable to classify.
-As these faces were not the intended targets of the recognition these faces were contributing to our understanding of the software.
-The same face size standard applied to crowd members, but focus was placed on the most prominent faces. For each of these faces, we collected information on the following attributes:
-
-```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image.
-The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
-kable(FaceAttributes, format = "pandoc", booktabs = TRUE)
-```
-
-####Manual Annotation
-To record the details of attributes for each face and scene a Shiny [-@shiny] App was created.
-We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassificationProgram.R].
-This helped to provide information for all attributes quickly and consistently.
-The Shiny [@shinyw] package provides a 'framework for building web applications using R'.
-It allows for the creation of web applications using R rather than 'requiring HTML, CSS, or JavaScript knowledge.'
-
-The program we created was an interactive application that worked by presenting an image, using the imager @imager package, from the sample of images that had not yet been considered, appearing underneath were a set of radio buttons corresponding to the Scene Attributes in \@ref(tab:Scene-Attributes-Table) as shown above.
-
-If there was a face in the image the annotator was able to highlight a section of the image to create a square 'Face Box'.
-This changed the display and presented a set of Attributes with radio buttons, this allowed information to be recorded for the face in the specific 'Face Box'.
-This recorded the x and y coordinates of the corner points of a box drawn by the mouse, and when the save button was hit it saved all the radio button selections and the 'Face Box' coordinates to a CSV file^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedFaces.csv].
-
-When a face was not selected, the radio buttons showed the Scene attributes and the radio buttons with the possible selections the annotated was able to choose from.
-When in this display, selecting the save button would then save the Scene selections to a specific CSV file^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedScenes.csv].
-
-If there were issues, the CSV files were able to be edited, this was reserved for extreme circumstances.
-As a lot of care was taken to ensure the first selections were correctly submitted and applied to the correct Faces and Scenes.
-
-All the annotations for this sample were completed by one author.
-This was chosen to provide consistency across the sample of faces annotated manually.
-However the initial choices of what would be reasonably detected were made by several of the authors.
-
-####Software Recognition
-The software choices allowed for POST requests to be sent via the internet.
-To access the APIs through R we enlisted the httr package, using functions from this package a script was written for Google, Animetrics^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/animetrics.R], Microsoft^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/microsoftAPI.R] and Skybiometry^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/autoSkybiometry.R].
-These scripts contained loops that would move through the images, individually posting a request for each image to be analysed.
-These scripts included retrieving the information provided and converting it into a usable format for our analysis.
-One interesting anomaly was found when using the Skybiometry software as it limited the amount of requests per minute.
-We accounted for this by stalling the posts for the amount of waiting time the software notified, and checking until the time lapsed and the script could continue looping.
-
-####Data Processing
-The data needed for our analysis was spread across six files.
-For each software we had the information on the location of the Facial Bounding Boxes, as well as the time taken for the software to find the information.
-Some of the software also provided a more detailed level of information.
-
-The collation of the results from the Manual Recognition Program created
-two CSVs, ManualClassifiedFaces^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedFaces.csv] and ManualClassifiedScenes^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedScenes.csv].
-
-A single data set was created to combine all necessary information in the previously mentioned files for our analysis.
-The information in the data set^[https://github.com/mvparrot/face-recognition/blob/master/ALLmetIMG.csv], was carefully considered.
-It considers the identify of each face, and all relative face attributes, as well as the image file the face was found in, from this information each face was able to be uniquely identified.
-Also included was information on the software that found it, and the time it took the software to identify the face.
-It also has a record of how many faces had been identified in the image by counting each additional recognized face.
-To do so, we gathered the name of the file the face was found in and the software Type the Face Bounding Box was determined by.
-The automatically determined time values were also included.
-The minimum and maximum x and y values were drawn from different values in each software's CSV files.
-This required some processing to align the differing values to be comparable.
-
-To find whether the software were recognizing the same faces a function was created.
-As the location and size of the boxes around the faces were recorded, these values were used to see if a particular identified face box matched a manually identified face, or a region found by another software.
-This function uses the information of each face and compares the intersecting regions of the polygons created by the x,y coordinates of Manual Faces and other software's faces, to determine if the same face was recognized.
-We determined the ratio of intersecting area to total area must be greater than 0.1 to be considered the same face.
-This allowed us to compare the identification areas, as well as contrast the identified faces of each software.
-This contributed another variable, boxID, to the data set^[https://github.com/mvparrot/face-recognition/blob/master/ALLmetIMG.csv].
-
-####Analysis
-The statistical analysis conducted to summarize and assess the validity of the method.
-This method allowed all the software and the faces they found to be compared.
-
-Using the data set^[ALLmetaIMG] of the combined API and manual results, we were able to compare the performance of the software.
-Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(Face-Bounding-Box-Data).
-
-However, individual faces are not beneficial if they do not correspond to the faces manually annotated.
-Figure \@ref(Face-Bounding-Box-Upset) was created by defining groups depending on the softwares that recognized each particular face.
-The UpSetR [-@UpSetR] package helps visualise set intersections.
-Where in this circumstance Face Bounding Boxes may overlap on the same face, each bar shows the number of individual faces that have Face Bounding Boxes resulting from each of the softwares highlighted below the bar.
-
-## Regression
-
-## Results
-
-```{r Face-Bounding-Box-Data, results='hide', fig.cap = "Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft.\\label{Face-Bounding-Box-Data}"}
-ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE)
-```
-
-To evaluate the performance in terms of the overall accuracy of each algorithm we considered the amount of faces they classified that matched faces that were selected manually.
-
-The sample used contains all the manually annotated faces and all the faces recognized by the four software.
-
-```{r Face-Bounding-Box-UpSet, fig.cap = "Face Bounding Boxes Per Software Combination.
-The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software.
-The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations.
-The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API.\\label{Face-Bounding-Box-Upset}"}
-createUpSet(ALLmetaIMGFaces)
-```
-
-```{r I3, results=TRUE, fig.cap = "There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face.\\label{fig:I3}"}
-imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
-overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
-```
-
-To consider how many Type I errors occurred, where a face was detected incorrectly, we look at the Bounding Boxes that do not match manually annotated faces.
-
-```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}
-
-NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
-NoManual<-NoManual %>% droplevels(NoManual$type) 
-Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
-CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
-```
-
-Table \@ref(Type-Matches-Manual) shows whether the potential Face Bounding Boxes match faces that were annotated during the manual classifications.
-Where the FALSE row denotes where software's Face Bounding Boxes do not coincide with manually annotated faces.
-The tables shows that Google found 38.70% of the 90.34% of the Faces found that matched Faces also identified manually.
-
-A potential face detected that does not match a face manually annotated occurs for 9.66% of all the Faces detected by the software. This is especially high for Google with 289 faces identified.
-
-All the Face Bounding Boxes that Google found which do not match manually annotated faces were correctly identifying faces. This exhibits the occurrences of errors.
-
-We then considered the characteristics of the images that the software found Potential Face Bounding Boxes^[These boxes represent an area of pixels that are a potentially recognized face.] in.
-
-```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
-ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
-ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
-ImageCharacteristics<-ImageCharacteristics[1:10,]
-kable(ImageCharacteristics, booktabs = TRUE)
-```
-
-\@ref(Image-Characteristics-Table) displays the feature combinations that produced the most potential face Bounding Boxes recognition by all four software. The most common shot is a crowd shot.
-The second row in the table with 830 faces recognized is more interesting than the first result.
-This useful scene is an image of a Court Player Close-Up in front of a Logo Wall, taken at Player Shoulder Height.
-
-These attributes typically represent an image similar to the following:
-
-```{r Typical-Best-Recognised, results=FALSE, fig.cap = "\\label{fig:Typical-Best-Recognised}"}
-imagesList1<-as.list("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png")
-overlayGgplot(imagesList1, ALLmetaIMG, matchBox = FALSE)
-```
-
-```{r Google-Errors-Characteristics-Table, fig.cap = "\\label{tab:Google-Errors-Characteristics-Table}"}
-library(dplyr)
-
-GoogleNoMatch <- ALLmetaIMG %>%
-  filter(type=="Google") %>%
-  filter(matchesManual==FALSE) %>%
-  group_by(person, situation, bg, shotangle) %>% dplyr::summarise(count=n())
-
-#use this list in the overlay function to view the images where Google found faces not annotated manually
-#GoogleImages<-GoogleNoMatch$file
-#GoogleImages<-as.list(GoogleImages)
-
-GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
-kable(GoogleNoMatch[1:10,], type = 'table')
-
-#overlayGgplot(GoogleImages, GoogleNoMatch, matchBox = TRUE)
-```
-
-Table \@ref(Google-Errors-Characteristics-Table)
- shows that the potential Face Bounding Boxes Google returned were found in images that had the same characteristics of those that were manually annotated for faces.
-<!-- This is shown by the same combinations of characteristics occuring in both Table 5 and Table 6.  keep as tables?-->
-Without looking at each individual image this Table confirms that the potential Face Bounding Boxes Google located will likely be reasonable, and actually contain faces.
-
-The best scenes for facial recognition have been found, given this information the following \@ref(Face-Characteristics-Table) considers the Characteristics of the individual faces found within those scenes.
-For this section we chose to consider only the faces that were manually annotated as players, with the intention of not basing results on recognition of undesirable faces.
-
-```{r Face-Characteristics-Table, fig.cap = "\\label{tab:Face-Characteristics-Table}"}
-FaceCharacteristics <- ALLmetaIMGPlayers %>%   filter(type=="Google")%>% filter(matchesManual==TRUE)%>% group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())
-FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
-FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
-kable(FaceCharacteristics, type = 'table')
-```
-
-Table \@ref(Face-Characteristics-Table)
-utilizes a set of faces that were Manually annotated and also found by Google. 
-Nine of the top ten facial characteristic combinations contained faces that were not wearing glasses.
-The head angle describing the face angle was 'Other'^[Definition for head-angle factor level 'Other' found in..]
-for nine of the top ten facial characteristic combinations.
-
-```{r Glasses, fig.cap = "This table shows the amount of faces recognised by google wearing glasses.
-The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally.\\label{tab:Glasses}"}
-GlassesGoogle <- ALLmetaIMGFaces %>% filter(type=="Google") %>%
-filter(matchesManual==TRUE)
-pander(table(GlassesGoogle$glasses))
-```
-
-```{r Glasses-Figure, fig.cap = "The figure above shows that Google outperforms the other software, with or without glasses.
-When there are no glasses worn Google finds over 60% of the manually annotated faces.\\label{fig:Glasses-Figure}"}
-ggplotProportion(ALLmetaIMGPlayers, glasses)+xlab("Glasses on Face")
-```
-
-```{r HeadAngles, fig.cap = "\\label{tab:HeadAngles}"}
-HeadangleGoogle <- ALLmetaIMGPlayers %>%   filter(type=="Google") %>%
-filter(matchesManual==TRUE)
-
-pander(table(HeadangleGoogle$headangle))
-```
-
-In Table \@ref(HeadAngles), the amount of faces found by Google with the head-angle "Other", is much larger than the amount of faces with the head-angle "Profile" or "Front On".
-Therefore this should also be considered proportionately.
-
-```{r Headangle-Figure, fig.cap = "Google performs much better in comparison to the other software when the head-angle is Profile.
-This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance.\\label{fig:Headangle-Figure}"}
-ggplotProportion(ALLmetaIMGPlayers, headangle)+xlab("Head Angle of Face")
-```
-
-Table 2 = Describe the images/boxes identified by the algorithms--what are they typically like? what is the area represented?
-
-Table 3= Evaluate the performance: what is the overall accuracy of each algorithm (sample should be annotated faces + all boxed identified by algorithms) 
-  How often is type I error made (a face detected incorrectly)?
-
-```{r Accuracy}
-Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
-kable(Accuracy)
-# make this a proportional table, would this be necessary if we have the UpSetR
-```
-
-  How often type II error (a face is incorrectly NOT detected)?   
-  3 of the four software's
-
-It should be noted that there were results where a single face was recognized twice within the same image.
-This was a very unusual result and is notable as a point of interest but given it only occurred for Animetrics, it is not worth basing decisions on this unusual result.
-
-Table 4 = Identify possible explanatory factors to performance; Does accuracy vary by lighting conditions? face size? obscuring factors? angle? etc.
-
-```{r Google-Characteristics-Table, fig.cap = "\\label{tab:Google-Characteristics-Table}"}
-GoogleCharacteristics <- ALLmetaIMG %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
-GoogleCharacteristics<-arrange(GoogleCharacteristics, desc(count))
-
-kable(GoogleCharacteristics, format = "pandoc", booktabs = TRUE)
-```
-
-Table \@ref(Google-Characteristics-Table)
-shows how many images with potential player's faces Google recognized.
-This displays a vast gap between the amount of potential faces found given the different shot angles.
-Shoulder height is an optimum angle for a Face Bounding Box.
-
-Considering only the Shoulder Height Angle, the following Graph looks at how accessories affected Google's recognition.
-
-### Discussion
-Graph 1, the Bar Chart of the Face Bounding Boxes promotes Google as the best possible software for a facial recognition application in tennis.
-According to Table 4 Google had 38.23% of the 9.66% potential face boxes not annotated manually.
-It was considered that this may have shown Google's API may have been finding more unwanted faces than the other software.
-However, visual inspection showed that these were actually faces.
-This is considered in Table 6, which showed that some of the faces were found in a crowd setting.
-Therefore some of these could be considered irrelevant, possibly being crowd faces.
-These were deemed unlikely to be detected and neglected during manual annotation.
-Interestingly, Animetrics had the least amount of matches to Manually annotated faces.
-Looking into this further showed that Animetrics results contained potential Face Bounding Boxes that did not contain faces.
-
-The images were all considered manually.
-The scene information was recorded and the combinations were shown to find how many potential face Bounding Boxes were found with the combination of scene attributes.
-This showed that crowd members faces were often recognized, this is both helpful and unhelpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
-
-Image 1 shows the images preferable for future research. Where the faces will be recognized and allow both the identity and emotion of the players to be recognized.
-
-Google gave the optimum results in this image as it found the face of the player, but did not locate the face of the staff member behind him on the court.
-
-While Google's recognition's mostly matched the Manually annotated set of faces, there were some that did not. These were all actually faces and were missed during manual annotations.
-
-Table 6 shows that 190 of the faces that were not found manually occurred in the scene of a Court player close-up, with a background of a logo wall, where the shot was taken at player shoulder height.
-
-This shows it was performing extremely well and not resulting in unexplained face Bounding Boxes as some of the other software were.
-This is a strong indicator that applying Google's software for further research would result in the recognition of desired faces.
-
-These results have contributed to the choice of Google given the optimum scene as described above.
-Implementing a filtering process, either using current or alternative footage^[See future research for further information on these options] would allow Google to provide Tennis Australia with the most applicable results.
-
-We moved to considering the characteristics of the faces. This helped to distinguish where Google performed well in comparison to the other software options.
-
-Table 7 showed the combinations of attributes that were found for each face[Given that information was not recorded where Google provided facial recognition for faces not Manually annotated these could not be considered.].
-The use of accessories, Glasses and Visors or Hats, was considered as the Australian Open takes place on both indoor and outdoor courts.
-To apply this research all courts that elite Tennis players compete on had to be included.
-It was assumed that outdoor courts would led to the use of these accessories and these accessories may contribute to the performance of a recognition software.
-It may be implied by the table that Glasses prohibits recognition as all but one of the combinations have 'No' for the Glasses variable.
-However, we are cautious of validating this as Table 8 tells that there are many more faces recognized, by both the Google recognition's and manual annotations, that do not have Glasses.
-This disproportionate sample of faces with Glasses means that we considered it proportionally rather than as a total.
-
-Graph 2 demonstrates that the presence of Glasses on faces annotated manually did affect recognition by Google's algorithm, while it outperformed the other software in both instances, faces were identified more often if the person did not wear glasses.
-
-Moving to looking at the characteristics that were considered manually shows that the use of glasses by players coincided with less faces being annotated.
-
-The box-plot in graph encourages our comparisons to not consider the size of face bounding box as a measure of how the software performs on small faces.
-
-#### Challenges
-It is understandable that there would be many more faces to recognize in these shots than in shots where there is only a player, and therefore many more faces recognized.
-This provides many faces to sort through to find emotions of a player.
-
-We faced the challenge of accessing usable images of players, and specifically their faces.
-- Availability of software
-- Using the software
-- Time constraints
-
-Method, automated the process to reduce data cleaning and help group characteristics
-
-Pricing
-
-## Conclusions 
-Employ the Google Vision API, which would allow the use of still images, or video (TEST VIDEO) files, reducing the need for stills.
-This product - cost in relation
-Ease of access - API calling
-
-## Future Work
-The Long Term goal of this research is to better understand how the emotion's felt by a player during a match affect player performance.
-Ultimately we would aim to create a program that automated the collection of player emotion data from throughout a match.
-This information would be presented in a timeline that allowed match performance, in the form of points won, to be aligned with the emotions felt at certain times throughout.
-
-Considering the images used during our study were stills derived from Broadcast video files, it would be useful to extend further research to deal with the video files directly.
-The Google Vision API used in this research which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.
-
-It should also be considered that these are software focused on providing recognition in certain controlled scenarios.
-If the study was controlled to focus on certain camera angles that align with the facial angles these security programs are intended to recognize faces in.
-
-Given that Google found many faces that did not match manually annotated face, we considered that we should check for manual errors.
-There is the possibility that we could create another app that shows the Facial Bounding Boxes identified by each program, this would allow the annotator to confirm manually whether or not these are faces.
-
-Given that certain Scene attribute combinations produced more facial recognition than other combinations we should consider limiting the sample of images sent to Google Vision API.
-This would not only reduce cost but also provide a greater level of detail of the emotions felt by a player during a match.
-To provide a greater level of information at all points in a match it would be beneficial to derive images from a single camera feed.
-This feed should match the Scene attributes that provided the most Google faces.
-
-To undertake sentiment analysis, we would take the boxes of faces found in this set of images.
-Allowing each face a border of pixels, we would crop the images and produce an individual face image that would form the data set for emotion recognition.
-We also feel that incorporating audio information from the microphones worn by players may assist in sentiment analysis.
-By including this information we would be able to define differences between certain emotions that may not be able to be found by facial features only.
-
-## References

### 2017-02-14 regressionWIP.R

@@ -14,7 +14,7 @@ glmFits <- ALLmetaIMGFaces %>%
   split(.$FaceKey) %>%
   map_df(~ hitmiss(.)) %>%
   split(.$type) %>%
-  map(~ glm(hit ~ ., data = select(., -type, -file, -boxID)))
+  map(~ glm(hit ~ 0 + situation + . + visorhat*glasses, data = select(., -type, -file), binomial(link = "logit")))
 
 glmSummary <- glmFits %>%
   map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname))
@@ -30,7 +30,30 @@ glmPlot %>%
 
 ## Significance of variables by software
 glmPlot %>%
-  mutate(significant = `Pr(>|t|)` < 0.05) %>%
-  ggplot(aes(x=type, y=`Pr(>|t|)`)) +
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
+  ggplot(aes(x=type, y=`Pr(<|z|)`)) +  
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
   geom_col(aes(fill=significant)) + 
   facet_wrap(~ variable)
+
+## Significance of Estimated variable influences by software
+glmPlot %>%
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  ggplot(aes(x=type, y=Estimate)) + 
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
+  geom_col(aes(fill=significant)) + 
+  facet_wrap(~ variable, scales = "free_y")
+
+summary(ALLmetaIMGFaces)
+
+
+#################
+#WIP attempt to include type in model
+glmFits <- ALLmetaIMGFaces %>%
+  split(.$FaceKey) %>%
+  map_df(~ hitmiss(.)) %>% 
+  #split(.$type) %>%
+  map(~ glm(hit ~ 0 + type*., data = select(., -file), binomial(link = "logit")))
+
+

### 2017-02-15 Report06-12.Rmd
Binary AMIFaces

@@
 #multinomail 
+#add hit or miss column, to utilise caret package
 ```

### 2017-02-15 Supplementary Materials.Rmd
Binary AMIFaces

@@
   split(.$type) %>%
-  map(~ glm(hit ~ ., data = select(., -type, -file)))
+  map(~ glm(hit ~ 0+., data = select(., -type, -file)))
 
@@
 ```
+
+```{r Caret, fig.cap = "\\label{Caret}"}
+library(caret)
+library(e1071)
+set.seed(100)
+
+ALLmetaIMGFaces
+inTrain <- createDataPartition(y = ALLmetaIMG$matchesManual, p = .75, 
+                               list = FALSE)
+
+training <- ALLmetaIMG[ inTrain,]
+testing <- ALLmetaIMG[-inTrain,]
+
+ctrl <- trainControl(method = "repeatedcv",
+repeats = 3,
+classProbs = TRUE,
+summaryFunction = twoClassSummary)
+
+plsFit <- train(hit ~ .,
+ data = training,
+ method = "pls",
+ ## Center and scale the predictors for the training
+ ## set and all future samples.
+ preProc = c("center", "scale"), metric="Accuracy")
+
+# plsFit <- train(hit ~ .,
+# data = training,
+# method = "glm", 
+# tuneLength = 15,
+# trControl = ctrl,
+# metric = "ROC",
+# preProc = c("center", "scale"))
+plsFit
+
+```

### 2017-02-15 regressionWIP.R

@@ -55,5 +55,13 @@ glmFits <- ALLmetaIMGFaces %>%
   map_df(~ hitmiss(.)) %>% 
   #split(.$type) %>%
   map(~ glm(hit ~ 0 + type*., data = select(., -file), binomial(link = "logit")))
+ 
 
 
+#### 
+# Create new data structure to model from
+
+ALLmetaIMGFacesWide<-ALLmetaIMGFaces %>%
+  split(.$FaceKey) %>%
+  map_df(~ hitmiss(.)) %>%
+  spread(type, hit)

### 2017-02-15 regressionWIP.R
Model Results function

@@ -1,7 +1,46 @@
 # Prepare data
 library(purrr)
-library(dplyr)
+library(tidyverse)
 library(ggplot2)
+library(gridExtra)
+
+
+ALLmetaIMG<-read_csv("ALLmetaIMG.csv",
+                     col_types = cols(type = col_factor(levels = c("Manual", 
+                      "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+
+
+ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
+ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
+ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
+ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
+ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
+
+ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:3, labels = c("Player", "Other staff on court", "Fan", "None"))
+ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
+ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 0:2, labels = c("Direct sunlight", "Shaded", "Partially shaded"))
+ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
+ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
+ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))
+
[…]

### 2017-02-16 Report06-12.Rmd

@@
 #csv files:
-ALLmetaIMG<-read_csv("ALLmetaIMG1.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+ALLmetaIMG<-read_csv("ALLmetaIMG.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
 SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")

### 2017-02-16 regressionWIP.R
Cleaned map function to multi-line readable version

@@ -119,9 +119,20 @@ GlmModelCreation <- function(model, data = ALLmetaIMGFaces) {
   map(~ glm(model, data = select(., -type, -file, -boxID), binomial(link = "logit")))
 }
 
+ConvertModel2Table <- function(model){
+  model %>%
+    summary %>%
+    coef %>%
+    as.data.frame %>%
+    cbind %>%
+    rownames_to_column %>%
+    cbind %>%
+    dplyr::rename(variable = rowname)
+}
+
 GlmModelEstimates <- function(model, data = GlmModelCreation(model)){
   glmSummary <- data %>% 
-    map(~ dplyr::rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname)) 
+    map(~ ConvertModel2Table(.)) 
   
   glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary))) 
   return(glmPlot)

### 2017-02-16 regressionWIP.R
Added AIC extraction function

@@ -166,5 +166,6 @@ ModelPlotResults<-function(model, data = GlmModelEstimates(model)){
 }
 
 
-ModelPlotResults(hit ~ glasses + visorhat + bg + visorhat*glasses)
-
+ModelPlotResults(hit ~ . -person)
+a <- GlmModelCreation(hit ~ . -person)
+map(a, ~ .$aic)

### 2017-02-24 Report06-12.Rmd
Fixed face box outside of range bug.

@@
       annotation_custom(rasterGrob(img)) +
-      scale_x_continuous(expand = c(0,0), limits = c(0,800)) +
-      scale_y_continuous(expand = c(0,0), limits = c(0,450))
+      coord_cartesian(xlim=c(0, 800), ylim=c(0,450))
 

### 2017-02-24 Report06-12.Rmd
Edits to code

@@
   for(i in imgList){
-
     img <- image_read(paste0("images/", i))
@@
     if(nrow(faceData) == 0){
-      return(p)
+      print(p)
+      next
     } else{
@@
     } 
-  return(p)
+  print(p)
   }
@@
 
-ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:3, labels = c("Player", "Other staff on court", "Fan", "None"))
+ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:2, labels = c("Player", "Other staff on court", "Fan"))
 ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))

### 2017-03-01 Report06-12.Rmd
Data cleaning, updated files

@@
 ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
+ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
+ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
 ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
-ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
 ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
-ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
 
@@
 ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
-ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 0:2, labels = c("Direct sunlight", "Shaded", "Partially shaded"))
+ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 1:2, labels = c("Shaded", "Partially shaded"))
 ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))

### 2017-03-01 mergeData.R

@@ -137,3 +137,4 @@ ALLmetaIMG <- merge(ALLmetaIMG, fileInfo, by="file")
 #Finding duplicates
 ALLmetaIMG <- ALLmetaIMG %>% group_by(file, boxID) %>%
   mutate(duplicates = duplicated(type))
+

### 2017-03-02 regressionWIP.R
glm regression model optimisation

@@ -16,14 +16,12 @@ ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Cou
 
 ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:3, labels = c("Player", "Other staff on court", "Fan", "None"))
 ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
-ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 0:2, labels = c("Direct sunlight", "Shaded", "Partially shaded"))
+ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 1:2, labels = c("Shaded", "Partially shaded"))
 ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
 ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
 ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))
 
-ALLmetaIMG$headangle <- as.character(ALLmetaIMG$headangle)
-ALLmetaIMG$headangle[ALLmetaIMG$headangle == "Back of head"] <- "Other"
-ALLmetaIMG$headangle <- as.factor(ALLmetaIMG$headangle)
+
 
 ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")
 
@@ -110,7 +108,6 @@ ALLmetaIMGFacesWide$Skybiometry<-as.numeric(ALLmetaIMGFacesWide$Skybiometry)
 ALLmetaIMGFacesWide$Microsoft<-as.numeric(ALLmetaIMGFacesWide$Microsoft)
 
 
-
 GlmModelCreation <- function(model, data = ALLmetaIMGFaces) {
   glmFits <- data %>% 
   split(.$FaceKey) %>% 
@@ -166,6 +163,38 @@ ModelPlotResults<-function(model, data = GlmModelEstimates(model)){
 }
 
 
-ModelPlotResults(hit ~ . -person)
-a <- GlmModelCreation(hit ~ . -person)
+#ModelPlotResults(hit ~ . + visorhat*glasses -person)
[…]

### 2017-03-03 Report06-12.Rmd
Regression added to report
Updated to include optimising Regression results and comments in report

@@
 output: bookdown::pdf_document2
+fig_caption: yes
 fontsize: 11pt
@@
 bibliography: references.bib
+link_citations: yes
 ---
@@
 
-Regression analysis showed that the situation attribute of an image was most influential in increasing the likelihood of a hit.
-And head angle was most influential in decreasing.
+Regression analysis showed that the situation variable had significant differences between all levels and the interecept level of "Court in Play".
 
-```{r}
+ The bar charts of the situations show that the situation is important in influencing the detection of a face.
+When the face is accessorised with them, all softwares have a significantly increased chance of finding the face in comparison to the base rate category of the "Court in Play".
+While the image being a Graphic had a large impact it was not significant, this is likely because of the small number of images with this attribute.
+It also shows that the shot angle is only significant for one or two softwares at each level.
+
+```{r Regression, fig.height=9.5, fig.width=7.5, fig.cap = "\\label{Regression} "}
 # Prepare data
 library(purrr)
+library(tidyverse)
+library(gridExtra)
 library(dplyr)
 library(ggplot2)
+
 hitmiss <- function(x){
@@
 
-glmFits <- ALLmetaIMGFaces %>%
+GlmModelCreation <- function(model, data = ALLmetaIMGFaces) {
+  glmFits <- data %>% 
   split(.$FaceKey) %>% 
@@
   split(.$type) %>% 
-  map(~ glm(hit ~ . + visorhat*glasses, data = select(., -type, -file), binomial(link = "logit")))
+  map(~ glm(model, data = dplyr::select(., -type, -file, -boxID), binomial(link = "logit")))
+}
 
-glmSummary <- glmFits %>%
-  map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname))
+ConvertModel2Table <- function(model){
+  model %>%
+    summary %>%
+    coef %>%
+    as.data.frame %>%
+    cbind %>%
+    rownames_to_column %>%
+    cbind %>%
+    dplyr::rename(variable = rowname)
+}
+
+GlmModelEstimates <- function(model, data = GlmModelCreation(model)){
+  glmSummary <- data %>% 
+    map(~ ConvertModel2Table(.))
 
   glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary))) 
+  return(glmPlot)
+}
+
+SignificancePlot <- function(model, data = GlmModelEstimates(model)) {
+  data %>%
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
+  ggplot(aes(x=type, y=`Pr(<|z|)`)) +  
+  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
+  geom_col(aes(fill=significant)) + 
+  facet_wrap(~ variable)
+}
+
+EstimatesPlot <- function(model, data = GlmModelEstimates(model)) {
+  data %>%
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  ggplot(aes(x=type, y=Estimate)) +  
+  theme(axis.text.x = element_text(angle = 30, hjust = 1), 
+        axis.text.y = element_text(angle = 30, hjust = 1)) +
+  geom_col(aes(fill=significant)) + 
+  facet_wrap(~ variable, scales = "free_y")
+}
+
+ModelPlotResults<-function(model, data = GlmModelEstimates(model)){
+  ep<-EstimatesPlot(model, data)
+  sp<- SignificancePlot(model, data)
+  grid.arrange(ep, sp)
+}
+
+ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat)
 
@@
 
-```{r, Regression-Significance-Plot, fig.cap = "\\label{Regression--Significance-Plot}"}
-## Significance of variables by software
-glmPlot %>%
-  mutate(significant = `Pr(>|z|)` < 0.05) %>%
-  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
-  ggplot(aes(x=type, y=`Pr(<|z|)`)) + 
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
-  geom_col(aes(fill=significant)) + 
-  facet_wrap(~ variable)
-```
-
-The bar chart of the interaction of Glasses and Visors in \@ref(Regression--Significance-Plot) or Hats shows that when the face is accessorised with both, Google has a significantly increased chance of finding the face
-
-```{r, Regression-Estimates-Plot, fig.cap = "\\label{Regression--Estimates-Plot}"}
-## Significance of Estimated variable influences by software
-glmPlot %>%
-  mutate(significant = `Pr(>|z|)` < 0.05) %>%
-  ggplot(aes(x=type, y=Estimate)) + 
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
-  geom_col(aes(fill=significant)) + 
-  facet_wrap(~ variable, scales = "free_y")
-
-#parallel coordinate plot, vars on x????
-#unpack intercept
-#don't force to zero
-#convert into full model decription - every single level combination
-#have every level and cross level - order combinations by p value
-#function for estimates for each treatment
-#multinomail 
-#add hit or miss column, to utilise caret package
-```
-
-```{r Regression-Situation-Table, fig.cap = "\\label{Regression-Situation-Table}"}
-
-RegSituation<-glmPlot %>% subset(grepl("situation*", variable)) %>% select(variable, Estimate, type)
-
-#RegSituation
-
-data_wide <- spread(RegSituation, variable, Estimate)
-
-names(data_wide)[names(data_wide)=="situationCourt player close-up"] <- "Court player close-up"
-names(data_wide)[names(data_wide)=="situationCrowd"] <- "Crowd"
-names(data_wide)[names(data_wide)=="situationOff court close up of player"] <- "Off court close up of player"
-names(data_wide)[names(data_wide)=="situationCourt close-up not player"] <- "Court close-up not player"
-
-kable(data_wide, format = "markdown", booktabs = TRUE, caption = "")
-```
-
-```{r Regression-Angle-Table, fig.cap = "\\label{Regression-Angle-Table}"}
-
-RegHeadAngle<-glmPlot %>% subset(grepl("headangle*", variable)) %>% select(variable, Estimate, type)
-
-#RegSituation
-
-data_wideHead <- spread(RegHeadAngle, variable, Estimate)
-
-names(data_wideHead)[names(data_wideHead)=="headangleOther"] <- "Other"
-names(data_wideHead)[names(data_wideHead)=="headangleProfile"] <- "Profile"
-
-kable(data_wideHead, format = "markdown", booktabs = TRUE, caption = "")
-```
+A stepwise method was used to determin the best regression model for predicting a hit or miss.
+The regression model that provided the best AIC, included the scene attributes: Shot Angle, Back Ground, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
+It also included the lighting on the particular face, and whether the specific face was accessorised with Glasses and a Visor or Hat.
 

### 2017-03-03 mergeData.R

@@ -13,10 +13,10 @@ ManualClassifiedFaces <- read.csv("ManualClassifiedFaces.csv")
 ManualClassifiedScenes <- read.csv("ManualClassifiedScenes.csv")
 
 #Check all equal length
-length(unique(ManualClassifiedScenes$file))
-length(unique(AnimetricsClassifiedFaces$file))
-length(unique(SkybiometryClassifiedFaces$file))
-length(unique(GoogleClassifiedFaces$file))
+#length(unique(ManualClassifiedScenes$file))
+#length(unique(AnimetricsClassifiedFaces$file))
+#length(unique(SkybiometryClassifiedFaces$file))
+#length(unique(GoogleClassifiedFaces$file))
 
 #Remove images with no faces
 MicrosoftClassifiedFaces <- MicrosoftClassifiedFaces[!is.na(MicrosoftClassifiedFaces$faceRectangle.top),]
@@ -33,17 +33,17 @@ MicrosoftMerge <- MicrosoftClassifiedFaces %>%
   mutate(type = "Microsoft", ID=NA,
          minX = faceRectangle.left, maxX = faceRectangle.left + faceRectangle.width,
          minY = faceRectangle.top, maxY = faceRectangle.top + faceRectangle.height) %>%
-  dplyr::select(file, type, ID, time.user.self, time.sys.self, time.elapsed, minX, maxX, minY, maxY)# %>% filter(file=="2016_RLA_R01_JDuckworth_AUS_vs_LHewitt_AUS_MS150_clip.0056.png")  
+  dplyr::select(file, type, ID, time.user.self, time.sys.self, time.elapsed, minX, maxX, minY, maxY)  
 AnimetricsMerge <- AnimetricsClassifiedFaces %>%
   mutate(type = "Animetrics",  ID=NA,
          minX = topLeftX, maxX = topLeftX + width,
          minY = topLeftY, maxY = topLeftY + height) %>%
-  dplyr::select(file, type, ID, time.user.self, time.sys.self, time.elapsed, minX, maxX, minY, maxY) #%>% filter(file=="2016_RLA_R01_JDuckworth_AUS_vs_LHewitt_AUS_MS150_clip.0056.png")  
+  dplyr::select(file, type, ID, time.user.self, time.sys.self, time.elapsed, minX, maxX, minY, maxY)  
[…]

### 2017-03-03 regressionWIP.R

@@ -1,7 +1,7 @@
 # Prepare data
 library(tidyverse)
 library(gridExtra)
-
+library(dplyr)
 
 ALLmetaIMG<-read_csv("ALLmetaIMG.csv",
                      col_types = cols(type = col_factor(levels = c("Manual", 
@@ -23,7 +23,7 @@ ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", 
 
 
 
-ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")
+#ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")
 
 # change this to facesVenn with binary information
 ALLmetaIMGFaces<-ALLmetaIMG%>%
@@ -97,10 +97,10 @@ hitmiss <- function(x){
 #### 
 # Create new data structure to model from
 
-ALLmetaIMGFacesWide<-ALLmetaIMGFaces %>%
-  split(.$FaceKey) %>%
-  map_df(~ hitmiss(.)) %>%
-  spread(type, hit)
+#ALLmetaIMGFacesWide<-ALLmetaIMGFaces %>%
+#  split(.$FaceKey) %>%
+#  map_df(~ hitmiss(.)) %>%
+#  spread(type, hit)
 
 ALLmetaIMGFacesWide$Animetrics<-as.numeric(ALLmetaIMGFacesWide$Animetrics)
 ALLmetaIMGFacesWide$Google<-as.numeric(ALLmetaIMGFacesWide$Google)
@@ -113,7 +113,7 @@ GlmModelCreation <- function(model, data = ALLmetaIMGFaces) {
   split(.$FaceKey) %>% 
   map_df(~ hitmiss(.)) %>% 
   split(.$type) %>% 
-  map(~ glm(model, data = select(., -type, -file, -boxID), binomial(link = "logit")))
+  map(~ glm(model, data = dplyr::select(., -type, -file, -boxID), binomial(link = "logit")))
 }
 
 ConvertModel2Table <- function(model){
@@ -155,7 +155,6 @@ EstimatesPlot <- function(model, data = GlmModelEstimates(model)) {
 }
 
 
-
 ModelPlotResults<-function(model, data = GlmModelEstimates(model)){
   ep<-EstimatesPlot(model, data)
   sp<- SignificancePlot(model, data)
[…]

### 2017-03-07 Report06-12.Rmd
report updates
kable table settings

@@
 bibliography: references.bib
-link_citations: yes
+biblio-style: apalike
+link-citations: true
 ---
@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-kable(SceneAttributes, format = "markdown", booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
+knitr::kable(SceneAttributes, format = "markdown", longtable=TRUE, booktabs = TRUE, caption = "Attributes of a Scene of an image.
+The most appropriate option from the list was selected for each attribute.")
 ```
@@
 ```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis',}
-kable(SolutionSpecs, format = "markdown", booktabs = TRUE, caption="")
+knitr::kable(SolutionSpecs, format = "markdown", longtable=TRUE, booktabs = TRUE, caption="")
 ```
@@
 The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
-kable(FaceAttributes, format = "markdown", booktabs = TRUE)
+knitr::kable(FaceAttributes, format = "markdown", longtable=TRUE, booktabs = TRUE)
 ```
@@
 ImageCharacteristics<-ImageCharacteristics[1:10,]
-kable(ImageCharacteristics, booktabs = TRUE, caption="", format = "markdown")
+knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="", format = "markdown")
 ```
@@
 GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
-kable(GoogleNoMatch[1:10,], caption="", format = "markdown")
+knitr::kable(GoogleNoMatch[1:10,], caption="", longtable=TRUE, format = "markdown")
 
@@
 FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
-kable(FaceCharacteristics, caption="", format = "markdown")
+knitr::kable(FaceCharacteristics, caption="", longtable=TRUE, format = "markdown")
 ```
@@
 Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
-kable(Accuracy, caption="", format = "markdown")
+knitr::kable(Accuracy, caption="", longtable=TRUE, format = "markdown")
 # make this a proportional table, would this be necessary if we have the UpSetR
@@
 
-kable(GoogleCharacteristics, format = "markdown", booktabs = TRUE, caption="")
+knitr::kable(GoogleCharacteristics, format = "markdown", longtable=TRUE, booktabs = TRUE, caption="")
 ```

### 2017-03-07 CreateFacesSet.R
Create New Data set

@@ -1,0 +1,16 @@
+
+library(magick)
+
+GoogleFaces<-ALLmetaIMGFaces %>% subset(type=="Google")
+
+#create data set of just faces
+data<-GoogleFaces
+#CreateFaceSet
+for(n in 1:NROW(GoogleFaces)){
+SubImage <- image_read(paste0("images/", data$file[n]))
+
+cropValue<-paste0(data$maxX[n]-data$minX[n]+20, "x",data$maxY[n]-data$minY[n]+20,"+", data$minX[n]-10,"+", data$minY[n]-10, collapse = ", ")
+Cropped<-image_crop(SubImage, cropValue)
+
+image_write(Cropped, path=(paste0("images/Faces/","face-", data$FaceID[n], ".png", collapse = ", ")))
+}

### 2017-03-07 mergeData.R

@@ -138,3 +138,5 @@ ALLmetaIMG <- merge(ALLmetaIMG, fileInfo, by="file")
 ALLmetaIMG <- ALLmetaIMG %>% group_by(file, boxID) %>%
   mutate(duplicates = duplicated(type))
 
+
+#write.csv(ALLmetaIMG,file = "ALLmetaIMG.csv")

### 2017-03-10 regressionWIP.R
Faces Set created

@@ -45,17 +45,16 @@ hitmiss <- function(x){
     cbind(type = allType, hit = hit)
 }
 
-#glmFits <- ALLmetaIMGFaces %>% 
-#  split(.$FaceKey) %>% 
-#  map_df(~ hitmiss(.)) %>% 
-#  split(.$type) %>% 
-#  map(~ glm(hit ~ . + visorhat*glasses, data = select(., -type, -file, -boxID), binomial(link = "logit"))) 
-#
-#glmSummary <- glmFits %>% 
-#  map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname)) 
-#
-#glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary))) 
+glmFits <- ALLmetaIMGFaces %>% 
+  split(.$FaceKey) %>% 
+  map_df(~ hitmiss(.)) %>% 
+  split(.$type) %>% 
+  map(~ glm(hit ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat, data = select(., -type, -file, -boxID), binomial(link = "logit"))) 
 
+glmSummary <- glmFits %>% 
+  map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname)) 
+
+glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary))) 
 
 # Graphs
 ## Coefficient of variables by software
@@ -174,3 +173,6 @@ a <- GlmModelCreation(hit ~ shotangle + bg + bg*shotangle + graphic + situation 
 a$Google$aic
 
 ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat)
+
+
+

### 2017-03-29 Report06-12.Rmd
Changed Table Formats

@@
 #csv files:
-ALLmetaIMG<-read_csv("ALLmetaIMG.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+ALLmetaIMGnamed<-read_csv("ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
 SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
@@
 
-    faceData <- ALLmetaIMGFaces %>% filter(file == i)
+    faceData <- ALLmetaIMGnamedFaces %>% filter(file == i)
 
@@
 
-#Factor Names 
-ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
-ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
-ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
-ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
-ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
-
-ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:2, labels = c("Player", "Other staff on court", "Fan"))
-ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
-ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 1:2, labels = c("Shaded", "Partially shaded"))
-ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
-ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
-ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))
-
-ALLmetaIMG$headangle <- as.character(ALLmetaIMG$headangle)
-ALLmetaIMG$headangle[ALLmetaIMG$headangle == "Back of head"] <- "Other"
-ALLmetaIMG$headangle <- as.factor(ALLmetaIMG$headangle)
-
-ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")
+ALLmetaIMGPlayers<- ALLmetaIMGnamed %>% filter(detect=="Player")
 
 # change this to facesVenn with binary information
-ALLmetaIMGFaces<-ALLmetaIMG%>%
-  filter(matchesManual) %>% 
+ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
+  #filter(matchesManual) %>% 
   dplyr::select(-ID, -facecounter)%>%
@@
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
-overlayGgplot(imagesList0, ALLmetaIMGFaces, matchBox = FALSE)
+overlayGgplot(imagesList0, ALLmetaIMGnamedFaces, matchBox = FALSE)
 ```
@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-knitr::kable(SceneAttributes, format = "markdown", longtable=TRUE, booktabs = TRUE, caption = "Attributes of a Scene of an image.
+knitr::kable(SceneAttributes, format = "latex", longtable=TRUE, booktabs = TRUE, caption = "Attributes of a Scene of an image.
 The most appropriate option from the list was selected for each attribute.")
@@
 
-```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis',}
-knitr::kable(SolutionSpecs, format = "markdown", longtable=TRUE, booktabs = TRUE, caption="")
+```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis'}
+knitr::kable(SolutionSpecs, format = "latex", longtable=TRUE, booktabs = TRUE, caption="")
 ```
@@
 The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
-knitr::kable(FaceAttributes, format = "markdown", longtable=TRUE, booktabs = TRUE)
+knitr::kable(FaceAttributes, format = "latex", longtable=TRUE, booktabs = TRUE)
 ```
@@
 
-Using the data set^[ALLmetaIMG] of the combined API and manual results, we were able to compare the performance of the software.
+Using the data set^[ALLmetaIMGnamed] of the combined API and manual results, we were able to compare the performance of the software.
 Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(Face-Bounding-Box-Data).
@@
 
-GlmModelCreation <- function(model, data = ALLmetaIMGFaces) {
+GlmModelCreation <- function(model, data = ALLmetaIMGnamedFaces) {
   glmFits <- data %>% 
@@
 ```{r Face-Bounding-Box-Data, results='hide', fig.cap = "\\label{Face-Bounding-Box-Data} Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft."}
-ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE) + labs(caption="")
+ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE) + labs(caption="")
 ```
@@
 The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API."}
-createUpSet(ALLmetaIMGFaces)
+createUpSet(ALLmetaIMGnamedFaces)
 ```
@@
 imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
-overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
+overlayGgplot(imagesList3, ALLmetaIMGnamedFaces, matchBox = FALSE)
 ```
@@
 ```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}
-NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
+NoManual<-ALLmetaIMGnamed %>% filter(ALLmetaIMGnamed$type!="Manual")
 NoManual<-NoManual %>% droplevels(NoManual$type) 
@@
 ```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
-ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
+ImageCharacteristics <- ALLmetaIMGnamed %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
 ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
 ImageCharacteristics<-ImageCharacteristics[1:10,]
-knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="", format = "markdown")
+knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="", format = "latex")
 ```
@@
 imagesList1<-as.list("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png")
-overlayGgplot(imagesList1, ALLmetaIMG, matchBox = FALSE)
+overlayGgplot(imagesList1, ALLmetaIMGnamed, matchBox = FALSE)
 ```
@@
 
-GoogleNoMatch <- ALLmetaIMG %>%
+GoogleNoMatch <- ALLmetaIMGnamed %>%
   filter(type=="Google") %>%
@@
 GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
-knitr::kable(GoogleNoMatch[1:10,], caption="", longtable=TRUE, format = "markdown")
+knitr::kable(GoogleNoMatch[1:10,], caption="", longtable=TRUE, format = "latex")
 
@@
 FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
-knitr::kable(FaceCharacteristics, caption="", longtable=TRUE, format = "markdown")
+knitr::kable(FaceCharacteristics, caption="", longtable=TRUE, format = "latex")
 ```
@@
 The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally."}
-GlassesGoogle <- ALLmetaIMGFaces %>% filter(type=="Google") %>%
+GlassesGoogle <- ALLmetaIMGnamedFaces %>% filter(type=="Google") %>%
 filter(matchesManual==TRUE)
@@
 ```{r Accuracy}
-Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
-knitr::kable(Accuracy, caption="", longtable=TRUE, format = "markdown")
+Accuracy<-with(ALLmetaIMGnamed, table(ALLmetaIMGnamed$matchesManual, ALLmetaIMGnamed$type))
+knitr::kable(Accuracy, caption="", longtable=TRUE, format = "latex")
 # make this a proportional table, would this be necessary if we have the UpSetR
@@
 ```{r Google-Characteristics-Table, fig.cap = "\\label{tab:Google-Characteristics-Table}"}
-GoogleCharacteristics <- ALLmetaIMG %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
+GoogleCharacteristics <- ALLmetaIMGnamed %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
 GoogleCharacteristics<-arrange(GoogleCharacteristics, desc(count))
 
-knitr::kable(GoogleCharacteristics, format = "markdown", longtable=TRUE, booktabs = TRUE, caption="")
+knitr::kable(GoogleCharacteristics, format = "latex", longtable=TRUE, booktabs = TRUE, caption="")
 ```

### 2017-03-29 BEX3012 ProjectReport.Rmd
Emotions Project Report

---
title: "BEX3012 Project Report \n Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian"
date: "28 March 2017"
output: bookdown::pdf_document2
fig_caption: yes
fontsize: 11pt
link-citations: true
---

```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F)

library(tidyverse)
library(readr)

#EmoM <-read_csv("data/EmotionsMerged.csv")
ME <- read_csv("data/MicrosoftEmotions.csv")
SB<-read_csv("data/SkybiometryEmotions.csv")
GE<- read_csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
EmotionSoftwareSpecs<-read_csv("TableCSVs/EmotionSoftwareSpecifications.csv")
ALLmetaIMGnamed <- read_csv("data/ALLmetaIMGnamed.csv")

#Create normalised SB values
sumf <- function(vec) sum(vec)

SB<-SB %>%
  rowwise %>%
  mutate(z = sumf(c(anger.confidence, disgust.confidence, fear.confidence, happiness.confidence, neutral_mood.confidence, sadness.confidence, surprise.confidence,  na.rm=T)))

SB<-SB %>%
  mutate(anger = anger.confidence/z,
         disgust = disgust.confidence/z,
         fear = fear.confidence/z,
         happiness = happiness.confidence/z,
         neutral = neutral_mood.confidence/z,
         sadness = sadness.confidence/z,
         surprise = surprise.confidence/z)

```

# Introduction

Facial Recognition is beginning to be explored in sports environments, this presents quality issues.

helpful for applications

# Method
## Materials
### Image Set
A subset of faces was created specifically for emotion recognition purposes. This set contains faces that were manually annotated as players.
It contains the area within the face bounding boxes found in the previous study, as well as a small border to fram the face. This resulted in images of differing sizes to be passed to the APIs.
These images were hosted on Google Drive to allow for URL access from the API to the individual images.

### Software APIs

We will consider three Emotion Recognition softwares.

```{r Emotion-Software-Specs-Table, echo=F, fig.cap = "\\label{tab:Emotion-Software-Specs-Table}"}

knitr::kable(EmotionSoftwareSpecs, longtable=TRUE, booktabs = TRUE, caption="This details the capabilities we considered important in recognising emotions in images of faces.")
```

As can be seen above, a noticable difference between the three is the amount of times the API can be called. Skybiometry had the largest imposition on Bath Processing as it only allowed 100 API calls to be processed per hour. Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within an hour, after accounting for the wait time betwwen each group of 20.
Google Vision's API batch processing limit had a minimal effect.

The range of outputs from the softwares is displayed as Google provides likelihoods of an emotion occuring on a particular face. Microsoft and Skybiometry provide outputs on the same emotions^[Based on Paul Ekmans emotion theories]. However the values that they provide differ as Microsoft provide Porportions whereas Skybiometry results in a Confidence of the emotion occuring in the specified face.

```{r Outputs, echo=F, fig.cap = "\\label{tab:Emotion-Software-Specs-Table}"}

GE[706,c(1,10:13)]

SB[6,1:19]

ME[6,1:9]

```

### 2017-03-29 SoftwareRequestScripts/autoSkybiometry.R
Emotion Scripts

@@ -1,6 +1,7 @@
 ### API loop function
 library(jsonlite)
-setwd("~/Desktop/face-recognition/")
+setwd("")
+
 reqsize <- 97
 
 # Starting script for SkyBiometry API
@@ -48,8 +49,8 @@ if (length(imagelist) == 0){
 #   image_urls <- paste0("http://on-the-t.com/assets/match_images/", image_urls)
 #   requests <- the_request(image_urls)
 #   SkyRequest <- lapply(requests, readLines)
-#   parse_json <- lapply(SkyRequest, fromJSON)
-#   parsedFaces <- lapply(parse_json, getFacesSkyBiometry)
+#   con <- lapply(SkyRequest, fromJSON)
+#   parsedFaces <- lapply(con, getFacesSkyBiometry)
 #   final_df <- do.call(rbind,parsedFaces)
 #   #Save backup file
 #   write.csv(final_df, file=paste0("SkybiometryBackup/SkybiometryClassifiedFaces_", Sys.Date(), "_", i, ".csv"), row.names = FALSE)
@@ -59,12 +60,11 @@ if (length(imagelist) == 0){
 #   write.csv(currentFaces, file="SkybiometryClassifiedFaces.csv", row.names = FALSE)
 #   
 #   message(paste0("Successfully completed batch ", i+1, " of ", ceiling(length(imagelist)/reqsize)))
-#   message(paste0("Time of next batch: ", as.POSIXct(parse_json[[1]]$usage$reset_time, origin="1970-01-01")))
-#   while(Sys.time() < as.POSIXct(parse_json[[1]]$usage$reset_time, origin="1970-01-01")){
+#   message(paste0("Time of next batch: ", as.POSIXct(con[[1]]$usage$reset_time, origin="1970-01-01")))
+#   while(Sys.time() < as.POSIXct(con[[1]]$usage$reset_time, origin="1970-01-01")){
 #     Sys.sleep(30)
 #   }
 # }
-
 
 for (img in imagelist){
   image_url <- paste0("http://on-the-t.com/assets/match_images/", img)
@@ -73,7 +73,6 @@ for (img in imagelist){
   while(class(SkyRequest) == "try-error"){
     message(paste0("ERROR: API call failed - ", img))
     message("Trying again in 10 minutes...")
-    Sys.sleep(600)
     time <- system.time(SkyRequest <- try(readLines(request)))
   }
   parse_json <- fromJSON(SkyRequest)
[…]

### 2017-03-29 SoftwareRequestScripts/microsoftAPI.R

@@ -1,23 +1,49 @@
 library(httr)
-a <- POST(url="https://api.projectoxford.ai/face/v1.0/detect?returnFaceId=false&returnFaceLandmarks=true",
-     add_headers(`Ocp-Apim-Subscription-Key` = "",
-                 `Content-Type` = "application/json"),
-     body = list(`url` = "http://mitchelloharawild.com/tennis/2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0003.png"))
 
 
-library(httr)
-
-faceURL = "https://api.projectoxford.ai/face/v1.0/detect?returnFaceId=true&returnFaceLandmarks=true&returnFaceAttributes=age,gender,smile,facialHair"
-img.url = "http://mitchelloharawild.com/tennis/2016_CT8_R02_TSmyczek_USA_vs_VTroicki_SRB_MS222_clip.0049.png"
-
+faceURL = "https://westus.api.cognitive.microsoft.com/face/v1.0/detect?returnFaceId=false&returnFaceLandmarks=true&returnFaceAttributes=age,gender,smile,facialHair"
+img.url = "https://www.whitehouse.gov/sites/whitehouse.gov/files/images/first-family/44_barack_obama[1].jpg"
 mybody = list(url = img.url)
+#faceKey = ""
 
+
+aFace <- POST(url=faceURL, 
+          content_type('application/json'),
+          add_headers(.headers = c('Ocp-Apim-Subscription-Key' = faceKey)),
+          body = mybody,
+          encode = 'json')
+
+faceResult=httr::content(aFace, as="text")
+faceResult
 
 
 MicrosoftAPI <- function(img.url){
-  POST(url = "https://api.projectoxford.ai/face/v1.0/detect?returnFaceId=false&returnFaceLandmarks=true", 
-    content_type('application/json'), add_headers(.headers = c('Ocp-Apim-Subscription-Key' = "")),
-    body = list(url = img.url),
+  POST(url = faceURL, 
+    content_type('application/json'), 
+    add_headers(.headers = c('Ocp-Apim-Subscription-Key' = faceKey)),
+    body = mybody,
     encode = 'json'
   )
 }
+
+#faceTags<-faceResult
+
+getMicrosoft <- function(faceTags){
+  if(length(faceTags[[1]]) > 1){
+    tagdata <- flatten(faceTags[[1]])[,-1]
+  }
+  else{
+    tagdata <- data.frame(label = NA, confirmed = NA, manual = NA, width = NA, height = NA,
[…]

### 2017-03-29 EmotionsAnalysis.R
Emotions Analysis

@@ -1,0 +1,146 @@
+##Emotions Analysis
+
+library(tidyverse)
+library(readr)
+EmoM <-read_csv("data/EmotionsMerged.csv")
+ME <- read_csv("data/MicrosoftEmotions.csv")
+SB<-read_csv("data/SkybiometryEmotions.csv")
+GE<- read_csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
+ALLmetaIMGnamed <- read.csv("ALLmetaIMGnamed.csv")
+
+ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
+  filter(matchesManual)%>%
+  dplyr::select(-ID, -facecounter)%>%
+  mutate(fileID = as.numeric(factor(file))) %>%
+  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
+  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-")) %>%
+  mutate(FileName=paste("face-", FaceID, ".png", sep=""))
+
+
+EmotionsMerged<-left_join(by="FileName", MicrosoftEmotions, ALLmetaIMGnamedFaces)
+#EmotionsMerged<-write.csv(EmotionsMerged, "EmotionsMerged.csv", row.names = FALSE)
+
+
+EmotionsMerged<-EmotionsMerged %>% mutate(s = sum(anger, contempt, disgust, fear, happiness, neutral, sadness, surprise, na.rm=TRUE))
+
+# Connect face id to original Google set
+
+GE <- GE %>% 
+  rowwise() %>%
+  mutate(minX = min(boundingPoly.x1, boundingPoly.x4), maxX = min(boundingPoly.x2, boundingPoly.x3),
+         minY = min(boundingPoly.y1, boundingPoly.y2), maxY = min(boundingPoly.y3, boundingPoly.y4)) %>%
+  ungroup() %>%
+  mutate(minX = ifelse(is.na(minX), 0, minX), minY = ifelse(is.na(minY), 0, minY))
+
+# create full Google DataSet
+GF1<-GoogleFaces[,c(1, 36, 18:21)]
+GE1<-GE[,c(1, 10:13,135:138)]
+GE <- left_join(GF1, GE1, by = c("file","minX","maxX","minY","maxY")) 
+
+
+
+
+#consider just players?
+#EmotionsMerged<-EmotionsMerged %>% filter(detect=="Player")
+
+
[…]

### 2017-03-29 MicrosoftEmotions.R

@@ -1,0 +1,92 @@
+library(httr)
+
+
+emotURL = "https://westus.api.cognitive.microsoft.com/emotion/v1.0/recognize"
+mybody = list(url = img.url)
+emotKey = ""
+
+
+#bEmot <- POST(url=emotURL, 
+#          content_type('application/json'),
+#          add_headers(.headers = c('Ocp-Apim-Subscription-Key' = emotKey)),
+#          body = list(url = img.url),
+#          encode = 'json')
+#
+#emotResult=httr::content(aEmot)[[1]]
+#emotResultdf <-as.data.frame((emotResult$scores))
+
+#keep for testing works img.url =  "https://drive.google.com/uc?export=download&id=0B0i5WV2jMQ1vSG1Va25wRmVkQkE"
+# works img.url =  "https://drive.google.com/uc?export=download&id=0B0i5WV2jMQ1vSVlvWjlZUktpMUU"
+
+
+#send the request to microsoft
+MicrosoftAPI <- function(id){
+  POST(url=emotURL,
+      content_type('application/json'),
+      add_headers(.headers = c('Ocp-Apim-Subscription-Key' = emotKey)),
+      body = list(url = paste0("https://drive.google.com/uc?export=download&id=", id)),
+      encode = 'json'
+  )
+}
+
+library(httr)
+library(dplyr)
+#expand into a dataframe
+getEmotionsMicrosoft <- function(a){
+  
+  if (length(content(a, "raw"))>2) {
+    emotResult = httr::content(a)[[1]]
+    tagdata <- as.data.frame((emotResult$scores))
+
+  }
+  else{
+    tagdata <- data.frame(
+      anger = NA,
+      contempt = NA,
+      disgust = NA,
+      fear = NA,
+      happiness = NA,
+      neutral = NA,
+      sadness = NA,
+      surprise = NA
+    )
+
+  }
+  
+}
+
+#combine with previous results
+EmotionsResult <- function(imagelist) {
+  for (img in 1:length(imagelist)) {
+    id <- substr(as.character(imgURLS$URL[img]), 33, 60)
+    a <- MicrosoftAPI(id)
+    result <- getEmotionsMicrosoft(a)
+    named<-cbind(imgURLS$Filename[img], result)
+    names(named)[1]<-"FileName"
+    print(img)
+    print(named)
+    currentFaces <- read.csv("MicrosoftEmotions.csv")
[…]

### 2017-04-21 Internship/BEX3012ProjectReport.Rmd
Rearrange Repo
Arrange Emotion Internship Sub section

---
title: "BEX3012 Project Report \n Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian"
date: "28 March 2017"
output: bookdown::pdf_document2
fig_caption: yes
fontsize: 11pt
link-citations: true
---

```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE)

library(tidyverse)
library(readr)
library(GGally)

#Read in data files
ME <- read_csv("data/MicrosoftEmotions.csv")
SB <- read_csv("data/SkybiometryEmotions.csv")
GE <- read_csv("data/GoogleFacesEmotions.csv")

EmotionSoftwareSpecs<-read_csv("Figures/EmotionSoftwareSpecifications.csv")

#Create normalised SB values
SB <- SB %>%
  rowwise %>% mutate(z = (anger.confidence+
               disgust.confidence+
               fear.confidence+
               happiness.confidence+
               neutral_mood.confidence+
               sadness.confidence+
               surprise.confidence)) %>%
  mutate(anger = anger.confidence/z,
         disgust = disgust.confidence/z,
         fear = fear.confidence/z,
         happiness = happiness.confidence/z,
         neutral = neutral_mood.confidence/z,
         sadness = sadness.confidence/z,
         surprise = surprise.confidence/z)

```

```{r}

#Create normalised GE values
Conf <- function(Emot){
ifelse(Emot=="VERY_UNLIKELY", 10,  
        ifelse(Emot == "UNLIKELY", 30, 
                ifelse(Emot == "POSSIBLE", 50, 
                ifelse(Emot == "LIKELY", 70, 
                ifelse(Emot == "VERY_LIKELY", 90, NA)))))
}

GE <- GE %>% mutate(joyConf = Conf(joyLikelihood)) %>%
  mutate(sorrowConf = Conf(sorrowLikelihood)) %>%
  mutate(angerConf = Conf(angerLikelihood)) %>%
  mutate(surpriseConf = Conf(surpriseLikelihood))

GE <- GE %>%
  rowwise %>% 
  mutate(neutralConf = 100 - (pmax(joyConf, sorrowConf, angerConf, surpriseConf))) %>%
  mutate(z = (joyConf+
                sorrowConf+
                angerConf+
                surpriseConf+
                neutralConf)) %>%
  mutate(anger = angerConf/z,
         joy = joyConf/z,
         neutral = neutralConf/z,
         sorrow = sorrowConf/z,
         surprise = surpriseConf/z)

```

\newpage

# Introduction

Facial Recognition is beginning to be explored in sports environments, this presents quality issues.

helpful for applications

\newpage

# Method

## Materials

### Pre Processing Images

A subset of faces was created specifically for emotion recognition purposes. To present only a single face to each software required cropping the region of the image based on Google’s bounding box result^[coordinates derived from prior study].
Each new image created contained the area within the face bounding boxes found in the previous study, as well as a small border to frame the face. This resulted in images of differing sizes to be passed to the APIs. These 1319 new images were hosted on Google Drive to allow for URL access from the API to the individual images.

```{r VisualSet, echo=F, fig.cap = "Here are six examples of Faces in the image set after extracting faces from the full broadcast video stills. \\label{tab:VisualSet}"}

library(magick)
library(grid)
library(gridExtra)
library(ggplot2)

plotFaces <- function(imgList){
  for(i in imgList){

  img <- image_read(paste0("Faces/", i))

    p <- ggplot(data.frame(x=c(0,350), y=c(0,350)), aes(x,y))+
      theme_classic() + xlab("") + ylab("") + 
      annotation_custom(rasterGrob(img)) +
      coord_cartesian(xlim=c(0, 350), ylim=c(0,400))

    } 
  return(p)
  }

f1 <- plotFaces("face-1635-1-Go.png")
f2 <- plotFaces("face-1128-1-Go.png")
f3 <- plotFaces("face-1746-1-Go.png")
f4 <- plotFaces("face-626-1-Go.png")
f5 <- plotFaces("face-450-1-Go.png")
f6 <- plotFaces("face-816-1-Go.png")

grid.arrange(f1, f2, f3, f4, f5, f6,nrow=2)

```

\newpage

### Software APIs

We will consider three Emotion Recognition software.

```{r Emotion-Software-Specs-Table, echo=F, fig.cap = "\\label{tab:Emotion-Software-Specs-Table}"}

knitr::kable(EmotionSoftwareSpecs, longtable=TRUE, booktabs = TRUE, caption="This details the capabilities we considered important in recognising emotions in images of faces.")
```

As can be seen above, a noticeable difference between the three is the amount of times the API can be called. Skybiometry had the largest imposition on Bath Processing as it only allowed 100 API calls to be processed per hour. Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within an hour, after accounting for the wait time between each group of 20.
Google Vision's API batch processing limit had a minimal effect.

The range of outputs from the software is displayed as Google provides likelihoods of an emotion occurring on a particular face. Microsoft and Skybiometry provide outputs on the same emotions^[Based on Paul Ekmans emotion theories]. However the values that they provide differ as Microsoft provide Proportions whereas Skybiometry results in a Confidence of the emotion occurring in the specified face.

### Processing API results

As the results provided by each of the software differed, processing was needed to create comparable sets.

#### Microsoft

```{r MEexample, echo=F, message=F, fig.cap = "\\label{tab:MEexample}"}
library(dplyr)
MEexample <- ME %>% subset(FileName=="face-1745-1-Go.png")

knitr::kable(MEexample[2:9], digits=6, longtable=TRUE, booktabs = TRUE, caption="The Microsoft API provided 8 numerical values, one for each emotion.")
```

#### Skybiometry

```{r SBexample, echo=F, fig.cap = "\\label{tab:SBexample}"}
SBexample <- SB %>% subset(aname=="face-1745-1-Go.png") %>% select(ends_with(".confidence"))

knitr::kable(SBexample[3:9], digits=6, longtable=TRUE, booktabs = TRUE,
             col.names = c("neutral", "anger", "disgust", "fear",
                           "happiness", "sadness", "surprise"),
             caption="The Skybiometry API provided 7 numerical Confidence values, one for each emotion.")
```

#### Google

```{r GEexample, echo=F, fig.cap = "\\label{tab:GEexample}"}
GEexample <- GE %>% subset(FileName=="face-1745-1-Go.png") %>% select(ends_with("Likelihood"))

knitr::kable(GEexample, longtable=TRUE, booktabs = TRUE,
             col.names = c("joy", "sorrow", "anger", "surprise"),
             caption="The Google Vision API provided four likelihood possibilities, one for each emotion.")
```

These differing outputs needed to be arranged in a comparable manner.
We began by considering the Microsoft output. Noticing that the sums of all emotion values was approximately one we considered that dividing the individual Skybiometry emotion confidences by the sum of the confidences would give the likelihood of each emotion being the dominant emotion in a face.

This calculation was simple to perform and resulted in numeric values comparable to Microsoft's values.

Skybiometry Transformed:

```{r SBT, echo=F, fig.cap = "\\label{tab:SBT}"}
SBT <- SB %>% subset(aname=="face-1745-1-Go.png") %>% select(neutral, anger, disgust, fear, happiness, sadness, surprise)

knitr::kable(SBT, digits=6, longtable=TRUE, booktabs = TRUE,
               caption="The Skybiometry API provided 7 numerical Confidence values, one for each emotion.")
```

We then needed to transform the Google output to also be comparable. This was the most challenging due to it's unusual form.

A numeric value was assigned to each possible likelihood value. This would allow for numeric comparisons to be made.
The values were assigned according to the table below:

```{r LT, echo=F, fig.cap = "\\label{tab:LT}"}
Likelihood <-c("VERY_UNLIKELY", "UNLIKELY", "POSSIBLE", "LIKELY", "VERY_LIKELY")
Value <- c(10, 30, 50, 70, 90)
LT <- cbind(Likelihood, Value)

knitr::kable(LT, longtable=TRUE, booktabs = TRUE,
               caption="")

```

As both Microsoft and Skybiometry included a neutral category we considered how we may incorporate this for the Google results.

Google Transformed

Our approach considered that when a face was "very unlikely" to be any of the four emotion categories it could be deemed "neutral". However when one emotion was stronger than other it could still be possible that the face only had a small lean toward this emotion. Therefore the Confidence value for neutral was derived as:

$$neutralConf_i = 100 - max(joyConf_i, sorrowConf_i, angerConf_i, surpriseConf_i)$$

The process to derive the numeric values followed the process undertaken for Skybiometry values. Where the individual emotion confidences were divided by the sum of the emotion confidence values for each face.

This resulted in congruent emotion data to be compared

```{r GET, echo=F, fig.cap = "\\label{tab:GET}"}

GET <- GE %>% subset(FileName=="face-1745-1-Go.png") %>% 
  select(joy, sorrow, anger, surprise, neutral)

knitr::kable(GET, longtable=TRUE, booktabs = TRUE,
             col.names = c("joy", "sorrow", "anger", "surprise", "neutral"),
             caption="The Google Vision API provided four likelihoods, one for each emotion.")
```

# Analysis
# Validation
We considered a subset of images where the emotions on the faces were manually considered.

### 2017-04-21 Internship/EmotionsAnalysis.Rmd
Rearrange Repo
Arrange Emotion Internship Sub section

---
title: "BEX3012 Project Analysis"
author: "Stephanie Kobakian"
date: "28 March 2017"
output: bookdown::pdf_document2
---

Emotions Analysis

```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, cache=T)

library(tidyverse)
library(readr)
library(GGally)
library(gridExtra)
```

Data used:
ME: Microsoft's results, emotion data
SB: Skybiometry's results, emotion data
GE: Google's results, emotion data
GoogleFaces: The Set of Faces found by Google in the intital study

```{r}
#EmoM <-read_csv("data/EmotionsMerged.csv")
ME <- read_csv("data/MicrosoftEmotions.csv")
SB <- read_csv("data/SkybiometryEmotions.csv")
GE <- read_csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
GF <- read_csv("data/GoogleFaces.csv")
#ALLmetaIMGnamed <- read.csv("ALLmetaIMGnamed.csv")

# ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
#   filter(matchesManual)%>%
#   dplyr::select(-ID, -facecounter)%>%
#   mutate(fileID = as.numeric(factor(file))) %>%
#   mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
#   mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-")) %>%
#   mutate(FileName=paste("face-", FaceID, ".png", sep=""))

#EmotionsMerged<-left_join(by="FileName", MicrosoftEmotions, ALLmetaIMGnamedFaces)
#EmotionsMerged<-write.csv(EmotionsMerged, "EmotionsMerged.csv", row.names = FALSE)

#EmotionsMerged<-EmotionsMerged %>% mutate(s = sum(anger, contempt, disgust, fear, happiness, neutral, sadness, surprise, na.rm=TRUE))

```

Connect face id to original Google set
```{r}
GEsub <- GE[,c(1, 10:13, 17:24)]

GE1 <- GEsub %>% 
  rowwise() %>%
  mutate(minX = pmin(cbind(boundingPoly.x1, boundingPoly.x4)), 
         maxX = pmin(cbind(boundingPoly.x2, boundingPoly.x3)),
         minY = pmin(cbind(boundingPoly.y1, boundingPoly.y2)), 
         maxY = pmin(cbind(boundingPoly.y3, boundingPoly.y4))) %>%
  ungroup()

GE1 <- GE1[,c(1:5, 14:17)]
```

Add meta data to Emotion results
```{r}
GE <- left_join(GF, GE1, by = c("file","minX","maxX","minY","maxY"))

ME <- left_join(ME, GF, by = "FileName") 
SB <- left_join(SB, GF, by = c("aname"="FileName")) 
```

Create normalized SB values
```{r}
SB<-SB %>%
  rowwise %>% mutate(z = (anger.confidence+
               disgust.confidence+
               fear.confidence+
               happiness.confidence+
               neutral_mood.confidence+
               sadness.confidence+
               surprise.confidence))

SB<-SB %>%
  mutate(anger = anger.confidence/z,
         disgust = disgust.confidence/z,
         fear = fear.confidence/z,
         happiness = happiness.confidence/z,
         neutral = neutral_mood.confidence/z,
         sadness = sadness.confidence/z,
         surprise = surprise.confidence/z)
```

Create normalized GE values
GE: Google results of player facial emotions in numeric confidences

```{r}
Conf <- function(Emot){
ifelse(Emot=="VERY_UNLIKELY", 10,  
        ifelse(Emot == "UNLIKELY", 30, 
                ifelse(Emot == "POSSIBLE", 50, 
                ifelse(Emot == "LIKELY", 70, 
                ifelse(Emot == "VERY_LIKELY", 90, NA)))))
}

GE <- GE %>% mutate(joyConf = Conf(joyLikelihood)) %>%
  mutate(sorrowConf = Conf(sorrowLikelihood)) %>%
  mutate(angerConf = Conf(angerLikelihood)) %>%
  mutate(surpriseConf = Conf(surpriseLikelihood))

GE <- GE %>%
  rowwise %>% 
  mutate(neutralConf = 100 - (pmax(joyConf, sorrowConf, angerConf, surpriseConf))) %>%
  mutate(z = (joyConf+sorrowConf+angerConf+surpriseConf+neutralConf)) %>%
  mutate(anger = angerConf/z,
         joy = joyConf/z,
         neutral = neutralConf/z,
         sorrow = sorrowConf/z,
         surprise = surpriseConf/z)

```

Convert to true or false emotion values

```{r}

ME <- ME %>% mutate(HappinessTF = ifelse(happiness > 0.5,TRUE,FALSE)) %>%
             mutate(SadnessTF = ifelse(sadness > 0.5,TRUE,FALSE))%>%
             mutate(AngerTF = ifelse(anger > 0.5,TRUE,FALSE))%>%
             mutate(FearTF = ifelse(fear > 0.5,TRUE,FALSE))%>%
             mutate(SurpriseTF = ifelse(surprise > 0.5,TRUE,FALSE))

# 
GE <- GE %>%
  mutate(JoyTF = ifelse((joyLikelihood=="LIKELY"|joyLikelihood=="VERY_LIKELY"), TRUE,FALSE)) %>%
  mutate(SorrowTF = ifelse((sorrowLikelihood=="LIKELY"|sorrowLikelihood=="VERY_LIKELY"), TRUE,FALSE))%>%
  mutate(AngerTF = ifelse((angerLikelihood=="LIKELY"|angerLikelihood=="VERY_LIKELY"), TRUE,FALSE))%>%
  mutate(SurpriseTF = ifelse((surpriseLikelihood=="LIKELY"|surpriseLikelihood=="VERY_LIKELY"), TRUE,FALSE))

GE <- GE %>% subset(!duplicated(GE$FaceID))

SB <- SB %>% mutate(HappinessTF = ifelse(happiness > 0.5,TRUE,FALSE)) %>%
  mutate(SadnessTF = ifelse(sadness > 0.5,TRUE,FALSE))%>%
  mutate(AngerTF = ifelse(anger > 0.5,TRUE,FALSE))%>%
  mutate(FearTF = ifelse(fear > 0.5,TRUE,FALSE))%>%
  mutate(SurpriseTF = ifelse(surprise > 0.5,TRUE,FALSE)) %>%
  mutate(NeutralTF = ifelse(neutral > 0.5,TRUE,FALSE))
```

Parallel coordinate plots
```{r}
#p1 <- ggparcoord(data = set1, columns = 2:9, groupColumn="file", order = "allClass")

#p2 <- ggparcoord(data = set2, columns = 2:9, groupColumn="file", order = "allClass")

#p3 <- ggparcoord(data = set3, columns = 2:9, groupColumn="file", order = "allClass")
```

Consider just players,
GEP: Microsoft's results, emotion data for only players
MEP: Skybiometry's results, emotion data for only players
SBP: Google's results, emotion data for only players
```{r}
GEP <- GE %>% filter(detect=="Player")
MEP <- ME %>% filter(detect=="Player")
SBP <- SB %>% filter(detect=="Player")

GFP <- GF %>% filter(detect=="Player")

MEP$anger %>% is.na() %>% sum
SBP$anger %>% is.na() %>% sum
```

Skybiometry Emotion plots

```{r}

ggSBPne <- ggplot(SBP, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBne <- ggplot(SB, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))

ggSBPan <- ggplot(SBP, aes(x=anger))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPdi <- ggplot(SBP, aes(x=disgust))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPfe <- ggplot(SBP, aes(x=fear))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPha <- ggplot(SBP, aes(x=happiness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPsa <- ggplot(SBP, aes(x=sadness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPsu <- ggplot(SBP, aes(x=surprise))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))

grid.arrange(ggSBPne,
             ggSBPan,
             ggSBPdi,
             ggSBPfe,
             ggSBPha,
             ggSBPsa,
             ggSBPsu, nrow=3)

```

SBPCL: Long form of Confidence levels of SB results
```{r}
SBPCL <- SBP %>% group_by(aname) %>% 
  gather(key = Emotion, value=EmotionValue, anger,disgust,fear,happiness,neutral,sadness,surprise)

SBPCL1 <- SBPCL %>% arrange(aname,desc(EmotionValue)) %>%
      group_by_(~ aname) %>% 
      slice(1)

table(SBPCL1$Emotion)

ggplot(SBPCL, aes(x=Emotion, y=EmotionValue)) + theme(axis.text.x = element_text(angle = 20)) + geom_boxplot()

#ggscatmat(as.data.frame(na.omit(SBEmotions[,3:9])))

```

GEP: Long form of Confidence levels of GE results
GEPN:  Long form of Confidence levels of GE results renamed to match
```{r}
#rename
GEPN <- GEP %>% select(FileName, anger, happiness=joy, sadness=sorrow, surprise, neutral, everything())

GEPCL <- GEPN %>% group_by(FileName) %>% 
  gather(key = Emotion, value=EmotionValue, anger, happiness, sadness, surprise, neutral)

GEPCL1 <- GEPCL %>% arrange(FileName,desc(EmotionValue)) %>%
      group_by_(~ FileName) %>% 
      slice(1)

table(GEPCL1$Emotion)

ggplot(GEPCL1, aes(x=Emotion, y=EmotionValue)) + theme(axis.text.x = element_text(angle = 20)) + geom_boxplot()

#ggscatmat(as.data.frame(na.omit(SBEmotions[,3:9])))

```

Microsoft Emotion plots
```{r}
ggMEPne<-ggplot(MEP, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPan<-ggplot(MEP, aes(x=anger))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPdi<-ggplot(MEP, aes(x=disgust))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPfe<-ggplot(MEP, aes(x=fear))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPha<-ggplot(MEP, aes(x=happiness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPsa<-ggplot(MEP, aes(x=sadness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPsu<-ggplot(MEP, aes(x=surprise))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))

grid.arrange(ggMEPne,
             ggMEPan,
             ggMEPdi,
             ggMEPfe,
             ggMEPha,
             ggMEPsa,
             ggMEPsu, nrow=3)

```

Microsoft Long form 
MEPCL: Long form of Confidence levels of ME results
```{r}
MEPCL<-MEP %>% group_by(FileName) %>% 
  gather(key = Emotion, value=EmotionValue, anger,contempt,disgust,fear,happiness,neutral,sadness,surprise)

MEPCL1 <- MEPCL %>% arrange(FileName, desc(EmotionValue)) %>%
      group_by_(~ FileName) %>% 
      slice(1)

ggplot(MEPCL, aes(x=Emotion, y=EmotionValue))+geom_boxplot()

table(MEPCL1$Emotion)
```

Tables
```{r}
# 
# table(ME$HappinessTF)
# 
# table(ME$HappinessTF, GE$JoyTF)
# 
# table(SB$HappinessTF, ME$HappinessTF)
# 
# table(MEL1$Emotion)
# table(SB$mood.value)
# table(MEL1$Emotion, SB$mood.value)

```

###
Join emotions for each face
```{r}
S1 <- select(SBPCL1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEPCL1, FileName, MEmotion = Emotion)
S3 <- select(GEPCL1, FileName, GEmotion = Emotion)
J1 <- full_join(S1, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

PS1 <- J2 %>% filter(SEmotion==MEmotion|SEmotion==GEmotion|MEmotion==GEmotion)
nrow(PS1)

J2L<-J2 %>% 
  gather(key = Software, value = Emotion, SEmotion, MEmotion, GEmotion)

ggplot(J2L, aes(x=Emotion)) + geom_bar(aes(fill = Software), position = "dodge")

```

Contingency Table of 50 image sample

```{r}
set.seed(300)
J2na<-na.omit(J2)
FL<-sample(J2na$FileName, 50)
J2na<-J2na %>% subset(FileName %in% FL)

ct<-table(J2na$SEmotion, J2na$MEmotion, J2na$GEmotion)
ftable(ct)

```

Plot images and compare to emotion data
```{r}
# for (i in 1:50){
# 
#   devAskNewPage()
#   plot(load.image(paste0("Faces/", J2na$FileName[i])), main = paste0( J2na$FileName[i]))
# 
# }

SER<-read_csv("SampleEmotionResults.csv")

t1<-table(SER$Manual, SER$SEmotion)
ftable(t1)

```

Find images from matches played by certain players
```{r}
a <- as.data.frame(table(GEP$player1))
a <- a %>% arrange(-Freq)

b <- as.data.frame(table(GEP$player2))
b <- b %>% arrange(-Freq)

PJ <- full_join(a, b, by = "Var1")

PJ$Freq.x<-ifelse(!is.na(PJ$Freq.x), PJ$Freq.x, 0) 
PJ$Freq.y<-ifelse(!is.na(PJ$Freq.y), PJ$Freq.y, 0) 
PJ$sum<-PJ$Freq.x+PJ$Freq.y
```

Player Subsetting
```{r}
#Create column for Player Names
#GoogleFaces$PlayerName<-NA

# PlayerSubset <- function(PlayerName, data = GF1) {
#   
#   PlayerSet<-filter(data, player1==PlayerName | player2==PlayerName)
#   
#   return(as.list(PlayerSet$FileName))
# }

# 
# MSlist <- PlayerSubset("MSakkari")
# MSlist

MSimgsG<-GEPCL1 %>% filter(player1=="ARadwanska")
MSimgsG <-MSimgsG %>% filter(detect=="Player")
MSlist <- as.list(MSimgsG$FileName)
length(MSlist)

library(imager)
DisplayFaces <- function(list) {
for (i in 1:length(list)){

   devAskNewPage()
   plot(load.image(paste0("Faces/", list[i])), 
        main = paste0(i, list[i]))

}
}

```

subset of Google where neutral = another category
```{r}
neutrals <- GEPCL1 %>% filter(neutralConf==joyConf | 
                    neutralConf==sorrowConf | 
                    neutralConf==surpriseConf | 
                    neutralConf==angerConf) %>%
  filter(neutralConf != 10)

```

Emotive Player Faces
EF: Emotive Player Faces to be used as sample.
It is hard to classify many of the faces as one of the seven possible options. Where hints of emotive expressions can be attributed to one or more faces
```{r}

EF <- as.list(c("face-70-1-Go.png", "face-227-2-Go.png", "face-399-1-Go.png",
        "face-450-1-Go.png", "face-475-1-Go.png", "face-626-1-Go.png",
        "face-730-1-Go.png", "face-762-1-Go.png", "face-781-1-Go.png",
        "face-790-1-Go.png", "face-801-1-Go.png", "face-816-1-Go.png",
        "face-945-1-Go.png", "face-947-1-Go.png", "face-1128-1-Go.png",
        "face-1173-1-Go.png", "face-1230-1-Go.png", "face-1355-1-Go.png",
        "face-1635-1-Go.png", "face-1764-1-Go.png"))

DisplayFaces(EF)
```

Player Emotion Tables

### 2017-04-21 Internship/R/BEX3012 ProjectReport.Rmd
Rearrange Repo
Arrange Emotion Internship Sub section

---
title: "BEX3012 Project Report \n Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian"
date: "28 March 2017"
output: bookdown::pdf_document2
fig_caption: yes
fontsize: 11pt
link-citations: true
---

```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F,cache=T)

library(tidyverse)
library(readr)
library(GGally)

#EmoM <-read_csv("data/EmotionsMerged.csv")
ME <- read_csv("../data/MicrosoftEmotions.csv")
SB <- read_csv("../data/SkybiometryEmotions.csv")
GE <- read_csv("../data/GoogleFacesEmotions.csv")

EmotionSoftwareSpecs <- read_csv("../TableCSVs/EmotionSoftwareSpecifications.csv")
ALLmetaIMGnamed <- read_csv("../data/ALLmetaIMGnamed.csv")

#Create normalised SB values
SB<-SB %>%
  rowwise %>% mutate(z = (anger.confidence+
               disgust.confidence+
               fear.confidence+
               happiness.confidence+
               neutral_mood.confidence+
               sadness.confidence+
               surprise.confidence))

SB<-SB %>%
  mutate(anger = anger.confidence/z,
         disgust = disgust.confidence/z, 
         fear = fear.confidence/z,
         happiness = happiness.confidence/z,
         neutral = neutral_mood.confidence/z,
         sadness = sadness.confidence/z,
         surprise = surprise.confidence/z)

```

# Introduction

Facial Recognition is beginning to be explored in sports environments, this presents quality issues.

helpful for applications

# Method
## Materials
### Pre Processing Images
A subset of faces was created specifically for emotion recognition purposes.
To present only a single face to each software required cropping the region of the image based on Google's bounding box result^[coordinates taken from prior study]

Each new image created contained the area within the face bounding boxes found in the previous study, as well as a small border to frame the face. This resulted in images of differing sizes to be passed to the APIs.
These 1319 new images were hosted on Google Drive to allow for URL access from the API to the individual images.

### Software APIs

We will consider three Emotion Recognition softwares.

```{r Emotion-Software-Specs-Table, echo=F, fig.cap = "\\label{tab:Emotion-Software-Specs-Table}"}

knitr::kable(EmotionSoftwareSpecs, longtable=TRUE, booktabs = TRUE, caption="This details the capabilities we considered important in recognising emotions in images of faces.")
```

As can be seen above, a noticable difference between the three is the amount of times the API can be called. Skybiometry had the largest imposition on Batch Processing as it only allowed 100 API calls to be processed per hour. Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within an hour, after accounting for the wait time per minute.
Google Vision's API batch processing limit had a minimal effect.

The range of outputs from the softwares is displayed as Google provides likelihoods of an emotion occuring on a particular face. Microsoft and Skybiometry provide outputs on the same emotions^[Based on Paul Ekmans emotion theories]. However the values that they provide differ as Microsoft provide Porportions whereas Skybiometry results in a Confidence of the emotion occuring in the specified face.

### Preprocessing of API results

#### Microsoft

```{r MEexample, echo=F, fig.cap = "\\label{tab:MEexample}"}
knitr::kable(ME[25,2:9], digits=6, longtable=TRUE, booktabs = TRUE, caption="The Microsoft API provided 8 numerical values.")
```

These numeric values approximately summed to a value of 1, there was no indication of how these categories were calculated.

#### Skybiometry

```{r SBexample, echo=F, message=F, fig.cap = "\\label{tab:SBexample}"}
library(dplyr)
SBexample <- SB %>% filter(aname=="face-1745-1-Go.png") %>%  select(ends_with(".confidence"))

knitr::kable(SBexample[,3:9], digits=6, longtable=TRUE, booktabs = TRUE, col.names = c("neutral", "anger", "disgust",
          "fear", "happiness", "sadness", "surprise"),
             caption="The Skybiometry API provided 7 numerical Confidence values.")

```

#### Google

```{r GEexample, echo=F, message=F, fig.cap = "\\label{tab:GEexample}"}

GEexample <- GE %>% subset(FileName=="face-1745-1-Go.png")

knitr::kable(GEexample, col.names = c("joy", "sorrow", "anger", "surprise"), caption="The Google API provided 4 categorical Likelihoods.")

```

# Analysis
# Within Software Variation

Microsoft:

```{r}

```

### 2017-04-21 R/Presentation1.Rmd
Rearrange Repo
Arrange Emotion Internship Sub section

---
title: "Facial Recognition in Tennis"
author: "Stephanie Kobakian"
date: "18 July 2016"
output: slidy_presentation
highlight: pygments
---

# Project Aim

##Begin to develop methods to collect accurate information about the facial expressions of elite tennis athletes during matchplay.

This beginning involves testing how well currently available facial recognition software performs at identifying faces of the two players in a tennis match.

# Current Recognition Software

### Current software has been intended for security purposes including:

- Access Points
- International Airports Passpoint points
- Watch List Screening in crowds

This presents issues as our use on Tennis Broadcasts provides multiple interchanging angles.
This is unlike the intended use of the softwares as a full frontal scan at an access point.

---

# Challenges

- The multiple angles presents issues of whether the faces will be detectable
- There are many softwares available for purchase online. The most accessible during our time frame were APIs
- Softwares were intended for use beyond latent still detection, they were intended for real time detection and alerts. These softwares had capabilities far beyond what is needed

# Opportunity

- We have a great opportunity to apply facial recognition software in an unusual and previously untested application
- Algorithms have certain capabilities that will allow for faces to be detected

# Our Sample

105 Singles Matches from 2016 AO differing by:

- Gender, either Male or Female
- Court, one of 7 possible courts

We then took:

- 5 minute segments from the 105 Broadcast video files
- Of these segments, a still was taken at every 3 seconds

## Computation Times for recognition of stills

- Skybiometry: 1.461
- Microsoft: 2.29
- Animetrics: 3.924

# Examples of Application

The following slides include stills and what was recognised when the softwares were applied.

- Green: Microsoft
- Red: Animetrics
- Blue: Skybiometry

# Accuracte Facial Recognition ![](presentationimages/GoodRecognition1.png)
The software that is chosen should be able to recognise this face even though it is not a front on angle.

# Accuracte Facial Recognition ![](presentationimages/GoodRecognition2.png)
The software that is chosen should also be able to recognise this face.

# Accuracte Facial Recognition ![](presentationimages/GoodRecognition3.png)
We would hope that this angle would still allow for accurate recognition, however it was only recognised by one software.

# Accuracte Facial Recognition ![](presentationimages/GoodRecognition4.png)
It would be unexpected that this size would still allow for recognition. It was only recognised by one software, note that the minimum pixel distance that will allow for recognition is 36.

# Accuracte Facial Recognition ![](presentationimages/plot15.png)
Only Animetrics was able to recognise this face, these shaded angles should be a high priority for recognition.

# Emotion Facial Recognition ![](presentationimages/plot16.png)
As this is the intended future use we would need the software to detect emotions and angles such as this.

# Emotion Facial Recognition ![](presentationimages/plot18.png)
This angle should also be detected by any software we would consider for this use.

# Emotion Facial Recognition ![](presentationimages/plot19.png)
This angle should also be detected by any software we would consider for this use.

# Inaccuracte Facial Recognition ![](presentationimages/plot5.png)
It was surprising that the softwares were not able to detect this face. Profile shots should also be distinguishable.

# Inaccuracte Facial Recognition ![](presentationimages/plot6.png)
The glasses and facial features may have impacted the lack of recognition, this will be investigated further.

# Inaccuracte Facial Recognition ![](presentationimages/plot7.png)
The glasses, facial features and face angle in this still frame may have impacted the lack of recognition, this will also be investigated further.

# Interesting Recognition ![](presentationimages/InterestingImage1.png)
Skybiometry was able to identify this 'face', created by the creases in the shirt.

# Interesting Recognition ![](presentationimages/InterestingImages2.png)
Animetrics was able to identify two faces in this image, one being a towel, the sensitivity will be investigated further.

# Interesting Recognition ![](presentationimages/Weird1.png)
Animetrics was able to correctly identify this face, twice. This presents an issue as the algorithm did not identify this.

# Interesting Recognition ![](presentationimages/plot4.png)
Animetrics also presented an interesting recognition on the 'face' despite it not being the intended face for recognition.

# Crowd Recognition ![](presentationimages/plot1.png)
In looking at the crowd shots insights can be gained as to how to programs contrast in their abilities. Skybiometry showed interesting recognition on a fist and Animetrics only found one face.

# Crowd Recognition ![](presentationimages/plot13.png)
This showed that the softwares struggled during a transition.

# Crowd Recognition ![](presentationimages/plot14.png)
Where the previous image only on software found one face. In this image all three softwares were able to locate both faces. This contrast gives insight into capabilities.

# Impractical Shots

Some shots result in difficulties when applying recognition software

### Upward Angle
This was difficult for recognition softwares that were intended for recognition of clear and well-lit faces.
### Birdseye View
This was difficult as the range of the angles meant that faces were too small and could not be distinguished.

# Upward Angle
![](presentationimages/plot2.png)
It was hoped that these situations would be able to be used in recognition as it is at these moments that emotions would be able to effect gameplay.

# Birds-eye View
![](presentationimages/plot3.png)
This view is common and completely impractical. There are no recognisable faces in this image.

# Obstructed Faces 
![](presentationimages/InterestingImages2.png)
It was expected that when faces are covered by objects used by players courtside that the recognition would be stunted. However it was unexpected that the recognition would be found on the towel. It was also unexpected that the face in the crowd would be recognised.

# Manual Recognition

Our Gold Standard to compare to the softwares selected

- The Shiny App was created to hasten the process of manual detection of faces using the packages imager, shiny and shinyjs
- We collected information on the general scenes, this included live shot, person in the frame, situation, background, angle of the shot
- For each individual face in the frame we found the location, how obscured is was, the light on the face, angle of the head and whether they were wearing glasses, and a hat or visor.

# Data Frame Creation
The information collected by myself and the three softwares differed. We collated it so that comparable information was captured in a single data frame for analysis. This allows us to create the mapped face boxes as seen in the previous images.

# Future Analysis to be reported
### Comparisons of:
- Facial features and structures that influence recognition
- The resulting recogised areas

# Intriguing Results
![](presentationimages/Rplot.png)
Two softwares both distinguished a face in the creases of the shirt.

# ![](presentationimages/Rplot01.png)
The different colours detail the faces found by all three softwares. It shows that only one software considered the Adidas shirt a face, and glasses tended to result in only two softwares recognising the face.

# Questions and Recommendations

### 2017-04-21 CreateFacesSet.R

@@ -1,16 +1,0 @@
-
-library(magick)
-
-GoogleFaces<-ALLmetaIMGFaces %>% subset(type=="Google")
-
-#create data set of just faces
-data<-GoogleFaces
-#CreateFaceSet
-for(n in 1:NROW(GoogleFaces)){
-SubImage <- image_read(paste0("images/", data$file[n]))
-
-cropValue<-paste0(data$maxX[n]-data$minX[n]+20, "x",data$maxY[n]-data$minY[n]+20,"+", data$minX[n]-10,"+", data$minY[n]-10, collapse = ", ")
-Cropped<-image_crop(SubImage, cropValue)
-
-image_write(Cropped, path=(paste0("images/Faces/","face-", data$FaceID[n], ".png", collapse = ", ")))
-}

### 2017-04-21 EmotionsAnalysis.R

@@ -1,146 +1,0 @@
-##Emotions Analysis
-
-library(tidyverse)
-library(readr)
-EmoM <-read_csv("data/EmotionsMerged.csv")
-ME <- read_csv("data/MicrosoftEmotions.csv")
-SB<-read_csv("data/SkybiometryEmotions.csv")
-GE<- read_csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
-ALLmetaIMGnamed <- read.csv("ALLmetaIMGnamed.csv")
-
-ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
-  filter(matchesManual)%>%
-  dplyr::select(-ID, -facecounter)%>%
-  mutate(fileID = as.numeric(factor(file))) %>%
-  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
-  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-")) %>%
-  mutate(FileName=paste("face-", FaceID, ".png", sep=""))
-
-
-EmotionsMerged<-left_join(by="FileName", MicrosoftEmotions, ALLmetaIMGnamedFaces)
-#EmotionsMerged<-write.csv(EmotionsMerged, "EmotionsMerged.csv", row.names = FALSE)
-
-
-EmotionsMerged<-EmotionsMerged %>% mutate(s = sum(anger, contempt, disgust, fear, happiness, neutral, sadness, surprise, na.rm=TRUE))
-
-# Connect face id to original Google set
-
-GE <- GE %>% 
-  rowwise() %>%
-  mutate(minX = min(boundingPoly.x1, boundingPoly.x4), maxX = min(boundingPoly.x2, boundingPoly.x3),
-         minY = min(boundingPoly.y1, boundingPoly.y2), maxY = min(boundingPoly.y3, boundingPoly.y4)) %>%
-  ungroup() %>%
-  mutate(minX = ifelse(is.na(minX), 0, minX), minY = ifelse(is.na(minY), 0, minY))
-
-# create full Google DataSet
-GF1<-GoogleFaces[,c(1, 36, 18:21)]
-GE1<-GE[,c(1, 10:13,135:138)]
-GE <- left_join(GF1, GE1, by = c("file","minX","maxX","minY","maxY")) 
-
-
-
-
-#consider just players?
-#EmotionsMerged<-EmotionsMerged %>% filter(detect=="Player")
-
-
[…]

### 2017-04-21 Internship/R/CreateFacesSet.R

@@ -1,0 +1,31 @@
+
+library(magick)
+ALLmetaIMGnamed<-read.csv("ALLmetaIMGnamed.csv")
+
+
+ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
+  filter(matchesManual) %>% 
+  dplyr::select(-ID, -facecounter)%>%
+  mutate(fileID = as.numeric(factor(file))) %>%
+  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
+  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))
+
+
+GoogleFaces<-ALLmetaIMGnamedFaces %>% subset(type=="Google")
+
+#create data set of just faces
+data<-GoogleFaces
+
+
+#CreateFaceSet
+for(n in 1:NROW(GoogleFaces)){
+SubImage <- image_read(paste0("images/", data$file[n]))
+
+cropValue<-paste0(data$maxX[n]-data$minX[n]+20, "x",data$maxY[n]-data$minY[n]+20,"+", data$minX[n]-10,"+", data$minY[n]-10, collapse = ", ")
+Cropped<-image_crop(SubImage, cropValue)
+
+image_write(Cropped, path=(paste0("Faces/","face-", data$FaceID[n], ".png", collapse = ", ")))
+}
+
+write.csv(GoogleFaces, "GoogleFaces.csv", row.names = FALSE)
+

### 2017-04-21 Internship/R/EmotionsAnalysis.R

@@ -1,0 +1,213 @@
+##Emotions Analysis
+
+library(tidyverse)
+library(readr)
+library(GGally)
+
+#EmoM <-read_csv("data/EmotionsMerged.csv")
+ME <- read_csv("data/MicrosoftEmotions.csv")
+SB<-read_csv("data/SkybiometryEmotions.csv")
+GE<- read_csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
+GoogleFaces <- read_csv("data/GoogleFaces.csv")
+ALLmetaIMGnamed <- read.csv("ALLmetaIMGnamed.csv")
+
+ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
+  filter(matchesManual)%>%
+  dplyr::select(-ID, -facecounter)%>%
+  mutate(fileID = as.numeric(factor(file))) %>%
+  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
+  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-")) %>%
+  mutate(FileName=paste("face-", FaceID, ".png", sep=""))
+
+
+#EmotionsMerged<-left_join(by="FileName", MicrosoftEmotions, ALLmetaIMGnamedFaces)
+#EmotionsMerged<-write.csv(EmotionsMerged, "EmotionsMerged.csv", row.names = FALSE)
+
+
+#EmotionsMerged<-EmotionsMerged %>% mutate(s = sum(anger, contempt, disgust, fear, happiness, neutral, sadness, surprise, na.rm=TRUE))
+
+# Connect face id to original Google set
+
+GE <- GE %>% 
+  rowwise() %>%
+  mutate(minX = min(boundingPoly.x1, boundingPoly.x4), maxX = min(boundingPoly.x2, boundingPoly.x3),
+         minY = min(boundingPoly.y1, boundingPoly.y2), maxY = min(boundingPoly.y3, boundingPoly.y4)) %>%
+  ungroup() %>%
+  mutate(minX = ifelse(is.na(minX), 0, minX), minY = ifelse(is.na(minY), 0, minY))
+
+
+# add meta data to Emotion results
+GF1<-GoogleFaces[,c(1, 35, 18:21, 2:14)]
+GE1<-GE[,c(1, 10:13, 135:138)]
+GE <- left_join(GF1, GE1, by = c("file","minX","maxX","minY","maxY")) 
+
+
[…]

### 2017-04-21 MicrosoftEmotions.R

@@ -1,92 +1,0 @@
-library(httr)
-
-
-emotURL = "https://westus.api.cognitive.microsoft.com/emotion/v1.0/recognize"
-mybody = list(url = img.url)
-emotKey = ""
-
-
-#bEmot <- POST(url=emotURL, 
-#          content_type('application/json'),
-#          add_headers(.headers = c('Ocp-Apim-Subscription-Key' = emotKey)),
-#          body = list(url = img.url),
-#          encode = 'json')
-#
-#emotResult=httr::content(aEmot)[[1]]
-#emotResultdf <-as.data.frame((emotResult$scores))
-
-#keep for testing works img.url =  "https://drive.google.com/uc?export=download&id=0B0i5WV2jMQ1vSG1Va25wRmVkQkE"
-# works img.url =  "https://drive.google.com/uc?export=download&id=0B0i5WV2jMQ1vSVlvWjlZUktpMUU"
-
-
-#send the request to microsoft
-MicrosoftAPI <- function(id){
-  POST(url=emotURL,
-      content_type('application/json'),
-      add_headers(.headers = c('Ocp-Apim-Subscription-Key' = emotKey)),
-      body = list(url = paste0("https://drive.google.com/uc?export=download&id=", id)),
-      encode = 'json'
-  )
-}
-
-library(httr)
-library(dplyr)
-#expand into a dataframe
-getEmotionsMicrosoft <- function(a){
-  
-  if (length(content(a, "raw"))>2) {
-    emotResult = httr::content(a)[[1]]
-    tagdata <- as.data.frame((emotResult$scores))
-
-  }
-  else{
-    tagdata <- data.frame(
-      anger = NA,
-      contempt = NA,
-      disgust = NA,
-      fear = NA,
-      happiness = NA,
-      neutral = NA,
-      sadness = NA,
-      surprise = NA
-    )
-
-  }
-  
-}
-
-#combine with previous results
-EmotionsResult <- function(imagelist) {
-  for (img in 1:length(imagelist)) {
-    id <- substr(as.character(imgURLS$URL[img]), 33, 60)
-    a <- MicrosoftAPI(id)
-    result <- getEmotionsMicrosoft(a)
-    named<-cbind(imgURLS$Filename[img], result)
-    names(named)[1]<-"FileName"
-    print(img)
-    print(named)
-    currentFaces <- read.csv("MicrosoftEmotions.csv")
[…]

### 2017-04-21 R/SoftwareScripts/autoSkybiometry.R

@@ -1,0 +1,221 @@
+### API loop function
+library(jsonlite)
+setwd("")
+
+reqsize <- 97
+
+# Starting script for SkyBiometry API
+api_key <- ""
+api_secret <- ""
+
+getFacesSkyBiometry <- function(faceTags){
+  if(length(faceTags$photos$tags[[1]]) > 1){
+    tagdata <- flatten(faceTags$photos$tags[[1]])[,-1]
+  }
+  else{
+    tagdata <- data.frame(label = NA, confirmed = NA, manual = NA, width = NA, height = NA,
+                          yaw = NA, roll = NA, pitch = NA, points = NA, similarities = NA, tid = NA, recognizable = NA,
+                          attributes.face.value = NA, attributes.face.confidence = NA, center.x = NA, center.y = NA,
+                          eye_left.x = NA, eye_left.y = NA, eye_left.confidence = NA, eye_left.id = NA,
+                          eye_right.x = NA, eye_right.y = NA, eye_right.confidence = NA, eye_right.id = NA,
+                          mouth_center.x = NA, mouth_center.y = NA, mouth_center.confidence = NA, mouth_center.id = NA,
+                          nose.x = NA, nose.y = NA, nose.confidence = NA, nose.id = NA)
+  }
+  cbind(file = strsplit(faceTags$photos$url, split = "/")[[1]][length(strsplit(faceTags$photos$url, split = "/")[[1]])], url = faceTags$photos$url, tagdata)
+}
+
+request_pattern <- "http://api.skybiometry.com/fc/faces/detect.json?api_key=KEY&api_secret=SECRET&urls=IMAGE"
+the_request <- function(url) 
+  sub("IMAGE", url, sub("SECRET", api_secret, sub("KEY", api_key, request_pattern)))
+the_request <- Vectorize(the_request)
+
+currentFaces <- read.csv("SkybiometryClassifiedFaces.csv")
+allimages <- read.csv("imagenames.csv")$imagelist
+imagelist <- allimages[-match(unique(na.omit(currentFaces[,"file"])), allimages)]
+if (length(imagelist) == 0){
+  imagelist <- allimages
+}
+
+
+## Manual check on http://mitchelloharawild.com/tennis/ image server
+# imagelist <- c(
[…]

### 2017-04-21 R/SoftwareScripts/microsoftAPI.R

@@ -1,0 +1,49 @@
+library(httr)
+
+
+faceURL = "https://westus.api.cognitive.microsoft.com/face/v1.0/detect?returnFaceId=false&returnFaceLandmarks=true&returnFaceAttributes=age,gender,smile,facialHair"
+img.url = "https://www.whitehouse.gov/sites/whitehouse.gov/files/images/first-family/44_barack_obama[1].jpg"
+mybody = list(url = img.url)
+#faceKey = ""
+
+
+aFace <- POST(url=faceURL, 
+          content_type('application/json'),
+          add_headers(.headers = c('Ocp-Apim-Subscription-Key' = faceKey)),
+          body = mybody,
+          encode = 'json')
+
+faceResult=httr::content(aFace, as="text")
+faceResult
+
+
+MicrosoftAPI <- function(img.url){
+  POST(url = faceURL, 
+    content_type('application/json'), 
+    add_headers(.headers = c('Ocp-Apim-Subscription-Key' = faceKey)),
+    body = mybody,
+    encode = 'json'
+  )
+}
+
+#faceTags<-faceResult
+
+getMicrosoft <- function(faceTags){
+  if(length(faceTags[[1]]) > 1){
+    tagdata <- flatten(faceTags[[1]])[,-1]
+  }
+  else{
+    tagdata <- data.frame(label = NA, confirmed = NA, manual = NA, width = NA, height = NA,
+                          yaw = NA, roll = NA, pitch = NA, points = NA, similarities = NA, tid = NA, recognizable = NA,
+                          attributes.face.value = NA, attributes.face.confidence = NA, center.x = NA, center.y = NA,
+                          eye_left.x = NA, eye_left.y = NA, eye_left.confidence = NA, eye_left.id = NA,
+                          eye_right.x = NA, eye_right.y = NA, eye_right.confidence = NA, eye_right.id = NA,
+                          mouth_center.x = NA, mouth_center.y = NA, mouth_center.confidence = NA, mouth_center.id = NA,
+                          nose.x = NA, nose.y = NA, nose.confidence = NA, nose.id = NA)
+  }
+  cbind(file = strsplit(faceTags$photos$url, split = "/")[[1]][length(strsplit(faceTags$photos$url, split = "/")[[1]])], url = faceTags$photos$url, tagdata)
+}
+getMicrosoft(faceResult)
+
+
+

### 2017-04-21 R/manual.R

@@ -1,0 +1,2 @@
+script.dir <- dirname(sys.frame(1)$ofile)
+print(script.dir)

### 2017-04-21 R/mergeData.R

@@ -1,0 +1,169 @@
+#Load Packages
+library(imager)
+library(dplyr)
+library(tidyr)
+library(purrr)
+
+
+
+#Load Data
+MicrosoftClassifiedFaces <- read.csv("SoftwareRequestScripts/MicrosoftClassifiedFaces.csv")
+AnimetricsClassifiedFaces <- read.csv("SoftwareRequestScripts/AnimetricsClassifiedFaces.csv")
+SkybiometryClassifiedFaces <- read.csv("SoftwareRequestScripts/SkybiometryClassifiedFaces.csv")
+GoogleClassifiedFaces <- read.csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
+ManualClassifiedFaces <- read.csv("ManualClassifiedFaces.csv")
+ManualClassifiedScenes <- read.csv("ManualClassifiedScenes.csv")
+
+#Check all equal length
+#length(unique(ManualClassifiedScenes$file))
+#length(unique(AnimetricsClassifiedFaces$file))
+#length(unique(SkybiometryClassifiedFaces$file))
+#length(unique(GoogleClassifiedFaces$file))
+
+#Remove images with no faces
+MicrosoftClassifiedFaces <- MicrosoftClassifiedFaces[!is.na(MicrosoftClassifiedFaces$faceRectangle.top),]
+AnimetricsClassifiedFaces <- AnimetricsClassifiedFaces[!is.na(AnimetricsClassifiedFaces$topLeftX),]
+SkybiometryClassifiedFaces <- SkybiometryClassifiedFaces[!is.na(SkybiometryClassifiedFaces$width),]
+GoogleClassifiedFaces <- GoogleClassifiedFaces[!is.na(GoogleClassifiedFaces$rollAngle),]
+
+#Manual Classified Faces
+ManualClassifiedFaces <- ManualClassifiedFaces %>%
+  mutate(type = "Manual", time.user.self=NA, time.sys.self=NA, time.elapsed=NA, ID=1:NROW(ManualClassifiedFaces))
+
+#Merge data
+MicrosoftMerge <- MicrosoftClassifiedFaces %>% 
+  mutate(type = "Microsoft", ID=NA,
+         minX = faceRectangle.left, maxX = faceRectangle.left + faceRectangle.width,
+         minY = faceRectangle.top, maxY = faceRectangle.top + faceRectangle.height) %>%
[…]

### 2017-04-21 R/regressionWIP.R

@@ -1,0 +1,178 @@
+# Prepare data
+library(tidyverse)
+library(gridExtra)
+library(dplyr)
+
+ALLmetaIMG<-read_csv("ALLmetaIMG.csv",
+                     col_types = cols(type = col_factor(levels = c("Manual", 
+                      "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+
+
+ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
+ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
+ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
+ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
+ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
+
+ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:3, labels = c("Player", "Other staff on court", "Fan", "None"))
+ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
+ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 1:2, labels = c("Shaded", "Partially shaded"))
+ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
+ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
+ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))
+
+
+
+#ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")
+
+# change this to facesVenn with binary information
+ALLmetaIMGFaces<-ALLmetaIMG%>%
[…]

### 2017-04-21 R/visualisation.R

@@ -1,0 +1,56 @@
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+
+#Load ALLmetaIMG in (from analysis.R)
+ggplot(ALLmetaIMG, aes(x = type)) + geom_bar(position="dodge")
+
+#NA refers to the boxes which don't match manual (hence we don't have info about the image classification)
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(visorhat)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(glasses)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(shotangle)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(graphic)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(person)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(situation)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(bg)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(detect)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(obscured)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(lighting)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMG, aes(x = factor(x = factor(headangle)), group=type, fill=type)) + geom_bar(position="dodge")
+
+
+## TODO: Proportions of manual classifications.
+a <- ALLmetaIMG %>% filter(matchesManual) %>% group_by(glasses, type) %>% summarise(a=n())
+ggplot(a, aes(x=factor(glasses), y=a, fill=type)) + geom_bar(stat="identity", position = "dodge")
+a$manVal <- rep(c(1344, 186), each=5) # MAKE THIS MORE GENERAL
+b <- a %>% mutate(prop = a/manVal)
+b
[…]

### 2017-04-21 SoftwareRequestScripts/animetrics.R

@@ -1,27 +1,0 @@
-# Starting script for Animetrics FaceR API
-a.api_key <- ""
-a.selection <- "FULL"
-
-image_urls <- c("mitchelloharawild.com/tennis/2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0003.png")
-                
-request_pattern <- "http://api.animetrics.com/v1/detect?api_key=KEY&selection=SELECTION&urls=IMAGE"
-
-the_request <- function(url)
-  sub("IMAGE", url, sub("SELECTION", a.selection, sub("KEY", a.api_key, request_pattern)))
-
-the_request <- Vectorize(the_request)
-
-requests <- the_request(image_urls)
-
-# for a single url request
-a <- readLines(requests)
-
-# convert from JSON
-fromJSON(a)
-
-#for multiple url requests
-a <- lapply(requests, readLines)
-
-#Test using some images uploaded to Mitchs server
-alllinks <- paste0("mitchelloharawild.com/tennis/", dir("images")[36:45])
-head(alllinks)

### 2017-04-21 SoftwareRequestScripts/autoKairos.R

@@ -1,21 +1,0 @@
-library(httr)
-#set up and return git web address for id
-a <- GET(url="https://api.kairos.com/v2/analytics/{https://github.com/srkob1/face-recognition/blob/master/TestFaces/face-947-1-Go.png}",
-          add_headers(`app_id` = "8078e093",
-                      `app_key` = "dd97f6d1afd17676f7130e180068b760")
-)
-
-#img.url = "The git img url"
-
-mybody = list(url = img.url)
-
-
-KairosAPI <- function(img.url){
-  GET(url="https://api.kairos.com/v2/analytics/{id}",
-      add_headers(`app_id` = "8078e093",
-                  `app_key` = "dd97f6d1afd17676f7130e180068b760")
-  )
-}
-
-         
-        

### 2017-04-21 SoftwareRequestScripts/autoSkybiometry.R

@@ -1,221 +1,0 @@
-### API loop function
-library(jsonlite)
-setwd("")
-
-reqsize <- 97
-
-# Starting script for SkyBiometry API
-api_key <- ""
-api_secret <- ""
-
-getFacesSkyBiometry <- function(faceTags){
-  if(length(faceTags$photos$tags[[1]]) > 1){
-    tagdata <- flatten(faceTags$photos$tags[[1]])[,-1]
-  }
-  else{
-    tagdata <- data.frame(label = NA, confirmed = NA, manual = NA, width = NA, height = NA,
-                          yaw = NA, roll = NA, pitch = NA, points = NA, similarities = NA, tid = NA, recognizable = NA,
-                          attributes.face.value = NA, attributes.face.confidence = NA, center.x = NA, center.y = NA,
-                          eye_left.x = NA, eye_left.y = NA, eye_left.confidence = NA, eye_left.id = NA,
-                          eye_right.x = NA, eye_right.y = NA, eye_right.confidence = NA, eye_right.id = NA,
-                          mouth_center.x = NA, mouth_center.y = NA, mouth_center.confidence = NA, mouth_center.id = NA,
-                          nose.x = NA, nose.y = NA, nose.confidence = NA, nose.id = NA)
-  }
-  cbind(file = strsplit(faceTags$photos$url, split = "/")[[1]][length(strsplit(faceTags$photos$url, split = "/")[[1]])], url = faceTags$photos$url, tagdata)
-}
-
-request_pattern <- "http://api.skybiometry.com/fc/faces/detect.json?api_key=KEY&api_secret=SECRET&urls=IMAGE"
-the_request <- function(url) 
-  sub("IMAGE", url, sub("SECRET", api_secret, sub("KEY", api_key, request_pattern)))
-the_request <- Vectorize(the_request)
-
-currentFaces <- read.csv("SkybiometryClassifiedFaces.csv")
-allimages <- read.csv("imagenames.csv")$imagelist
-imagelist <- allimages[-match(unique(na.omit(currentFaces[,"file"])), allimages)]
-if (length(imagelist) == 0){
-  imagelist <- allimages
-}
-
-
-## Manual check on http://mitchelloharawild.com/tennis/ image server
-# imagelist <- c(
[…]

### 2017-04-21 SoftwareRequestScripts/microsoftAPI.R

@@ -1,49 +1,0 @@
-library(httr)
-
-
-faceURL = "https://westus.api.cognitive.microsoft.com/face/v1.0/detect?returnFaceId=false&returnFaceLandmarks=true&returnFaceAttributes=age,gender,smile,facialHair"
-img.url = "https://www.whitehouse.gov/sites/whitehouse.gov/files/images/first-family/44_barack_obama[1].jpg"
-mybody = list(url = img.url)
-#faceKey = ""
-
-
-aFace <- POST(url=faceURL, 
-          content_type('application/json'),
-          add_headers(.headers = c('Ocp-Apim-Subscription-Key' = faceKey)),
-          body = mybody,
-          encode = 'json')
-
-faceResult=httr::content(aFace, as="text")
-faceResult
-
-
-MicrosoftAPI <- function(img.url){
-  POST(url = faceURL, 
-    content_type('application/json'), 
-    add_headers(.headers = c('Ocp-Apim-Subscription-Key' = faceKey)),
-    body = mybody,
-    encode = 'json'
-  )
-}
-
-#faceTags<-faceResult
-
-getMicrosoft <- function(faceTags){
-  if(length(faceTags[[1]]) > 1){
-    tagdata <- flatten(faceTags[[1]])[,-1]
-  }
-  else{
-    tagdata <- data.frame(label = NA, confirmed = NA, manual = NA, width = NA, height = NA,
-                          yaw = NA, roll = NA, pitch = NA, points = NA, similarities = NA, tid = NA, recognizable = NA,
-                          attributes.face.value = NA, attributes.face.confidence = NA, center.x = NA, center.y = NA,
-                          eye_left.x = NA, eye_left.y = NA, eye_left.confidence = NA, eye_left.id = NA,
-                          eye_right.x = NA, eye_right.y = NA, eye_right.confidence = NA, eye_right.id = NA,
-                          mouth_center.x = NA, mouth_center.y = NA, mouth_center.confidence = NA, mouth_center.id = NA,
-                          nose.x = NA, nose.y = NA, nose.confidence = NA, nose.id = NA)
-  }
-  cbind(file = strsplit(faceTags$photos$url, split = "/")[[1]][length(strsplit(faceTags$photos$url, split = "/")[[1]])], url = faceTags$photos$url, tagdata)
-}
-getMicrosoft(faceResult)
-
-
-

### 2017-04-21 manual.R

@@ -1,2 +1,0 @@
-script.dir <- dirname(sys.frame(1)$ofile)
-print(script.dir)

### 2017-04-21 mergeData.R

@@ -1,142 +1,0 @@
-#Load Packages
-library(imager)
-library(dplyr)
-library(tidyr)
-library(purrr)
-
-#Load Data
-MicrosoftClassifiedFaces <- read.csv("SoftwareRequestScripts/MicrosoftClassifiedFaces.csv")
-AnimetricsClassifiedFaces <- read.csv("SoftwareRequestScripts/AnimetricsClassifiedFaces.csv")
-SkybiometryClassifiedFaces <- read.csv("SoftwareRequestScripts/SkybiometryClassifiedFaces.csv")
-GoogleClassifiedFaces <- read.csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
-ManualClassifiedFaces <- read.csv("ManualClassifiedFaces.csv")
-ManualClassifiedScenes <- read.csv("ManualClassifiedScenes.csv")
-
-#Check all equal length
-#length(unique(ManualClassifiedScenes$file))
-#length(unique(AnimetricsClassifiedFaces$file))
-#length(unique(SkybiometryClassifiedFaces$file))
-#length(unique(GoogleClassifiedFaces$file))
-
-#Remove images with no faces
-MicrosoftClassifiedFaces <- MicrosoftClassifiedFaces[!is.na(MicrosoftClassifiedFaces$faceRectangle.top),]
-AnimetricsClassifiedFaces <- AnimetricsClassifiedFaces[!is.na(AnimetricsClassifiedFaces$topLeftX),]
-SkybiometryClassifiedFaces <- SkybiometryClassifiedFaces[!is.na(SkybiometryClassifiedFaces$width),]
-GoogleClassifiedFaces <- GoogleClassifiedFaces[!is.na(GoogleClassifiedFaces$rollAngle),]
-
-#Manual Classified Faces
-ManualClassifiedFaces <- ManualClassifiedFaces %>%
-  mutate(type = "Manual", time.user.self=NA, time.sys.self=NA, time.elapsed=NA, ID=1:NROW(ManualClassifiedFaces))
-
-#Merge data
-MicrosoftMerge <- MicrosoftClassifiedFaces %>% 
-  mutate(type = "Microsoft", ID=NA,
-         minX = faceRectangle.left, maxX = faceRectangle.left + faceRectangle.width,
-         minY = faceRectangle.top, maxY = faceRectangle.top + faceRectangle.height) %>%
-  dplyr::select(file, type, ID, time.user.self, time.sys.self, time.elapsed, minX, maxX, minY, maxY)  
[…]

### 2017-04-21 regressionWIP.R

@@ -1,178 +1,0 @@
-# Prepare data
-library(tidyverse)
-library(gridExtra)
-library(dplyr)
-
-ALLmetaIMG<-read_csv("ALLmetaIMG.csv",
-                     col_types = cols(type = col_factor(levels = c("Manual", 
-                      "Animetrics", "Google", "Microsoft", "Skybiometry"))))
-
-
-ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
-ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
-ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
-ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
-ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
-
-ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:3, labels = c("Player", "Other staff on court", "Fan", "None"))
-ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
-ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 1:2, labels = c("Shaded", "Partially shaded"))
-ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
-ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
-ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))
-
-
-
-#ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")
-
-# change this to facesVenn with binary information
-ALLmetaIMGFaces<-ALLmetaIMG%>%
[…]

### 2017-04-21 skybiometry.R

@@ -1,90 +1,0 @@
-library(jsonlite) # Adding jsonlite for parsing
-library(imager)
-library(forecast)
-library(httr)
-
-# Starting script for SkyBiometry API
-api_key <- "2411ca5a7294462b9923e6ef7f97eb24"
-api_secret <- "f57d0bc3b0eb427389f6c890700b4749"
-
-# Go to directory with images
-#setwd("~/Courses/mvparrot/data/match_clips/images")
-
-#image_urls <- file.path("http://on-the-t.com/assets/match_images", list.files())
-#image_urls <- grep("RLA.*R07", image_urls, val = TRUE) # Only RLA R07 are posted
-image_urls <- c(
-  "http://mitchelloharawild.com/tennis/2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0003.png",
-  "http://mitchelloharawild.com/tennis/2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0020.png"
-)
-
-request_pattern <- "http://api.skybiometry.com/fc/faces/detect.json?api_key=KEY&api_secret=SECRET&urls=IMAGE"
-
-request_url<-"{http://api.skybiometry.com/fc/faces/detect.json?returnFaceId=false&returnFaceLAndmarks=true}"
-headers<-"add_headers(Content-Type='application/json', Ocp-Apim-Subscription-Key ='2411ca5a7294462b9923e6ef7f97eb24')"
-
-
-httr_request<-POST(request_url, headers, encode = "multipart")
-
-??POST
-
-the_request <- function(url) 
-	sub("IMAGE", url, sub("SECRET", api_secret, sub("KEY", api_key, request_pattern)))
-	
-
-the_request <- Vectorize(the_request)
-
-requests <- the_request(image_urls)
-
-SkyRequest <- lapply(requests, readLines)
-
-
-# Initial parsing attempt
-parse_json <- lapply(SkyRequest, fromJSON)
-# faceTags is the individual photos within SkyRequest
-faceTags <- fromJSON(SkyRequest[[1]])
-faceTags <- fromJSON(SkyRequest[[2]])
-
-faceTags$photos$tags #gives the values without labelled pairs
-faceTags$photos$tags[[1]] #gives the full set of labelled pairs
-
-#create the face box that will be applied
[…]

### 2017-04-21 visualisation.R

@@ -1,56 +1,0 @@
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-
-#Load ALLmetaIMG in (from analysis.R)
-ggplot(ALLmetaIMG, aes(x = type)) + geom_bar(position="dodge")
-
-#NA refers to the boxes which don't match manual (hence we don't have info about the image classification)
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(visorhat)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(glasses)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(shotangle)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(graphic)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(person)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(situation)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(bg)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(detect)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(obscured)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(lighting)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(headangle)), group=type, fill=type)) + geom_bar(position="dodge")
-
-
-## TODO: Proportions of manual classifications.
-a <- ALLmetaIMG %>% filter(matchesManual) %>% group_by(glasses, type) %>% summarise(a=n())
-ggplot(a, aes(x=factor(glasses), y=a, fill=type)) + geom_bar(stat="identity", position = "dodge")
-a$manVal <- rep(c(1344, 186), each=5) # MAKE THIS MORE GENERAL
-b <- a %>% mutate(prop = a/manVal)
-b
[…]

### 2017-04-21 Internship/BEX3012ProjectReport.Rmd
Emotion Distribution Plotting

@@
 GE <- read_csv("data/GoogleFacesEmotions.csv")
+DE <- read_csv("data/DominantEmotion.csv")
 
-EmotionSoftwareSpecs<-read_csv("Figures/EmotionSoftwareSpecifications.csv")
+EmotionSoftwareSpecs <- read_csv("Figures/EmotionSoftwareSpecifications.csv")
 
@@
 ```{r}
-
 #Create normalised GE values
@@
 
-```{r VisualSet, echo=F, fig.cap = "Here are six examples of Faces in the image set after extracting faces from the full broadcast video stills. \\label{tab:VisualSet}"}
+```{r VisualSet, echo=F, fig.cap = "Three Faces in the image set, after extracting faces from the full broadcast video stills, and the dominant emotion each software recognised for them.
+\\label{fig:VisualSet}"}
 
@@
     p <- ggplot(data.frame(x=c(0,350), y=c(0,350)), aes(x,y))+
-      theme_classic() + xlab("") + ylab("") + 
+      theme_void() + 
       annotation_custom(rasterGrob(img)) +
@@
 
-f1 <- plotFaces("face-1635-1-Go.png")
-f2 <- plotFaces("face-1128-1-Go.png")
-f3 <- plotFaces("face-1746-1-Go.png")
-f4 <- plotFaces("face-626-1-Go.png")
-f5 <- plotFaces("face-450-1-Go.png")
-f6 <- plotFaces("face-816-1-Go.png")
+TableEmotions <- function(imgList){
+  for(i in imgList){
 
-grid.arrange(f1, f2, f3, f4, f5, f6,nrow=2)
+   d <- DE %>% filter(FileName== i)
+
+  dl <- d %>% 
+  select(Skybiometry = SEmotion, Microsoft = MEmotion, Google = GEmotion) %>%
+    gather(key = Software, value = Emotion, Microsoft, Skybiometry, Google)
+
+  t <- tableGrob(dl, theme = ttheme_minimal(), rows = c("", "", ""))
+
+  } 
+  return(t)
+  }
+
+#Faces 
+f1 <- "face-1635-1-Go.png"
+f2 <- "face-1128-1-Go.png"
+f3 <- "face-1746-1-Go.png"
+
+i1 <- plotFaces(f1)
+i2 <- plotFaces(f2)
+i3 <- plotFaces(f3)
+
+# Tables of their resulting emotion value
+t1 <- TableEmotions(f1)
+t2 <- TableEmotions(f2)
+t3 <- TableEmotions(f3)
+
+#f4 <- "face-626-1-Go.png"
+#f5 <- "face-450-1-Go.png"
+#f6 <- "face-816-1-Go.png"
+
+grid.arrange(i1, i2, i3, t1, t2, t3, nrow=2)
 
@@
 
-We will consider three Emotion Recognition software.
+We have considered three Emotion Recognition APIS.
+They were chosen for their accessibility and online reviews, as these are well recognised options for Facial recongition currently available.
 
@@
 
-As can be seen above, a noticeable difference between the three is the amount of times the API can be called.
-Skybiometry had the largest imposition on Bath Processing as it only allowed 100 API calls to be processed per hour.
-Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within an hour, after accounting for the wait time between each group of 20.
-Google Vision's API batch processing limit had a minimal effect.
+As can be seen above, a noticeable difference between the three is the amount of times the API can be called within a given time frame.
+Skybiometry had the largest imposition on Call Limits as it only allowed 100 API calls to be processed per hour.
+Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within one hour, after accounting for the wait time between each group of 20.
+Google Vision's API call limit had a minimal effect for our purposes.
 
-The range of outputs from the software is displayed as Google provides likelihoods of an emotion occurring on a particular face.
-Microsoft and Skybiometry provide outputs on the same emotions^[Based on Paul Ekmans emotion theories].
-However the values that they provide differ as Microsoft provide Proportions whereas Skybiometry results in a Confidence of the emotion occurring in the specified face.
+The number of emotions shown in the results were not congruent. These differences required pre processing to find the most comparable results for analysis.
+Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only giving the options for four different emotions.
+
+The outputs from the APIs were very different.
+Google provides likelihoods of an emotion occurring on a particular face in categorical options ranging from Very Unlikely to Very Likely.
+Microsoft provide Proportions, ranging between 0 and , whereas Skybiometry results in a Confidence of the emotion occurring in the specified face in values from 0 to 100.
 
@@
 ```{r MEexample, echo=F, message=F, fig.cap = "\\label{tab:MEexample}"}
-library(dplyr)
+
 MEexample <- ME %>% subset(FileName=="face-1745-1-Go.png")

### 2017-04-21 Internship/EmotionsAnalysis.Rmd
Emotion Distribution Plotting

@@
 
-```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, cache=T)
@@
 
-```{r}
+```{r readdata}
 #EmoM <-read_csv("data/EmotionsMerged.csv")
@@
 SB <- read_csv("data/SkybiometryEmotions.csv")
-GE <- read_csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
+GE <- read_csv("data/GoogleFacesEmotions.csv")
 GF <- read_csv("data/GoogleFaces.csv")
@@
 
+#Create column for Player Names
+#GF$PlayerNumber<-NA
+
+# PlayerSubset <- function(PlayerName, data = GF1) {
+#   
+#   PlayerSet<-filter(data, player1==PlayerName | player2==PlayerName)
+#   
+#   return(as.list(PlayerSet$FileName))
+# }
+
+# 
+# MSlist <- PlayerSubset("MSakkari")
+# MSlist
+
+GF <- GF %>% rowwise %>%
+  mutate(playerName = ifelse(PlayerNumber == 1, player1,
+                                            ifelse(PlayerNumber == 2, player2,
+                                                   ifelse(is.na(PlayerNumber), NA, NA))))
+
+GE <- GE %>% rowwise %>%
+  mutate(playerName = ifelse(PlayerNumber == 1, player1,
+                                            ifelse(PlayerNumber == 2, player2,
+                                                   ifelse(is.na(PlayerNumber), NA, NA))))
+
 ```
@@
 Connect face id to original Google set
-```{r}
-GEsub <- GE[,c(1, 10:13, 17:24)]
-
-GE1 <- GEsub %>% 
-  rowwise() %>%
-  mutate(minX = pmin(cbind(boundingPoly.x1, boundingPoly.x4)), 
-         maxX = pmin(cbind(boundingPoly.x2, boundingPoly.x3)),
-         minY = pmin(cbind(boundingPoly.y1, boundingPoly.y2)), 
-         maxY = pmin(cbind(boundingPoly.y3, boundingPoly.y4))) %>%
-  ungroup()
-
-GE1 <- GE1[,c(1:5, 14:17)]
+```{r googleSubset}
+# GEsub <- GE[,c(1, 10:13, 17:24)]
+# 
+# GE1 <- GEsub %>% 
+#   rowwise() %>%
+#   mutate(minX = pmin(cbind(boundingPoly.x1, boundingPoly.x4)), 
+#          maxX = pmin(cbind(boundingPoly.x2, boundingPoly.x3)),
+#          minY = pmin(cbind(boundingPoly.y1, boundingPoly.y2)), 
+#          maxY = pmin(cbind(boundingPoly.y3, boundingPoly.y4))) %>%
+#   ungroup()
+# 
+# GE1 <- GE1[,c(1:5, 14:17)]
 ```
@@
 Add meta data to Emotion results
-```{r}
-GE <- left_join(GF, GE1, by = c("file","minX","maxX","minY","maxY"))
+```{r mergeEmotMeta}
+#GE <- left_join(GF, GE1, by = c("file","minX","maxX","minY","maxY"))
 
@@
 Create normalized SB values
-```{r}
+```{r normaliseSB}
 SB<-SB %>%
@@
 
-```{r}
+```{r normaliseGE}
 Conf <- function(Emot){
@@
 
-```{r}
+```{r TFemotions}
 
@@
 
-Parallel coordinate plots
-```{r}
-#p1 <- ggparcoord(data = set1, columns = 2:9, groupColumn="file", order = "allClass")
-
-#p2 <- ggparcoord(data = set2, columns = 2:9, groupColumn="file", order = "allClass")
-
-#p3 <- ggparcoord(data = set3, columns = 2:9, groupColumn="file", order = "allClass")
-```
-
 Consider just players,
@@
 SBP: Google's results, emotion data for only players
-```{r}
+```{r playerSubset}
 GEP <- GE %>% filter(detect=="Player")
@@
 
-```{r}
+```{r SBhists}
 
-ggSBPne <- ggplot(SBP, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggSBne <- ggplot(SB, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-
-ggSBPan <- ggplot(SBP, aes(x=anger))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggSBPdi <- ggplot(SBP, aes(x=disgust))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggSBPfe <- ggplot(SBP, aes(x=fear))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggSBPha <- ggplot(SBP, aes(x=happiness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggSBPsa <- ggplot(SBP, aes(x=sadness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggSBPsu <- ggplot(SBP, aes(x=surprise))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
+ggSBPne <- ggplot(SBP, aes(x=neutral))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggSBPan <- ggplot(SBP, aes(x=anger))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggSBPdi <- ggplot(SBP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggSBPfe <- ggplot(SBP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggSBPha <- ggplot(SBP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggSBPsa <- ggplot(SBP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggSBPsu <- ggplot(SBP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
 
@@
              ggSBPsu, nrow=3)
-
 ```
@@
 ```{r}
-ggMEPne<-ggplot(MEP, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggMEPan<-ggplot(MEP, aes(x=anger))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggMEPdi<-ggplot(MEP, aes(x=disgust))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggMEPfe<-ggplot(MEP, aes(x=fear))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggMEPha<-ggplot(MEP, aes(x=happiness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggMEPsa<-ggplot(MEP, aes(x=sadness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
-ggMEPsu<-ggplot(MEP, aes(x=surprise))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
+ggMEPne<-ggplot(MEP, aes(x=neutral)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
+ggMEPan<-ggplot(MEP, aes(x=anger)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
+ggMEPdi<-ggplot(MEP, aes(x=disgust)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
+ggMEPfe<-ggplot(MEP, aes(x=fear)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
+ggMEPha<-ggplot(MEP, aes(x=happiness)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
+ggMEPsa<-ggplot(MEP, aes(x=sadness)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
+ggMEPsu<-ggplot(MEP, aes(x=surprise)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
 
@@
 Join emotions for each face
+J2: Table of FileNames and associated dominant emotion
 ```{r}
@@
 
-J2L<-J2 %>% 
+J2L <- J2 %>% 
   gather(key = Software, value = Emotion, SEmotion, MEmotion, GEmotion)
@@
 
-SER<-read_csv("SampleEmotionResults.csv")
+SER<-read_csv("Figures/SampleEmotionResults.csv")
 
@@
 Player Subsetting
-```{r}
-#Create column for Player Names
-#GoogleFaces$PlayerName<-NA
-
-# PlayerSubset <- function(PlayerName, data = GF1) {
-#   
-#   PlayerSet<-filter(data, player1==PlayerName | player2==PlayerName)
-#   
-#   return(as.list(PlayerSet$FileName))
-# }
-
-# 
-# MSlist <- PlayerSubset("MSakkari")
-# MSlist
+```{r DisplayFaces}
 
@@
 Player Emotion Tables
+Distribution of emotion values for particular emotions across all images of a player
+```{r Playerhists}
+ggplot(na.omit(SBP), aes(x=playerName))+geom_bar()+ theme(axis.text.x = element_text(angle = 20))
+
+Name <- "GSimon"
+
+  SBPplayer <- SBP %>% filter(playerName == Name)
+
+  ggSBPan <- 
+    ggplot(SBPplayer, aes(x = anger)) + ggtitle("Skybiometry") +
+    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))
+
+  GEPplayer <- GEP %>% filter(playerName == Name)
+
+  ggGEPan <-
+    ggplot(GEPplayer, aes(x = anger)) +  ggtitle("Google") +
+    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))
+
+  MEPplayer <- MEP %>% filter(playerName == Name)
+
+  ggMEPan <-
+    ggplot(MEPplayer, aes(x = anger)) +  ggtitle("Microsoft") +
+    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))
+
+grid.arrange(ggMEPan,ggSBPan,ggGEPan, nrow = 3)
+
+TB<- as.list(MEPplayer$FileName)
+DisplayFaces(TB)
+```

### 2017-04-24 Internship/BEX3012ProjectReport.Rmd
Report cache change
Additions to BEXreport
structure, processing sections

@@
 
-```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE)
+```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE, fig.width = 8)
 
 library(tidyverse)
+library(dplyr)
 library(readr)
 library(GGally)
+library(magick)
+library(grid)
+library(gridExtra)
+library(ggplot2)
 
@@
 EmotionSoftwareSpecs <- read_csv("Figures/EmotionSoftwareSpecifications.csv")
+```
 
+```{r normalise, cache=FALSE}
 #Create normalised SB values
@@
 
-```
-
-```{r}
 #Create normalised GE values
@@
 }
+```
 
+```{r mutate}
+#confidence columns
 GE <- GE %>% mutate(joyConf = Conf(joyLikelihood)) %>%
@@
 
+#proportion columns
 GE <- GE %>%
@@
 
+#player name column
+GE <- GE %>% rowwise %>%
+  mutate(playerName = ifelse(PlayerNumber == 1, player1,
+                                            ifelse(PlayerNumber == 2, player2,
+                                                   ifelse(is.na(PlayerNumber), NA, NA))))
+```
+
+```{r playerSubset}
+GEP <- GE %>% filter(detect == "Player")
+MEP <- ME %>% filter(detect == "Player")
+SBP <- SB %>% filter(detect == "Player")
 ```
@@
 \newpage
-
 # Introduction
@@
 
-# Method
+# Materials
 
-## Materials
+## Images
 
-### Pre Processing Images
+The image set contained 6406 still shot 800x450px size video frames, taken every 3 seconds from 5 minute segments sampled from 105 Australian Open 2016 match broadcast videos.
+The broadcast videos are a combination of multiple camera feeds, these angles vary depending on the court the match was played on.
 
-A subset of faces was created specifically for emotion recognition purposes.
-To present only a single face to each software required cropping the region of the image based on Google’s bounding box result^[coordinates derived from prior study].
-Each new image created contained the area within the face bounding boxes found in the previous study, as well as a small border to frame the face.
-This resulted in images of differing sizes to be passed to the APIs.
-These 1319 new images were hosted on Google Drive to allow for URL access from the API to the individual images.
+```{r ExampleImage, echo=F, fig.cap = "Example Image: 2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0020.png\\label{fig:ExampleImage}"}
+
+img <- image_read("Figures/2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0020.png")
+
+p <- ggplot() + theme_void() + annotation_custom(rasterGrob(img)) +
+      coord_cartesian(xlim=c(0, 800), ylim=c(0,450))
+p
+```
+
+## Software APIs
+
+Three emotion recognition APIS were considered.
+They were chosen for their accessibility and online reviews of their performance, and these are well recognised options for Facial recognition currently available.
+
+```{r Emotion-Software-Specs-Table, echo=F, fig.cap = "\\label{tab:Emotion-Software-Specs-Table}"}
+
+knitr::kable(EmotionSoftwareSpecs, longtable=TRUE, booktabs = TRUE, caption="This details the capabilities we considered important in recognising emotions in images of faces.")
+```
+
+As can be seen above, a noticeable difference between the three is the amount of times the API can be called within a given time frame.
+Skybiometry had the largest imposition on Call Limits as it only allowed 100 API calls to be processed per hour.
+Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within one hour, after accounting for the wait time between each group of 20.
+Google Vision's API call limit had a minimal effect for our purposes.
+
+The number of emotions shown in the results were not congruent. These differences made it necessary to pre process the result to provide the most comparable results for analysis.
+Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only giving the options for four different emotions.
+
+The outputs from the APIs were very different.
+Google provides likelihoods of an emotion occurring on a particular face in categorical options ranging from Very Unlikely to Very Likely.
+Microsoft provide Proportions, ranging between 0 and , whereas Skybiometry results in a Confidence of the emotion occurring in the specified face in values from 0 to 100.
+
+\newpage
+# Procedure
+
+## Process Images
+
+The original image set was subset to create images of faces specifically suited for emotion recognition purposes. 
+A crop was performed to create a new image that focused on the area marked as a face by Google^[based on Google’s bounding box coordinates].
+A border to frame the face was also included for visual appeal.
+These 1319 new images, of varying sizes, were hosted on Google Drive to allow for URL access from the API to the individual images.
 
@@
 \\label{fig:VisualSet}"}
-
-library(magick)
-library(grid)
-library(gridExtra)
-library(ggplot2)
 
@@
 
-  t <- tableGrob(dl, theme = ttheme_minimal(), rows = c("", "", ""))
+  t <- tableGrob(dl, theme = ttheme_minimal(core=list(fg_params=list(hjust=0, x=0.1)),
+                      rowhead=list(fg_params=list(hjust=0, x=0))), rows = c("", "", ""))
 
@@
 
-\newpage
+## Process API results
 
-### Software APIs
+The results extracted from each of the APIs differed, re configuring of these results was needed to create comparable sets for analysis.
 
-We have considered three Emotion Recognition APIS.
-They were chosen for their accessibility and online reviews, as these are well recognised options for Facial recongition currently available.
-
-```{r Emotion-Software-Specs-Table, echo=F, fig.cap = "\\label{tab:Emotion-Software-Specs-Table}"}
-
-knitr::kable(EmotionSoftwareSpecs, longtable=TRUE, booktabs = TRUE, caption="This details the capabilities we considered important in recognising emotions in images of faces.")
-```
-
-As can be seen above, a noticeable difference between the three is the amount of times the API can be called within a given time frame.
-Skybiometry had the largest imposition on Call Limits as it only allowed 100 API calls to be processed per hour.
-Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within one hour, after accounting for the wait time between each group of 20.
-Google Vision's API call limit had a minimal effect for our purposes.
-
-The number of emotions shown in the results were not congruent. These differences required pre processing to find the most comparable results for analysis.
-Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only giving the options for four different emotions.
-
-The outputs from the APIs were very different.
-Google provides likelihoods of an emotion occurring on a particular face in categorical options ranging from Very Unlikely to Very Likely.
-Microsoft provide Proportions, ranging between 0 and , whereas Skybiometry results in a Confidence of the emotion occurring in the specified face in values from 0 to 100.
-
-### Processing API results
-
-As the results provided by each of the software differed, processing was needed to create comparable sets.
-
-#### Microsoft
+Microsoft provided a POST request object in a JSON format. 
+This was easily formatted to create a data set of the eight numeric emotion values provided for each face.
+In the event that emotion values were not returned for a certain face, NAs were presented in the data set.
 
@@
 
-knitr::kable(MEexample[2:9], digits=6, longtable=TRUE, booktabs = TRUE, caption="The Microsoft API provided 8 numerical values, one for each emotion.")
+knitr::kable(MEexample[2:9], digits=6, longtable=TRUE, booktabs = TRUE, caption="The Microsoft API provided eight numerical values, one for each emotion.")
 ```
 
-#### Skybiometry
+Skybiometry as provided a POST request object in a JSON format.
+However, unlike Microsoft, the results included a True or False Value for each of the seven emotions and a confidence level   'confidence value as a percentage from 0 to 100'^[https://skybiometry.com/documentation/#document-21] representing the confidence of the emotion being present on a player's face.
 
 ```{r SBexample, echo=F, fig.cap = "\\label{tab:SBexample}"}
+
 SBexample <- SB %>% subset(aname=="face-1745-1-Go.png") %>% select(ends_with(".confidence"))
@@
                            "happiness", "sadness", "surprise"),
-             caption="The Skybiometry API provided 7 numerical Confidence values, one for each emotion.")
+             caption="The Skybiometry API provided seven numerical Confidence values, one for each emotion.")
 ```
 
-#### Google
+The process undertaken to receive results Google produces was the same as the previous APIs.
+However rather than numeric values, it returned categorical likelihoods for the four emotions it considered.
 
@@
 These differing outputs needed to be arranged in a comparable manner.
-We began by considering the Microsoft output.
-Noticing that the sums of all emotion values was approximately one we considered that dividing the individual Skybiometry emotion confidences by the sum of the confidences would give the likelihood of each emotion being the dominant emotion in a face.
+Noticing that the sums of the individual emotions for each face in the Microsoft results was approximately one provided the basis for transformation for the other APIs.
+Dividing the individual Skybiometry emotion confidences by the sum of the confidences would give the proportional likelihood of each emotion being the dominant emotion in a face.
 
@@
 
-We then needed to transform the Google output to also be comparable. This was the most challenging due to it's unusual form.
+Google's results then required a more complex transformation for the output to also be comparable.
 
-A numeric value was assigned to each possible likelihood value. This would allow for numeric comparisons to be made.
+As there were five possible categories assigned to each emotion the numeric values were chosen to sit in the middle of five 20 point ranges.
+This allowed a numerical representation of each possible likelihood value and would allow for numeric comparisons to be made.
 The values were assigned according to the table below:
@@
 
-knitr::kable(LT, longtable=TRUE, booktabs = TRUE,
-               caption="")
-
+knitr::kable(LT, longtable=TRUE, booktabs = TRUE, caption="")
 ```
 
-As both Microsoft and Skybiometry included a neutral category we considered how we may incorporate this for the Google results.
-
-Google Transformed
+As both Microsoft and Skybiometry included a neutral category we considered how to incorporate a neutral category for the Google results.
 
 Our approach considered that when a face was "very unlikely" to be any of the four emotion categories it could be deemed "neutral".
-However when one emotion was stronger than other it could still be possible that the face only had a small lean toward this emotion.
-Therefore the Confidence value for neutral was derived as:
+However when one emotion was stronger than other it could still be possible that the face only had a small lean toward this emotion and it may not be the obvious choice.
+Therefore the Confidence value for neutral was calculated according to the formula below:
 
@@
 
-The process to derive the numeric values followed the process undertaken for Skybiometry values.
+The process to derive the numeric values for Google followed the process undertaken for Skybiometry values.
 Where the individual emotion confidences were divided by the sum of the emotion confidence values for each face.
-
-This resulted in congruent emotion data to be compared
+This resulted in congruent emotion data.
 
@@
 
-GET <- GE %>% subset(FileName=="face-1745-1-Go.png") %>% 
+GET <- GEP %>% subset(FileName=="face-1745-1-Go.png") %>% 
   select(joy, sorrow, anger, surprise, neutral)
@@
 
+\newpage
 # Analysis
+
+Each API returned a different amount of non null results.
+Microsoft produced emotion results for `r sum(!is.na(ME$anger))` faces.
+This was more than Skybiometry, as it produced only `r sum(!is.na(SB$anger))` results for emotions on faces.
+Google provided the most, with  `r sum(!is.na(GE$anger))` emotion results^[As the initial set was faces identified by Google there is the possibility of bias toward being able to identify emotions in faces it was able to find originally.].
+
+```{r GEPhists}
+gganG <- ggplot(GEP, aes(x=anger))+geom_histogram(binwidth=0.055)+
+  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
+ggjoG <- ggplot(GEP, aes(x=joy))+geom_histogram(binwidth=0.055) +
+  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
+ggneG <- ggplot(GEP, aes(x=neutral))+geom_histogram(binwidth=0.055) +
+  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
+ggsoG <- ggplot(GEP, aes(x=sorrow))+geom_histogram(binwidth=0.055) +
+  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
+ggsuG <- ggplot(GEP, aes(x=surprise))+geom_histogram(binwidth=0.055) +
+  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
+
+grid.arrange(gganG,ggjoG,ggneG,ggsoG,ggsuG,nrow=2,
+             top=textGrob("Google Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))
+
+```
+
+```{r SBPhists}
+gganS <- ggplot(SBP, aes(x=anger))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+gghaS <- ggplot(SBP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggneS <- ggplot(SBP, aes(x=neutral))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggsaS <- ggplot(SBP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggsuS <- ggplot(SBP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggdiS <- ggplot(SBP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggfeS <- ggplot(SBP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+
+grid.arrange(gganS, gghaS, ggneS, ggsaS, ggsuS, ggdiS, ggfeS,nrow=3,
+             top=textGrob("Skybiometryh Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))
+
+```
+
+```{r MEPhists}
+gganM <- ggplot(MEP, aes(x=anger))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+gghaM <- ggplot(MEP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggneM <- ggplot(MEP, aes(x=neutral))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggsaM <- ggplot(MEP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggsuM <- ggplot(MEP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggdiM <- ggplot(MEP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggfeM <- ggplot(MEP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+ggcoM <- ggplot(MEP, aes(x=contempt))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+
+grid.arrange(gganM, gghaM, ggneM, ggsaM, ggsuM, ggdiM, ggfeM, ggcoM,nrow=3, 
+             top=textGrob("Microsoft Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))
+
+```
+
+\newpage
 # Validation

### 2017-04-24 Internship/EmotionsAnalysis.Rmd
Additions to BEXreport
structure, processing sections

@@
 ```{r SBhists}
+plotSBHists<-function(data) {
+ggne <- ggplot(data, aes(x=neutral))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggan <- ggplot(data, aes(x=anger))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggdi <- ggplot(data, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggfe <- ggplot(data, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggha <- ggplot(data, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggsa <- ggplot(data, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+ggsu <- ggplot(data, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
 
-ggSBPne <- ggplot(SBP, aes(x=neutral))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
-ggSBPan <- ggplot(SBP, aes(x=anger))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
-ggSBPdi <- ggplot(SBP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
-ggSBPfe <- ggplot(SBP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
-ggSBPha <- ggplot(SBP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
-ggSBPsa <- ggplot(SBP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
-ggSBPsu <- ggplot(SBP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+grid.arrange(ggne,ggan,ggdi,ggfe,ggha,ggsa,ggsu,nrow=3)
+}
 
-grid.arrange(ggSBPne,
-             ggSBPan,
-             ggSBPdi,
-             ggSBPfe,
-             ggSBPha,
-             ggSBPsa,
-             ggSBPsu, nrow=3)
+plotEmotion<-function(data, Emotion) {
+ggEmot <- ggplot(data, aes_string(x=Emotion))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
+}
+
 ```
@@
 SBPCL: Long form of Confidence levels of SB results
-```{r}
+```{r SBPlong}
 SBPCL <- SBP %>% group_by(aname) %>% 
@@
 GEPN:  Long form of Confidence levels of GE results renamed to match
-```{r}
+```{r GEPlong}
 #rename
@@
 Microsoft Emotion plots
-```{r}
+```{r MEhists}
+plotMEHists<-function(data) {
 ggMEPne<-ggplot(MEP, aes(x=neutral)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
@@
 ggMEPsu<-ggplot(MEP, aes(x=surprise)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
+ggMEPco<-ggplot(MEP, aes(x=contempt)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
 
@@
              ggMEPsa,
-             ggMEPsu, nrow=3)
+             ggMEPsu, 
+             ggMEPco,nrow=3)
+}
 
@@
 MEPCL: Long form of Confidence levels of ME results
-```{r}
+```{r MElong}
 MEPCL<-MEP %>% group_by(FileName) %>% 
@@
 J2: Table of FileNames and associated dominant emotion
-```{r}
+```{r combined}
 S1 <- select(SBPCL1, FileName = aname , SEmotion = Emotion)
@@
 
-```{r}
+```{r table}
 set.seed(300)
@@
 Find images from matches played by certain players
-```{r}
+```{r playerMatches}
 a <- as.data.frame(table(GEP$player1))
@@
 subset of Google where neutral = another category
-```{r}
+```{r GoogleNeutral}
 neutrals <- GEPCL1 %>% filter(neutralConf==joyConf | 
@@
 It is hard to classify many of the faces as one of the seven possible options. Where hints of emotive expressions can be attributed to one or more faces
-```{r}
+```{r EmotiveFaces}
 
@@
 Distribution of emotion values for particular emotions across all images of a player
-```{r Playerhists}
+```{r PlayerHists}
 ggplot(na.omit(SBP), aes(x=playerName))+geom_bar()+ theme(axis.text.x = element_text(angle = 20))
@@
 
+EmotionHists <- function(Emotion, Name){
+
   SBPplayer <- SBP %>% filter(playerName == Name)
@@
   ggSBPan <- 
-    ggplot(SBPplayer, aes(x = anger)) + ggtitle("Skybiometry") +
+    ggplot(SBPplayer, aes_string(x = Emotion)) + ggtitle("Skybiometry") +
     geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))
 
-  GEPplayer <- GEP %>% filter(playerName == Name)
+  GEPplayer <- GEPN %>% filter(playerName == Name)
 
   ggGEPan <-
-    ggplot(GEPplayer, aes(x = anger)) +  ggtitle("Google") +
+    ggplot(GEPplayer, aes_string(x = Emotion)) +  ggtitle("Google") +
     geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))
@@
   ggMEPan <-
-    ggplot(MEPplayer, aes(x = anger)) +  ggtitle("Microsoft") +
+    ggplot(MEPplayer, aes_string(x = Emotion)) +  ggtitle("Microsoft") +
     geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))
@@
 grid.arrange(ggMEPan,ggSBPan,ggGEPan, nrow = 3) 
+}
 
-TB<- as.list(MEPplayer$FileName)
-DisplayFaces(TB)
+EmotionHists(Emotion = "anger", "GSimon")
+EmotionHists(Emotion = "surprise", "GSimon")
+EmotionHists(Emotion = "happiness", "GSimon")
+EmotionHists(Emotion = "sadness", "GSimon")
+
 ```
+
+Neutrality in Faces
+```{r}
+sum(MEPCL1$Emotion=="neutral")/nrow(MEPCL1)
+sum(SBPCL1$Emotion=="neutral")/nrow(SBPCL1)
+sum(GEPCL1$Emotion=="neutral")/nrow(GEPCL1)
+
+nrow(MEPCL1)-sum(MEPCL1$Emotion=="neutral")
+nrow(SBPCL1)-sum(SBPCL1$Emotion=="neutral")
+nrow(GEPCL1)-sum(GEPCL1$Emotion=="neutral")
+
+```
+
+Pairwise comparison of neutral overlaps
+```{r neutrality}
+J2ne<-J2 %>% rowwise() %>%
+  mutate(SEneutral = ifelse(SEmotion=="neutral", "neutral","non-neutral")) %>%
+  mutate(MEneutral = ifelse(MEmotion=="neutral", "neutral","non-neutral")) %>%
+  mutate(GEneutral = ifelse(GEmotion=="neutral", "neutral","non-neutral"))
+
+S4 <- select(SBP, FileName = aname, Skybiometry = neutral)
+S5 <- select(MEP, FileName, Microsoft = neutral)
+S6 <- select(GEP, FileName, Google = neutral)
+J3 <- full_join(S4, S5, by = "FileName")
+J4 <- full_join(J3, S6, by = "FileName")
+
+J4 <- J4 %>% rowwise %>% mutate(GoogleJitter = jitter(Google))
+
+library(GGally)
+ggscatmat(as.data.frame(na.omit(J4[,c(2:3,5)])))
+
+table(J2ne$MEmotion, J2$GEmotion)
+table(J2ne$MEneutral, J2ne$GEneutral)
+```
+
+Bar chart of attributes for neutral categorisations
+Need to consider that higher levels of values across the population may create misleading plots.
+
+```{r}
+Gneutral <- GEPCL1 %>% filter(Emotion=="neutral")
+Mneutral <- MEPCL1 %>% filter(Emotion=="neutral")
+Sneutral <- SBPCL1 %>% filter(Emotion=="neutral")
+
+NeutralBars <- function(Attribute){
+
+  ggSBPne <- 
+    ggplot(Sneutral, aes_string(x = Attribute)) + ggtitle("Skybiometry") +
+    geom_bar()
+
+  ggGEPne <-
+    ggplot(Gneutral, aes_string(x = Attribute)) + ggtitle("Google") +
+    geom_bar()
+
+  ggMEPne <-
+    ggplot(Mneutral, aes_string(x = Attribute)) + ggtitle("Microsoft") +
+    geom_bar()
+
+grid.arrange(ggMEPne,ggSBPne,ggGEPne, nrow = 3) 
+}
+
+NeutralBars(Attribute = "bg")
+```

### 2017-04-26 Internship/BEX3012ProjectReport.Rmd
Cross Tables added to report

@@
 fig_caption: yes
+out_width: 7
 fontsize: 11pt
@@
 ```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE, fig.width = 8)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE)
 
@@
 GE <- read_csv("data/GoogleFacesEmotions.csv")
+GF <- read_csv("data/GoogleFaces.csv")
 DE <- read_csv("data/DominantEmotion.csv")
+# 
+# MEP <- read_csv("data/MicrosoftEmotions.csv")
+# SBP <- read_csv("data/SkybiometryEmotions.csv")
+# GEP <- read_csv("data/GoogleFacesEmotions.csv")
 
@@
 
+```{r join}
+ME <- left_join(ME, GF, by = "FileName") 
+SB <- left_join(SB, GF, by = c("aname"="FileName")) 
+```
+
 ```{r playerSubset}
-GEP <- GE %>% filter(detect == "Player")
-MEP <- ME %>% filter(detect == "Player")
-SBP <- SB %>% filter(detect == "Player")
+library(dplyr)
+GEP <- GE %>% dplyr::filter(detect == "Player")
+MEP <- ME %>% dplyr::filter(detect == "Player")
+SBP <- SB %>% dplyr::filter(detect == "Player")
+```
+
+```{r NeutralProportions}
+S4 <- select(SBP, FileName = aname, Skybiometry = neutral)
+S5 <- select(MEP, FileName, Microsoft = neutral)
+S6 <- select(GEP, FileName, Google = neutral)
+J3 <- full_join(S4, S5, by = "FileName")
+J4 <- full_join(J3, S6, by = "FileName")
 ```
@@
 
-```{r GEPhists}
-gganG <- ggplot(GEP, aes(x=anger))+geom_histogram(binwidth=0.055)+
-  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
-ggjoG <- ggplot(GEP, aes(x=joy))+geom_histogram(binwidth=0.055) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
-ggneG <- ggplot(GEP, aes(x=neutral))+geom_histogram(binwidth=0.055) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
-ggsoG <- ggplot(GEP, aes(x=sorrow))+geom_histogram(binwidth=0.055) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
-ggsuG <- ggplot(GEP, aes(x=surprise))+geom_histogram(binwidth=0.055) +
-  coord_cartesian(xlim = c(0, 1), ylim = c(0,800))
+```{r NonNullFaces, fig.cap = "\\label{fig:NonNullFaces}", results = 'asis'}
+
+J4 <-J4 %>% rowwise() %>%
+  mutate(Gna = ifelse(!is.na(Google), TRUE, FALSE)) %>%
+  mutate(Sna = ifelse(!is.na(Skybiometry), TRUE, FALSE)) %>%
+  mutate(Mna = ifelse(!is.na(Microsoft), TRUE, FALSE))
+
+nfft<-ftable(J4$Gna, J4$Mna, J4$Sna, dnn = c("Google", "Microsoft", "Skybiometry"))
+
+library(stargazer)
+stargazer(format(nfft, quote=FALSE, justify="right"),title = "Emotion results were found by all three APIs for 364 common faces, none of the APIs produced results for 10 player faces.
+Google was able to produce 382 results that Skybiometry and Microoft did not.", header=FALSE, type="latex")
+```
+
+### Emotion Proportion Distributions
+For the following distributions only the faces of players were considered.
+
+```{r GEPhists, fig.cap = "It can be seen that there are significant proportions of faces where the non neutral emotions occur close to zero.
+This is balanced by the large percentage, over 75%, where the neutral value of just under .75 occurred.
+The faces used showed higher levels of Joy than any other non neutral emotion as the percentage occuring at zero was less than the percentages of the other emotions.\\label{fig:GEPhists}"}
+gganG <- ggplot(GEP, aes(x=anger)) + 
+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+ggjoG <- ggplot(GEP, aes(x=joy)) + 
+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+ggneG <- ggplot(GEP, aes(x=neutral)) + 
+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+ggsoG <- ggplot(GEP, aes(x=sorrow)) + 
+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+ggsuG <- ggplot(GEP, aes(x=surprise)) + 
+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
 
 grid.arrange(gganG,ggjoG,ggneG,ggsoG,ggsuG,nrow=2,
-             top=textGrob("Google Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))
+             top=textGrob("Google Distribution of Emotion Porportions",
+             gp=gpar(fontsize=20,font=3)), 
+             left = ("Percentage of Emotion values"))
 
@@
 
-```{r SBPhists}
-gganS <- ggplot(SBP, aes(x=anger))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-gghaS <- ggplot(SBP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggneS <- ggplot(SBP, aes(x=neutral))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggsaS <- ggplot(SBP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggsuS <- ggplot(SBP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggdiS <- ggplot(SBP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggfeS <- ggplot(SBP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+```{r SBPhists, fig.cap = "The distributions show that over 70% of faces had levels of happiness and neutrality at, or close to, 0.
+The distributions show that there are very little faces with specific emotion levels above 50%.
+Instead there are low levels of all emotions found on many faces.
+\\label{fig:SBPhists}"}
+gganS <- ggplot(SBP, aes(x=anger))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+gghaS <- ggplot(SBP, aes(x=happiness))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggneS <- ggplot(SBP, aes(x=neutral))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggsaS <- ggplot(SBP, aes(x=sadness))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggsuS <- ggplot(SBP, aes(x=surprise))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggdiS <- ggplot(SBP, aes(x=disgust))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggfeS <- ggplot(SBP, aes(x=fear))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
 
 grid.arrange(gganS, gghaS, ggneS, ggsaS, ggsuS, ggdiS, ggfeS,nrow=3,
-             top=textGrob("Skybiometryh Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))
+             top=textGrob("Skybiometry Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)), 
+             left = ("Percentage of Emotion values"))
 
@@
 
-```{r MEPhists}
-gganM <- ggplot(MEP, aes(x=anger))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-gghaM <- ggplot(MEP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggneM <- ggplot(MEP, aes(x=neutral))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggsaM <- ggplot(MEP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggsuM <- ggplot(MEP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggdiM <- ggplot(MEP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggfeM <- ggplot(MEP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
-ggcoM <- ggplot(MEP, aes(x=contempt))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,500))
+```{r MEPhists, fig.cap="Unlike the previous two softwares, there were many faces that returned high neutral values.
+This is matched by the high percentages of faces where the proportion levels were at, or close to, zero.
+While the happiness emotion was most varied, with values between 0 and 1, over 40% of faces returned surprise levels above zero.\\label{fig:MEPhists}"}
+
+gganM <- ggplot(MEP, aes(x=anger)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+gghaM <- ggplot(MEP, aes(x=happiness)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggneM <- ggplot(MEP, aes(x=neutral)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggsaM <- ggplot(MEP, aes (x=sadness)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggsuM <- ggplot(MEP, aes(x=surprise)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggdiM <- ggplot(MEP, aes(x=disgust)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggfeM <- ggplot(MEP, aes(x=fear)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggcoM <- ggplot(MEP, aes(x=contempt)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
 
 grid.arrange(gganM, gghaM, ggneM, ggsaM, ggsuM, ggdiM, ggfeM, ggcoM,nrow=3, 
-             top=textGrob("Microsoft Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)))
+             top=textGrob("Microsoft Distribution of Emotion Porportions", gp=gpar(fontsize=20,font=3)),
+             left =("Percentage of Emotion values"))
 
@@
 \newpage
-# Validation
+
+###Predominant Emotions
+To contrast the emotion results for certain faces a 'predominant' emotion was designated to each face.
+Where the emotion with the maximum proportion value was deemed the 'predominant' emotion for a particular face.
+
+This resulted in one of seven emotions for Google, one of eight for Microsoft, and one of five for Google. This also required the assumption that joy is equivalent to happiness, and sorrow to sadness.
+
+```{r predominant, results = 'asis', fig.cap = "\\label{tab:predominant}"}
+#Table including Google
+#ftable(DE$GEmotion, DE$SEmotion, DE$MEmotion, dnn = c("Google", "Skybiometry", "Microsoft"))
+
+ft<-ftable( DE$MEmotion, DE$SEmotion, dnn = c("Microsoft","Skybiometry"))
+
+stargazer(format(ft, quote=FALSE, justify="right"),title = "This shows the agreement between the emotions recognised by Microsoft and Skybiometry", header=FALSE, type = "latex")
+```
+
+There was only one occurence of all three APIs gaving the same emotional result. This occured when there was agreement for 11 faces that the dominant emotion was anger. 
+In Table \@ref(tab:predominant) where Skybiometry emotion recognitions are shown in the rows, and Microsoft's in the columns. 
+It is reasonable to only consider Microsoft and Skybiomertry it can be seen that they agreed 408 faces were predominantly showing anger, and 12 were showing surprise.
+
+As neutral was a prominent category for Microsoft and Google, we considered where neutral was the dominant emotion and grouped the remaining emotions into a non-neutral category.
+
+```{r neutral-non, results='asis', fig.cap="\\label{tab:neutral-non}"}
+DEne<-DE %>% rowwise()%>%
+  mutate(GEneutral = ifelse(GEmotion=="neutral", "neutral","non-neutral")) %>%
+  mutate(SEneutral = ifelse(SEmotion=="neutral", "neutral","non-neutral")) %>%
+  mutate(MEneutral = ifelse(MEmotion=="neutral", "neutral","non-neutral"))
+
+# neutral flat table
+nft<-ftable(DEne$GEneutral, DEne$MEneutral,DEne$SEneutral, dnn = c("Google","Microsoft","Skybiometry"))
+
+stargazer(format(nft, quote=FALSE, justify="right"), header=FALSE, type = "latex", title ="This shows the agreement between non-neutral and neutral faces recognised by Goole, Microsoft and, Skybiometry.
+Only three faces were categorised as neutral.
+Of these, Google was much more likely to categorise as neutral.")
+```
+
+The following Figure \@ref(fig:neutrality) displays a Scatter Plot Matrix that captures the pairwise variablitiy in the Neutral proportion levels across APIs.
+
+```{r neutrality, fig.cap = "The Scatter Plot Matrix shows the variablitiy in the Neutral proportion levels.
+The -0.01 correlation value for Google and Skybiometry show that they do not behave either in a similar way, or inversely.
+They are uncorrelated.\n Some high values of neutrality for Google are matched to some high levels found by Skybiometry.
+However, in the lower ranges of both there is a lot of variability in proportion values.\\label{fig:neutrality}"}
+
+library(GGally)
+ggscatmat(as.data.frame(na.omit(J4[,c(2:4)])), alpha = 0.4)
+```
+
+\newpage
+## Validation
 We considered a subset of images where the emotions on the faces were manually considered.

### 2017-04-26 Internship/EmotionsAnalysis.Rmd
Cross Tables added to report

@@
 
-MEPCL1 <- MEPCL %>% arrange(FileName, desc(EmotionValue)) %>%
+MEPCL1 <- MEP %>% group_by(FileName) %>% 
+  gather(key = Emotion, value=EmotionValue, anger,contempt,disgust,fear,happiness,neutral,sadness,surprise)  %>% 
+  arrange(FileName, desc(EmotionValue)) %>%
       group_by_(~ FileName) %>% 
@@
 ```
+
+```{r}
+#Find missing player
+nrow(GEP)
+nrow(MEP)
+nrow(SBP)
+
+dupe <- subset(duplicated(SBP$aname))
+duplicated(SBP$aname)
+SBP[264,]
+SBP %>% View()
+```

### 2017-04-28 Internship/BEX3012ProjectReport.Rmd
Neutral Logistic Regression

@@
 ```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)
 
 library(tidyverse)
-library(dplyr)
 library(readr)
@@
 
+```
+
+```{r mutate}
 #Create normalised GE values
@@
 }
-```
 
-```{r mutate}
 #confidence columns
@@
 ```{r playerSubset}
-library(dplyr)
 GEP <- GE %>% dplyr::filter(detect == "Player")
@@
 SBP <- SB %>% dplyr::filter(detect == "Player")
+```
+
+```{r predominantEmotion}
+#shows only the rank 1 emotion and value for each face
+GEP1 <- GEP %>% group_by(FileName) %>% 
+  gather(key = Emotion, value=EmotionValue, 
+         anger, joy, sorrow, surprise,neutral)  %>% 
+  arrange(FileName, desc(EmotionValue)) %>%
+      group_by_(~ FileName) %>% 
+      slice(1)
+
+SBP1 <- SBP %>% group_by(aname) %>% 
+  gather(key = Emotion, value=EmotionValue, 
+         anger,disgust,fear,happiness,neutral,sadness,surprise)  %>% 
+  arrange(aname, desc(EmotionValue)) %>%
+      group_by_(~ aname) %>% 
+      slice(1)
+
+MEP1 <- MEP %>% group_by(FileName) %>% 
+  gather(key = Emotion, value=EmotionValue,
+         anger,contempt,disgust,fear,happiness,neutral,sadness,surprise)  %>% 
+  arrange(FileName, desc(EmotionValue)) %>%
+      group_by_(~ FileName) %>% 
+      slice(1)
+
 ```
@@
 gganS <- ggplot(SBP, aes(x=anger))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 gghaS <- ggplot(SBP, aes(x=happiness))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggneS <- ggplot(SBP, aes(x=neutral))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggsaS <- ggplot(SBP, aes(x=sadness))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggsuS <- ggplot(SBP, aes(x=surprise))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggdiS <- ggplot(SBP, aes(x=disgust))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggfeS <- ggplot(SBP, aes(x=fear))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
@@
 gganM <- ggplot(MEP, aes(x=anger)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 gghaM <- ggplot(MEP, aes(x=happiness)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggneM <- ggplot(MEP, aes(x=neutral)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggsaM <- ggplot(MEP, aes (x=sadness)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggsuM <- ggplot(MEP, aes(x=surprise)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggdiM <- ggplot(MEP, aes(x=disgust)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggfeM <- ggplot(MEP, aes(x=fear)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
 ggcoM <- ggplot(MEP, aes(x=contempt)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
@@
 
-library(GGally)
 ggscatmat(as.data.frame(na.omit(J4[,c(2:4)])), alpha = 0.4)
+```
+
+We consider that there were attributes of the faces captured that may have influenced the likelihood of a neutral result in the cases of Google and Skybiometry.
+To understand this we consider the associations between differing attribute values and the neutral results.
+
+```{r Regression, fig.height=9.5, fig.width=7.5, fig.cap = "The logistic regression returned statistically significant results when the face was captured in the presence of a graphic.
+\\label{Regression}"}
+#Add neutral columns to data sets
+
+GEP1 <- GEP1 %>% rowwise %>% mutate(Gneutral = ifelse(Emotion=="neutral", "neutral","non-neutral")) %>%  mutate(neutral01 = ifelse(Gneutral=="neutral",1,0))
+
+MEP1 <- MEP1 %>% rowwise %>% mutate(Mneutral = ifelse(Emotion=="neutral", "neutral","non-neutral")) %>% mutate(neutral01 = ifelse(Mneutral=="neutral",1,0))
+
+SBP1 <- SBP1 %>% rowwise %>% mutate(Sneutral = ifelse(Emotion=="neutral", "neutral","non-neutral")) %>% mutate(neutral01 = ifelse(Sneutral=="neutral",1,0))
+
+ModelTable <- function(model){
+  model %>%
+    summary %>%
+    coef %>%
+    as.data.frame %>%
+    cbind %>%
+    rownames_to_column %>%
+    cbind %>%
+    dplyr::rename(variable = rowname)
+}
+
+SignificancePlot <- function(model, data = ModelTable(model)) {
+  data %>%
+  mutate(significant = `Pr(>|t|)` < 0.05) %>%
+  mutate(`Pr(<|t|)` = 1 - `Pr(>|t|)`) %>%
+  ggplot(aes(x=variable, y=`Pr(<|t|)`)) +  
+  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
+  geom_col(aes(fill=significant))
+}
+
+EstimatesPlot <- function(model, data = ModelTable(model)) {
+  data %>%
+  mutate(significant = `Pr(>|t|)` < 0.05) %>%
+  ggplot(aes(x= variable, y=Estimate)) +  
+  theme(axis.text.x = element_text(angle = 30, hjust = 1), 
+        axis.text.y = element_text(angle = 30, hjust = 1)) +
+  geom_col(aes(fill=significant))
+}
+
+ModelPlotResults<-function(model, data = ModelTable(model)){
+  ep<-EstimatesPlot(model, data)
+  sp<- SignificancePlot(model, data)
+  grid.arrange(ep, sp, nrow=1)
+}
+
+#A backward stepwise regression approach led to the following nmodel with a low AIC:
+mod <- glm(neutral01 ~ headangle + shotangle, data = GEP1)
+
+ModelPlotResults(mod)
+
 ```

### 2017-05-05 Internship/EmotionsAnalysis.Rmd
Player subset updates

@@
 ```{r combined}
-S1 <- select(SBPCL1, FileName = aname , SEmotion = Emotion)
-S2 <- select(MEPCL1, FileName, MEmotion = Emotion)
-S3 <- select(GEPCL1, FileName, GEmotion = Emotion)
+S1 <- select(SBP1, FileName = aname , SEmotion = Emotion)
+S2 <- select(MEP1, FileName, MEmotion = Emotion)
+S3 <- select(GEP1, FileName, GEmotion = Emotion)
 J1 <- full_join(S1, S2, by = "FileName")
@@
 ```{r DisplayFaces}
+AKimgsG<-GEP %>% filter(player1=="JSousa")
+AKimgsG<-AKimgsG %>% filter(detect=="Player")
+AKlist <- as.list(AKimgsG$FileName)
+length(AKlist)
 
-MSimgsG<-GEPCL1 %>% filter(player1=="ARadwanska")
-MSimgsG <-MSimgsG %>% filter(detect=="Player")
-MSlist <- as.list(MSimgsG$FileName)
-length(MSlist)
+DisplayFaces(AKlist)
 
@@
 DisplayFaces <- function(list) {
-for (i in 1:length(list)){
+    for (i in 1:15){
 
@@
 ```
+
+``` {r playerSpecificEmotions}
+player <- "AMurray"
+GEPAM <- GEP %>% filter(playerName == player)
+MEPAM <- MEP %>% filter(playerName == player)
+SBPAM <- SBP %>% filter(playerName == player)
+
+```

### 2017-05-06 Internship/BEX3012ProjectReport.Rmd
Column changes
playerName column added, joy & sorrow to happiness and sadness

@@
 library(ggplot2)
+library(stargazer)
+library(glmnet)
 
@@
 DE <- read_csv("data/DominantEmotion.csv")
-# 
-# MEP <- read_csv("data/MicrosoftEmotions.csv")
-# SBP <- read_csv("data/SkybiometryEmotions.csv")
-# GEP <- read_csv("data/GoogleFacesEmotions.csv")
 
 EmotionSoftwareSpecs <- read_csv("Figures/EmotionSoftwareSpecifications.csv")
+
+#player name column
+GE <- GE %>% rowwise %>%
+  mutate(playerName = ifelse(PlayerNumber == 1, player1,
+                                            ifelse(PlayerNumber == 2, player2,
+                                                   ifelse(is.na(PlayerNumber), NA, NA))))
+
+GF <- GF %>% rowwise %>%
+  mutate(playerName = ifelse(PlayerNumber == 1, player1,
+                                            ifelse(PlayerNumber == 2, player2,
+                                                   ifelse(is.na(PlayerNumber), NA, NA))))
+
 ```
@@
 
+#refer to joy results as happiness, and sorrow as sadness
+
 #confidence columns
-GE <- GE %>% mutate(joyConf = Conf(joyLikelihood)) %>%
-  mutate(sorrowConf = Conf(sorrowLikelihood)) %>%
+GE <- GE %>% mutate(happinessConf = Conf(joyLikelihood)) %>%
+  mutate(sadnessConf = Conf(sorrowLikelihood)) %>%
   mutate(angerConf = Conf(angerLikelihood)) %>%
@@
   rowwise %>% 
-  mutate(neutralConf = 100 - (pmax(joyConf, sorrowConf, angerConf, surpriseConf))) %>%
-  mutate(z = (joyConf+
-                sorrowConf+
+  mutate(neutralConf = 100 - (pmax(happinessConf, sadnessConf, angerConf, surpriseConf))) %>%
+  mutate(z = (happinessConf+
+                sadnessConf+
                 angerConf+
@@
   mutate(anger = angerConf/z,
-         joy = joyConf/z,
+         happiness = happinessConf/z,
          neutral = neutralConf/z,
-         sorrow = sorrowConf/z,
+         sadness = sadnessConf/z,
          surprise = surpriseConf/z)
 
-#player name column
-GE <- GE %>% rowwise %>%
-  mutate(playerName = ifelse(PlayerNumber == 1, player1,
-                                            ifelse(PlayerNumber == 2, player2,
-                                                   ifelse(is.na(PlayerNumber), NA, NA))))
 ```
@@
 #shows only the rank 1 emotion and value for each face
-GEP1 <- GEP %>% group_by(FileName) %>% 
+GEP1 <- GEP %>% 
+  filter(!is.na(anger)) %>%
+  group_by(FileName) %>% 
   gather(key = Emotion, value=EmotionValue, 
-         anger, joy, sorrow, surprise,neutral)  %>% 
+         anger, happiness, sadness, surprise, neutral)  %>% 
   arrange(FileName, desc(EmotionValue)) %>%
@@
 
-SBP1 <- SBP %>% group_by(aname) %>% 
+GEP1$Emotion <- as.factor(GEP1$Emotion)
+
+SBP1 <- SBP %>% 
+  filter(!is.na(anger)) %>%
+  group_by(aname) %>% 
   gather(key = Emotion, value=EmotionValue, 
@@
 
-MEP1 <- MEP %>% group_by(FileName) %>% 
+SBP1$Emotion <- as.factor(SBP1$Emotion)
+
+MEP1 <- MEP %>% 
+  filter(!is.na(anger)) %>%
+  group_by(FileName) %>% 
   gather(key = Emotion, value=EmotionValue,
@@
 
+MEP1$Emotion <- as.factor(MEP1$Emotion)
 ```
@@
 J4 <- full_join(J3, S6, by = "FileName")
+```
+
+```{r regressionFunctions}
+
+ModelTable <- function(model){
+  model %>%
+    summary %>%
+    coef %>%
+    as.data.frame %>%
+    cbind %>%
+    rownames_to_column %>%
+    cbind %>%
+    dplyr::rename(variable = rowname)
+}
+
+SignificancePlot <- function(model, data = GlmModelEstimates(model)) {
+  data %>%
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
+  ggplot(aes(x=variable, y=`Pr(<|z|)`)) +  
+  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
+  geom_col(aes(fill=significant)) 
+}
+
+EstimatesPlot <- function(model, data = GlmModelEstimates(model)) {
+  data %>%
+  mutate(significant = `Pr(>|z|)` < 0.05) %>%
+  ggplot(aes(x=variable, y=Estimate)) +  
+  theme(axis.text.x = element_text(angle = 30, hjust = 1), 
+        axis.text.y = element_text(angle = 30, hjust = 1)) +
+  geom_col(aes(fill=significant)) 
+}
+
+ModelPlotResults<-function(model, data = ModelTable(model)){
+  ep<-EstimatesPlot(model, data)
+  sp<- SignificancePlot(model, data)
+  grid.arrange(ep, sp, nrow=1)
+}
+
 ```
@@
 
-The image set contained 6406 still shot 800x450px size video frames, taken every 3 seconds from 5 minute segments sampled from 105 Australian Open 2016 match broadcast videos.
+The image set used to derive emotion information contained 6406 still shot images.
+These were 800x450px video frames, taken every 3 seconds from 5 minute video segments.
+These segments were sampled from 105 Australian Open 2016 match broadcast videos.
 The broadcast videos are a combination of multiple camera feeds, these angles vary depending on the court the match was played on.
 
-```{r ExampleImage, echo=F, fig.cap = "Example Image: 2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0020.png\\label{fig:ExampleImage}"}
+```{r ExampleImage, echo=F, fig.cap = "This image was derived from a match played between JMillman and DSchwartzmann in the first Round of the 2016 Australian Open. \\label{fig:ExampleImage}"}
 
@@
 
-The number of emotions shown in the results were not congruent. These differences made it necessary to pre process the result to provide the most comparable results for analysis.
-Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only giving the options for four different emotions.
+The number of emotions shown in the results were not congruent. These differences made it necessary to process the outputs to provide the most comparable results for analysis.
+Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only providing four different emotions.
 
-The outputs from the APIs were very different.
+The observations of these emotions from the APIs were also different.
 Google provides likelihoods of an emotion occurring on a particular face in categorical options ranging from Very Unlikely to Very Likely.
-Microsoft provide Proportions, ranging between 0 and , whereas Skybiometry results in a Confidence of the emotion occurring in the specified face in values from 0 to 100.
+Microsoft provide Proportions, ranging between 0 and 1, whereas Skybiometry results in a Confidence value for the emotion occurring in the specified face in values from 0 to 100.
 
@@
 
-The original image set was subset to create images of faces specifically suited for emotion recognition purposes. 
-A crop was performed to create a new image that focused on the area marked as a face by Google^[based on Google’s bounding box coordinates].
+To create a set of individual faces for the APIs to consider we derived small images that were cropped subsets of the 450x800px images.
+The crop was performed to create a new image with a unique name that focused on the area marked as a face by Google^[based on Google’s bounding box coordinates].
 A border to frame the face was also included for visual appeal.
-These 1319 new images, of varying sizes, were hosted on Google Drive to allow for URL access from the API to the individual images.
+These 1319 new images, of varying sizes, were hosted on Google Drive as individual images.
 
@@
 
-The results extracted from each of the APIs differed, re configuring of these results was needed to create comparable sets for analysis.
+As mentioned previously, the results extracted for each face differed across the APIs this made it necessary to produce a comparable set of results for analysis.
 
 Microsoft provided a POST request object in a JSON format. 
-This was easily formatted to create a data set of the eight numeric emotion values provided for each face.
-In the event that emotion values were not returned for a certain face, NAs were presented in the data set.
+This was easily manipulated to create a data set of the eight numeric emotion values provided for each face.
+In the event that emotion values were not returned for a certain face, a row of NAs will be associated with the unique face ID in the data set.
 
@@
 
-Skybiometry as provided a POST request object in a JSON format.
-However, unlike Microsoft, the results included a True or False Value for each of the seven emotions and a confidence level   'confidence value as a percentage from 0 to 100'^[https://skybiometry.com/documentation/#document-21] representing the confidence of the emotion being present on a player's face.
+Skybiometry also provided a POST request object in a JSON format.
+However, unlike Microsoft, the results included a True or False Value for each of the seven emotions and a 'confidence value as a percentage from 0 to 100'^[https://skybiometry.com/documentation/#document-21] representing the confidence of the emotion being present on a player's face.
 
@@
 
-The process undertaken to receive results Google produces was the same as the previous APIs.
+The process undertaken to receive the results Google produced was the same as the previous APIs.
 However rather than numeric values, it returned categorical likelihoods for the four emotions it considered.
@@
 knitr::kable(GEexample, longtable=TRUE, booktabs = TRUE,
-             col.names = c("joy", "sorrow", "anger", "surprise"),
+             col.names = c("happiness", "sadness", "anger", "surprise"),
              caption="The Google Vision API provided four likelihood possibilities, one for each emotion.")
@@
 
-These differing outputs needed to be arranged in a comparable manner.
 Noticing that the sums of the individual emotions for each face in the Microsoft results was approximately one provided the basis for transformation for the other APIs.
@@
 
-As both Microsoft and Skybiometry included a neutral category we considered how to incorporate a neutral category for the Google results.
+As both Microsoft and Skybiometry included a neutral category we incorporated a neutral category for the Google results.
 
 Our approach considered that when a face was "very unlikely" to be any of the four emotion categories it could be deemed "neutral".
-However when one emotion was stronger than other it could still be possible that the face only had a small lean toward this emotion and it may not be the obvious choice.
+However when one emotion was stronger than others it could still be possible that the face only had a small lean toward this emotion and it may not be a dominant expression .
 Therefore the Confidence value for neutral was calculated according to the formula below:
 
-$$neutralConf_i = 100 - max(joyConf_i, sorrowConf_i, angerConf_i, surpriseConf_i)$$
+$$neutralConf_i = 100 - max(happinessConf_i, sadnessConf_i, angerConf_i, surpriseConf_i)$$
 
@@
 GET <- GEP %>% subset(FileName=="face-1745-1-Go.png") %>% 
-  select(joy, sorrow, anger, surprise, neutral)
+  select(happiness, sadness, anger, surprise, neutral)
 
 knitr::kable(GET, longtable=TRUE, booktabs = TRUE,
-             col.names = c("joy", "sorrow", "anger", "surprise", "neutral"),
+             col.names = c("happiness", "sadness", "anger", "surprise", "neutral"),
              caption="The Google Vision API provided four likelihoods, one for each emotion.")
@@
 
+```{r playerNonplayer, eval=FALSE,fig.cap="\\label{tab:playerNonPlayer}"}
+#Apply a machine learning algorithm to face recognition data, and software provided for fitting model, aiming to classify whether an identified face is a player or not player
+ME <- ME %>% rowwise %>% mutate(Player = ifelse(detect=="Player", "Player","NotPlayer")) %>%  mutate(Player01 = ifelse(Player=="Player",1,0))
+
+gplayer = glm(Player01 ~ bg+shotangle+obscured+headangle+glasses+visorhat, data = GE, family=binomial(logit))
+
+gpm <- model.matrix(gplayer)
+
+gpmNet = glmnet(gpm, as.vector(GE$Player01))
+
+pot(gpmNet)
+
+#cv of model
+cvgpmNet = cv.glmnet(gpm, as.vector(GE$Player01),family = "binomial", type.measure = "class")
+
+plot(cvgpmNet)
+summary(gplayer)
+coef(cvgpmNet, s = "lambda.min")
+```
+
 ```{r NonNullFaces, fig.cap = "\\label{fig:NonNullFaces}", results = 'asis'}
@@
 
-library(stargazer)
 stargazer(format(nfft, quote=FALSE, justify="right"),title = "Emotion results were found by all three APIs for 364 common faces, none of the APIs produced results for 10 player faces.
-Google was able to produce 382 results that Skybiometry and Microoft did not.", header=FALSE, type="latex")
+Google was able to produce 382 results that Skybiometry and Microsoft did not.", header=FALSE, type="latex")
 ```
 
+In the following sections we will only consider the faces of players, as they would be the intended targets for our applications of this research.
+Microsoft produced emotion results for `r sum(!is.na(MEP$anger))` player's faces.
+Skybiometry, produced `r sum(!is.na(SBP$anger))` and Google provided `r sum(!is.na(GEP$anger))` emotion results.
+
+\newpage
 ### Emotion Proportion Distributions
-For the following distributions only the faces of players were considered.
 
@@
 This is balanced by the large percentage, over 75%, where the neutral value of just under .75 occurred.
-The faces used showed higher levels of Joy than any other non neutral emotion as the percentage occuring at zero was less than the percentages of the other emotions.\\label{fig:GEPhists}"}
+The faces used showed higher levels of happiness than any other non neutral emotion as the percentage occuring at zero was less than the percentages of the other emotions.\\label{fig:GEPhists}"}
 gganG <- ggplot(GEP, aes(x=anger)) + 
@@
 
-ggjoG <- ggplot(GEP, aes(x=joy)) + 
+ggjoG <- ggplot(GEP, aes(x=happiness)) + 
   geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
@@
 
-ggsoG <- ggplot(GEP, aes(x=sorrow)) + 
+ggsoG <- ggplot(GEP, aes(x=sadness)) + 
   geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
@@
              left = ("Percentage of Emotion values"))
-
 ```
 
-```{r MEPhists, fig.cap="Unlike the previous two softwares, there were many faces that returned high neutral values.
+```{r MEPhists, fig.cap="There were many faces that returned high neutral values.
 This is matched by the high percentages of faces where the proportion levels were at, or close to, zero.
@@
 grid.arrange(gganM, gghaM, ggneM, ggsaM, ggsuM, ggdiM, ggfeM, ggcoM,nrow=3, 
-             top=textGrob("Microsoft Distribution of Emotion Porportions", gp=gpar(fontsize=20,font=3)),
-             left =("Percentage of Emotion values"))
+             top=textGrob("Microsoft Distribution of Emotion Porportions", gp=gpar(fontsize=20,font=3)), left =("Percentage of Emotion values"))
 
@@
 
-This resulted in one of seven emotions for Google, one of eight for Microsoft, and one of five for Google. This also required the assumption that joy is equivalent to happiness, and sorrow to sadness.
+This resulted in one of seven emotions for Google, one of eight for Microsoft, and one of five for Google.
+This also required the assumption that happiness is equivalent to happiness, and sadness to sadness.
 
@@
 
-ft<-ftable( DE$MEmotion, DE$SEmotion, dnn = c("Microsoft","Skybiometry"))
+ft<-ftable(DE$GEmotion, DE$MEmotion, DE$SEmotion, dnn = c("Google","Microsoft","Skybiometry"))
 
@@
 ```
-
-There was only one occurence of all three APIs gaving the same emotional result. This occured when there was agreement for 11 faces that the dominant emotion was anger. 
-In Table \@ref(tab:predominant) where Skybiometry emotion recognitions are shown in the rows, and Microsoft's in the columns. 
-It is reasonable to only consider Microsoft and Skybiomertry it can be seen that they agreed 408 faces were predominantly showing anger, and 12 were showing surprise.
+Skybiometry emotion recognition's are shown in the rows, and Microsoft's in the columns. 
+There were many instances where Skybiometry allocated an emotion as the predominant expression while Google and Microsoft designated it as neutral, this was expected as only 3 faces were categorised as neutral by Skybiometry.
+These faces were categorised as neutral by both Google and Microsoft.
 
@@
 
-The following Figure \@ref(fig:neutrality) displays a Scatter Plot Matrix that captures the pairwise variablitiy in the Neutral proportion levels across APIs.
+The following Figure \@ref(fig:neutrality) displays a Scatter Plot Matrix that captures the pairwise variability in the Neutral proportion levels across APIs.
 
@@
 
-```{r Regression, fig.height=9.5, fig.width=7.5, fig.cap = "The logistic regression returned statistically significant results when the face was captured in the presence of a graphic.
-\\label{Regression}"}
+```{r LogisticRegression, eval= FALSE, fig.width=7, fig.cap = "\\label{LogisticRegression}"}
 #Add neutral columns to data sets
@@
 
-ModelTable <- function(model){
-  model %>%
-    summary %>%
-    coef %>%
-    as.data.frame %>%
-    cbind %>%
-    rownames_to_column %>%
-    cbind %>%
-    dplyr::rename(variable = rowname)
-}
+#create a model
+Mne = glm(neutral01 ~ bg+shotangle+obscured+headangle+glasses+visorhat+, data = MEP1, family=binomial(logit))
 
-SignificancePlot <- function(model, data = ModelTable(model)) {
-  data %>%
-  mutate(significant = `Pr(>|t|)` < 0.05) %>%
-  mutate(`Pr(<|t|)` = 1 - `Pr(>|t|)`) %>%
-  ggplot(aes(x=variable, y=`Pr(<|t|)`)) +  
-  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
-  geom_col(aes(fill=significant))
-}
+Mnemm <- model.matrix(Mne)
 
-EstimatesPlot <- function(model, data = ModelTable(model)) {
-  data %>%
-  mutate(significant = `Pr(>|t|)` < 0.05) %>%
-  ggplot(aes(x= variable, y=Estimate)) +  
-  theme(axis.text.x = element_text(angle = 30, hjust = 1), 
-        axis.text.y = element_text(angle = 30, hjust = 1)) +
-  geom_col(aes(fill=significant))
-}
+Mnegn = glmnet(Mnemm, as.vector(MEP1$neutral01))
 
-ModelPlotResults<-function(model, data = ModelTable(model)){
-  ep<-EstimatesPlot(model, data)
-  sp<- SignificancePlot(model, data)
-  grid.arrange(ep, sp, nrow=1)
-}
+#cv of model
+cvMnegn = cv.glmnet(Mnemm, as.vector(MEP1$neutral01))
+
+plot(cvMnegn)
+
+coef(cvMnegn, s = "lambda.min")
 
 #A backward stepwise regression approach led to the following nmodel with a low AIC:
-mod <- glm(neutral01 ~ headangle + shotangle, data = GEP1)
-
-ModelPlotResults(mod)
 
@@
 
+## Selecting an API
+For these purposes an API that would provide informative and accurate results was a top priority.
+This required it to return emotion information for a reasonable amount of faces, and that this information was reliable.
+
+It has been shown through the report that Goggle returned emotional information for `r sum(!is.na(GEP$anger))` player's faces, the highest amount of emotion results for the faces provided to three APIs.
+However, in Table \@ref(fig:neutrality) it is seen that only 31 of these faces gave results that considered the faces to be premoninantly a non-neutral expression.
+This limited resulting information is not helpful in extracting a player's emotional state.
+Figure \@ref(fig:GEPhists) shows that anger, happiness, sadness and surprise often had a level of 0.10 for faces.
+This is equivalent to the original output of it being 'Very Unlikely' that the emotion appeared on the given face.
+Due to these results, Google will not be appropriate for further exploration.
+
+Microsoft provided `r sum(!is.na(MEP$anger))` emotion results for player's faces, these numeric results shown in Table \@ref(tab:MEexample) were in an optimal format for analyses.
+These results also had the most variability is possible emotions, this could be seen as a positive as it may allow an emotion to be directly identified in comparison to the assumptions needed to be applied to Google's results in Table \@ref(tab:GEexample).
+
+Microsoft provided many results where the amount attributed to an emotion was zero, this was accompanied by high values of neutral being counted in these faces, as shown in Figure \@ref(MEPhists).
+This is not unreasonable as there are many factors that may have influenced the neutral results we were given, such as the players having strong control over their facial expressions or the faces passed to the software being sub optimal for recognition.
+
+The results from Microsoft were still deemed to be preferrable to those of Microsoft due to the limits on it's API impeding on any future use of the API for our purposes.
+While more facial emotion results were gained, majority of the emotion proportions after tranformations were still below 0.5 for the predominant emotions.
+
+The conclusion of these comparisons points to Microsoft as a good API that provides a useful output.
+Its limits do not impose as heavily as Skybiometry's do, and it provided many of the same neutral results that Google did, showing that it may be image, rather than API, reasons for returning a neutral dominant emotion result.
+
 \newpage
-## Validation
-We considered a subset of images where the emotions on the faces were manually considered.
+## Possible Application
+From this point we will give an example of an application of this emotional data in a tennis setting.
+This information would help to understand a player's emotional variability on the court, and may help in coaches training players to control what is physically visible as to not advantage their opponent by giving them an indication to a players emotional state.
+
+## Player Variablity
+
+We consider the subsets corresponding to individual players. This allowed a visual inspection of a players emotional variability according to each software.
+
+```{r playerHists}
+
+MicrosoftHists <- function(player = NA, data = MEP){
+
+  if (!is.na(player)){
+    data <- MEP %>% dplyr::filter(playerName == player) 
+  }
+
+  ggMEPne<-ggplot(data, aes(x=neutral)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+  ggMEPan<-ggplot(data, aes(x=anger)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+  ggMEPdi<-ggplot(data, aes(x=disgust)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+  ggMEPfe<-ggplot(data, aes(x=fear)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+  ggMEPha<-ggplot(data, aes(x=happiness)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+  ggMEPsa<-ggplot(data, aes(x=sadness)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+  ggMEPsu<-ggplot(data, aes(x=surprise)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+  ggMEPco<-ggplot(data, aes(x=contempt)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+
+  grid.arrange(ggMEPne,
+               ggMEPan,
+               ggMEPdi,
+               ggMEPfe,
+               ggMEPha,
+               ggMEPsa,
+               ggMEPsu, 
+               ggMEPco,nrow=3,
+             top=textGrob(paste0("Microsoft Distribution of Emotion Porportions for ", player), gp=gpar(fontsize=10,font=3)), 
+             left = ("Percentage of Emotion values"))
+}
+
+MicrosoftHists()
+
+```
+
+```{r playerProfiles}
+
+playerProfileBars <- function(player = NA, data=MEP1){
+
+  if (!is.na(player)){
+     data <- data %>% dplyr::filter(playerName == player) 
+  }
+  title <- "Emotional Variability"
+  if (!is.na(player)){
+     title <- paste0(player, " Emotional Variability")
+  }
+
+  Ecolours<-c(anger = "#b2454C",
+              disgust ="#21d19f",
+              happiness = "#f7874f",
+              neutral = "#a0988a",
+              sadness = "#50a1d3",
+              surprise = "#883677",
+              fear = "#037171")
+
+ ggplot(data, aes(x=Emotion, fill=Emotion))+ geom_bar(position = "dodge") + scale_fill_manual("Emotions", values = Ecolours, drop=FALSE) + ggtitle(title)
+
+}
+
+ppbM <- playerProfileBars(data=MEP1)
+ppbS <- playerProfileBars(data=SBP1)
+
+grid.arrange(ppbM, ppbS, nrow=1)
+
+playerProfileBars("CSurezNavarro", data=MEP1) 
+playerProfileBars("AFriedsam", data=MEP1)
+playerProfileBars("ACornet", data=MEP1) 
+table(GEP1$playerName)
+```

### 2017-05-06 Internship/EmotionsAnalysis.Rmd
Column changes
playerName column added, joy & sorrow to happiness and sadness

@@
 ```{r DisplayFaces}
-AKimgsG<-GEP %>% filter(player1=="JSousa")
+AKimgsG<-GEP %>% filter(player2=="ACornet")
 AKimgsG<-AKimgsG %>% filter(detect=="Player")
@@
 ```
+
+```{r GoogleJoy}
+Gjoy <- GEP1 %>% filter(Emotion=="joy")
+
+Gjoylist<- as.list(Gjoy$FileName)
+
+Mjoy <- MEP1 %>% filter(FileName %in% Gjoylist)
+
+table(Mjoy$Emotion)
+
+```

### 2017-06-18 Internship/BEX3012ProjectReport.Rmd
Presentation Changes

@@
 author: "Stephanie Kobakian"
-date: "28 March 2017"
+date: "12 May 2017"
 output: bookdown::pdf_document2
@@
 out_width: 7
-fontsize: 11pt
+fontsize: 10pt
 link-citations: true
@@
 ```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache=FALSE)
 
@@
 library(ggplot2)
+library(glmnet)
 library(stargazer)
-library(glmnet)
 
@@
 GF <- read_csv("data/GoogleFaces.csv")
-DE <- read_csv("data/DominantEmotion.csv")
+DE <- read_csv("data/DominantEmotions.csv")
+DEne<-DE
 
@@
 
-```{r mutate}
+```{r mutate, cache =FALSE}
 #Create normalised GE values
@@
 
-```{r join}
+```{r join, cache=FALSE}
 ME <- left_join(ME, GF, by = "FileName") 
@@
 
-```{r playerSubset}
+```{r playerSubset, cache=FALSE}
 GEP <- GE %>% dplyr::filter(detect == "Player")
@@
 
-```{r predominantEmotion}
+```{r predominantEmotion, cache=FALSE}
 #shows only the rank 1 emotion and value for each face
@@
 
-```{r NeutralProportions}
+```{r NeutralProportions, cache = FALSE}
 S4 <- select(SBP, FileName = aname, Skybiometry = neutral)
@@
 
-```{r regressionFunctions}
+```{r regressionFunctions, cache =FALSE}
 
@@
 \newpage
-# Introduction
 
-Facial Recognition is beginning to be explored in sports environments, this presents quality issues.
-
-helpful for applications
+Tennis is often considered a mental game due to the pressures placed on the two, or four, individuals during match play.
+This report explores the application of emotion recognition technology to elite tennis match broadcasts.
+This extends on research of the facial detection performance of these APIs.
+By understanding the emotions expressed on a face we have the opportunity to consider a player's mental state as a match progresses.
+This would help players to improve their performance if correlations can be found between match performance and their emotional state.
+By analysing a players mental state from observations rather than self reporting we may be able to gain information that a player will not recall after a match.
+It is predicted that the software will be able to derive the emotional expression shown by a player.
+It is expected that emotional recognition may be impaired by certain features of the face captured.
+This research exposes the impact of presenting APIs with faces captured from unexpected angles and in unusual poses, and how this may be impacting the performance of the APIs.
+The analyses undertaken show the differing results returned from the three APIs used, validation of these results was not achieveable within the time frame of this project.
 
 \newpage
-
 # Materials
@@
 These segments were sampled from 105 Australian Open 2016 match broadcast videos.
-The broadcast videos are a combination of multiple camera feeds, these angles vary depending on the court the match was played on.
+The broadcast videos are the televised match play shown on Channel Seven. They contain shots from various cameras, these angles vary depending on the court the match was played on.
 
-```{r ExampleImage, echo=F, fig.cap = "This image was derived from a match played between JMillman and DSchwartzmann in the first Round of the 2016 Australian Open. \\label{fig:ExampleImage}"}
+```{r ExampleImage, echo=F, fig.cap = "This image of John Millman was taken from the broadcast video of a match played against DSchwartzmann in the first Round of the 2016 Australian Open.
+This image is representative of the most commmon group of faces found.
+It captures a player's face close up on the court, taken at the player's shoulder height, with the logo wall in the back ground.
+\\label{fig:ExampleImage}"}
 
-img <- image_read("Figures/2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0020.png")
+img <- image_read("Figures/2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png")
 
@@
 
-Three emotion recognition APIS were considered.
-They were chosen for their accessibility and online reviews of their performance, and these are well recognised options for Facial recognition currently available.
+Three emotion recognition APIs were considered.
+They were chosen for their accessibility and online reviews of their performance. Each API is a well recognised Facial and Emotion recognition solution currently available online.
 
-```{r Emotion-Software-Specs-Table, echo=F, fig.cap = "\\label{tab:Emotion-Software-Specs-Table}"}
+```{r Emotion-Software-Specs-Table, echo=F,results = 'asis', fig.cap = "\\label{tab:Emotion-Software-Specs-Table}"}
 
-knitr::kable(EmotionSoftwareSpecs, longtable=TRUE, booktabs = TRUE, caption="This details the capabilities we considered important in recognising emotions in images of faces.")
+knitr::kable(EmotionSoftwareSpecs, longtable=TRUE, booktabs = TRUE, caption="This table details the capabilities that were considered in contrasting the accessibility and outputs of APIs that recognise emotions in images of faces.")
 ```
 
-As can be seen above, a noticeable difference between the three is the amount of times the API can be called within a given time frame.
-Skybiometry had the largest imposition on Call Limits as it only allowed 100 API calls to be processed per hour.
+The three APIs reviewed in this report have been summarised in Table \@ref(tab:Emotion-Software-Specs-Table) above.
+A noticeable difference between the three is the amount of times the API can be called within a given time frame.
+Skybiometry had the largest imposition on Call Limits as it only allowed 100 API calls to b e processed per hour.
 Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within one hour, after accounting for the wait time between each group of 20.
@@
 
-The number of emotions shown in the results were not congruent. These differences made it necessary to process the outputs to provide the most comparable results for analysis.
-Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only providing four different emotions.
+There were a different set of emotions in the results provided by each API.
+These differences made it necessary to process the outputs to provide the most comparable results for analysis.
+Microsoft provided the most emotional categories, 'contempt' being the addition that was not provided by Skybiometry or Google.
+Google provided the least, only providing four emotions, joy, sorrow, surprise and anger.
 
@@
 Google provides likelihoods of an emotion occurring on a particular face in categorical options ranging from Very Unlikely to Very Likely.
-Microsoft provide Proportions, ranging between 0 and 1, whereas Skybiometry results in a Confidence value for the emotion occurring in the specified face in values from 0 to 100.
+Microsoft provide Proportions, ranging between 0 and 1, the sum of the emotion values for each face summed to approximately one.
+Whereas Skybiometry results in a confidence value of the emotion occurring in the specified face in values from 0 to 100, these values were not mutually exclusive and resulted in a different sum across each face.
 
-\newpage
+Cost and Access refers to the steps that must be undertaken for a new user to begin Emotion Recognition using each API.
+All options require an account be created with a current email address.
+Google and Skybiometry require payments to be made.
+The Google Vision API provides Facial and Emotion Recognition for $1.50 for Units 1001 - 5,000,000 per month^[https://cloud.Google.com/vision/docs/pricing].
+Skybiometry have three API subscription options that vary in the amount of API calls that can be made per month, day and hour^[https://skybiometry.com/pricing/].
+
 # Procedure
@@
 
-To create a set of individual faces for the APIs to consider we derived small images that were cropped subsets of the 450x800px images.
-The crop was performed to create a new image with a unique name that focused on the area marked as a face by Google^[based on Google’s bounding box coordinates].
-A border to frame the face was also included for visual appeal.
+To create a set of individual faces for the APIs to consider we derived small images that were subsets of the 450x800px images.
+The crop was performed to focus on the area marked as a face by Google^[based on Google’s bounding box coordinates].
 These 1319 new images, of varying sizes, were hosted on Google Drive as individual images.
 
-```{r VisualSet, echo=F, fig.cap = "Three Faces in the image set, after extracting faces from the full broadcast video stills, and the dominant emotion each software recognised for them.
+```{r VisualSet, echo=F, fig.cap = "This figure provides three faces in the image set, after extracting faces from the full broadcast video stills.
+Below the faces are the APIs predominant emotion category recognised in the face.
 \\label{fig:VisualSet}"}
@@
   dl <- d %>% 
-  select(Skybiometry = SEmotion, Microsoft = MEmotion, Google = GEmotion) %>%
+  select(Skybiometry = Skybiometry, Microsoft = Microsoft, Google = Google) %>%
     gather(key = Software, value = Emotion, Microsoft, Skybiometry, Google)
 
-  t <- tableGrob(dl, theme = ttheme_minimal(core=list(fg_params=list(hjust=0, x=0.1)),
-                      rowhead=list(fg_params=list(hjust=0, x=0))), rows = c("", "", ""))
+  t <- tableGrob(dl, theme = ttheme_minimal(core=list(fg_params=list(hjust=0, x=0.1)),rowhead=list(fg_params=list(hjust=0, x=0))), rows = c("", "", ""))
 
@@
 grid.arrange(i1, i2, i3, t1, t2, t3, nrow=2)
-
 ```
@@
 
-As mentioned previously, the results extracted for each face differed across the APIs this made it necessary to produce a comparable set of results for analysis.
+For each individual face a POST request as submitted to each API, these returned POST request objects in a JSON format.
+When this object contained values for the emotional state of a face we considered this to be a 'response'.
+Where the alternative was NA results being returned.
+
+Given the different forms of the outputs produced by each API, we felt a  harmonization process was required prior to undertaking a comparative analysis.
+The goal of the harmonization was to produce Emotion values for each face that would be comparable across the three APIs.
 
@@
 This was easily manipulated to create a data set of the eight numeric emotion values provided for each face.
-In the event that emotion values were not returned for a certain face, a row of NAs will be associated with the unique face ID in the data set.
+In the event that emotion values were not returned for a certain face, a row of NAs is associated with the unique face ID in the data set.
+This data set contained a column for the following emotions: anger, contempt, disgust, fear, happiness,
+neutral, sadness, surprise.
 
-```{r MEexample, echo=F, message=F, fig.cap = "\\label{tab:MEexample}"}
+```{r MEexample, echo=F, results = 'asis', message=F, fig.cap = "\\label{tab:MEexample}"}
 
-MEexample <- ME %>% subset(FileName=="face-1745-1-Go.png")
+MEexample <- ME %>% subset(FileName=="face-1635-1-Go.png")
 
-knitr::kable(MEexample[2:9], digits=6, longtable=TRUE, booktabs = TRUE, caption="The Microsoft API provided eight numerical values, one for each emotion.")
+MEexample <- lapply(MEexample[2:9], function(x){replace(x, x <0.001,0)})
+
+knitr::kable(as.data.frame(MEexample),longtable=TRUE, booktabs = TRUE, digits=3, format.args = list(nsmall=3, digits=3, scientific=FALSE), caption="The Microsoft API provided eight numerical values, one for each emotion.")
 ```
 
-Skybiometry also provided a POST request object in a JSON format.
-However, unlike Microsoft, the results included a True or False Value for each of the seven emotions and a 'confidence value as a percentage from 0 to 100'^[https://skybiometry.com/documentation/#document-21] representing the confidence of the emotion being present on a player's face.
+Table \@ref(tab:MEexample) details the emotion category levels for the first face in Figure \@ref(fig:VisualSet).
+The highest emotion level is for surprise, and the lowest value of 2.78e-05 is associated with contempt.
 
-```{r SBexample, echo=F, fig.cap = "\\label{tab:SBexample}"}
+Skybiometry, unlike Microsoft, the results included a True or False Value for each of the seven emotions and a 'confidence value as a percentage from 0 to 100'^[https://skybiometry.com/documentation/#document-21] representing the confidence of the emotion being present on a player's face.
+Table \@ref(tab:SBexample) contains the confidence values for the first face in Figure \@ref(fig:VisualSet).
+If a confidence value was 50 or above, the emotion 'value' would be labelled True.
+This would have occurred for surprise and disgust.
 
-SBexample <- SB %>% subset(aname=="face-1745-1-Go.png") %>% select(ends_with(".confidence"))
+```{r SBexample, echo=F, results = 'asis', fig.cap = "\\label{tab:SBexample}"}
 
-knitr::kable(SBexample[3:9], digits=6, longtable=TRUE, booktabs = TRUE,
-             col.names = c("neutral", "anger", "disgust", "fear",
-                           "happiness", "sadness", "surprise"),
+SBexample <- SB %>% subset(aname=="face-1635-1-Go.png") %>% select(ends_with(".confidence"))
+
+knitr::kable(SBexample[3:9], longtable=TRUE, booktabs = TRUE,col.names = c("neutral", "anger", "disgust", "fear", "happiness", "sadness", "surprise"),
              caption="The Skybiometry API provided seven numerical Confidence values, one for each emotion.")
@@
 ```{r GEexample, echo=F, fig.cap = "\\label{tab:GEexample}"}
-GEexample <- GE %>% subset(FileName=="face-1745-1-Go.png") %>% select(ends_with("Likelihood"))
+GEexample <- GE %>% subset(FileName=="face-1635-1-Go.png") %>% select(ends_with("Likelihood"))
 
@@
 
-Noticing that the sums of the individual emotions for each face in the Microsoft results was approximately one provided the basis for transformation for the other APIs.
+The same face that had produced high levels of surprise for Microsoft and Skybiometry produced the results in Table \@ref(tab:GEexample).
+The most positive result was the 'Unlikely' categorisation for surprise, this proposes that surprise was more prominent than other emotions but less significant than the other APIs intimated.
+
+\newpage
+### API Result Transformations
+
+Noticing that the sums of the individual emotions for each face in the Microsoft results was approximately one, provided the basis for transformation for the other APIs.
 Dividing the individual Skybiometry emotion confidences by the sum of the confidences would give the proportional likelihood of each emotion being the dominant emotion in a face.
@@
 ```{r SBT, echo=F, fig.cap = "\\label{tab:SBT}"}
-SBT <- SB %>% subset(aname=="face-1745-1-Go.png") %>% select(neutral, anger, disgust, fear, happiness, sadness, surprise)
+SBT <- SB %>% subset(aname=="face-1635-1-Go.png") %>% select(neutral, anger, disgust, fear, happiness, sadness, surprise)
 
-knitr::kable(SBT, digits=6, longtable=TRUE, booktabs = TRUE,
-               caption="The Skybiometry API provided 7 numerical Confidence values, one for each emotion.")
+SBTexample <- lapply(SBT, function(x){replace(x, x <0.001,0)})
+
+knitr::kable(as.data.frame(SBTexample), longtable=TRUE, booktabs = TRUE, digits=3, caption="The Skybiometry API provided 7 numerical Confidence values, one for each emotion.")
 ```
@@
 
-knitr::kable(LT, longtable=TRUE, booktabs = TRUE, caption="")
+knitr::kable(LT,longtable=TRUE, booktabs = TRUE, caption="")
 ```
@@
 
-The process to derive the numeric values for Google followed the process undertaken for Skybiometry values.
+The process to derive the numeric values for Google followed the steps undertaken for Skybiometry values.
 Where the individual emotion confidences were divided by the sum of the emotion confidence values for each face.
-This resulted in congruent emotion data.
+This transformation results in the values seen in Table \@ref(tab:GET), the faces can now be analysed numerical and compared to the other APIs numerical results.
 
@@
 
-GET <- GEP %>% subset(FileName=="face-1745-1-Go.png") %>% 
+GET <- GEP %>% subset(FileName=="face-1635-1-Go.png") %>% 
   select(happiness, sadness, anger, surprise, neutral)
 
-knitr::kable(GET, longtable=TRUE, booktabs = TRUE,
-             col.names = c("happiness", "sadness", "anger", "surprise", "neutral"),
-             caption="The Google Vision API provided four likelihoods, one for each emotion.")
+GETexample <- lapply(GET, function(x){replace(x, x <0.001,0)})
+
+knitr::kable(as.data.frame(GETexample), longtable=TRUE, booktabs = TRUE, digits=3, caption="The Google Vision API provided five proportions, one for each emotion and a neutral category.")
 ```
 
+### Predominant Emotion Categorisations
+
+To simplify the analysis, we assigned a predominant emotion for each API result. This allowed for clearer comparisons of the emotion results for individual faces across the three APIs.
+For Google, Skybiometry and Microsoft, the emotion proportion levels for each individual face were considered, the maximum proportion value of each APIs emotion set was deemed the dominant emotion for each face.
+Recalling that there is a difference in the amount of emotion categories considered by each software.
+
+For each individual face this resulted in three dominant emotion classifications, one per API.
+The dominant emotion would be one of seven emotions for Google, one of eight for Microsoft, and one of five for Google.
+
 \newpage
-# Analysis
+# Results
 
-Each API returned a different amount of non null results.
-Microsoft produced emotion results for `r sum(!is.na(ME$anger))` faces.
-This was more than Skybiometry, as it produced only `r sum(!is.na(SB$anger))` results for emotions on faces.
-Google provided the most, with  `r sum(!is.na(GE$anger))` emotion results^[As the initial set was faces identified by Google there is the possibility of bias toward being able to identify emotions in faces it was able to find originally.].
-
-```{r playerNonplayer, eval=FALSE,fig.cap="\\label{tab:playerNonPlayer}"}
-#Apply a machine learning algorithm to face recognition data, and software provided for fitting model, aiming to classify whether an identified face is a player or not player
-ME <- ME %>% rowwise %>% mutate(Player = ifelse(detect=="Player", "Player","NotPlayer")) %>%  mutate(Player01 = ifelse(Player=="Player",1,0))
-
-gplayer = glm(Player01 ~ bg+shotangle+obscured+headangle+glasses+visorhat, data = GE, family=binomial(logit))
-
-gpm <- model.matrix(gplayer)
-
-gpmNet = glmnet(gpm, as.vector(GE$Player01))
-
-pot(gpmNet)
-
-#cv of model
-cvgpmNet = cv.glmnet(gpm, as.vector(GE$Player01),family = "binomial", type.measure = "class")
-
-plot(cvgpmNet)
-summary(gplayer)
-coef(cvgpmNet, s = "lambda.min")
-```
+Each API returned a different amount of total responses. Microsoft produced emotion results for `r sum(!is.na(ME$anger))` faces, 55.497% of the faces provided.
+This was more than Skybiometry, as it produced only `r sum(!is.na(SB$anger))` results for emotions on faces. This is 48.103% of the set of faces.
+Google provided the most, 94.162% of the faces, `r sum(!is.na(GE$anger))`, were given emotion results^[As the initial set was faces identified by Google there is the possibility of bias toward being able to identify emotions in faces it was able to find originally.].
 
 ```{r NonNullFaces, fig.cap = "\\label{fig:NonNullFaces}", results = 'asis'}
-
-J4 <-J4 %>% rowwise() %>%
+J4 <- J4 %>% rowwise() %>%
   mutate(Gna = ifelse(!is.na(Google), TRUE, FALSE)) %>%
@@
 
+#Gneu <- DE %>% filter(is.na(Microsoft) & is.na(Skybiometry))
+#table(Gneu$Google)
+
 nfft<-ftable(J4$Gna, J4$Mna, J4$Sna, dnn = c("Google", "Microsoft", "Skybiometry"))
@@
 stargazer(format(nfft, quote=FALSE, justify="right"),title = "Emotion results were found by all three APIs for 364 common faces, none of the APIs produced results for 10 player faces.
-Google was able to produce 382 results that Skybiometry and Microsoft did not.", header=FALSE, type="latex")
+Google was able to produce 380 results that Skybiometry and Microsoft did not.", header=FALSE, type="latex")
 ```
+
+### Player Faces
+
+```{r playerNonplayer,results = 'asis', fig.cap=" \\label{tab:playerNonPlayer}"}
+#Apply a machine learning algorithm to face recognition data, and software provided for fitting model, aiming to classify whether an identified face is a player or not player
+ME <- ME %>% rowwise %>% mutate(Player = ifelse(detect=="Player", "Player","NotPlayer")) %>%  mutate(Player01 = ifelse(Player=="Player",1,0)) 
+GE <- GE %>% rowwise %>% mutate(Player = ifelse(detect=="Player", "Player","NotPlayer")) %>%  mutate(Player01 = ifelse(Player=="Player",1,0))
+
+gplayer = glm(Player01 ~ bg+shotangle+obscured+headangle+glasses+visorhat, data = GE, family=binomial(logit))
+
+gplconfint <- as.data.frame(confint(gplayer)) %>% 
+  mutate(`exp(2.5%)` = exp(`2.5 %`)) %>% 
+  mutate(`exp(97.5%)` = exp(`97.5 %`)) %>%
+  cbind(rownames(confint(gplayer)), exp(gplayer$coefficients), .) %>%
+  select(`exp(Estimates)` = `exp(gplayer$coefficients)`, `exp(2.5%)`, `exp(97.5%)`)
+
+knitr::kable(gplconfint[2:9,] ,longtable=TRUE, booktabs = TRUE, digits=3, caption="A logisitic regression was undertaken to show how certain image attributes contribute to the likelihood of the face being a player.")
+```
+
+The regression coefficients are the change in the likelihood of a face being a player if the category is true for a face.
+The most significant predictors of a response are outlined in the table above.
+It can be seen that when the image was taken at a player's "Shoulder Height" then it is, on average, 4.45 times more likely to be a "Player" than a fan or staff member on court.
+When the head angle is "Other", it is between 1.34 and 3.87 times more likely to be a Player than faces that have been captured front on, at the 5% level of confidence.
 
@@
 Microsoft produced emotion results for `r sum(!is.na(MEP$anger))` player's faces.
-Skybiometry, produced `r sum(!is.na(SBP$anger))` and Google provided `r sum(!is.na(GEP$anger))` emotion results.
+Skybiometry, produced `r sum(!is.na(SBP$anger))` and Google provided `r sum(!is.na(GEP$anger))` emotion results for faces.
 
@@
 
-```{r GEPhists, fig.cap = "It can be seen that there are significant proportions of faces where the non neutral emotions occur close to zero.
+```{r GEPhists, fig.width=9, fig.cap = "It can be seen that there are significant proportions of faces where the non neutral emotions occur close to zero.
 This is balanced by the large percentage, over 75%, where the neutral value of just under .75 occurred.
@@
   geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
-  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("") + theme(axis.text.x = element_text(angle = 20))
 
-ggjoG <- ggplot(GEP, aes(x=happiness)) + 
+gghaG <- ggplot(GEP, aes(x=happiness)) + 
   geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
-  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("") + theme(axis.text.x = element_text(angle = 20))
 
@@
   geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
-  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("") + theme(axis.text.x = element_text(angle = 20))
 
-ggsoG <- ggplot(GEP, aes(x=sadness)) + 
+ggsaG <- ggplot(GEP, aes(x=sadness)) + 
   geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
-  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("") + theme(axis.text.x = element_text(angle = 20))
 
@@
   geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +
-  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("") + theme(axis.text.x = element_text(angle = 20))
 
-grid.arrange(gganG,ggjoG,ggneG,ggsoG,ggsuG,nrow=2,
+grid.arrange(ggneG,
+             gganG,
+             gghaG,
+             ggsaG,
+             ggsuG,
+             nrow=2,
              top=textGrob("Google Distribution of Emotion Porportions",
@@
 
-```{r SBPhists, fig.cap = "The distributions show that over 70% of faces had levels of happiness and neutrality at, or close to, 0.
+```{r SBPhists, fig.width=9, fig.cap = "The distributions show that over 70% of faces had levels of happiness and neutrality at, or close to, 0.
 The distributions show that there are very little faces with specific emotion levels above 50%.
@@
 \\label{fig:SBPhists}"}
-gganS <- ggplot(SBP, aes(x=anger))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+gganS <- ggplot(SBP, aes(x=anger))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("") + theme(axis.text.x = element_text(angle = 20))
 
-gghaS <- ggplot(SBP, aes(x=happiness))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+gghaS <- ggplot(SBP, aes(x=happiness))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggneS <- ggplot(SBP, aes(x=neutral))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggneS <- ggplot(SBP, aes(x=neutral))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggsaS <- ggplot(SBP, aes(x=sadness))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggsaS <- ggplot(SBP, aes(x=sadness))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggsuS <- ggplot(SBP, aes(x=surprise))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggsuS <- ggplot(SBP, aes(x=surprise))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggdiS <- ggplot(SBP, aes(x=disgust))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggdiS <- ggplot(SBP, aes(x=disgust))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggfeS <- ggplot(SBP, aes(x=fear))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggfeS <- ggplot(SBP, aes(x=fear))+  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-grid.arrange(gganS, gghaS, ggneS, ggsaS, ggsuS, ggdiS, ggfeS,nrow=3,
+grid.arrange(ggneS,
+             gganS, 
+             ggdiS, 
+             ggfeS, 
+             gghaS, 
+             ggsaS, 
+             ggsuS,nrow=2,
              top=textGrob("Skybiometry Distribution of Emotion Porportions",gp=gpar(fontsize=20,font=3)), 
@@
 
-```{r MEPhists, fig.cap="There were many faces that returned high neutral values.
+```{r MEPhists,fig.width=9, fig.cap="There were many faces that returned high neutral values.
 This is matched by the high percentages of faces where the proportion levels were at, or close to, zero.
@@
 
-gganM <- ggplot(MEP, aes(x=anger)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+gganM <- ggplot(MEP, aes(x=anger)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-gghaM <- ggplot(MEP, aes(x=happiness)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+gghaM <- ggplot(MEP, aes(x=happiness)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggneM <- ggplot(MEP, aes(x=neutral)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggneM <- ggplot(MEP, aes(x=neutral)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggsaM <- ggplot(MEP, aes (x=sadness)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggsaM <- ggplot(MEP, aes (x=sadness)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggsuM <- ggplot(MEP, aes(x=surprise)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggsuM <- ggplot(MEP, aes(x=surprise)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggdiM <- ggplot(MEP, aes(x=disgust)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggdiM <- ggplot(MEP, aes(x=disgust)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggfeM <- ggplot(MEP, aes(x=fear)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggfeM <- ggplot(MEP, aes(x=fear)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-ggcoM <- ggplot(MEP, aes(x=contempt)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+ggcoM <- ggplot(MEP, aes(x=contempt)) +  geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) + coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-grid.arrange(gganM, gghaM, ggneM, ggsaM, ggsuM, ggdiM, ggfeM, ggcoM,nrow=3, 
-             top=textGrob("Microsoft Distribution of Emotion Porportions", gp=gpar(fontsize=20,font=3)), left =("Percentage of Emotion values"))
-
+grid.arrange(ggneM, 
+             gganM, 
+             ggcoM, 
+             ggdiM, 
+             ggfeM, 
+             gghaM, 
+             ggsaM, 
+             ggsuM,
+             nrow=2,top=textGrob("Microsoft Distribution of Emotion Porportions", gp=gpar(fontsize=20,font=3)), left =("Percentage of Emotion values"))
 ```
@@
 ###Predominant Emotions
-To contrast the emotion results for certain faces a 'predominant' emotion was designated to each face.
-Where the emotion with the maximum proportion value was deemed the 'predominant' emotion for a particular face.
+Alize Cornet's predominant emotion in the first example image in Figure \@ref(fig:VisualSet) has been considered by all three APIs and their classifications can be seen in the table below her image.
+Table \@ref(tab:MEexample), and Table \@ref(tab:SBexample), show the numeric proportions of all emotions for this image and they show that surprise is the predominant expression according Microsoft and Skybiometry.
+This differs from Google's classification as the Unlikely classification in Table \@ref(tab:GEexample) resulted in a high neutral value being incorporated into the emotion category proportions considered when allocating the predominant emotion to the face.
 
-This resulted in one of seven emotions for Google, one of eight for Microsoft, and one of five for Google.
-This also required the assumption that happiness is equivalent to happiness, and sadness to sadness.
+If we consider the predominant emotions of the faces considered by the Google API, given a reasonable number of faces, the Predominant Emotions would be expected to support the results shown previously in Figure \@ref(fig:GEPhists).
 
-```{r predominant, results = 'asis', fig.cap = "\\label{tab:predominant}"}
+Google provided the least possible emotion categories, this drove the choice to split the results below according to the predominant emotion classifications made by Google.
+
+The following tables have the predominant emotion classifications for Microsoft in the rows, and the columns denoted classifications by Skybiometry.
+
+```{r Gneutpredom, results = 'asis', fig.cap = "\\label{tab:Gneutpredom}"}
 #Table including Google
-#ftable(DE$GEmotion, DE$SEmotion, DE$MEmotion, dnn = c("Google", "Skybiometry", "Microsoft"))
+#ftable(DE$Google, DE$Skybiometry, DE$Microsoft, dnn = c("Google", "Skybiometry", "Microsoft"))
 
-ft<-ftable(DE$GEmotion, DE$MEmotion, DE$SEmotion, dnn = c("Google","Microsoft","Skybiometry"))
+DE <- read_csv("data/DominantEmotions.csv")
+DE$Microsoft <- factor(DE$Microsoft, levels =c("neutral", "anger", "happiness", "sadness", "surprise"))
+DE$Skybiometry <- factor(DE$Skybiometry, levels =c("neutral", "anger", "disgust", "fear", "sadness", "surprise"))
 
-stargazer(format(ft, quote=FALSE, justify="right"),title = "This shows the agreement between the emotions recognised by Microsoft and Skybiometry", header=FALSE, type = "latex")
+PGneu <- subset(DE, DE$Google=="neutral") 
+PGneut <- table(PGneu$Microsoft, PGneu$Skybiometry, dnn = c("Microsoft","Skybiometry"), useNA="always")
+
+knitr::kable(PGneut,longtable=TRUE, booktabs = TRUE,
+        caption="Where Google provided the Emotional Result of Neutral; Microsoft associated high neutral values with many of these faces, however Skybiometry only classifed 3 of these faces as neutral.")
 ```
-Skybiometry emotion recognition's are shown in the rows, and Microsoft's in the columns. 
-There were many instances where Skybiometry allocated an emotion as the predominant expression while Google and Microsoft designated it as neutral, this was expected as only 3 faces were categorised as neutral by Skybiometry.
-These faces were categorised as neutral by both Google and Microsoft.
 
-As neutral was a prominent category for Microsoft and Google, we considered where neutral was the dominant emotion and grouped the remaining emotions into a non-neutral category.
+This result supports the analysis of the numeric proportions found by Skybiometry in Figure \@ref(fig:SBPhists).
+The three faces categorised as neutral must have had unusually high levels of neutral compared to the proportions of other emotions.
+This low number of occurrences is likely due to almost 75% of faces having a neutral level at 0.
 
-```{r neutral-non, results='asis', fig.cap="\\label{tab:neutral-non}"}
-DEne<-DE %>% rowwise()%>%
-  mutate(GEneutral = ifelse(GEmotion=="neutral", "neutral","non-neutral")) %>%
-  mutate(SEneutral = ifelse(SEmotion=="neutral", "neutral","non-neutral")) %>%
-  mutate(MEneutral = ifelse(MEmotion=="neutral", "neutral","non-neutral"))
+Recalling that a neutral proportion was implied when Google did not allocate high likelihoods of emotions being present.
+The bias Google showed to allocating a neutral predominant emotion resulted from the high amount of low proportions of emotions, shown visually in \@ref(fig:GEPhists).
+Over 75% of faces had a neutral level of 0.75.
+This is an extremely high amount of faces with little emotion recognised.
+This is why Table \@ref(tab:Gneutpredom) above showing NA values for many faces when Google considered them to be predominantly neutral may imply that it is inclined to return results, even if these results are not informative.
+
+```{r Ghappredom, results = 'asis', fig.cap = "\\label{tab:Ghappredom}"}
+DE$Microsoft <- factor(DE$Microsoft, 
+                    levels =c("neutral","happiness"))
+DE$Skybiometry <- factor(DE$Skybiometry, levels =c("anger", "sadness", "surprise"))
+
+PGhap <- subset(DE, DE$Google=="happiness")
+PGhapt<-table(PGhap$Microsoft, PGhap$Skybiometry, dnn = c("Microsoft","Skybiometry"), useNA="always")
+
+knitr::kable(PGhapt,longtable=TRUE, booktabs = TRUE, caption="Where Google provided the Emotional Result of Happiness. The most common Skybiometry response was ")
+```
+
+It can be seen that when Google classified faces as Happiness Table \@ref(tab:Ghappredom) shows less faces to be considered by Microsoft and Skybiometry than Table \@ref(tab:Gneutpredom) above when Google classified faces as Neutral.
+Many of these faces were not emotionally classified by Microsoft and Skybiometry resulting in 34 NAs.
+There were no faces considered to be displaying Happiness by all three APIs, however Microsoft did consider 9 faces to be happiness that Skybiometry did not return emotion results for.
+
+These results were expected given that in Figure \@ref(fig:GEPhists) the Happiness histogram showed almost 90% of faces with the lowest possible level of happiness.
+Leaving just over 10% to be showing even a small level of the likelihood of happiness appearing on the face.
+
+```{r Gangpredom, results = 'asis', fig.cap = "\\label{tab:Gangpredom}"}
+
+DE$Microsoft <- factor(DE$Microsoft, 
+                    levels =c("neutral"))
+DE$Skybiometry <- factor(DE$Skybiometry, 
+                    levels =c("anger", "sadness"))
+
+PGang <- subset(DE, DE$Google=="anger")
+PGangt<-table(PGang$Microsoft, PGang$Skybiometry, dnn = c("Microsoft","Skybiometry"), useNA="always")
+
+knitr::kable(PGangt,longtable=TRUE, booktabs = TRUE, caption="Where Google provided the Emotional Result of Anger")
+
+DE$Microsoft <- factor(DE$Microsoft, 
+                    levels =c("anger", "disgust", "happiness","neutral",  "sadness","surprise"))
+```
+
+When Google provided a result of Anger, the only predominant emotion supplied by Microsoft was Neutral.
+It is a very a small group of faces, 13 of the set of 1319, and 5 of these were also considered to be anger by Skybiometry.
+
+The difference between the amount of neutral predominant categorisations by Microsoft and Google in comparison to Skybiometry lead to further investigations into neutral compared to non neutral predominant categorisations.
+
+As neutral was a prominent category for Microsoft and Google, we considered two groups in the following analyses, one where neutral was the predominant emotion and the other group was created by combining the remaining emotions into a non-neutral category.
+
+```{r neutralnon, results='asis', fig.cap=" \\label{tab:neutralnon}", cache=FALSE}
+DEne <- DEne %>% rowwise() %>%
+  mutate(Skybiometry = ifelse(is.na(Skybiometry), "NA", 
+         ifelse( Skybiometry=="neutral", "neutral", "non-neutral")))%>%
+    mutate(Google = ifelse(is.na(Google), "NA", 
+         ifelse(Google=="neutral", "neutral", "non-neutral")))%>%
+    mutate(Microsoft = ifelse(is.na(Microsoft), "NA", 
+         ifelse(Microsoft=="neutral", "neutral", "non-neutral")))
 
 # neutral flat table
-nft<-ftable(DEne$GEneutral, DEne$MEneutral,DEne$SEneutral, dnn = c("Google","Microsoft","Skybiometry"))
+DEne$Microsoft <- factor(DEne$Microsoft, 
+                    levels =c("neutral", "non-neutral", "NA"))
+DEne$Skybiometry <- factor(DEne$Skybiometry, 
+                    levels =c("neutral", "non-neutral", "NA"))
+DEne$Google <- factor(DEne$Google, 
+                    levels =c("neutral", "non-neutral", "NA"))
 
-stargazer(format(nft, quote=FALSE, justify="right"), header=FALSE, type = "latex", title ="This shows the agreement between non-neutral and neutral faces recognised by Goole, Microsoft and, Skybiometry.
+nft<- ftable(DEne, row.vars = c("Google", "Microsoft"), col.vars = c("Skybiometry"))
+
+stargazer(format(nft, quote=FALSE, justify="right"), title = "This shows the agreement between non-neutral and neutral faces recognised by Goole, Microsoft and, Skybiometry.
 Only three faces were categorised as neutral.
-Of these, Google was much more likely to categorise as neutral.")
+Of these, Google was much more likely to categorise as neutral.", header=FALSE, type="latex")
 ```
 
-The following Figure \@ref(fig:neutrality) displays a Scatter Plot Matrix that captures the pairwise variability in the Neutral proportion levels across APIs.
+Skybiometry is less likely to categorise a face as neutral than Microsoft or Google.
+It can be seen that 348 faces were considered neutral by Google but no emotional information was gained from Microsoft or Skybiometry. 
+A large cross section category is where Google and Microsoft categorised a face as neutral and Skybiometry considered it to be non neutral, this happened for 299 faces.
+There is only one face that was found by Skybiometry to be non-neutral that Google and Microsoft did not return emotional information for.
+
+Focusing only on the neutral proportion levels for every face leads us to examine the following.
+Figure \@ref(fig:neutrality) displays a Scatter Plot Matrix that captures the pairwise variability in the Neutral proportion levels across APIs.
 
 ```{r neutrality, fig.cap = "The Scatter Plot Matrix shows the variablitiy in the Neutral proportion levels.
-The -0.01 correlation value for Google and Skybiometry show that they do not behave either in a similar way, or inversely.
-They are uncorrelated.\n Some high values of neutrality for Google are matched to some high levels found by Skybiometry.
+The -0.01 correlation value for Google and Skybiometry show that they do not behave in a similar way, or inversely.
+They are uncorrelated.
+Some high values of neutrality for Google are matched to some high levels found by Skybiometry.
 However, in the lower ranges of both there is a lot of variability in proportion values.\\label{fig:neutrality}"}
@@
 We consider that there were attributes of the faces captured that may have influenced the likelihood of a neutral result in the cases of Google and Skybiometry.
-To understand this we consider the associations between differing attribute values and the neutral results.
+To understand this we consider the associations between the different attribute values and the neutral results.
 
-```{r LogisticRegression, eval= FALSE, fig.width=7, fig.cap = "\\label{LogisticRegression}"}
+```{r LogisticRegression, results = 'asis', fig.width=7, fig.cap = " This table \\label{tab:LogisticRegression}"}
 #Add neutral columns to data sets
@@
 #create a model
-Mne = glm(neutral01 ~ bg+shotangle+obscured+headangle+glasses+visorhat+, data = MEP1, family=binomial(logit))
+Mne = glm(neutral01 ~ bg+obscured+glasses, data = MEP1, family=binomial(logit))
 
-Mnemm <- model.matrix(Mne)
+#summary(Mne)
 
-Mnegn = glmnet(Mnemm, as.vector(MEP1$neutral01))
+Mneconfint <- as.data.frame(confint(Mne)) %>% 
+  mutate(`exp(2.5%)` = exp(`2.5 %`)) %>% 
+  mutate(`exp(97.5%)` = exp(`97.5 %`)) %>%
+  cbind(rownames(confint(Mne)), exp(Mne$coefficients), .) %>%
+  select(`exp(Estimates)` = `exp(Mne$coefficients)`, `exp(2.5%)`, `exp(97.5%)`)
 
-#cv of model
-cvMnegn = cv.glmnet(Mnemm, as.vector(MEP1$neutral01))
-
-plot(cvMnegn)
-
-coef(cvMnegn, s = "lambda.min")
-
-#A backward stepwise regression approach led to the following nmodel with a low AIC:
-
+knitr::kable(Mneconfint[2:5,],longtable=TRUE, booktabs = TRUE, digits=3, caption=" ")
 ```
 
-## Selecting an API
-For these purposes an API that would provide informative and accurate results was a top priority.
-This required it to return emotion information for a reasonable amount of faces, and that this information was reliable.
-
-It has been shown through the report that Goggle returned emotional information for `r sum(!is.na(GEP$anger))` player's faces, the highest amount of emotion results for the faces provided to three APIs.
-However, in Table \@ref(fig:neutrality) it is seen that only 31 of these faces gave results that considered the faces to be premoninantly a non-neutral expression.
-This limited resulting information is not helpful in extracting a player's emotional state.
-Figure \@ref(fig:GEPhists) shows that anger, happiness, sadness and surprise often had a level of 0.10 for faces.
-This is equivalent to the original output of it being 'Very Unlikely' that the emotion appeared on the given face.
-Due to these results, Google will not be appropriate for further exploration.
-
-Microsoft provided `r sum(!is.na(MEP$anger))` emotion results for player's faces, these numeric results shown in Table \@ref(tab:MEexample) were in an optimal format for analyses.
-These results also had the most variability is possible emotions, this could be seen as a positive as it may allow an emotion to be directly identified in comparison to the assumptions needed to be applied to Google's results in Table \@ref(tab:GEexample).
-
-Microsoft provided many results where the amount attributed to an emotion was zero, this was accompanied by high values of neutral being counted in these faces, as shown in Figure \@ref(MEPhists).
-This is not unreasonable as there are many factors that may have influenced the neutral results we were given, such as the players having strong control over their facial expressions or the faces passed to the software being sub optimal for recognition.
-
-The results from Microsoft were still deemed to be preferrable to those of Microsoft due to the limits on it's API impeding on any future use of the API for our purposes.
-While more facial emotion results were gained, majority of the emotion proportions after tranformations were still below 0.5 for the predominant emotions.
-
-The conclusion of these comparisons points to Microsoft as a good API that provides a useful output.
-Its limits do not impose as heavily as Skybiometry's do, and it provided many of the same neutral results that Google did, showing that it may be image, rather than API, reasons for returning a neutral dominant emotion result.
+When a player's face is obscured it is, on average, 1.95 times more likely to to be considered as predominantly neutral in expression.
+This was expected as it may interfere with the Microsoft API's ability to distinguish features necessary to determine a predominant emotion on a face.
 
 \newpage
-## Possible Application
-From this point we will give an example of an application of this emotional data in a tennis setting.
-This information would help to understand a player's emotional variability on the court, and may help in coaches training players to control what is physically visible as to not advantage their opponent by giving them an indication to a players emotional state.
+# Possible Application
+From this point we will give an example of a use for this emotional data in a tennis setting.
+Should an API prove to be returning valid emotion categorizations this information would help to understand a player's emotional variability on the court.
+It could then be used help coaches training players to control what is physically visible as to not advantage their opponent by giving them an indication to a player's emotional state.
 
@@
 
-```{r playerHists}
+```{r playerHists, fig.width=9}
 
@@
 
-  ggMEPne<-ggplot(data, aes(x=neutral)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  ggMEPne<-ggplot(data, aes(x=neutral)) + geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("") + theme(axis.text.x = element_text(angle = 20))
 
-  ggMEPan<-ggplot(data, aes(x=anger)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  ggMEPan<-ggplot(data, aes(x=anger)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-  ggMEPdi<-ggplot(data, aes(x=disgust)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  ggMEPdi<-ggplot(data, aes(x=disgust)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-  ggMEPfe<-ggplot(data, aes(x=fear)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  ggMEPfe<-ggplot(data, aes(x=fear)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-  ggMEPha<-ggplot(data, aes(x=happiness)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  ggMEPha<-ggplot(data, aes(x=happiness)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-  ggMEPsa<-ggplot(data, aes(x=sadness)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  ggMEPsa<-ggplot(data, aes(x=sadness)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-  ggMEPsu<-ggplot(data, aes(x=surprise)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  ggMEPsu<-ggplot(data, aes(x=surprise)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
-  ggMEPco<-ggplot(data, aes(x=contempt)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")
+  ggMEPco<-ggplot(data, aes(x=contempt)) +    geom_histogram(binwidth=0.055, aes(y=..count../sum(..count..))) +   coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + ylab("")+ theme(axis.text.x = element_text(angle = 20))
 
@@
                ggMEPan, 
+               ggMEPco,
                ggMEPdi,
@@
                ggMEPsa,
-               ggMEPsu, 
-               ggMEPco,nrow=3,
-             top=textGrob(paste0("Microsoft Distribution of Emotion Porportions for ", player), gp=gpar(fontsize=10,font=3)), 
+               ggMEPsu,nrow=2,
+             top=textGrob(paste0("Microsoft Distribution of Emotion Porportions for ", player), gp=gpar(fontsize=18,font=3)), 
              left = ("Percentage of Emotion values"))
@@
 
-MicrosoftHists()
-
 ```
 
+```{r TBHists, fig.width=9, fig.cap = "\\label{fig:TBHists}"}
+MicrosoftHists("TBerdych")
+```
+
+Tomas Berdych had the most faces recognised, 25 of the 943 player faces.
+Figure \@ref(fig:TBHists) shows a similar distribution to that seen in the full Microsoft Distribution in \@ref(fig:MEPhists).
+There are no values of neutral that occur for more than 0.25 of the total set of images of Berdych's face however the neutral values are all above 0.10 for Berdych.
+Similarly to the full distribution, the distribution that departs the furtherst from the distribution of the whole sample is for anger, where there are proportionally less faces with an anger value of zero, with around .25 of the faces having an anger value of 0.1.
+
+```{r ACHists, fig.width=9, fig.cap = "\\label{fig:ACHists}"}
+MicrosoftHists("ACornet")
+```
+
+Assumptions about the algorithm's performance cannot be made based on the results produced when considering Alize Cornet's expressions.
+Microsoft was only able to produce emotional information for 6 of the 12 images captured of Cornet's face.
+However it does show levels of surprise that are quite high, especially when compared to the full distribution.
+
 ```{r playerProfiles}
-
 playerProfileBars <- function(player = NA, data=MEP1){
@@
   }
-  title <- "Emotional Variability"
+  title <- "Predominant Emotions"
   if (!is.na(player)){
@@
 
-ppbM <- playerProfileBars(data=MEP1)
-ppbS <- playerProfileBars(data=SBP1)
+```
 
-grid.arrange(ppbM, ppbS, nrow=1)
+The bar charts in Figure \@ref(fig:ACHists) below show the amount of images of a player that were classified as each predominant emotion.
+This analysis applied to a larger set of faces of each player would begin to show which emotions a player often displays.
+In the case of a software being biased by a player's facial features you would see a similar situation to what is displayed below in the case of Cornet.
 
-playerProfileBars("CSurezNavarro", data=MEP1) 
-playerProfileBars("AFriedsam", data=MEP1)
-playerProfileBars("ACornet", data=MEP1) 
-table(GEP1$playerName)
+```{r TBbars, fig.cap = "\\label{fig:ACHists}"}
+TBbar<- playerProfileBars("TBerdych", data=MEP1)
+ACbar<- playerProfileBars("ACornet", data=MEP1)
+
+grid.arrange(TBbar, ACbar, nrow=1)
 ```
+
+\newpage
+# Discussion
+
+We attempted to derive emotional information for faces captured in frames of broadcast streams of tennis matches. 
+Three APIs were accessed online and we were able to collect the emotional information they provided for the 1319 faces in the set.
+However, responses did not contain emotional information for all of the provided faces.
+Microsoft and Skybiometry responded with many NA results, meaning they did not find any emotional information for the face, and Google responded that a large proportion of the faces were "very unlikely" to be displaying emotions.
+
+It has been shown that Goggle returned emotional information for `r sum(!is.na(GEP$anger))` player's faces, the highest amount of emotion results for the faces provided to three APIs.
+This may have been due to the faces being used already having been detected by Google previously.
+It was unexpected that Skybiometry would only be able to produce emotional results for just under half of the images presented to it.
+
+There were only 364 faces were found by all APIs, 113 by only Microsoft and Google as well as 53 found by Skybiometry and Google.
+However the amount of faces found by only Google, 380, was higher than anticipated.
+
+As there was already disagreement between the APIs in finding faces we were inclined to believe that the approaches to classifying faces, and therefore emotions, may be different.
+While more facial emotion results were found by Google, the majority of the emotion proportions after transformations were still below 0.5 for the predominant emotions.
+This amount of 'Very Unlikely' responses to emotions being present on a faces was surprising.
+We did not expect that Google would be reserved in aknowledging the prescence of emotion.
+Microsoft provided `r sum(!is.na(MEP$anger))` emotion results for player's faces.
+These results had the most emotion categories, we considered this to be a benefit to us as it may allow an emotion to be directly identified beyond the four Google categories.
+After the calculation of a predominant emotion we were surprised to find `r sum(DEne$Google=="non-neutral")/sum(DEne$Google!="NA")` of the faces Google returned results for were non-neutral.
+This small amount of emotional information would not be helpful in extracting a player's emotional state and tracking changes throughout a match.
+Given that both Google and Microsoft were not inclined to allocate high proportion levels to the array of emotions it was worrisome that Skybiometry would return high confidence values for the emotion being present on the face.
+However, Microsoft provided many results where the amount attributed to an emotion was zero, this was accompanied by high values of neutral being counted in these faces, as shown in the emotion histograms of Google and Microsoft.
+This is not unreasonable as there are factors that may have influenced the neutral results, such as the faces passed to the software being sub optimal for recognition.
+
+We suspected that the amount of faces classified as neutral would mean that only extremely obvious facial expressions would be considered predominant emotions.
+Therefore the intersections of the predominant emotion classifications were expected to be quite high, and the strong disagreement between the APIs was unexpected.
+It was surprising that no faces in the set had the same predominant emotion result from all three softwares, though there were a small portion of faces classified as the same predominant emotion by Microsoft and Skybiometry.
+This enforces the need for further validation to be conducted on these APIs.
+This blatant disagreement led to confusion in a choice of API should further work using this method be pursued.
+
+The research aim was to develop methods to collect accurate information about the facial expressions of elite tennis athletes during matchplay.
+We cannot establish, without further validation, that three currently available APIs are not capable of accurate detection of player's emotions when analyzing the broadcast video matches.
+Yet, the alternative approach to answer the question of whether a player's mental state correlates with their on court performance is worth pursuing.
+This would allow the coaches and players evidence of the player's ability to focus and perform mentally in elite tennis matches.
+If there are correlations between the engagement or concentration levels and their performance during a match this would help players recognise how their mental state impacts them.
+
+Given the low amounts of emotion classifications we considered that the FACS method may not be the most effective for our purposes as the amount of neutral results may detract from any attempt to discover correlations between emotions and performance.
+In this elite tennis setting we may gain more informative insights into the mental state of a player from searching for the levels of concentration and engagement rather than emotions.
+We should also recognise that the APIs are attempting to perform with sub optimal images and any further work may also be limited if the sample will be the size used for this set.
+To make inferences about a player and their mental state the set would need to be expanded to consider individuals in more depth.
+If the solution is able to be trained for individuals this would help prevent facial features influencing FACS results.

### 2017-06-18 Internship/EmotionsAnalysis.Rmd
Presentation Changes

@@
 ```{r combined}
+S0 <- select(GFP, FileName, type)
 S1 <- select(SBP1, FileName = aname , SEmotion = Emotion)
@@
 S3 <- select(GEP1, FileName, GEmotion = Emotion)
-J1 <- full_join(S1, S2, by = "FileName")
+J <- full_join(S0, S1, by = "FileName")
+J1 <- full_join(J, S2, by = "FileName")
 J2 <- full_join(J1, S3, by = "FileName")
+
+J2 <- select(J2, FileName, Skybiometry = SEmotion,
+             Microsoft = MEmotion, Google = GEmotion)
+
+write.csv(J2, "DominantEmotions.csv", row.names = FALSE)
 
@@
 ```{r DisplayFaces}
-AKimgsG<-GEP %>% filter(player2=="ACornet")
+AKimgsG<-GEP %>% filter(player1=="NDjokovic")
 AKimgsG<-AKimgsG %>% filter(detect=="Player")
@@
 length(AKlist)
-
+AKlist[6]
 DisplayFaces(AKlist)

### 2017-06-20 Report06-12.Rmd
moved folders

@@
 #csv files:
-ALLmetaIMGnamed<-read_csv("ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
-SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
-FaceAttributes<-read_csv("TableCSVs/FaceAttributes.csv")
-SolutionSpecs<-read_csv("TableCSVs/SolutionSpecifications.csv")
+ALLmetaIMGnamed<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+SceneAttributes<-read_csv("../TableCSVs/SceneAttributes.csv")
+FaceAttributes<-read_csv("../TableCSVs/FaceAttributes.csv")
+SolutionSpecs<-read_csv("../TableCSVs/SolutionSpecifications.csv")
 

### 2017-06-20 Report06-12.Rmd
directory references

--- 2017-03-29 Report06-12.Rmd
@@
 #csv files:
-ALLmetaIMGnamed<-read_csv("ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+ALLmetaIMGnamed<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
 SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")

### 2017-06-20 Report06-12.Rmd
figures directory reference

@@
   for(i in imgList){
-    img <- image_read(paste0("images/", i))
+    img <- image_read(paste0("figures/", i))
 

### 2017-06-27 Report06-12.Rmd
Section Headings
changed the nme of section headings

--- 2017-06-20 Report06-12.Rmd
@@
 
-####Selecting the software
+####Software Selection
 The choice of the initial software considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'
@@
 
-####Software Recognition
+####Software Interaction
 The software choices allowed for POST requests to be sent via the internet.
@@
 
-## Regression
+### Modelling Face Detection Probabiity
 
@@
 
-### Discussion
+### Results Overview
 Graph 1, the Bar Chart of the Face Bounding Boxes promotes Google as the best possible software for a facial recognition application in tennis.
@@
 
-## Conclusions 
 Employ the Google Vision API, which would allow the use of still images, or video (TEST VIDEO) files, reducing the need for stills.

### 2017-06-27 Report06-12.Rmd
Auto stash before merge of "master" and "steffMVP/master"

@@
 library(xtable)
+library(ggthemes)
+library(EBimage)
 
@@
   ggplot(aes(x=type, y=`Pr(<|z|)`)) +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
   geom_col(aes(fill=significant)) + 
-  facet_wrap(~ variable)
+  facet_wrap(~ variable) +
+  coord_flip()
 }
@@
   ggplot(aes(x=type, y=Estimate)) +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1), 
-        axis.text.y = element_text(angle = 30, hjust = 1)) +
   geom_col(aes(fill=significant)) + 
-  facet_wrap(~ variable, scales = "free_y")
+  facet_wrap(~ variable) +
+  coord_flip()
 }
@@
 A stepwise method was used to determin the best regression model for predicting a hit or miss.
-The regression model that provided the best AIC, included the scene attributes: Shot Angle, Back Ground, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
+The regression model that provided the best AIC, included the scene attributes: Shot Angle, Background, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
 It also included the lighting on the particular face, and whether the specific face was accessorised with Glasses and a Visor or Hat.

### 2017-06-30 Report06-12.Rmd
Order the bar chart type bars

@@
 library(ggthemes)
-library(EBimage)
+library(EBImage)
 
@@
     mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
-  ggplot(dataset, aes(x=factor(xvar), y=proportion, group = type, fill=type)) + geom_bar(stat = "identity", position = "dodge") +
+   ggplot(dataset, aes(x=xvar, y=proportion, group = reorder(type, -proportion), fill=type)) + geom_bar(stat = "identity", position = "dodge") +
     ylab("Proportion of faces matched") + xlab(factorVar)

### 2017-06-30 Internship/BEX3012ProjectReport.Rmd
Auto stash before merge of "master" and "steffMVP/master"

@@
 
-To simplify the analysis, we assigned a predominant emotion for each API result. This allowed for clearer comparisons of the emotion results for individual faces across the three APIs.
+To simplify the analysis, we assigned a predominant emotion for each API result. This allowed for comparisons of a singular emotion result for individual faces across the three APIs.
 For Google, Skybiometry and Microsoft, the emotion proportion levels for each individual face were considered, the maximum proportion value of each APIs emotion set was deemed the dominant emotion for each face.
@@
 
-Each API returned a different amount of total responses. Microsoft produced emotion results for `r sum(!is.na(ME$anger))` faces, 55.497% of the faces provided.
-This was more than Skybiometry, as it produced only `r sum(!is.na(SB$anger))` results for emotions on faces. This is 48.103% of the set of faces.
-Google provided the most, 94.162% of the faces, `r sum(!is.na(GE$anger))`, were given emotion results^[As the initial set was faces identified by Google there is the possibility of bias toward being able to identify emotions in faces it was able to find originally.].
+Each API returned a different amount of total responses. Microsoft produced emotion results for `r sum(!is.na(ME$anger))` faces, 55.50% of the faces provided.
+This was more than Skybiometry, as it produced only `r sum(!is.na(SB$anger))` results for emotions on faces. This is 48.10% of the set of faces.
+Google provided the most, 94.16% of the faces, `r sum(!is.na(GE$anger))`, were given emotion results^[As the initial set was faces identified by Google there is the possibility of bias toward being able to identify emotions in faces it was able to find originally.].
 
@@
 
-knitr::kable(gplconfint[2:9,] ,longtable=TRUE, booktabs = TRUE, digits=3, caption="A logisitic regression was undertaken to show how certain image attributes contribute to the likelihood of the face being a player.")
+knitr::kable(gplconfint[2:9,] ,longtable=TRUE, booktabs = TRUE, digits=3, caption="A logisitic regression was undertaken to show how certain image attributes contribute to the likelihood of the face being a player.
+The base categories used include: background of Court, bird's eye shot angle, the individual face unobscured by objects, not wearing glasses and a head angle front on to the camera")
+levels(as.factor(ME$shotangle))
 ```
@@
 The regression coefficients are the change in the likelihood of a face being a player if the category is true for a face.
-The most significant predictors of a response are outlined in the table above.
+The most significant predictors of a face belonging to a player are outlined in the table above.
 It can be seen that when the image was taken at a player's "Shoulder Height" then it is, on average, 4.45 times more likely to be a "Player" than a fan or staff member on court.
-When the head angle is "Other", it is between 1.34 and 3.87 times more likely to be a Player than faces that have been captured front on, at the 5% level of confidence.
+When the head angle is "Other", it is between 1.34 and 3.87 times more likely to be a Player than faces that have been captured "Front On", at the 5% level of confidence.
 
@@
 
-There were only 364 faces were found by all APIs, 113 by only Microsoft and Google as well as 53 found by Skybiometry and Google.
-However the amount of faces found by only Google, 380, was higher than anticipated.
+The amount of faces that all three APIs returned emotion results for was 27.60%; Microsoft and Google returned emotion results for 8.58% of faces, and 4.02% of faces had emotion results found by Skybiometry and Google.
+However the amount of faces found by only Google, 28.81%, was higher than anticipated.
 
-As there was already disagreement between the APIs in finding faces we were inclined to believe that the approaches to classifying faces, and therefore emotions, may be different.
+As there was already disagreement between the APIs in finding faces we were inclined to believe that the approaches to classifying faces, and therefore emotions, were likely to be different.
 While more facial emotion results were found by Google, the majority of the emotion proportions after transformations were still below 0.5 for the predominant emotions.
 This amount of 'Very Unlikely' responses to emotions being present on a faces was surprising.
-We did not expect that Google would be reserved in aknowledging the prescence of emotion.
+We did not expect that Google would be reserved in aknowledging the prescence of emotion, rather we expected more non-neutral results from the Google algorithm given that the faces used were previously detected faces by Google.
 Microsoft provided `r sum(!is.na(MEP$anger))` emotion results for player's faces.
@@
 The research aim was to develop methods to collect accurate information about the facial expressions of elite tennis athletes during matchplay.
+It was expected that emotions would not be difficult to distinguish as tennis is known to be an emotionally charged game.
 We cannot establish, without further validation, that three currently available APIs are not capable of accurate detection of player's emotions when analyzing the broadcast video matches.

### 2017-06-30 Report06-12.Rmd
Changed section heading levels

@@
 
-## Methodology
+# Methodology
 An annotation tool was constructed to create a base for comparative analysis, we refer to this as Manual Classifications.
@@
 
-## Results
+# Results
 
@@
 
-### Results Overview
+## Results Overview
 Graph 1, the Bar Chart of the Face Bounding Boxes promotes Google as the best possible software for a facial recognition application in tennis.
@@
 
-## Future Work
+# Future Work
 The Long Term goal of this research is to better understand how the emotion's felt by a player during a match affect player performance.
@@
 
-## References
+# References

### 2017-06-30 Report06-12.Rmd
New Image with Face Box plot
geom_tile, and EBImage used to overlay rectangles on faces

@@
   for(i in imgList){
-    img <- image_read(paste0("figures/", i))
 
-    p <- ggplot(data.frame(x=c(0,800), y=c(0,450)), aes(x,y)) +
-      theme_void()+ coord_fixed()+
-      annotation_custom(rasterGrob(img)) +
-      coord_cartesian(xlim=c(0, 800), ylim=c(0,450))
+    #read in image
+    image <- readImage(paste0("figures/", i))
 
+    #convert image to a df, add hex value
+    image_df <- data.frame(x=rep(1:nrow(image), ncol(image)),
+                           y=rep(1:ncol(image),
+                                 rep(nrow(image),
+                                     ncol(image))),
+                           r=as.vector(image[,,1]),
+                           g=as.vector(image[,,2]),
+                           b=as.vector(image[,,3]))
+    image_df$h <- rgb(image_df[,3:5])
+
+    #Create the plot of the image
+    p <- ggplot() +
+      scale_fill_identity() + 
+      geom_tile(data=image_df, aes(x,-y, fill=h)) + 
+      theme_void()
+
+    # Find associated Face Box information for specific image
     faceData <- ALLmetaIMGnamedFaces %>% filter(file == i)
@@
     if(nrow(faceData) == 0){
-      print(p)
-      next
+      return(p)
     } else{
@@
         mutate(posCoord = substr(corner, 1, 1), posID = substr(corner, 2, 2)) %>%
-        dplyr::select(-corner) %>% spread(posCoord, boxPos)
+        dplyr::select(-corner) %>% spread(posCoord, boxPos) %>% 
+        dplyr::select(file, type, minX, maxX, minY, maxY, FaceKey, FaceID, posID, x, y)
+    }
 
@@
   if(matchBox){
-      p <- p + geom_path(aes(x=x, y=450-y, group = c(type, boxID), colour=boxID), faceData) + guides(colour="none")
+    p1 <- p + geom_rect(data=faceData, 
+                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
+                            color=FaceKey, group=FaceID), fill=NA) +
+      guides(colour = "none")
   }
   else{
-      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData) + scale_color_manual(values = c(Skybiometry="#ffe093", Microsoft="#5cc3f6", Google="#5cba82", Animetrics="#FF959c", Manual="#db70ff"))
+    p1 <- p + geom_rect(data=faceData, 
+                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
+                            color=type, group=FaceID), fill=NA) +
+      guides(colour = guide_legend(""))  + theme(legend.position = "bottom") + 
+      coord_fixed(ratio=0.85)
     }
-  print(p)
-  }
+
+  return(p1)
 }
@@
 
-##Introduction
+#Introduction
 

### 2017-07-18 R/mergeData.R
Change merge type

@@ -7,12 +7,12 @@ library(purrr)
 
 
 #Load Data
-MicrosoftClassifiedFaces <- read.csv("SoftwareRequestScripts/MicrosoftClassifiedFaces.csv")
-AnimetricsClassifiedFaces <- read.csv("SoftwareRequestScripts/AnimetricsClassifiedFaces.csv")
-SkybiometryClassifiedFaces <- read.csv("SoftwareRequestScripts/SkybiometryClassifiedFaces.csv")
-GoogleClassifiedFaces <- read.csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
-ManualClassifiedFaces <- read.csv("ManualClassifiedFaces.csv")
-ManualClassifiedScenes <- read.csv("ManualClassifiedScenes.csv")
+MicrosoftClassifiedFaces <- read_csv("data/ClassifiedFaces/MicrosoftClassifiedFaces.csv")
+AnimetricsClassifiedFaces <- read_csv("data/ClassifiedFaces/AnimetricsClassifiedFaces.csv")
+SkybiometryClassifiedFaces <- read_csv("data/ClassifiedFaces/SkybiometryClassifiedFaces.csv")
+GoogleClassifiedFaces <- read_csv("data/ClassifiedFaces/GoogleClassifiedFaces.csv")
+ManualClassifiedFaces <- read_csv("data/ManualClassifiedFaces.csv")
+ManualClassifiedScenes <- read_csv("data/ManualClassifiedScenes.csv")
 
 #Check all equal length
 #length(unique(ManualClassifiedScenes$file))
@@ -28,35 +28,34 @@ GoogleClassifiedFaces <- GoogleClassifiedFaces[!is.na(GoogleClassifiedFaces$roll
 
 #Manual Classified Faces
 ManualClassifiedFaces <- ManualClassifiedFaces %>%
-  mutate(type = "Manual", time.user.self=NA, time.sys.self=NA, time.elapsed=NA, ID=1:NROW(ManualClassifiedFaces))
+  dplyr::mutate(type = "Manual", time.user.self=NA, time.sys.self=NA, time.elapsed=NA, ID=1:NROW(ManualClassifiedFaces))
 
 #Merge data
 MicrosoftMerge <- MicrosoftClassifiedFaces %>% 
-  mutate(type = "Microsoft", ID=NA,
+  dplyr::mutate(type = "Microsoft", ID=NA,
          minX = faceRectangle.left, maxX = faceRectangle.left + faceRectangle.width,
[…]

### 2017-07-18 Report06-12.Rmd
Refining Report

@@
 title: "Detecting Facial Expressions in Professional Tennis Matches"
-author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
+author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
 date: "13 February 2017"
@@
 library(descr)
-library(tables)
+#library(tables)
 library(xtable)
@@
 ALLmetaIMGnamed<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
-SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
-FaceAttributes<-read_csv("TableCSVs/FaceAttributes.csv")
-SolutionSpecs<-read_csv("TableCSVs/SolutionSpecifications.csv")
+SceneAttributes<-read_csv("figures/SceneAttributes.csv")
+FaceAttributes<-read_csv("figures/FaceAttributes.csv")
+SolutionSpecs<-read_csv("figures/SolutionSpecifications.csv")
 
@@
 ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
-  #filter(matchesManual) %>% 
+  filter(!is.na(type)) %>% 
   dplyr::select(-ID, -facecounter)%>%
@@
 
-####Project Aim
+##Project Aim
 The aims of the present study were to determine the feasibility of using currently available facial recognition algorithms for extracting facial information from players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
@@
 
-####Sample and sampling approach
+##Sample and sampling approach
 The goal of the sample was to be representative of the video files that will be used for future facial recognition analysis.
@@
 
-####Software Selection
+##Software Selection
 The choice of the initial software considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'
@@
 
-We were able to try the online demos to see whether these software were viable, we used the following Image displayed below in Figure \@ref(Trial-Image):
+We were able to try the online demos to see whether these software were viable, we used the following Image displayed below in Figure \@ref(fig:Trial-Image):
 
-```{r Trial-Image, fig.cap = "Initial Image Used For Testing\\label{Trial-Image}", message=TRUE, warning=TRUE}
+```{r Trial-Image, fig.cap = "This image of Bernard Tomic was chosen as a trial image to be presented to each of the software before they were included in the research.
+It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE}
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-knitr::kable(SceneAttributes, format = "latex", longtable=TRUE, booktabs = TRUE, caption = "Attributes of a Scene of an image.
-The most appropriate option from the list was selected for each attribute.")
+knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "This table lists the possible image descriptions that are associated with the attributes of each image.
+The most appropriate descrition from each list was selected.
+There are more options for more complex attributes, there were five expected situations the image may depict.")
 ```
@@
 To determine which of the sometimes many faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
-This was based on the attributes provided in Table
-\@ref(tab:Solution-Specifications-Table), below:
 
-```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis'}
-knitr::kable(SolutionSpecs, format = "latex", longtable=TRUE, booktabs = TRUE, caption="")
+The faces of players were recorded if it showed their face at a minimum of 20 by 20 pixels.
+The back of the head was not detected as a face by any software, these faces were classified manually but reclassified as other.
+Crowd shots provided difficultly in determining which faces were reasonable to classify.
+These faces were not the intended targets of the recognition however these faces contributed to our understanding of the software.
+The same face size standard applied to crowd members, but focus was placed on the most prominent faces. For each of these faces, we collected information on the following attributes:
+
+```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
+knitr::kable(FaceAttributes, format = "latex", longtable=TRUE, booktabs = TRUE, caption = "This table lists the possible face descriptions that were appropriate for each individual face.
+The most appropriate descrition for each face was built by selecting one option from each list describing a particular attribute of the face that was selected.
+Most of these categories selections were made obvious in the image, Obscured and Head Angle were more difficult to choose for some faces.")
 ```
 
-It was decided that it would be reasonable for a software to detect was decided to be a face size larger than 20 by 20 pixels, as it was specified that the software had minimum distances between the eyes on a face for recognition.
-(reference table with values)
-If it was the face of a player it was recorded if it obviously showed their face.
-The back of the head was not able to be picked up by any software, so after a demo trial these faces were classified manually  but reclassified as other.
-Crowd shots provided difficultly in determining which faces were reasonable to classify.
-As these faces were not the intended targets of the recognition these faces were contributing to our understanding of the software.
-The same face size standard applied to crowd members, but focus was placed on the most prominent faces. For each of these faces, we collected information on the following attributes:
-
-```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image.
-The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
-knitr::kable(FaceAttributes, format = "latex", longtable=TRUE, booktabs = TRUE)
-```
-
-####Manual Annotation
+##Manual Annotation
 To record the details of attributes for each face and scene a Shiny [-@shiny] App was created.
@@
 
-####Software Interaction
+##Software Interaction
 The software choices allowed for POST requests to be sent via the internet.
@@
 
-####Data Processing
+##Data Processing
 The data needed for our analysis was spread across six files.
@@
 
-####Analysis
+##Analysis
 
 Using the data set^[ALLmetaIMGnamed] of the combined API and manual results, we were able to compare the performance of the software.
-Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(Face-Bounding-Box-Data).
+Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(fig:Face-Bounding-Box-Data).
 
 However, individual faces are not beneficial if they do not correspond to the faces manually annotated.
-Figure \@ref(Face-Bounding-Box-Upset) was created by defining groups depending on the softwares that recognized each particular face.
+Figure \@ref(fig:Face-Bounding-Box-Upset) was created by defining groups depending on the softwares that recognized each particular face.
 The UpSetR [-@UpSetR] package helps visualise set intersections.
@@
 
-This shows how influential certain attributes are in determining whether a face will be detected or not.
+This shows how influential certain attributes are in determining whether a face will be detected, a hit, or not, a miss.
 
-Regression analysis showed that the situation variable had significant differences between all levels and the interecept level of "Court in Play".
+A stepwise method was used to determine the best regression model for predicting a hit or miss.
+The regression model that provided the best AIC, included the scene attributes: Shot Angle, Background, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
+It also included the lighting on the particular face, and whether the specific face was accessorised with Glasses and a Visor or Hat.
+
+Regression analysis showed that the situation variable had significant differences between interecept level of "Court Close-Up Not Player" and the categories of "Court in Play" and "Court Player Close Up".
+This would mean that the probability of all the APIs finding the face that had been found manually was significantly less if the situation depicted was "Court in Play" and "Court Player Close Up" rather than a "Court Close-Up Not Player".
 
@@
 
-```{r Regression, fig.height=9.5, fig.width=7.5, fig.cap = "\\label{Regression} "}
+```{r Regression, fig.width=7.5, fig.cap = "The figure depicts the change in the probability of a face being detected by the APIs given a certain attribute level associated with the face.
+Wearing either glasses, or visor or a hat significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression} "}
 # Prepare data
@@
   split(.$type) %>% 
-  map(~ glm(model, data = dplyr::select(., -type, -file, -boxID), binomial(link = "logit")))
+  map(~ glm(model, data = dplyr::select(., -type, -file), binomial(link = "logit")))
 }
@@
 
-SignificancePlot <- function(model, data = GlmModelEstimates(model)) {
-  data %>%
-  mutate(significant = `Pr(>|z|)` < 0.05) %>%
-  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
-  ggplot(aes(x=type, y=`Pr(<|z|)`)) +
-  geom_col(aes(fill=significant)) + 
-  facet_wrap(~ variable) +
-  coord_flip()
+GlmModelEstimates <- function(model, data = GlmModelCreation(model)){
+  glmSummary <- data %>% 
+    map(~ ConvertModel2Table(.))
+
+  glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary))) 
+  return(glmPlot)
 }
+
+# SignificancePlot <- function(model, data = GlmModelEstimates(model)) {
+#   data %>%
+#   mutate(significant = `Pr(>|z|)` < 0.05) %>%
+#   ggplot(aes(x=type, y=`Pr(>|z|)`)) +
+#   geom_col(aes(fill=significant)) + 
+#   facet_wrap(~ variable) +
+#   coord_flip()
+# }
 
@@
   geom_col(aes(fill=significant)) +
-  facet_wrap(~ variable) +
+  facet_wrap(~ variable, scales="free_x", labeller=label_wrap_gen(width = 25, multi_line = TRUE)) +
   coord_flip()
@@
   ep<-EstimatesPlot(model, data)
-  sp<- SignificancePlot(model, data)
-  grid.arrange(ep, sp)
+  #sp<- SignificancePlot(model, data) 
+  grid.arrange(ep)#, sp)
 }
@@
 ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat)
+```
+
+```{r Mosaic, fig.cap = "\\label{fig:Mosaic}"}
+library(ggmosaic)
+#dev tools version has scale_y_productlist but cannot use it yet
+
+ggplot(data=ALLmetaIMGnamedFaces) + 
+  geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
+  #geom_text(aes(label="test", x=1, y=0.6)) +
+  guides(fill = guide_legend(title="API Faces Match \nManual Faces"))
+```
+
+The odds of a face found by one of the APIs matching a face found manually is  r or times higher when the camera angled captured the face from Player Shoulder Height as opposed to a Birds Eye shot.
+
+```{r DoubleDecker, fig.cap = "\\label{fig:DoubleDecker}"}
+library(ggmosaic)
+#add hit miss column to the data frame used in plotting below
+
+ggplot(data=ALLmetaIMGnamedFaces) +
+   geom_bar(aes(x= shotangle, fill = bg), position = position_stack(reverse = TRUE)) +
+ coord_flip() +
+  guides(fill = guide_legend(title="Background"))
 
@@
 
-A stepwise method was used to determin the best regression model for predicting a hit or miss.
-The regression model that provided the best AIC, included the scene attributes: Shot Angle, Background, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
-It also included the lighting on the particular face, and whether the specific face was accessorised with Glasses and a Visor or Hat.
+\newpage
 
@@
 
-```{r Face-Bounding-Box-Data, results='hide', fig.cap = "\\label{Face-Bounding-Box-Data} Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft."}
-ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE) + labs(caption="")
+Each API returned areas that indicated the potential location of a face.
+These areas were defined by a Bounding Box, created using the four points returned by the APIs to make a box around each face.
+The Google Vision API detected a large amount of potential faces, much more than Microsoft, Skybiometry or Animetrics.
+This can be seen below in \@ref(fig:Face-Bounding-Box-Data).
+
+```{r Face-Bounding-Box-Data, fig.cap = "\\label{fig:Face-Bounding-Box-Data} Face Bounding Boxes Per Software: The bar chart shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more potential faces than the next best software, Microsoft."}
+ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + 
+  geom_bar(position="dodge") +
+  xlab("Facial Recognition Softwares") +
+  scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +
+  ylab("Number of Potential Faces") + 
+  guides(fill=FALSE) +
+  labs(caption="")
 ```
@@
 
-The sample used contains all the manually annotated faces and all the faces recognized by the four software.
+The sample used contains all the manually annotated faces and all the faces recognized by the four APIs.
 
-```{r Face-Bounding-Box-UpSet, fig.cap = "\\label{Face-Bounding-Box-Upset} Face Bounding Boxes Per Software Combination.
-The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software.
-The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations.
-The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API."}
+```{r Face-Bounding-Box-UpSet, fig.cap = "\\label{fig:Face-Bounding-Box-Upset} Face Bounding Boxes Per Software Combination.
+The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software or found manually.
+The largest group, with 809 faces, is Face Bounding Boxes only found by Manual annotations.
+The following group were the 716 faces recognized both Manually and by the Google API."}
 createUpSet(ALLmetaIMGnamedFaces)
@@
 
-```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}
+```{r Type-Matches-Manual, fig.cap = "The potential Face Bounding Boxes that were found by the APIs are compared to those annotated manually.
+Where the FALSE row denotes API Face Bounding Boxes do not coincide with manually annotated faces.
+The tables shows that Google found 46.96% of the Faces identified manually.\\label{tab:Type-Matches-Manual}"}
+
 NoManual<-ALLmetaIMGnamed %>% filter(ALLmetaIMGnamed$type!="Manual")
 NoManual<-NoManual %>% droplevels(NoManual$type) 
-Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
-ct<-CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
-print(ct)
+ct<-CrossTable(table(NoManual$matchesManual, NoManual$type), 
+               prop.chisq = FALSE, 
+               digits=4,
+               expected = FALSE,
+           prop.r = TRUE, prop.c = TRUE, prop.t = TRUE,
+           drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
+           dnn = NULL)
+ct
+
 ```
 
-Table \@ref(Type-Matches-Manual) shows whether the potential Face Bounding Boxes match faces that were annotated during the manual classifications.
-Where the FALSE row denotes where software's Face Bounding Boxes do not coincide with manually annotated faces.
-The tables shows that Google found 38.70% of the 90.34% of the Faces found that matched Faces also identified manually.
+All the Face Bounding Boxes that Google found which do not match manually annotated faces were correctly identifying faces.
 
-A potential face detected that does not match a face manually annotated occurs for 9.66% of all the Faces detected by the software. This is especially high for Google with 289 faces identified.
-
-All the Face Bounding Boxes that Google found which do not match manually annotated faces were correctly identifying faces. This exhibits the occurrences of errors.
-
-We then considered the characteristics of the images that the software found Potential Face Bounding Boxes^[These boxes represent an area of pixels that are a potentially recognized face.] in.
+We then considered the characteristics of the images that the API found Potential Face Bounding Boxes in.
 

### 2017-07-18 R/ManualClassificationProgram.R

@@ -1,210 +1,0 @@
-#Mitchell O'Hara-Wild
-
-#setwd() to your github repository before running
-#In this repository, create a folder called "images" and store your images there.
-
-workerID = ""
-
-require(imager)
-require(shiny)
-require(shinyjs)
-
-ui <- fluidPage(
-  useShinyjs(),
-  textOutput("info", h3),
-  plotOutput("plot1",
-             click = "plot_click",
-             dblclick = "plot_dblclick",
-             hover = "plot_hover",
-             brush = "plot_brush",
-             height="auto"
-  ),# Partial example
-  conditionalPanel(
-    condition = "input.plot_brush",
-    #Face
-    h3("Face description"),
-    
-    fluidRow(
-      column(4, 
-             radioButtons("detect", label = h3("Detect Face"), 
-                         choices = list("Player" = 0,
-                                        "Other staff on court" = 1, "Fan" = 2, "None" = 3), selected = 0)
-      ),
-      column(4,
-             radioButtons("obscured", label = h3("Face obscured"),
-                          choices = list("Yes" = 1, "No" = 0), selected = 0)
-      ),
-      column(4,
-             radioButtons("lighting", label = h3("Lighting"),
-                          choices = list("Direct sunlight" = 0, "Shaded" = 1, "Partially shaded" = 2), selected = 0)
-      )
-    ),
-    
-    fluidRow(
-      
-      column(4, 
-             radioButtons("headangle", label = h3("Head angle"), 
-                         choices = list("Front on" = 0, "Back of head" = 1, 
-                                        "Profile" = 2, "Other" = 3), selected = 0)
-      ),
-      column(4,
-             radioButtons("glasses", label = h3("Glasses"),
-                          choices = list("Yes" = 1, "No" = 0), selected = 0),
-             actionButton("cancelface", "Cancel")
-      ),
-      column(4,
-             radioButtons("visorhat", label = h3("Visor/hat"),
-                          choices = list("Yes" = 1, "No" = 0), selected = 0),
-             actionButton("nextface", "Save")
-      )
-    )
-  ),
-  conditionalPanel(
-    condition = "!input.plot_brush",
-    #Scene
-    h3("Scene description"),
-    
-    fluidRow(
-      column(4, 
-             radioButtons("graphic", label = h3("2D Graphic"), 
[…]

### 2017-07-26 Internship/EmotionsAnalysis.Rmd
update

@@
                                                    ifelse(is.na(PlayerNumber), NA, NA))))
-
 ```

### 2017-07-26 Report06-12.Rmd
update

@@
 library(descr)
-#library(tables)
 library(xtable)
@@
 
+ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
+  filter(!is.na(type)) %>% 
+  dplyr::select(-ID, -facecounter)%>%
+  mutate(fileID = as.numeric(factor(file))) %>%
+  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
+  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))
+
 #plot images with overlaid boxes
@@
     #read in image
-    image <- readImage(paste0("figures/", i))
+    #image <- readImage(paste0("figures/", i))
+    #used in analyses
+    image <- readImage(paste0("images/", i))
 
@@
 
-ALLmetaIMGPlayers<- ALLmetaIMGnamed %>% filter(detect=="Player")
-
-# change this to facesVenn with binary information
-ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
-  filter(!is.na(type)) %>% 
-  dplyr::select(-ID, -facecounter)%>%
-  mutate(fileID = as.numeric(factor(file))) %>%
-  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
-  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))
+ALLmetaIMGPlayers <- ALLmetaIMGnamed %>% filter(detect=="Player")
 
@@
 }
-
 ```
@@
 @Boston addresses the 'lack of robustness of current tools in unstructured environments' that this paper faces and applies to a sports environment.
-This report aims to analyse the application of these software's to a broadcast to find a suitable software and API to use to analyse a pre-recorded tennis broadcast file.
+This report aims to analyse the application of these software's to a broadcast to find a suitable software and API to use to analyse a previously recorded tennis broadcast file.
 
@@
 It also has a record of how many faces had been identified in the image by counting each additional recognized face.
-To do so, we gathered the name of the file the face was found in and the software Type the Face Bounding Box was determined by.
+To do so, we gathered the name of the file the face was found in and the software Type the potential Face Boxes was determined by.
 The automatically determined time values were also included.
@@
 Using the data set^[ALLmetaIMGnamed] of the combined API and manual results, we were able to compare the performance of the software.
-Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(fig:Face-Bounding-Box-Data).
+Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(fig:PotentialFaceData).
 
 However, individual faces are not beneficial if they do not correspond to the faces manually annotated.
-Figure \@ref(fig:Face-Bounding-Box-Upset) was created by defining groups depending on the softwares that recognized each particular face.
+Figure \@ref(fig:PotentialFaceUpset) was created by defining groups depending on the API that recognized each particular face.
 The UpSetR [-@UpSetR] package helps visualise set intersections.
-Where in this circumstance Face Bounding Boxes may overlap on the same face, each bar shows the number of individual faces that have Face Bounding Boxes resulting from each of the softwares highlighted below the bar.
+Where in this circumstance potential Faces Boxes may overlap on the same face, each bar shows the number of individual faces that have potential Face Boxes resulting from each of the APIs highlighted below the bar.
 
@@
 
-A stepwise method was used to determine the best regression model for predicting a hit or miss.
+A step wise method was used to determine the best regression model for predicting a hit or miss.
 The regression model that provided the best AIC, included the scene attributes: Shot Angle, Background, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
@@
 
-Regression analysis showed that the situation variable had significant differences between interecept level of "Court Close-Up Not Player" and the categories of "Court in Play" and "Court Player Close Up".
+Regression analysis showed that the situation variable had significant differences between intercept level of "Court Close-Up Not Player" and the categories of "Court in Play" and "Court Player Close Up".
 This would mean that the probability of all the APIs finding the face that had been found manually was significantly less if the situation depicted was "Court in Play" and "Court Player Close Up" rather than a "Court Close-Up Not Player".
@@
 The bar charts of the situations show that the situation is important in influencing the detection of a face.
-When the face is accessorised with them, all softwares have a significantly increased chance of finding the face in comparison to the base rate category of the "Court in Play".
+When the face is accessorised with them, all APIs have a significantly increased chance of finding the face in comparison to the base rate category of the "Court in Play".
 While the image being a Graphic had a large impact it was not significant, this is likely because of the small number of images with this attribute.
-It also shows that the shot angle is only significant for one or two softwares at each level.
+It also shows that the shot angle is only significant for one or two APIs at each level.
 
 ```{r Regression, fig.width=7.5, fig.cap = "The figure depicts the change in the probability of a face being detected by the APIs given a certain attribute level associated with the face.
-Wearing either glasses, or visor or a hat significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression} "}
+Wearing either glasses, or visor or a hat significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}"}
 # Prepare data
@@
 
-```{r Mosaic, fig.cap = "\\label{fig:Mosaic}"}
-library(ggmosaic)
-#dev tools version has scale_y_productlist but cannot use it yet
-
-ggplot(data=ALLmetaIMGnamedFaces) + 
-  geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
-  #geom_text(aes(label="test", x=1, y=0.6)) +
-  guides(fill = guide_legend(title="API Faces Match \nManual Faces"))
-```
-
-The odds of a face found by one of the APIs matching a face found manually is  r or times higher when the camera angled captured the face from Player Shoulder Height as opposed to a Birds Eye shot.
-
-```{r DoubleDecker, fig.cap = "\\label{fig:DoubleDecker}"}
-library(ggmosaic)
-#add hit miss column to the data frame used in plotting below
-
-ggplot(data=ALLmetaIMGnamedFaces) +
-   geom_bar(aes(x= shotangle, fill = bg), position = position_stack(reverse = TRUE)) +
- coord_flip() +
-  guides(fill = guide_legend(title="Background"))
-
-```
-
 \newpage
@@
 The Google Vision API detected a large amount of potential faces, much more than Microsoft, Skybiometry or Animetrics.
-This can be seen below in \@ref(fig:Face-Bounding-Box-Data).
+This can be seen below in Figure \@ref(fig:PotentialFaceData).
 
-```{r Face-Bounding-Box-Data, fig.cap = "\\label{fig:Face-Bounding-Box-Data} Face Bounding Boxes Per Software: The bar chart shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more potential faces than the next best software, Microsoft."}
+```{r PotentialFaceData, fig.cap = "\\label{fig:PotentialFaceData}  Potential Face Boxes Per API: The bar chart shows the number of Potential Face Boxes produced by each API, comparing the height of the bars indicates that Google's Facial Recognition API recognized almost 1000 more potential faces than the next best API, Microsoft."}
 ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + 
   geom_bar(position="dodge") +
-  xlab("Facial Recognition Softwares") +
+  xlab("Facial Recognition APIs") +
   scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +
@@
 To evaluate the performance in terms of the overall accuracy of each algorithm we considered the amount of faces they classified that matched faces that were selected manually.
+Using a sample that contains all the manually annotated faces and all the faces recognized by the four APIs.
 
-The sample used contains all the manually annotated faces and all the faces recognized by the four APIs.
+To consider how many Type I errors occurred, where a face was detected incorrectly, we look at the potential faces that do not match manually annotated faces.
 
-```{r Face-Bounding-Box-UpSet, fig.cap = "\\label{fig:Face-Bounding-Box-Upset} Face Bounding Boxes Per Software Combination.
-The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software or found manually.
-The largest group, with 809 faces, is Face Bounding Boxes only found by Manual annotations.
-The following group were the 716 faces recognized both Manually and by the Google API."}
-createUpSet(ALLmetaIMGnamedFaces)
-```
+\newpage
 
-```{r I3, results=TRUE, fig.cap = "\\label{fig:I3} There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face."}
-imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
-overlayGgplot(imagesList3, ALLmetaIMGnamedFaces, matchBox = FALSE)
-```
-
-To consider how many Type I errors occurred, where a face was detected incorrectly, we look at the Bounding Boxes that do not match manually annotated faces.
-
-```{r Type-Matches-Manual, fig.cap = "The potential Face Bounding Boxes that were found by the APIs are compared to those annotated manually.
-Where the FALSE row denotes API Face Bounding Boxes do not coincide with manually annotated faces.
+```{r Type-Matches-Manual, fig.cap = "This table shows the amount potential faces that were found by the APIs and whether they compare to those annotated manually.
+Where the FALSE row denotes API Face potential facees do not coincide with manually annotated faces.
 The tables shows that Google found 46.96% of the Faces identified manually.\\label{tab:Type-Matches-Manual}"}
 
-NoManual<-ALLmetaIMGnamed %>% filter(ALLmetaIMGnamed$type!="Manual")
+NoManual<-ALLmetaIMGnamedFaces %>% filter(ALLmetaIMGnamedFaces$type!="Manual")
 NoManual<-NoManual %>% droplevels(NoManual$type) 
@@
            drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
-           dnn = NULL)
-ct
+           dnn = c("Matches Manual","API Type"))
+
+pander(ct)
+```
+
+All the potential facees that Google found which do not match manually annotated faces were correctly identifying faces.
+
+\newpage
+
+```{r PotentialFaceUpSet, fig.cap = "\\label{fig:PotentialFaceUpset} potential facees Per API Combination.
+The Bar Chart shows the potential facees that were recognised by multiple API or found manually.
+The largest group, with 809 faces, is potential facees only found by Manual annotations.
+The following group were the 716 faces recognized both Manually and by the Google API."}
+createUpSet(ALLmetaIMGnamedFaces)
+```
+
+This shows that there are many faces that were identified by some APIs and not others. These combinations may give some indication as to the circumstances when some APIs perform better than others.
+
+\newpage
+The image below is an example of how some faces were only found by certain APIs, and how some APIs produced unusual false discoveries.
+
+```{r UnusualImage, results=TRUE, fig.cap = "\\label{fig:UnusualImage} There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face."}
+imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
+overlayGgplot(imagesList3, ALLmetaIMGnamedFaces, matchBox = FALSE)
+```
+
+\newpage
+We then considered the characteristics of the images that the API found Potential Faces in.
+
+```{r Image-Characteristics-Table, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
+ImageCharacteristics <- ALLmetaIMGnamed %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
+ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
+ImageCharacteristics<-ImageCharacteristics[1:5,]
+knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="This table outlines the combinations of image attibutes that are most common in the image set.
+The combination of the Logo Wall background and the Player Shoulder Height angle are shared by three of the five image combinations.", format = "latex")
+```
+
+We then considered that there would be an uneven amount of faces with certain image attributes. This is considered in the mosaics below in Figure \@ref(fig:Mosaic).
+
+```{r MosaicShotangle, fig.cap = "The colours in the mosaic show the amount of faces that matched those found manually given the angle the faces were captured from.
+There is a greater amount of API faces that matched the faces found manually than those that did not match.
+However given the face was captured from a birds eye angle there were less faces that matched those found manually.
+The most common faces in our set were those captured at Player Shoulder Height and found manually and by an APIs.\\label{fig:Mosaic}"}
+library(ggmosaic)
+#dev tools version has scale_y_productlist but cannot use it yet
+#ALLmetaIMGnamedFaces$shotangle 
+ALLmetaIMGnamedFaces$shotangle <- factor(ALLmetaIMGnamedFaces$shotangle, levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))
+
+ggplot(data=ALLmetaIMGnamedFaces) + 
+  geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
+  #geom_text(aes(label="test", x=1, y=0.6)) +
+  guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
+  labs(caption="") +
+  ylab("Proportion of faces") + xlab("Angle the face was captured from ")
+```
+
+```{r ShotangleCompare, eval=FALSE, fig.cap:".\\label{fig:ShotangleCompare}"}
+CompShot <- ALLmetaIMGnamedFaces %>% 
+  filter(shotangle=="Player Shoulder Height", 
+         bg=="Logo wall", 
+         situation=="Court player close−up",
+         type=="Google" | type=="Manual",
+         player2=="AMurray", player2:"AMurray")
+
+mylist<-as.list(CompShot$file)
+#6,7,8,
+View(CompShot)
+lapply(mylist[1:5], overlayGgplot)
+overlayGgplot(mylist)
+#decide on a comparison, one where images had faces both recognised manually, only one recognised by a software
+```
+
+```{r MosaicSit, fig.cap = "This mosaic shows the number of Faces captured during each possible situation.
+It contrasts how many of the images captured in situations either did or did not match the faces annotated manually using the colour pink for potential faces that did not match, and blue for those that did.
+It can be seen that the largest portion of the faces were captured in a close up situation while the players were on court.\\label{fig:Mosaic}"}
+
+ALLmetaIMGnamedFaces$situation <- factor(ALLmetaIMGnamedFaces$situation, levels = c("Court close−up not player",
+          "Court in play",
+          "Off court close up of player",
+          "Crowd",
+          "Court player close−up"))
+
+ggplot(data=ALLmetaIMGnamedFaces) + 
+  geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
+  guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
+  labs(caption="") + coord_flip() +
+  ylab("Proportion of faces") + xlab("Situation the face was captured during")
+```
+
+```{r DDbgshot, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes.
+We are able to see that the background being the Logo Wall and the angle of Player Shoulder Height is common to the highest amount of faces.
+There are also no images that were taken at an upward angle with the background of the court.
+\\label{fig:DDbgshot}"}
+
+ggplot(data=ALLmetaIMGnamedFaces) +
+   geom_bar(aes(x=shotangle, fill = bg), 
+            position = position_stack(reverse = TRUE), 
+            na.rm=TRUE) +
+  coord_flip() +
+  guides(fill = guide_legend(title="Background")) +
+  labs(caption="") +
+  ylab("Amount of faces") + xlab("Angle the face was captured from")
 
@@
 
-All the Face Bounding Boxes that Google found which do not match manually annotated faces were correctly identifying faces.
+```{r DDbgsit, fig.cap = "This stacked bar chart allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
+As seen previously, the logo wall is the most common background, but it is never the background to an image of the crowd.
+The court is the background of an image only when players are captured, this occurs during close ups and while the court is in play.\\label{fig:DDbgsit}"}
 
-We then considered the characteristics of the images that the API found Potential Face Bounding Boxes in.
+ggplot(data=ALLmetaIMGnamedFaces) +
+   geom_bar(aes(x=situation, fill = bg), 
+            position = position_stack(reverse = TRUE), 
+            na.rm=TRUE) +
+  coord_flip() +
+  guides(fill = guide_legend(title="Background")) +
+  labs(caption="") +
+  ylab("Amount of faces") + xlab("Situation the face was captured during")
 
-```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
-ImageCharacteristics <- ALLmetaIMGnamed %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
-ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
-ImageCharacteristics<-ImageCharacteristics[1:10,]
-knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="", format = "latex")
 ```
 
-\@ref(Image-Characteristics-Table) displays the feature combinations that produced the most potential face Bounding Boxes recognition by all four software. The most common shot is a crowd shot.
-The second row in the table with 830 faces recognized is more interesting than the first result.
-This useful scene is an image of a Court Player Close-Up in front of a Logo Wall, taken at Player Shoulder Height.
-
-These attributes typically represent an image similar to the following:
-
-```{r Typical-Best-Recognised, results=FALSE, fig.cap = "\\label{fig:Typical-Best-Recognised}"}
-imagesList1<-as.list("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png")
-overlayGgplot(imagesList1, ALLmetaIMGnamed, matchBox = FALSE)
-```
-
-```{r Google-Errors-Characteristics-Table, fig.cap = "\\label{tab:Google-Errors-Characteristics-Table}"}
-library(dplyr)
-
-GoogleNoMatch <- ALLmetaIMGnamed %>%
-  filter(type=="Google") %>%
-  filter(matchesManual==FALSE) %>%
-  group_by(person, situation, bg, shotangle) %>% dplyr::summarise(count=n())
-
-#use this list in the overlay function to view the images where Google found faces not annotated manually
-#GoogleImages<-GoogleNoMatch$file
-#GoogleImages<-as.list(GoogleImages)
-
-GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
-knitr::kable(GoogleNoMatch[1:10,], caption="", longtable=TRUE, format = "latex")
-
-#overlayGgplot(GoogleImages, GoogleNoMatch, matchBox = TRUE)
-```
-
-Table \@ref(Google-Errors-Characteristics-Table)
- shows that the potential Face Bounding Boxes Google returned were found in images that had the same characteristics of those that were manually annotated for faces.
-<!-- This is shown by the same combinations of characteristics occuring in both Table 5 and Table 6.  keep as tables?-->
-Without looking at each individual image this Table confirms that the potential Face Bounding Boxes Google located will likely be reasonable, and actually contain faces.
-
-The best scenes for facial recognition have been found, given this information the following \@ref(Face-Characteristics-Table) considers the Characteristics of the individual faces found within those scenes.
-For this section we chose to consider only the faces that were manually annotated as players, with the intention of not basing results on recognition of undesirable faces.
-
-```{r Face-Characteristics-Table, fig.cap = "\\label{tab:Face-Characteristics-Table}"}
-FaceCharacteristics <- ALLmetaIMGPlayers %>%
-  filter(type=="Google") %>%
-  filter(matchesManual==TRUE) %>%
-  group_by(visorhat, glasses, headangle, lighting, obscured, detect) %>% dplyr::summarise(count=n())
-
-FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
-FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
-knitr::kable(FaceCharacteristics, caption="", longtable=TRUE, format = "latex")
-```
-
-Table \@ref(Face-Characteristics-Table)
-utilizes a set of faces that were Manually annotated and also found by Google. 
-Nine of the top ten facial characteristic combinations contained faces that were not wearing glasses.
-The head angle describing the face angle was 'Other'^[Definition for head-angle factor level 'Other' found in..]
-for nine of the top ten facial characteristic combinations.
-
-```{r Glasses, fig.cap = "\\label{tab:Glasses} This table shows the amount of faces recognised by google wearing glasses.
-The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally."}
-GlassesGoogle <- ALLmetaIMGnamedFaces %>% filter(type=="Google") %>%
-filter(matchesManual==TRUE)
-pander(table(GlassesGoogle$glasses))
-```
-
-```{r Glasses-Figure, fig.cap = "\\label{fig:Glasses-Figure} The figure above shows that Google outperforms the other software, with or without glasses.
-When there are no glasses worn Google finds over 60% of the manually annotated faces."}
-ggplotProportion(ALLmetaIMGPlayers, glasses)+xlab("Glasses on Face")
-```
-
-```{r HeadAngles, fig.cap = "\\label{tab:HeadAngles}"}
+```{r HeadAngles, fig.cap = "The amount of faces found by Google with the head-angle Other, is much larger than the amount of faces with the head-angle Profile or Front On.
+Therefore this should also be considered proportionately.\\label{tab:HeadAngles}"}
 HeadangleGoogle <- ALLmetaIMGPlayers %>%   filter(type=="Google") %>%
@@
 
-In Table \@ref(HeadAngles), the amount of faces found by Google with the head-angle "Other", is much larger than the amount of faces with the head-angle "Profile" or "Front On".
-Therefore this should also be considered proportionately.
-
-```{r Headangle-Figure, fig.cap = "\\label{fig:Headangle-Figure} Google performs much better in comparison to the other software when the head-angle is Profile.
-This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance."}
+```{r Headangle-Figure, fig.cap = "\\label{fig:Headangle-Figure} Google performs much better in comparison to the other API when the head-angle is Profile.
+This is outperforming unusually well, however this could also be due to the poor performance of the API in this circumstance."}
 ggplotProportion(ALLmetaIMGPlayers, headangle)+xlab("Head Angle of Face")
@@
 
-Table 2 = Describe the images/boxes identified by the algorithms--what are they typically like? what is the area represented?
+## Results Overview
+Figure \@ref(fig:PotentialFaceData), the bar chart of the potential faces shows Google produces the most detections.
+This would be a strong incentive to use Google for facial recognition in sports application.
+It was considered that Google's API may have been finding more unwanted faces than the other APIs.
+Table \@ref(tab:Type-Matches-Manual) details the amounts of faces that were found by each API that matched or did not match a face found manually.
+There are slightly more faces found by APIs that do match the faces found manually, 56.34%, than faces that do not match, 43.66%.
+This was unexpected as it was presumed that majority of the faces annotated manually would be found.
 
-Table 3= Evaluate the performance: what is the overall accuracy of each algorithm (sample should be annotated faces + all boxed identified by algorithms) 
-  How often is type I error made (a face detected incorrectly)?
+The largest group of images were those annotated by manual annotations and found by the Google API, these faces consisted of 26.46% of the total sample.
+This set of images are also seen in Figure \@ref(fig:PotentialFaceUpset), which shows the amount of faces that were found by each combination of APIs.
+The group of faces that were found by manually and by the Google API are represented across the various bars.
+Their ownership of the faces is denoted by the black bubbles below the bars.
 
-```{r Accuracy}
-Accuracy<-with(ALLmetaIMGnamed, table(ALLmetaIMGnamed$matchesManual, ALLmetaIMGnamed$type))
-knitr::kable(Accuracy, caption="", longtable=TRUE, format = "latex")
-# make this a proportional table, would this be necessary if we have the UpSetR
-```
+Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:Type-Matches-Manual) that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd memebers were beyond what would be expected of an emotion recognition application for tennis players.
+These were deemed unlikely to be detected and neglected during manual annotation.
 
-  How often type II error (a face is incorrectly NOT detected)?   
-  3 of the four software's
+Table \@ref(tab:Type-Matches-Manual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces.
+Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were not faces.
 
-It should be noted that there were results where a single face was recognized twice within the same image.
-This was a very unusual result and is notable as a point of interest but given it only occurred for Animetrics, it is not worth basing decisions on this unusual result.
-
-Table 4 = Identify possible explanatory factors to performance; Does accuracy vary by lighting conditions? face size? obscuring factors? angle? etc.
-
-```{r Google-Characteristics-Table, fig.cap = "\\label{tab:Google-Characteristics-Table}"}
-GoogleCharacteristics <- ALLmetaIMGnamed %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
-GoogleCharacteristics<-arrange(GoogleCharacteristics, desc(count))
-
-knitr::kable(GoogleCharacteristics, format = "latex", longtable=TRUE, booktabs = TRUE, caption="")
-```
-
-Table \@ref(Google-Characteristics-Table)
-shows how many images with potential player's faces Google recognized.
-This displays a vast gap between the amount of potential faces found given the different shot angles.
-Shoulder height is an optimum angle for a Face Bounding Box.
-
-Considering only the Shoulder Height Angle, the following Graph looks at how accessories affected Google's recognition.
-
-## Results Overview
-Graph 1, the Bar Chart of the Face Bounding Boxes promotes Google as the best possible software for a facial recognition application in tennis.
-According to Table 4 Google had 38.23% of the 9.66% potential face boxes not annotated manually.
-It was considered that this may have shown Google's API may have been finding more unwanted faces than the other software.
-However, visual inspection showed that these were actually faces.
-This is considered in Table 6, which showed that some of the faces were found in a crowd setting.
-Therefore some of these could be considered irrelevant, possibly being crowd faces.
-These were deemed unlikely to be detected and neglected during manual annotation.
-Interestingly, Animetrics had the least amount of matches to Manually annotated faces.
-Looking into this further showed that Animetrics results contained potential Face Bounding Boxes that did not contain faces.
-
-The images were all considered manually.
-The scene information was recorded and the combinations were shown to find how many potential face Bounding Boxes were found with the combination of scene attributes.
+The images were all considered manually. The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
 This showed that crowd members faces were often recognized, this is both helpful and unhelpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
@@
 
-This shows it was performing extremely well and not resulting in unexplained face Bounding Boxes as some of the other software were.
+This shows it was performing extremely well and not resulting in unexplained potential faces as some of the other software were.
 This is a strong indicator that applying Google's software for further research would result in the recognition of desired faces.
@@
 
-The box-plot in graph encourages our comparisons to not consider the size of face bounding box as a measure of how the software performs on small faces.
+The box-plot in graph encourages our comparisons to not consider the size of potential face boxes as a measure of how the software performs on small faces.
 

### 2017-07-26 R/mergeData.R

@@ -116,7 +116,7 @@ classifiedIMG <- mergedFaceMatches %>% dplyr::mutate(size = (maxX - minX) * (max
 
 metaManualClassifiedFaces <- merge(dplyr::select(ManualClassifiedFaces, file, facecounter, 
                                                  detect, obscured, lighting, headangle, glasses, visorhat, ID),
-                                   dplyr::select(dplyr::ungroup(dplyr::filter(mergedFaceMatches, type=="Manual")), ID, boxID), by=c("file", "boxID"))
+                                   dplyr::select(dplyr::ungroup(dplyr::filter(mergedFaceMatches, type=="Manual")), ID, boxID), by=c("ID"))
 
 
 
@@ -146,7 +146,7 @@ write.csv(ALLmetaIMG,file = "ALLmetaIMG.csv", row.names = FALSE)
 
 library(readr)
 # creating named
-ALLmetaIMG<-read_csv("ALLmetaIMG.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+ALLmetaIMG<-read_csv("data/ALLmetaIMG.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
 
 
 #Factor Names 
@@ -168,3 +168,12 @@ ALLmetaIMG$headangle[ALLmetaIMG$headangle == "Back of head"] <- "Other"
 ALLmetaIMG$headangle <- as.factor(ALLmetaIMG$headangle)
 
 write.csv(ALLmetaIMG, "ALLmetaIMGnamed.csv", row.names = FALSE)
+
+#check for NAs in variables
+
+ALLmetaIMGPlayers <- ALLmetaIMG %>% 
+  #filter(detect==0) %>%
+  dplyr::select(graphic,person,situation,bg, shotangle,visorhat,
+                detect, obscured, lighting, headangle, glasses, visorhat)
+
+summary(ALLmetaIMGPlayers)

### 2017-07-28 Report06-12.Rmd
typo

@@
 
-```{r ShotangleCompare, eval=FALSE, fig.cap:".\\label{fig:ShotangleCompare}"}
+```{r ShotangleCompare, eval=FALSE, fig.cap=".\\label{fig:ShotangleCompare}"}
 CompShot <- ALLmetaIMGnamedFaces %>% 

### 2017-07-28 Report06-12.Rmd
AnimetricsFigure

@@
   else{
+    group.colors <- c(Animetrics = "#B3E2CD",
+                      Google = "#FDCDAC",
+                      Manual = "#CBD5E8",
+                      Microsoft = "#F4CAE4",
+                      Skybiometry = "#E6F5C9")
+
     p1 <- p + geom_rect(data=faceData, 
@@
       guides(colour = guide_legend(""))  + theme(legend.position = "bottom") + 
-      coord_fixed(ratio=0.85)
+      coord_fixed(ratio=0.85) + scale_colour_manual(values=group.colors)
     }
@@
 \newpage
+# Results
 
-# Results
+## Amount of Potential Faces
 
@@
 Using a sample that contains all the manually annotated faces and all the faces recognized by the four APIs.
+
+## Potential Faces Matching Manual Annotations
 
@@
 \newpage
+
+## False Discoveries
 The image below is an example of how some faces were only found by certain APIs, and how some APIs produced unusual false discoveries.
@@
 \newpage
+
+## Image Characteristics
+
 We then considered the characteristics of the images that the API found Potential Faces in.
@@
 
-mylist<-as.list(CompShot$file)
+#mylist<-as.list(CompShot$file)
 #6,7,8,
-View(CompShot)
-lapply(mylist[1:5], overlayGgplot)
-overlayGgplot(mylist)
+#View(CompShot)
+#lapply(mylist[1:5], overlayGgplot)
+#overlayGgplot(mylist)
 #decide on a comparison, one where images had faces both recognised manually, only one recognised by a software
@@
 
+```{r animetricsWeird, fig.cap=" Animetrics provided results that were quite unusual \\label{fig:animetricsWeird}" }
+i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot()
+i2 <- "2016_CT6_R01_EKulichkova_RUS_vs_APetkovic_GER_WS128_clip.0080.png" %>% overlayGgplot()
+i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot()
+grid.arrange(i1, i2, i3, nrow=2)
+
+```
+
 The images were all considered manually. The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.

### 2017-07-28 Report06-12.Rmd
Line for figures not images folder
moved blocks of text to subsections of results

@@
     #read in image
-    #image <- readImage(paste0("figures/", i))
+    image <- readImage(paste0("figures/", i))
     #used in analyses
-    image <- readImage(paste0("images/", i))
+    #image <- readImage(paste0("images/", i))
 
@@
 
-In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcasted videos of elite tennis matches.
-Using the broadcasted videos gives an objective insight to emotions as the player progresses through a match.
+In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcast videos of elite tennis matches.
+Using the broadcast videos gives an objective insight to emotions as the player progresses through a match.
 While it is impossible to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through results produced by a recognition software.
@@
 ##Manual Annotation
-To record the details of attributes for each face and scene a Shiny [-@shiny] App was created.
+To record the details of attributes for each face and scene a Shiny [@shiny] App was created.
 We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassificationProgram.R].
@@
 We accounted for this by stalling the posts for the amount of waiting time the software notified, and checking until the time lapsed and the script could continue looping.
+
+COMMENT: Add a paragraph on time taken to find faces for each software
 
@@
 
-\newpage
 # Results
@@
 
+Figure \@ref(fig:PotentialFaceData), the bar chart of the potential faces shows Google produces the most detections.
+This would be a strong incentive to use Google for facial recognition in sports application.
+It was considered that Google's API may have been finding more unwanted faces than the other APIs.
+Table \@ref(tab:Type-Matches-Manual) details the amounts of faces that were found by each API that matched or did not match a face found manually.
+There are slightly more faces found by APIs that do match the faces found manually, 56.34%, than faces that do not match, 43.66%.
+This was unexpected as it was presumed that majority of the faces annotated manually would be found.
+
+The largest group of images were those annotated by manual annotations and found by the Google API, these faces consisted of 26.46% of the total sample.
+This set of images are also seen in Figure \@ref(fig:PotentialFaceUpset), which shows the amount of faces that were found by each combination of APIs.
+The group of faces that were found by manually and by the Google API are represented across the various bars.
+Their ownership of the faces is denoted by the black bubbles below the bars.
+
 ## Potential Faces Matching Manual Annotations
@@
 To consider how many Type I errors occurred, where a face was detected incorrectly, we look at the potential faces that do not match manually annotated faces.
-
-\newpage
 
@@
 
-All the potential facees that Google found which do not match manually annotated faces were correctly identifying faces.
+Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:Type-Matches-Manual) that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd members were beyond what would be expected of an emotion recognition application for tennis players.
+These were deemed unlikely to be detected and neglected during manual annotation.
 
-\newpage
+Table \@ref(tab:Type-Matches-Manual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces.
+Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were not faces.
+
+All the potential faces that Google found which do not match manually annotated faces were correctly identifying faces.
 
@@
 
-\newpage
-
 ## False Discoveries
@@
 
-\newpage
+```{r animetricsWeird, fig.cap=" Animetrics provided results that were quite unusual \\label{fig:animetricsWeird}" }
+i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot()
+i2 <- "2016_CT6_R01_EKulichkova_RUS_vs_APetkovic_GER_WS128_clip.0080.png" %>% overlayGgplot()
+i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot()
+grid.arrange(i1, i2, i3, nrow=2)
+
+```
 
@@
 We then considered that there would be an uneven amount of faces with certain image attributes. This is considered in the mosaics below in Figure \@ref(fig:Mosaic).
+
+The images were all considered manually. The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
+This showed that crowd members faces were often recognized, this is both helpful and unhelpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
 
@@
 ## Results Overview
-Figure \@ref(fig:PotentialFaceData), the bar chart of the potential faces shows Google produces the most detections.
-This would be a strong incentive to use Google for facial recognition in sports application.
-It was considered that Google's API may have been finding more unwanted faces than the other APIs.
-Table \@ref(tab:Type-Matches-Manual) details the amounts of faces that were found by each API that matched or did not match a face found manually.
-There are slightly more faces found by APIs that do match the faces found manually, 56.34%, than faces that do not match, 43.66%.
-This was unexpected as it was presumed that majority of the faces annotated manually would be found.
-
-The largest group of images were those annotated by manual annotations and found by the Google API, these faces consisted of 26.46% of the total sample.
-This set of images are also seen in Figure \@ref(fig:PotentialFaceUpset), which shows the amount of faces that were found by each combination of APIs.
-The group of faces that were found by manually and by the Google API are represented across the various bars.
-Their ownership of the faces is denoted by the black bubbles below the bars.
-
-Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:Type-Matches-Manual) that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd memebers were beyond what would be expected of an emotion recognition application for tennis players.
-These were deemed unlikely to be detected and neglected during manual annotation.
-
-Table \@ref(tab:Type-Matches-Manual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces.
-Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were not faces.
-
-```{r animetricsWeird, fig.cap=" Animetrics provided results that were quite unusual \\label{fig:animetricsWeird}" }
-i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot()
-i2 <- "2016_CT6_R01_EKulichkova_RUS_vs_APetkovic_GER_WS128_clip.0080.png" %>% overlayGgplot()
-i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot()
-grid.arrange(i1, i2, i3, nrow=2)
-
-```
-
-The images were all considered manually. The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
-This showed that crowd members faces were often recognized, this is both helpful and unhelpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
 
@@
 
+# Acknowledgements
+
+COMMENT: Add your software and data file list here, list packages used here, e.g. The R package ggplot2 [@ggplot2] was used to make the plots.
+
 # References

### 2017-07-28 Report06-12.Rmd
Added colour scheme

@@
 author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
-date: "13 February 2017"
+date: "28 July 2017"
 output: bookdown::pdf_document2
@@
 
+# colour scheme
+type.colours <- c(Animetrics = "#B3E2CD",
+                      Google = "#FDCDAC",
+                      Manual = "#CBD5E8",
+                      Microsoft = "#F4CAE4",
+                      Skybiometry = "#E6F5C9")
+
 #plot images with overlaid boxes
@@
     #read in image
-    image <- readImage(paste0("figures/", i))
+    #image <- readImage(paste0("figures/", i))
     #used in analyses
-    #image <- readImage(paste0("images/", i))
+    image <- readImage(paste0("images/", i))
 
@@
   else{
-    group.colors <- c(Animetrics = "#B3E2CD",
-                      Google = "#FDCDAC",
-                      Manual = "#CBD5E8",
-                      Microsoft = "#F4CAE4",
-                      Skybiometry = "#E6F5C9")
-
     p1 <- p + geom_rect(data=faceData, 
@@
       guides(colour = guide_legend(""))  + theme(legend.position = "bottom") +
-      coord_fixed(ratio=0.85) + scale_colour_manual(values=group.colors)
+      coord_fixed(ratio=0.85) + scale_color_manual(type.colours)
     }
@@
     mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
-   ggplot(dataset, aes(x=xvar, y=proportion, group = reorder(type, -proportion), fill=type)) + geom_bar(stat = "identity", position = "dodge") +
-    ylab("Proportion of faces matched") + xlab(factorVar)
+   ggplot(dataset, aes(x=xvar, y=proportion, group = reorder(type, -proportion), fill=type)) + geom_bar(stat = "identity", position = "dodge") +  ylab("Proportion of faces matched") + xlab(factorVar) + scale_colour_manual(values=type.colours)
 }
@@
   guides(fill=FALSE) +
-  labs(caption="")
+  labs(caption="") + scale_fill_manual(values=type.colours)
 ```

### 2017-07-28 R/visualisation.R

@@ -1,22 +1,31 @@
 library(ggplot2)
 library(dplyr)
 library(tidyr)
+library(RColorBrewer)
+
+# colour scheme
+type.colours <- c(Animetrics = "#B3E2CD",
+                  Google = "#FDCDAC",
+                  Manual = "#CBD5E8",
+                  Microsoft = "#F4CAE4",
+                  Skybiometry = "#E6F5C9")
+
 
 #Load ALLmetaIMG in (from analysis.R)
 ggplot(ALLmetaIMG, aes(x = type)) + geom_bar(position="dodge")
 
 #NA refers to the boxes which don't match manual (hence we don't have info about the image classification)
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(visorhat)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(glasses)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(shotangle)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(graphic)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(person)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(situation)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(bg)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(detect)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(obscured)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(lighting)), group=type, fill=type)) + geom_bar(position="dodge")
-ggplot(ALLmetaIMG, aes(x = factor(x = factor(headangle)), group=type, fill=type)) + geom_bar(position="dodge")
+ggplot(ALLmetaIMGnamed, aes(x = factor(x = factor(visorhat)), group=type, fill=type)) + geom_bar(position="dodge")  + scale_colour_manual(values=type.colours)
[…]

### 2017-07-28 Report06-12.Rmd
Time Taken Paragraph

@@
 
-COMMENT: Add a paragraph on time taken to find faces for each software
+The amount of time taken for each software to process facial detetion on the individual images is presented in the histogram below:
+
+```{r timeDensity, fig.cap="This density plots diplays the common lengths of time each API took to detect faces in each image. It can be seen that the\\label{fig:timeDensity}"}
+times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual")
+ggplot(times, na.rm=T) + 
+  scale_color_manual(values = type.colours) +
+  geom_density(aes(x=time.user.self, colour=type)) +
+  xlab("Time Taken") +
+  theme(panel.background = element_rect(fill="grey"))
+```
 
@@
 
-```{r Type-Matches-Manual, fig.cap = "This table shows the amount potential faces that were found by the APIs and whether they compare to those annotated manually.
-Where the FALSE row denotes API Face potential facees do not coincide with manually annotated faces.
-The tables shows that Google found 46.96% of the Faces identified manually.\\label{tab:Type-Matches-Manual}"}
+```{r TypeMatchesManual, results='asis', fig.cap = "\\label{tab:TypeMatchesManual}"}
 
@@
 
-pander(ct)
+pander(ct, caption = "This table shows the amount potential faces that were found by the APIs and whether they compare to those annotated manually.
+Where the FALSE row denotes API Face potential facees do not coincide with manually annotated faces.
+The tables shows that Google found 46.96% of the Faces identified manually.")
 ```
 
-Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:Type-Matches-Manual) that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd members were beyond what would be expected of an emotion recognition application for tennis players.
+Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:TypeMatchesManual), that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd members were beyond what would be expected of an emotion recognition application for tennis players.
 These were deemed unlikely to be detected and neglected during manual annotation.
 
-Table \@ref(tab:Type-Matches-Manual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces.
+Table \@ref(tab:TypeMatchesManual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces.
 Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were not faces.

### 2017-08-04 Report06-12.Rmd
overlayggplot update
allow for new colour scheme, argument for legend

@@
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=FALSE, fig.env = TRUE)
 
@@
 # colour scheme
-type.colours <- c(Animetrics = "#B3E2CD",
-                      Google = "#FDCDAC",
-                      Manual = "#CBD5E8",
-                      Microsoft = "#F4CAE4",
-                      Skybiometry = "#E6F5C9")
+type.colours <- c(Animetrics =     "#1B9E77",
+                      Google =     "#D95F02",
+                      Manual =     "#E6AB02",
+                      Microsoft =  "#E7298A",
+                      Skybiometry ="#66A61E")
 
 #plot images with overlaid boxes
-overlayGgplot <- function(imgList, mergeData, matchBox=FALSE){
+overlayGgplot <- function(imgList, mergeData, matchBox=FALSE, colourScheme = type.colours, legend=TRUE){
   for(i in imgList){
@@
   }
-  else{
-    p1 <- p + geom_rect(data=faceData, 
+  else {
+    pa <- p + geom_rect(data=faceData, 
                         aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                             color=type, group=FaceID), fill=NA)  +
-      guides(colour = guide_legend(""))  + theme(legend.position = "bottom") +
-      coord_fixed(ratio=0.85) + scale_color_manual(type.colours)
+      coord_fixed(ratio=0.85) + scale_color_manual(values = colourScheme)
+
+    if (legend) p1 <- pa + guides(colour = guide_legend("")) + theme(legend.position = "bottom")
+    else p1<- pa + theme(legend.position = "none")
     }
@@
 Each API returned areas that indicated the potential location of a face.
-These areas were defined by a Bounding Box, created using the four points returned by the APIs to make a box around each face.
+These areas are defined using the four points returned by the APIs..
 The Google Vision API detected a large amount of potential faces, much more than Microsoft, Skybiometry or Animetrics.
@@
 To evaluate the performance in terms of the overall accuracy of each algorithm we considered the amount of faces they classified that matched faces that were selected manually.
-Using a sample that contains all the manually annotated faces and all the faces recognized by the four APIs.
+This sample contains all the manually annotated faces and all the faces recognized by the four APIs.
 
 Figure \@ref(fig:PotentialFaceData), the bar chart of the potential faces shows Google produces the most detections.
-This would be a strong incentive to use Google for facial recognition in sports application.
+Having a high volume of detected faces returned is valuable for the future use of applying facial recognition during sports.
 It was considered that Google's API may have been finding more unwanted faces than the other APIs.
@@
 The largest group of images were those annotated by manual annotations and found by the Google API, these faces consisted of 26.46% of the total sample.
-This set of images are also seen in Figure \@ref(fig:PotentialFaceUpset), which shows the amount of faces that were found by each combination of APIs.
-The group of faces that were found by manually and by the Google API are represented across the various bars.
-Their ownership of the faces is denoted by the black bubbles below the bars.
+
+Figure \@ref(fig:PotentialFaceUpset) helps to understand faces that were found by a combination of APIs, and the manual annotations.
+The black bubbles below the bars show the API combination that detected all the faces counted in the bar above.
+
+```{r PotentialFaceUpSet, fig.cap = "\\label{fig:PotentialFaceUpset} potential facees Per API Combination.
+The Bar Chart shows the potential facees that were recognised by multiple API or found manually.
+The largest group, with 809 faces, is potential facees only found by Manual annotations.
+The following group were the 716 faces recognized both Manually and by the Google API.
+These combinations may give some indication as to the circumstances when some APIs perform better than others."}
+createUpSet(ALLmetaIMGnamedFaces)
+```
 
@@
 
-To consider how many Type I errors occurred, where a face was detected incorrectly, we look at the potential faces that do not match manually annotated faces.
+To consider how many Type II errors occurred, where a potential face was detected incorrectly, we look at the potential faces that do not match manually annotated faces.
 
-```{r TypeMatchesManual, results='asis', fig.cap = "\\label{tab:TypeMatchesManual}"}
+```{r TypeMatchesManual, results='asis', fig.cap = "\\ label{tab:TypeMatchesManual}"}
 
@@
 Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:TypeMatchesManual), that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd members were beyond what would be expected of an emotion recognition application for tennis players.
-These were deemed unlikely to be detected and neglected during manual annotation.
+These were deemed unlikely to be necessary when attempting to find faces of players during tennis matches, and neglected during manual annotation.
 
 Table \@ref(tab:TypeMatchesManual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces.
-Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were not faces.
-
-All the potential faces that Google found which do not match manually annotated faces were correctly identifying faces.
-
-```{r PotentialFaceUpSet, fig.cap = "\\label{fig:PotentialFaceUpset} potential facees Per API Combination.
-The Bar Chart shows the potential facees that were recognised by multiple API or found manually.
-The largest group, with 809 faces, is potential facees only found by Manual annotations.
-The following group were the 716 faces recognized both Manually and by the Google API."}
-createUpSet(ALLmetaIMGnamedFaces)
-```
-
-This shows that there are many faces that were identified by some APIs and not others. These combinations may give some indication as to the circumstances when some APIs perform better than others.
+Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were actually very unusual results.
 
 ## False Discoveries
-The image below is an example of how some faces were only found by certain APIs, and how some APIs produced unusual false discoveries.
+Below are some examples of when faces were only found by one of the APIs, and how the APIs produced unusual false discoveries.
 
-```{r UnusualImage, results=TRUE, fig.cap = "\\label{fig:UnusualImage} There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face."}
-imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
-overlayGgplot(imagesList3, ALLmetaIMGnamedFaces, matchBox = FALSE)
-```
+```{r UnusualImages, fig.cap = "Animetrics provided results that were quite unusual.
+The top left image presents a potential faces that actually defines an area containing a player's back and a ballboy's torso.
+\\label{fig:UnusualImages}" }
+i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE)
+i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE)
+i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE)
+i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE)
 
-```{r animetricsWeird, fig.cap=" Animetrics provided results that were quite unusual \\label{fig:animetricsWeird}" }
-i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot()
-i2 <- "2016_CT6_R01_EKulichkova_RUS_vs_APetkovic_GER_WS128_clip.0080.png" %>% overlayGgplot()
-i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot()
-grid.arrange(i1, i2, i3, nrow=2)
+gridExtra::grid.arrange(i1, i2, i3, i4, nrow=2)
 

### 2017-08-08 Report06-12.Rmd
Added API citations

@@
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=FALSE, fig.env = TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE)
 
@@
 # colour scheme
-type.colours <- c(Animetrics =     "#1B9E77",
-                      Google =     "#D95F02",
-                      Manual =     "#E6AB02",
-                      Microsoft =  "#E7298A",
-                      Skybiometry ="#66A61E")
+type.colours <- c(Animetrics =     "#7BCCC4",
+                      Google =     "#FC9272",
+                      Manual =     "#C994C7",
+                      Microsoft =  "#FA9FB5",
+                      Skybiometry ="#ADDD8E")
 
@@
 To record the details of attributes for each face and scene a Shiny [@shiny] App was created.
-We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassificationProgram.R].
+We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/master/ManualClassificationProgram.R].
 This helped to provide information for all attributes quickly and consistently.
@@
 
-The amount of time taken for each software to process facial detetion on the individual images is presented in the histogram below:
+The amount of time taken for each software to process facial detection on the individual images is presented in the histogram below:
 
-```{r timeDensity, fig.cap="This density plots diplays the common lengths of time each API took to detect faces in each image. It can be seen that the\\label{fig:timeDensity}"}
-times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual")
+```{r timeDensity, fig.cap="This density plot diplays the lengths of time each API took to detect faces in each image.
+Most of the images take less than one second to process.
+There is an outlier for Skybiometry that took almost 5 seconds to process.
+\\label{fig:timeDensity}"}
+times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual") %>% arrange(-time.user.self)
 ggplot(times, na.rm=T) + 
@@
   geom_density(aes(x=time.user.self, colour=type)) +
-  xlab("Time Taken") +
-  theme(panel.background = element_rect(fill="grey"))
+  xlab("Time Taken")
 ```
+
+It should be considered that the time taken may be an issue for 'real time' processing.
+It would depend on the amount of frames sampled.
+This also does not account for the time taken to manipulate and save the information returned.
 
@@
 ```{r PotentialFaceData, fig.cap = "\\label{fig:PotentialFaceData}  Potential Face Boxes Per API: The bar chart shows the number of Potential Face Boxes produced by each API, comparing the height of the bars indicates that Google's Facial Recognition API recognized almost 1000 more potential faces than the next best API, Microsoft."}
+
 ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + 
@@
 Having a high volume of detected faces returned is valuable for the future use of applying facial recognition during sports.
-It was considered that Google's API may have been finding more unwanted faces than the other APIs.
-Table \@ref(tab:Type-Matches-Manual) details the amounts of faces that were found by each API that matched or did not match a face found manually.
+Table \@ref(tab:TypeMatchesManual) details the amounts of faces that were found by each API that matched or did not match a face found manually.
 There are slightly more faces found by APIs that do match the faces found manually, 56.34%, than faces that do not match, 43.66%.
@@
 
-To consider how many Type II errors occurred, where a potential face was detected incorrectly, we look at the potential faces that do not match manually annotated faces.
+We have two possible results for each potential face returned by the APIs.
+The first is presented in the form of our null hypothesis:
+
+$H_0:$ The potential face captured by the API is not an actual face.
+
+$H_A:$ The potential face captured by the API is an actual face.
+
+If the null hypothesis is true, the potential face location would not match the location of a manually annotated face.
+We would expect to see this for several reasons, when the face returned was deemed impractical or it would not be required that the chosen API would return the face in future use.
+Also when the potential face returned was a false discovery, in the instance where there was no face within the area deemed a potential face.
+
+This compares to the alternative hypothesis, where the potential face location matched the location of a manual face.
+They were then given an identical ID to denote they captured the same face if the overlapping area of the two boxes was 1/3, or greater, of the potential face location area.
+
+These definitions allowed us to define the four different scenarios of a hypothesis test.
+
+To consider how many Type II errors occurred, where an actual face was detected by an API, and incorrectly it was not annotated manually, and how many Type I errors occurred where a potential face was found by an API, and it was actually a face, but was not detected manually.
+we look at the potential faces that do not match manually annotated faces.
 
@@
 Below are some examples of when faces were only found by one of the APIs, and how the APIs produced unusual false discoveries.
+These highlight the potential differences in the detection methods used by each of the APIs.
+This would need to be taken under consideration to prevent time wasted on sorting actual faces from false discoveries in future applications.
 
-```{r UnusualImages, fig.cap = "Animetrics provided results that were quite unusual.
-The top left image presents a potential faces that actually defines an area containing a player's back and a ballboy's torso.
+```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual.
+The top left image presents a potential faces that actually defines an area containing a player's back and a ball boy's torso.
+The top right shows two potential faces that are actually the KIA logo on the net.
+The bottom left image was very interesting as the player's face was found, but the shirts of both the player and ball boy were deemed potential faces.
+The bottom right image had a lot more faces that usually recognised.
+Animetrics found a fist to the right on the centre that it considered a potential face.
 \\label{fig:UnusualImages}" }
@@
 gridExtra::grid.arrange(i1, i2, i3, i4, nrow=2)
-
 ```
@@
 The images were all considered manually. The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
-This showed that crowd members faces were often recognized, this is both helpful and unhelpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
+This showed that crowd members faces were often recognized, this is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
+It also allowed for an increase in understanding how attributes of a face impact on the APIs detetion capabilities.
 
@@
   ylab("Amount of faces") + xlab("Situation the face was captured during")
+```
+
+## Player Faces
+
+Tennis players faces will be the main focus of this use of facial detection. 
+It is important that the selected API be able to return strong and consitent results for player's faces.
+
+```{r Player, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes. \\label{fig:DDPbgshot}"}
+
+#ALLmetaIMGPlayers
+
+ggplot(data=ALLmetaIMGPlayers) +
+     geom_bar(aes(x=bg, fill = shotangle), 
+            position = position_stack(reverse = TRUE), 
+            na.rm=TRUE) +
+  coord_flip() +
+  guides(fill = guide_legend(title="Background")) +
+  labs(caption="") +
+  ylab("Amount of faces") + xlab("Angle the face was captured from")
+```
+
+## Accessories
+
+The use of accessories, Glasses and Visors or Hats, was considered as the Australian Open takes place on both indoor and outdoor courts. 
+It was assumed that outdoor courts would lead to the use of these accessories and these accessories may contribute to the performance of a recognition software.
+There are many more faces recognized, by both the Google recognition's and manual annotations, that do not have Glasses.
+This disproportionate sample of faces with Glasses means that we considered it proportionally rather than as a total.
+
+```{r Misc, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes. \\label{fig:DDPbgshot}"}
+
+ALLmetaIMGnamedFaces %>%
+  filter(type=="Manual") -> ManFaces
+
+#upset(order.by="freq", nsets=100)
 
@@
 
-```{r HeadAngles, fig.cap = "The amount of faces found by Google with the head-angle Other, is much larger than the amount of faces with the head-angle Profile or Front On.
-Therefore this should also be considered proportionately.\\label{tab:HeadAngles}"}
-HeadangleGoogle <- ALLmetaIMGPlayers %>%   filter(type=="Google") %>%
-filter(matchesManual==TRUE)
-
-pander(table(HeadangleGoogle$headangle))
-```
-
-```{r Headangle-Figure, fig.cap = "\\label{fig:Headangle-Figure} Google performs much better in comparison to the other API when the head-angle is Profile.
-This is outperforming unusually well, however this could also be due to the poor performance of the API in this circumstance."}
-ggplotProportion(ALLmetaIMGPlayers, headangle)+xlab("Head Angle of Face")
-```
-
-## Results Overview
-
-Image 1 shows the images preferable for future research. Where the faces will be recognized and allow both the identity and emotion of the players to be recognized.
-
-Google gave the optimum results in this image as it found the face of the player, but did not locate the face of the staff member behind him on the court.
-
-While Google's recognition's mostly matched the Manually annotated set of faces, there were some that did not. These were all actually faces and were missed during manual annotations.
-
-Table 6 shows that 190 of the faces that were not found manually occurred in the scene of a Court player close-up, with a background of a logo wall, where the shot was taken at player shoulder height.
-
-This shows it was performing extremely well and not resulting in unexplained potential faces as some of the other software were.
-This is a strong indicator that applying Google's software for further research would result in the recognition of desired faces.
-
-These results have contributed to the choice of Google given the optimum scene as described above.
-Implementing a filtering process, either using current or alternative footage^[See future research for further information on these options] would allow Google to provide Tennis Australia with the most applicable results.
-
-We moved to considering the characteristics of the faces. This helped to distinguish where Google performed well in comparison to the other software options.
-
-Table 7 showed the combinations of attributes that were found for each face[Given that information was not recorded where Google provided facial recognition for faces not Manually annotated these could not be considered.].
-The use of accessories, Glasses and Visors or Hats, was considered as the Australian Open takes place on both indoor and outdoor courts.
-To apply this research all courts that elite Tennis players compete on had to be included.
-It was assumed that outdoor courts would led to the use of these accessories and these accessories may contribute to the performance of a recognition software.
-It may be implied by the table that Glasses prohibits recognition as all but one of the combinations have 'No' for the Glasses variable.
-However, we are cautious of validating this as Table 8 tells that there are many more faces recognized, by both the Google recognition's and manual annotations, that do not have Glasses.
-This disproportionate sample of faces with Glasses means that we considered it proportionally rather than as a total.
-
-Graph 2 demonstrates that the presence of Glasses on faces annotated manually did affect recognition by Google's algorithm, while it outperformed the other software in both instances, faces were identified more often if the person did not wear glasses.
-
-Moving to looking at the characteristics that were considered manually shows that the use of glasses by players coincided with less faces being annotated.
-
-The box-plot in graph encourages our comparisons to not consider the size of potential face boxes as a measure of how the software performs on small faces.
+## Miscellaneous
 
@@
 
-COMMENT: Add your software and data file list here, list packages used here, e.g. The R package ggplot2 [@ggplot2] was used to make the plots.
+## APIs
+Animetrics: This name used throughout the paper refers to the Animetrics Face Recognition API, FaceR API by @Animetrics.
+
+Google: @Google
+
+Microsoft: This has been used to refer to the Microsoft Azure Cognitive Services Face API, published by @Microsoft.
+
+Skybiometry: @Skybiometry
+
+## Data Files
+
+## Packages
+The R package ggplot2 [@ggplot2] was used to make the plots.
 

### 2017-08-08 Report06-12.Rmd
figure locations
Accessories crosstable

@@
 
-```{r timeDensity, fig.cap="This density plot diplays the lengths of time each API took to detect faces in each image.
+```{r timeTable, results='asis', fig.cap="\\label{tab:timeTable}"}
+
+times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual") %>% droplevels()
+
+times %>% 
+  split(.$type) %>%  map_df(~ summary(.$time.user.self, digits=max(2, getOption("digits")-2))) %>%
+  rownames_to_column %>%  gather(var, value, -rowname) %>% 
+  spread(rowname, value) %>% select(c("API" = `var`,
+                            "Min" = `1`,
+                        "1st Qrt" = `2`,
+                        "Median"  = `3`,
+                        "3rd Qrt" = `5`,
+                        "Max"     = `6`)) -> usertime
+times %>% 
+  split(.$type) %>%  map_df(~ summary(.$time.sys.self, digits=max(2, getOption("digits")-2))) %>%
+  rownames_to_column %>%  gather(var, value, -rowname) %>% 
+  spread(rowname, value) %>% select(c("API" = `var`,
+                            "Min" = `1`,
+                        "1st Qrt" = `2`,
+                        "Median"  = `3`,
+                        "3rd Qrt" = `5`,
+                        "Max"     = `6`)) -> systime
+
+cbind(usertime, systime) -> timetable
+
+knitr::kable(timetable, booktabs = TRUE, longtable=TRUE, caption="This table allows comparisons to be made between the  amount of time taken for each API took to detect faces in each image.
 Most of the images take less than one second to process.
-There is an outlier for Skybiometry that took almost 5 seconds to process.
-\\label{fig:timeDensity}"}
-times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual") %>% arrange(-time.user.self)
-ggplot(times, na.rm=T) + 
-  scale_color_manual(values = type.colours) +
-  geom_density(aes(x=time.user.self, colour=type)) +
-  xlab("Time Taken")
+Google had the highest maximum time of 4.936", format = "latex")
 ```

### 2017-08-08 Report06-12.Rmd
API figure names

@@
   rownames_to_column %>%  gather(var, value, -rowname) %>% 
-  spread(rowname, value) %>% select(c("API" = `var`,
+  spread(rowname, value) %>% select(c(
                             "Min" = `1`,
@@
 It also has a record of how many faces had been identified in the image by counting each additional recognized face.
-To do so, we gathered the name of the file the face was found in and the software Type the potential Face Boxes was determined by.
+To do so, we gathered the name of the file the face was found in and the API that found the potential face.
 The automatically determined time values were also included.
@@
 The regression model that provided the best AIC, included the scene attributes: Shot Angle, Background, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
-It also included the lighting on the particular face, and whether the specific face was accessorised with Glasses and a Visor or Hat.
+It also included the lighting on the particular face, and whether the specific face was accessorised with glasses and headwear, a visor or hat.
 
@@
 ```{r Regression, fig.width=7.5, fig.cap = "The figure depicts the change in the probability of a face being detected by the APIs given a certain attribute level associated with the face.
-Wearing either glasses, or visor or a hat significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}"}
+Wearing either glasses, or headwear, a visor or a hat, significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}"}
 # Prepare data
@@
            drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
-           dnn = c("Matches Manual","API Type"))
+           dnn = c("Matches Manual","API"))
 
@@
 Tennis players faces will be the main focus of this use of facial detection. 
-It is important that the selected API be able to return strong and consitent results for player's faces.
+It is important that the selected API be able to return strong and consistent results for player's faces.
 
-```{r Player, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes. \\label{fig:DDPbgshot}"}
+```{r Player, fig.cap = c("This stacked bar chart allows consideration ", "of the interaction between two image attributes. \\label{fig:DDPbgshot}")}
 
 #ALLmetaIMGPlayers
+
+ggplot(data=ALLmetaIMGPlayers) +
+     geom_bar(aes(x=bg, fill = shotangle), 
+            position = position_stack(reverse = TRUE), 
+            na.rm=TRUE) +
+  coord_flip() +
+  guides(fill = guide_legend(title="Background")) +
+  labs(caption="") +
+  ylab("Amount of faces") + xlab("Angle the face was captured from")
 
@@
 
-The use of accessories, Glasses and Visors or Hats, was considered as the Australian Open takes place on both indoor and outdoor courts. 
+The use of accessories, glasses and headwear, visors or hats, was considered as the Australian Open takes place on both indoor and outdoor courts. 
 It was assumed that outdoor courts would lead to the use of these accessories and these accessories may contribute to the performance of a recognition software.
@@
 
-```{r Misc, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes. \\label{fig:DDPbgshot}"}
+```{r accessories, fig.cap = "\\label{tab:accessories}"}
 
@@
 
-#upset(order.by="freq", nsets=100)
+ct<-CrossTable(table(ManFaces$glasses, ManFaces$visorhat), 
+               prop.chisq = FALSE, 
+               digits=2,
+               expected = FALSE,
+           prop.r = FALSE, prop.c = FALSE, prop.t = TRUE,
+           drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
+           dnn = c("Glasses","Headwear"))
 
+pander(ct, caption = "This cross table compares the amount of faces that were captured wearing accessories.")
 ```

### 2017-08-08 Report06-12.Rmd
time taken

@@
 
-```{r timeTable, results='asis', fig.cap="\\label{tab:timeTable}"}
+```{r timeTable, results='asis', fig.cap="System time taken by the four APIs to finish searching individual images, plotted against number of faces discovered.
+Skybiometry is the fastest, and Microsoft is the slowest.
+The largest variability is when no faces are found.\\label{tab:timeTable}"}
+times <- ALLmetaIMGnamed %>% 
+  filter(type!="Manual") %>%
+  select(file, type, time.user.self, time.sys.self) %>%
+  group_by(file, type) %>%
+  mutate(n=n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self)) 
+ggplot(times) + 
+  geom_jitter(aes(x=n, y=time.sys.self, colour=type), alpha=0.2, width=0.3, height=0.01) + 
+  #facet_wrap(~type) + 
+  ylim(c(0, 0.1)) + 
+  geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) +
+  xlab("Number of faces detected") + ylab("System time (sec)") + 
+  scale_colour_manual("API", values=type.colours)
+```
 
-times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual") %>% droplevels()
-
+```{r eval=FALSE}
 times %>% 

### 2017-08-08 Report06-12.Rmd
Auto stash before merge of "master" and "steffMVP/master"

@@
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.)
 
@@
 
-```{r Player, fig.cap = c("This stacked bar chart allows consideration ", "of the interaction between two image attributes. \\label{fig:DDPbgshot}")}
+```{r Player, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes. \\label{fig:DDPbgshot}"}
 
 #ALLmetaIMGPlayers
-
-ggplot(data=ALLmetaIMGPlayers) +
-     geom_bar(aes(x=bg, fill = shotangle), 
-            position = position_stack(reverse = TRUE), 
-            na.rm=TRUE) +
-  coord_flip() +
-  guides(fill = guide_legend(title="Background")) +
-  labs(caption="") +
-  ylab("Amount of faces") + xlab("Angle the face was captured from")
 

### 2017-08-11 Report06-12.Rmd
remove footnotes

@@
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE)
 
@@
 To record the details of attributes for each face and scene a Shiny [@shiny] App was created.
-We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/master/ManualClassificationProgram.R].
+We called this Application our ManualClassificationProgram.
 This helped to provide information for all attributes quickly and consistently.
@@
 The collation of the results from the Manual Recognition Program created
-two CSVs, ManualClassifiedFaces^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedFaces.csv] and ManualClassifiedScenes^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedScenes.csv].
+two CSVs.
 
@@
 ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat)
+```
+
+```{r GoogleRegression, fig.width=7.5, fig.cap = "Google Regression\\label{fig:GoogleRegression}"}
+ALLmetaIMGnamedFaces %>% filter(type=="Manual" | type=="Google") %>%
+  mutate(isplayer = ifelse(detect=="Player", 1, 0)) -> players
+
+glm(isplayer ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat, data=players) %>% summary()
+
+# currently same model as earlier, give two?
 ```
@@
 
-## Player Faces
-
-Tennis players faces will be the main focus of this use of facial detection. 
-It is important that the selected API be able to return strong and consistent results for player's faces.
-
-```{r Player, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes. \\label{fig:DDPbgshot}"}
-
-#ALLmetaIMGPlayers
-
-ggplot(data=ALLmetaIMGPlayers) +
-     geom_bar(aes(x=bg, fill = shotangle), 
-            position = position_stack(reverse = TRUE), 
-            na.rm=TRUE) +
-  coord_flip() +
-  guides(fill = guide_legend(title="Background")) +
-  labs(caption="") +
-  ylab("Amount of faces") + xlab("Angle the face was captured from")
-```
-
 ## Accessories
@@
 
+All data files used are available on the github page.
+
+ManualClassifiedFaces.csv resulted from the use of the Manual Classification Program, it has information about each face identified manually.
+ManualClassifiedScenes.csv also resulted from the use of the app, it contains information about each image.
+
 ## Packages

### 2017-08-16 Report06-12.Rmd
Edits

@@
 library(xtable)
+library(gtable)
 library(ggthemes)
@@
 
-We were able to try the online demos to see whether these software were viable, we used the following Image displayed below in Figure \@ref(fig:Trial-Image):
+We were able to try the online demos to see whether these software were viable, we used the following Image displayed  in Figure \@ref(fig:Trial-Image):
 
@@
 This changed the display and presented a set of Attributes with radio buttons, this allowed information to be recorded for the face in the specific 'Face Box'.
-This recorded the x and y coordinates of the corner points of a box drawn by the mouse, and when the save button was hit it saved all the radio button selections and the 'Face Box' coordinates to a CSV file^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedFaces.csv].
+This recorded the x and y coordinates of the corner points of a box drawn by the mouse, and when the save button was hit it saved all the radio button selections and the 'Face Box' coordinates to a CSV file.
 
 When a face was not selected, the radio buttons showed the Scene attributes and the radio buttons with the possible selections the annotated was able to choose from.
-When in this display, selecting the save button would then save the Scene selections to a specific CSV file^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedScenes.csv].
+When in this display, selecting the save button would then save the Scene selections to a specific CSV file.
 
@@
 The software choices allowed for POST requests to be sent via the internet.
-To access the APIs through R we enlisted the httr package, using functions from this package a script was written for Google, Animetrics^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/animetrics.R], Microsoft^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/microsoftAPI.R] and Skybiometry^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/autoSkybiometry.R].
+To access the APIs through R we enlisted the httr package, using functions from this package a script was written for Google, Animetrics, Microsoft and Skybiometry.
 These scripts contained loops that would move through the images, individually posting a request for each image to be analysed.
@@
 
-The amount of time taken for each software to process facial detection on the individual images is presented in the histogram below:
+The amount of time taken for each software to process facial detection on the individual images is presented in the histogram :
 
@@
 A single data set was created to combine all necessary information in the previously mentioned files for our analysis.
-The information in the data set^[https://github.com/mvparrot/face-recognition/blob/master/ALLmetIMG.csv], was carefully considered.
+The information in the data set, was carefully considered.
 It considers the identify of each face, and all relative face attributes, as well as the image file the face was found in, from this information each face was able to be uniquely identified.
@@
 It also has a record of how many faces had been identified in the image by counting each additional recognized face.
-To do so, we gathered the name of the file the face was found in and the API that found the potential face.
+To do so, we gathered the name of the file the face was found in and the API that found it.
 The automatically determined time values were also included.
@@
 This allowed us to compare the identification areas, as well as contrast the identified faces of each software.
-This contributed another variable, boxID, to the data set^[https://github.com/mvparrot/face-recognition/blob/master/ALLmetIMG.csv].
+This contributed another variable, boxID, to the data set.
 
@@
 Using the data set^[ALLmetaIMGnamed] of the combined API and manual results, we were able to compare the performance of the software.
-Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(fig:PotentialFaceData).
+Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(fig:FaceData).
 
 However, individual faces are not beneficial if they do not correspond to the faces manually annotated.
-Figure \@ref(fig:PotentialFaceUpset) was created by defining groups depending on the API that recognized each particular face.
+Figure \@ref(fig:FaceUpset) was created by defining groups depending on the API that recognized each particular face.
 The UpSetR [-@UpSetR] package helps visualise set intersections.
-Where in this circumstance potential Faces Boxes may overlap on the same face, each bar shows the number of individual faces that have potential Face Boxes resulting from each of the APIs highlighted below the bar.
+Where in this circumstance faces boxes may overlap on the same face, each bar shows the number of individual faces that have boxes resulting from each of the APIs highlighted below the bar.
 
-### Modelling Face Detection Probabiity
+### Modeling Face Detection Probabiity
 
@@
 ## False Discoveries
-Below are some examples of when faces were only found by one of the APIs, and how the APIs produced unusual false discoveries.
+ are some examples of when faces were only found by one of the APIs, and how the APIs produced unusual false discoveries.
 These highlight the potential differences in the detection methods used by each of the APIs.
@@
 
-We then considered that there would be an uneven amount of faces with certain image attributes. This is considered in the mosaics below in Figure \@ref(fig:Mosaic).
+We then considered that there would be an uneven amount of faces with certain image attributes. This is considered in the mosaics  in Figure \@ref(fig:Mosaic).
 

### 2017-08-16 Report06-12.Rmd
New time plots

@@
 #csv files:
-ALLmetaIMGnamed<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
+ALLmetaIMGnamed<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry")))) %>% 
+  filter(!duplicates)
 SceneAttributes<-read_csv("figures/SceneAttributes.csv")
@@
 
-ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
+ALLmetaIMGnamedFaces <- ALLmetaIMGnamed%>%
   filter(!is.na(type)) %>% 
-  dplyr::select(-ID, -facecounter)%>%
   mutate(fileID = as.numeric(factor(file))) %>%
@@
   mutate(n=n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))
-ggplot(times) +  
+
+t1 <- ggplot(times) +  
+  geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) + 
+  xlab("Number of faces detected") + ylab("System time (sec)") +  
+  scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")
+
+t2 <- ggplot(times) +  
   geom_jitter(aes(x=n, y=time.sys.self, colour=type), alpha=0.2, width=0.3, height=0.01) +  
-  #facet_wrap(~type) +  
+  facet_wrap(~type) +  
   ylim(c(0, 0.1)) +  
   geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) + 
-  xlab("Number of faces detected") + ylab("System time (sec)") +  
-  scale_colour_manual("API", values=type.colours) 
+  xlab("Number of faces detected") +  
+  scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")
+
+grid.arrange(t1,t2,nrow=1)
 ```
@@
 Most of the images take less than one second to process.
-Google had the highest maximum time of 4.936", format = "latex")
+Google had the highest maximum time of 4.936", format = "latex") #%>%
+ # add_header_above(c(" " = 1, "Group 1" = 5, "Group 2" = 5))
 ```
@@
 
-```{r Regression, fig.width=7.5, fig.cap = "The figure depicts the change in the probability of a face being detected by the APIs given a certain attribute level associated with the face.
-Wearing either glasses, or headwear, a visor or a hat, significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}"}
+```{r RegressionFunctions}
 # Prepare data
@@
 
-ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat)
 ```
 
-```{r GoogleRegression, fig.width=7.5, fig.cap = "Google Regression\\label{fig:GoogleRegression}"}
+```{r CheckModels}
+
+mods<-GlmModelCreation(model = hit ~ 0 + 
+              shotangle + 
+              bg + 
+              bg*shotangle + 
+              situation + 
+              obscured +
+              headangle +
+              lighting + 
+              glasses + 
+              visorhat, 
+              data=ALLmetaIMGnamedFaces)
+
+#mods$Animetrics %>% drop1(., test="Chisq")
+#mods$Google %>% drop1(., test="Chisq")
+#interaction significant
+#mods$Microsoft %>% drop1(., test="Chisq")
+#mods$Skybiometry %>% drop1(., test="Chisq")
+
+# mods$Animetrics %>% 
+#   summary %>%
+#   .$coefficients %>%
+#   as.data.frame() %>% select(Estimate, `Pr(>|z|)`) -> a
+
+```
+
+The model selection technique was undertaking a Chi-Square test comparing the model deviance with all variables to the model deviance when each particular variable was excluded.
+If there was a low Pr(>Chi) value associated with a variable, that would show the variable was significant in predicting whether the faces annotated manually would be detected by the API.
+
+```{r Regression, fig.width=7.5, fig.cap = "The figure depicts the change in the probability of a face being detected by the APIs given a certain attribute level associated with the face.
+Wearing either glasses, or headwear, a visor or a hat, significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}"}
+
+ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + situation + lighting + glasses + visorhat)
+
+```
+
+```{r GoogleRegression, fig.cap = "Google Regression\\label{fig:GoogleRegression}"}
 ALLmetaIMGnamedFaces %>% filter(type=="Manual" | type=="Google") %>%
@@
 
-glm(isplayer ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat, data=players) %>% summary()
+mod1 <- glm(isplayer ~ 0 + 
+              shotangle + 
+              bg + 
+              bg*shotangle + 
+              situation + 
+              obscured +
+              headangle +
+              lighting + 
+              glasses + 
+              visorhat, data=players, family=binomial(link="logit"))
+
+drop1(mod1, test="Chisq")
 
 # currently same model as earlier, give two?
+
+colnames(players)
 ```
+When forcing no intercept, all variables are significant at the 0 level, and obscured is only significant at the 0.001 level.
 
@@
 
-## Amount of Potential Faces
+## Amount of Faces
 
 Each API returned areas that indicated the potential location of a face.
-These areas are defined using the four points returned by the APIs..
-The Google Vision API detected a large amount of potential faces, much more than Microsoft, Skybiometry or Animetrics.
-This can be seen below in Figure \@ref(fig:PotentialFaceData).
+These areas are defined using the four points returned by the APIs.
+The Google Vision API detected a large amount of faces, much more than Microsoft, Skybiometry or Animetrics.
+This can be seen  in Figure \@ref(fig:FaceData).
 
-```{r PotentialFaceData, fig.cap = "\\label{fig:PotentialFaceData}  Potential Face Boxes Per API: The bar chart shows the number of Potential Face Boxes produced by each API, comparing the height of the bars indicates that Google's Facial Recognition API recognized almost 1000 more potential faces than the next best API, Microsoft."}
+```{r FaceData, fig.cap = "\\label{fig:FaceData}   Face Boxes Per API: The bar chart shows the number of  Face Boxes produced by each API, comparing the height of the bars indicates that Google's Facial Recognition API recognized almost 1000 more faces than the next best API, Microsoft."}
 
@@
   scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +
-  ylab("Number of Potential Faces") + 
+  ylab("Number of Faces") + 
   guides(fill=FALSE) +
@@
 
-Figure \@ref(fig:PotentialFaceData), the bar chart of the potential faces shows Google produces the most detections.
+Figure \@ref(fig:FaceData), the bar chart of thefaces shows Google produces the most detections.
 Having a high volume of detected faces returned is valuable for the future use of applying facial recognition during sports.
@@
 
-Figure \@ref(fig:PotentialFaceUpset) helps to understand faces that were found by a combination of APIs, and the manual annotations.
-The black bubbles below the bars show the API combination that detected all the faces counted in the bar above.
+Figure \@ref(fig:FaceUpset) helps to understand faces that were found by a combination of APIs, and the manual annotations.
+The black bubbles  the bars show the API combination that detected all the faces counted in the bar above.
 
-```{r PotentialFaceUpSet, fig.cap = "\\label{fig:PotentialFaceUpset} potential facees Per API Combination.
-The Bar Chart shows the potential facees that were recognised by multiple API or found manually.
-The largest group, with 809 faces, is potential facees only found by Manual annotations.
+```{r FaceUpSet, fig.cap = "\\label{fig:FaceUpset} Faces Per API Combination.
+The Bar Chart shows the faces that were recognised by multiple API or found manually.
+The largest group, with 809 faces, is faces only found by Manual annotations.
 The following group were the 716 faces recognized both Manually and by the Google API.
@@
 
-## Potential Faces Matching Manual Annotations
+## Comparing Faces Found
 
-We have two possible results for each potential face returned by the APIs.
-The first is presented in the form of our null hypothesis:
+The faces found by each API are compared to those found manually.
+The upper left box of all tables shows that there was no tagging system for areas in the image not designated to be a face by either manual annotations or API detections.
 
-$H_0:$ The potential face captured by the API is not an actual face.
+```{r table}
+FacesAPI <- ALLmetaIMGnamedFaces %>% 
+  filter(!duplicates) %>%
+  select(FaceKey, type) %>%
+  table() %>%
+  as.data.frame() %>%
+  spread(key=type, value=Freq) %>%
+  mutate(Animetrics = ifelse(Animetrics==0, "No Face", "Face"),
+         Google = ifelse(Google==0, "No Face", "Face"),
+         Microsoft = ifelse(Microsoft==0, "No Face", "Face"),
+         Manual = ifelse(Manual==0, "No Face", "Face"),
+         Skybiometry = ifelse(Skybiometry==0, "No Face", "Face"))
 
-$H_A:$ The potential face captured by the API is an actual face.
+AM <- table(FacesAPI$Manual, FacesAPI$Animetrics, dnn = c("Manual", "Animetrics"))
+GM <- table(FacesAPI$Manual, FacesAPI$Google, dnn = c("Manual", "Google"))
+MM <- table(FacesAPI$Manual, FacesAPI$Microsoft, dnn = c("Manual", "Microsoft"))
+SM <- table(FacesAPI$Manual, FacesAPI$Skybiometry, dnn = c("Manual", "Skybiometry"))
+```
 
-If the null hypothesis is true, the potential face location would not match the location of a manually annotated face.
-We would expect to see this for several reasons, when the face returned was deemed impractical or it would not be required that the chosen API would return the face in future use.
-Also when the potential face returned was a false discovery, in the instance where there was no face within the area deemed a potential face.
+```{r tableAMt, results='asis', eval=FALSE}
 
-This compares to the alternative hypothesis, where the potential face location matched the location of a manual face.
-They were then given an identical ID to denote they captured the same face if the overlapping area of the two boxes was 1/3, or greater, of the potential face location area.
+AM <- table(FacesAPI$Manual, FacesAPI$Animetrics, dnn = c("Manual", "Animetrics"))
 
-These definitions allowed us to define the four different scenarios of a hypothesis test.
+AMt <- tableGrob(as.matrix(AM), rows = rownames(AM), cols = colnames(AM), theme = ttheme_minimal())
 
-To consider how many Type II errors occurred, where an actual face was detected by an API, and incorrectly it was not annotated manually, and how many Type I errors occurred where a potential face was found by an API, and it was actually a face, but was not detected manually.
-we look at the potential faces that do not match manually annotated faces.
+titleAM <- textGrob("   Animetrics", gp = gpar(fontsize = 15))
+padding <- unit(0.5,"line")
+AMt <- gtable_add_rows(AMt, heights = grobHeight(titleAM) + padding, pos = 0)
 
-```{r TypeMatchesManual, results='asis', fig.cap = "\\ label{tab:TypeMatchesManual}"}
+grid.arrange(AMt)
+tab <- gtable_add_grob(AMt,titleAM, 1, 1)
 
-NoManual<-ALLmetaIMGnamedFaces %>% filter(ALLmetaIMGnamedFaces$type!="Manual")
-NoManual<-NoManual %>% droplevels(NoManual$type) 
-ct<-CrossTable(table(NoManual$matchesManual, NoManual$type), 
-               prop.chisq = FALSE, 
-               digits=4,
-               expected = FALSE,
-           prop.r = TRUE, prop.c = TRUE, prop.t = TRUE,
-           drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
-           dnn = c("Matches Manual","API"))
+```
 
-pander(ct, caption = "This table shows the amount potential faces that were found by the APIs and whether they compare to those annotated manually.
-Where the FALSE row denotes API Face potential facees do not coincide with manually annotated faces.
-The tables shows that Google found 46.96% of the Faces identified manually.")
+```{r tableGMt, reaults='asis', fig.width=1}
+```
+
+```{r tableMMt, reaults='asis'}
+knitr::kable(MMt, booktabs = TRUE, longtable=F, format="latex")
+```
+
+```{r tableSMt, reaults='asis'}
+knitr::kable(SMt, booktabs = TRUE, longtable=F, format="latex")
 ```

### 2017-08-29 Report06-12.Rmd
Minor text edits

@@
 library(tidyverse)
-library(magick)
 library(kfigr)
@@
 ##Software Selection
-The choice of the initial software considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'
+The choice of the initial software considered for this research was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'
 
@@
 
-From the software's analysed we considered availability for use within the time frame of the report.
+From the software analysed we considered availability for use within the time frame of the report.
 This led us to choose Animetrics FaceR.
@@
 
-colnames(players)
 ```

### 2017-08-29 Report06-12.Rmd
Latex table

@@
 library(EBImage)
+library(gridExtra)
+library(ggmosaic)
 
@@
 ##Software Selection
-The choice of the initial software considered for this research was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'
+The choice of the initial software considered for this research was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.' [@Survey]
 
 The process of software selection to determine which we would compare was based on several criteria.
-Firstly, we based our choices on the results of the report as it considered processing speed and feature selection techniques, as well as the ability to perform both still-to-video and video-to-video recognition.
+The results of the report, as it considered processing speed and feature selection techniques, as well as the ability to perform both still-to-video and video-to-video recognition.
 
@@
 This led us to choose Animetrics FaceR.
-The report outlines that for Animetrics, 'one requirement is that image/face proportion
-should be at least 1:8 and that at least 64 pixels between eyes are required'. We realize this could present challenges given our data set.
+The report outlines that for Animetrics, 'one requirement is that image/face proportion should be at least 1:8 and that at least 64 pixels between eyes are required'.
+We realize this could present challenges given the pixel sizes of faces in the image set.
 It will also allow for an extension from detecting to recognizing people in the data set.
@@
 
-```{r tableAMt, results='asis', eval=FALSE}
+\begin{table}[]
+\centering
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{|l|l|}
+\hline
+434 & 1861 \\ \hline
+527 & 787 \\ \hline
+\end{tabular}%
+}
+\caption{My caption}
+\label{my-label}
+\end{table}
 
-AM <- table(FacesAPI$Manual, FacesAPI$Animetrics, dnn = c("Manual", "Animetrics"))
-
-AMt <- tableGrob(as.matrix(AM), rows = rownames(AM), cols = colnames(AM), theme = ttheme_minimal())
-
-titleAM <- textGrob("   Animetrics", gp = gpar(fontsize = 15))
-padding <- unit(0.5,"line")
-AMt <- gtable_add_rows(AMt, heights = grobHeight(titleAM) + padding, pos = 0)
-
-grid.arrange(AMt)
-tab <- gtable_add_grob(AMt,titleAM, 1, 1)
-
+```{r tableAMt, reaults='asis', fig.width=1}
+knitr::kable(AM, booktabs = TRUE, longtable=F, format="latex")
 ```
@@
 ```{r tableGMt, reaults='asis', fig.width=1}
+knitr::kable(GM, booktabs = TRUE, longtable=F, format="latex")
 ```
@@
 ```{r tableMMt, reaults='asis'}
-knitr::kable(MMt, booktabs = TRUE, longtable=F, format="latex")
+knitr::kable(MM, booktabs = TRUE, longtable=F, format="latex")
 ```
@@
 ```{r tableSMt, reaults='asis'}
-knitr::kable(SMt, booktabs = TRUE, longtable=F, format="latex")
+knitr::kable(SM, booktabs = TRUE, longtable=F, format="latex")
 ```

### 2017-08-29 Report06-12.Rmd
single figure for image characteristic tables

@@
 
-```{r MosaicShotangle, fig.cap = "The colours in the mosaic show the amount of faces that matched those found manually given the angle the faces were captured from.
-There is a greater amount of API faces that matched the faces found manually than those that did not match.
-However given the face was captured from a birds eye angle there were less faces that matched those found manually.
-The most common faces in our set were those captured at Player Shoulder Height and found manually and by an APIs.\\label{fig:Mosaic}"}
+```{r MosaicShotangle, fig.cap = "\\label{fig:Mosaic}"}
 library(ggmosaic)
@@
 
-ggplot(data=ALLmetaIMGnamedFaces) + 
+MosaicShotangle<- ggplot(data=ALLmetaIMGnamedFaces) + 
   geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
@@
   labs(caption="") +
-  ylab("Proportion of faces") + xlab("Angle the face was captured from ")
+  ylab("Proportion of faces") + xlab("Angle the face was captured from ") + theme(legend.position = "none")
 ```
 
+The colours in the mosaic in Figure \@ref(fig:ICFigs) Plot a.
+show the amount of faces that matched those found manually given the angle the faces were captured from.
+There is a greater amount of API faces that matched the faces found manually than those that did not match.
+However given the face was captured from a birds eye angle there were less faces that matched those found manually.
+The most common faces in our set were those captured at Player Shoulder Height and found manually and by an APIs.
+
 ```{r ShotangleCompare, eval=FALSE, fig.cap=".\\label{fig:ShotangleCompare}"}
-CompShot <- ALLmetaIMGnamedFaces %>% 
-  filter(shotangle=="Player Shoulder Height", 
-         bg=="Logo wall", 
-         situation=="Court player close−up",
-         type=="Google" | type=="Manual",
-         player2=="AMurray", player2:"AMurray")
+# CompShot <- ALLmetaIMGnamedFaces %>% 
+#   filter(shotangle=="Player Shoulder Height", 
+#          bg=="Logo wall", 
+#          situation=="Court player close−up",
+#          type=="Google" | type=="Manual",
+#          player2=="AMurray", player2:"AMurray")
 
@@
 
-```{r MosaicSit, fig.cap = "This mosaic shows the number of Faces captured during each possible situation.
-It contrasts how many of the images captured in situations either did or did not match the faces annotated manually using the colour pink for potential faces that did not match, and blue for those that did.
-It can be seen that the largest portion of the faces were captured in a close up situation while the players were on court.\\label{fig:Mosaic}"}
+```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}"}
 
@@
 
-ggplot(data=ALLmetaIMGnamedFaces) + 
+MosaicSit<- ggplot(data=ALLmetaIMGnamedFaces) + 
   geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
@@
   labs(caption="") + coord_flip() +
-  ylab("Proportion of faces") + xlab("Situation the face was captured during")
+  ylab("Proportion of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")
 ```
 
-```{r DDbgshot, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes.
-We are able to see that the background being the Logo Wall and the angle of Player Shoulder Height is common to the highest amount of faces.
-There are also no images that were taken at an upward angle with the background of the court.
-\\label{fig:DDbgshot}"}
+The mosaic in \@ref(fig:ICFigs), Plot b shows the number of Faces captured during each possible situation.
+It contrasts how many of the images captured in situations either did or did not match the faces annotated manually using the colour pink for potential faces that did not match, and blue for those that did.
+It can be seen that the largest portion of the faces were captured in a close up situation while the players were on court.
 
-ggplot(data=ALLmetaIMGnamedFaces) +
+```{r sbbgshot, fig.cap = "\\label{fig:sbbgshot}"}
+
+sbbgshot <- ggplot(data=ALLmetaIMGnamedFaces) +
    geom_bar(aes(x=shotangle, fill = bg), 
@@
   labs(caption="") +
-  ylab("Amount of faces") + xlab("Angle the face was captured from")
+  ylab("Amount of faces") + xlab("Angle the face was captured from") + theme(legend.position = "none")
 
@@
 
-```{r DDbgsit, fig.cap = "This stacked bar chart allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
-As seen previously, the logo wall is the most common background, but it is never the background to an image of the crowd.
-The court is the background of an image only when players are captured, this occurs during close ups and while the court is in play.\\label{fig:DDbgsit}"}
+This stacked bar chart, Figure \@ref(fig:ICFigs) Plot c, allows consideration of the interaction between two image attributes.
+We are able to see that the background being the Logo Wall and the angle of Player Shoulder Height is common to the highest amount of faces.
+There are also no images that were taken at an upward angle with the background of the court.
 
-ggplot(data=ALLmetaIMGnamedFaces) +
+```{r sbbgsit, fig.cap = "\\label{fig:sbbgsit}"}
+
+sbbgsit <- ggplot(data=ALLmetaIMGnamedFaces) +
    geom_bar(aes(x=situation, fill = bg), 
@@
   labs(caption="") +
-  ylab("Amount of faces") + xlab("Situation the face was captured during")
+  ylab("Amount of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")
 ```
 
+This stacked bar chart, Figure \@ref(fig:ICFigs) Plot d, allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
+As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd.
+The court is the background of an image only when players are captured, this occurs during close ups and while the court is in play.
+
+```{r ICFigs, out.width = 0.8, fig.cap = "\\label{fig:ICFigs}"}
+
+grid.arrange(MosaicShotangle, MosaicSit, sbbgshot, sbbgsit,
+             nrow=2, ncol=2)
+```
 ## Accessories

### 2017-09-01 Report06-12.Rmd
Change name of data set

@@
 library(ggplot2)
-library(imager)
-library(devtools)
 library(knitcitations)
@@
 #csv files:
-ALLmetaIMGnamed<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry")))) %>% 
+amin<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry")))) %>% 
   filter(!duplicates)
@@
 
-ALLmetaIMGnamedFaces <- ALLmetaIMGnamed%>%
+aminFaces <- amin %>%
   filter(!is.na(type)) %>% 
@@
     # Find associated Face Box information for specific image
-    faceData <- ALLmetaIMGnamedFaces %>% filter(file == i)
+    faceData <- aminFaces %>% filter(file == i)
 
@@
 
-ALLmetaIMGPlayers <- ALLmetaIMGnamed %>% filter(detect=="Player")
+ALLmetaIMGPlayers <- amin %>% filter(detect=="Player")
 
@@
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
-overlayGgplot(imagesList0, ALLmetaIMGnamedFaces, matchBox = FALSE)
+overlayGgplot(imagesList0, aminFaces, matchBox = FALSE)
 ```
@@
 # Methodology
-An annotation tool was constructed to create a base for comparative analysis, we refer to this as Manual Classifications.
-These manual Classifications involved describing the features of the Scenes.
+
+A 'face' is considered to be any area designated manually or by an API as a location that encloses a human face. These may or may not be actual faces.
+
+## Manual Annotations
+
+An annotation tool was constructed to allow image annotations that would capture the location of areas selected manually. We refer to the faces in these areas as Manual Face Classifications.
+This tool also allowed selections of attributes of each face, and attributes describing the features of the Scenes.
 
@@
 The largest variability is when no faces are found.\\label{tab:timeTable}"}
-times <- ALLmetaIMGnamed %>%  
+
+times <- amin %>%  
   filter(type!="Manual") %>% 
@@
   group_by(file, type) %>% 
-  mutate(n=n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))
+  mutate(n=dplyr::n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))
 
@@
 
-Using the data set^[ALLmetaIMGnamed] of the combined API and manual results, we were able to compare the performance of the software.
+Using the data set of the combined API and manual results, we were able to compare the performance of the software.
 Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(fig:FaceData).
@@
 
-GlmModelCreation <- function(model, data = ALLmetaIMGnamedFaces) {
+GlmModelCreation <- function(model, data = aminFaces) {
   glmFits <- data %>% 
@@
 
-ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + 
+ggplot(amin, aes(x = type, fill=type)) + 
   geom_bar(position="dodge") +
@@
 
-Figure \@ref(fig:FaceData), the bar chart of thefaces shows Google produces the most detections.
-Having a high volume of detected faces returned is valuable for the future use of applying facial recognition during sports.
-Table \@ref(tab:TypeMatchesManual) details the amounts of faces that were found by each API that matched or did not match a face found manually.
-There are slightly more faces found by APIs that do match the faces found manually, 56.34%, than faces that do not match, 43.66%.
-This was unexpected as it was presumed that majority of the faces annotated manually would be found.
-
-The largest group of images were those annotated by manual annotations and found by the Google API, these faces consisted of 26.46% of the total sample.
-
-Figure \@ref(fig:FaceUpset) helps to understand faces that were found by a combination of APIs, and the manual annotations.
-The black bubbles  the bars show the API combination that detected all the faces counted in the bar above.
-
-```{r FaceUpSet, fig.cap = "\\label{fig:FaceUpset} Faces Per API Combination.
-The Bar Chart shows the faces that were recognised by multiple API or found manually.
-The largest group, with 809 faces, is faces only found by Manual annotations.
-The following group were the 716 faces recognized both Manually and by the Google API.
-These combinations may give some indication as to the circumstances when some APIs perform better than others."}
-createUpSet(ALLmetaIMGnamedFaces)
-```
+Figure \@ref(fig:FaceData), the bar chart of faces per API shows Google produces the most detections.
+Having a high volume of detected faces returned is valuable for the future use where faces of the player must be captured over time during sports matches.
 
@@
 
-The faces found by each API are compared to those found manually.
-The upper left box of all tables shows that there was no tagging system for areas in the image not designated to be a face by either manual annotations or API detections.
+The individual faces, the specified area of the image, found by each API are compared to those found manually and by the other APIs.
 
 ```{r table}
-FacesAPI <- ALLmetaIMGnamedFaces %>% 
+FacesAPI <- aminFaces %>% 
   filter(!duplicates) %>%
@@
 #dev tools version has scale_y_productlist but cannot use it yet
-#ALLmetaIMGnamedFaces$shotangle 
-ALLmetaIMGnamedFaces$shotangle <- factor(ALLmetaIMGnamedFaces$shotangle, levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))
+#aminFaces$shotangle 
+aminFaces$shotangle <- factor(aminFaces$shotangle, levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))
 
-MosaicShotangle<- ggplot(data=ALLmetaIMGnamedFaces) + 
+MosaicShotangle<- ggplot(data=aminFaces) + 
   geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
@@
   guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
-  labs(caption="") +
-  ylab("Proportion of faces") + xlab("Angle the face was captured from ") + theme(legend.position = "none")
+  labs(caption="") + coord_flip() +
+  ylab("Proportion of faces") + xlab("Angle the face was captured from ") + theme(legend.position = "none") +
+  ggtitle("Plot a. Proportion of faces captured at each angle")
 ```
@@
 ```{r ShotangleCompare, eval=FALSE, fig.cap=".\\label{fig:ShotangleCompare}"}
-# CompShot <- ALLmetaIMGnamedFaces %>% 
+# CompShot <- aminFaces %>% 
 #   filter(shotangle=="Player Shoulder Height", 
@@
 
-ALLmetaIMGnamedFaces$situation <- factor(ALLmetaIMGnamedFaces$situation, levels = c("Court close−up not player",
+aminFaces$situation <- factor(aminFaces$situation, levels = c("Court close−up not player",
           "Court in play",
@@
 
-MosaicSit<- ggplot(data=ALLmetaIMGnamedFaces) + 
+MosaicSit<- ggplot(data=aminFaces) + 
   geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
@@
   labs(caption="") + coord_flip() +
-  ylab("Proportion of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")
+  ylab("Proportion of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")  +
+  ggtitle("Plot b. Proportion of faces captured in each situation")
 ```
@@
 
-sbbgshot <- ggplot(data=ALLmetaIMGnamedFaces) +
+sbbgshot <- ggplot(data=aminFaces) +
    geom_bar(aes(x=shotangle, fill = bg), 
@@
   labs(caption="") +
-  ylab("Amount of faces") + xlab("Angle the face was captured from") + theme(legend.position = "none")
+  ylab("Amount of faces") + xlab("Angle the face was captured from") + theme(legend.position = "none") +
+  ggtitle("Plot c. Proportion of faces captured at each angle \nwith various backgrounds")
 
@@
 
-sbbgsit <- ggplot(data=ALLmetaIMGnamedFaces) +
+sbbgsit <- ggplot(data=aminFaces) +
    geom_bar(aes(x=situation, fill = bg), 
@@
   labs(caption="") +
-  ylab("Amount of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")
+  ylab("Amount of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none") +
+  ggtitle("Plot d. Proportion of faces captured in each situation \nwith various backgrounds")
 ```
@@
 
-```{r ICFigs, out.width = 0.8, fig.cap = "\\label{fig:ICFigs}"}
+```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "These plots indicate the proportion or amount of faces with certain attributes, or attribute combinations.\\label{fig:ICFigs}"}
 
@@
 ```
+
 ## Accessories
@@
 
-ALLmetaIMGnamedFaces %>%
+aminFaces %>%
   filter(type=="Manual") -> ManFaces

### 2017-09-01 Report06-12.Rmd
New regression model table

@@
 }
-
 ```
 
-```{r CheckModels}
-
-mods<-GlmModelCreation(model = hit ~ 0 + 
+```{r ModelEstimates, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
+GlmModelEstimates(model = hit ~ 0 + 
               shotangle + 
@@
               glasses + 
-              visorhat, 
-              data=ALLmetaIMGnamedFaces)
+              visorhat) -> ModelEstimates
+#Create estimates columns
+ModelEstimates %>% mutate(Estimate = round(Estimate,2)) %>%
+select(variable, type, Estimate) %>%
+  spread(key=type, value=Estimate) %>%
+  select(variable, A.e=Animetrics, G.e=Google, M.e=Microsoft, S.e=Skybiometry)-> ModelEstimatesTypes
 
-#mods$Animetrics %>% drop1(., test="Chisq")
-#mods$Google %>% drop1(., test="Chisq")
-#interaction significant
-#mods$Microsoft %>% drop1(., test="Chisq")
-#mods$Skybiometry %>% drop1(., test="Chisq")
+#Create significance columns
+ModelEstimates %>% mutate(sig = ifelse(`Pr(>|z|)` <= 0, "***", 
+                            ifelse(`Pr(>|z|)` <= 0.001, "** ",
+                            ifelse(`Pr(>|z|)` <= 0.010, "*  ",
+                            ifelse(`Pr(>|z|)` <= 0.050, ".  ", 
+                                                        "   ")))))  %>%
+select(variable, type, sig) %>% 
+  spread(key=type, value=sig) %>% 
+  select(variable, A.s=Animetrics, G.s=Google, M.s=Microsoft, S.s=Skybiometry) -> ModelEstimatesSign
 
-# mods$Animetrics %>% 
-#   summary %>%
-#   .$coefficients %>%
-#   as.data.frame() %>% select(Estimate, `Pr(>|z|)`) -> a
+ModelEstimatesTable <- as.data.frame(cbind(ModelEstimatesTypes, ModelEstimatesSign[,2:5])) %>% 
+  unite(Animetrics, A.e, A.s, sep="") %>% 
+  unite(Google, G.e, G.s, sep="") %>% 
+  unite(Microsoft, M.e, M.s, sep="") %>% 
+  unite(Skybiometry, S.e, S.s, sep="")
 
+knitr::kable(ModelEstimatesTable, align=c("l", "r", "r", "r", "r"),
+             booktabs = TRUE, longtable=TRUE, caption="", format = "latex")
 ```
 
-The model selection technique was undertaking a Chi-Square test comparing the model deviance with all variables to the model deviance when each particular variable was excluded.
-If there was a low Pr(>Chi) value associated with a variable, that would show the variable was significant in predicting whether the faces annotated manually would be detected by the API.
+The variables were kept if they were significant.
 
 ```{r Regression, fig.width=7.5, fig.cap = "The figure depicts the change in the probability of a face being detected by the APIs given a certain attribute level associated with the face.
-Wearing either glasses, or headwear, a visor or a hat, significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}"}
+Wearing either glasses, or headwear, a visor or a hat, significantly decreased the likelihood of a manually annotated face being detected by the APIs.\\label{fig:Regression}", eval=FALSE}
 
-ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + situation + lighting + glasses + visorhat)
+#unnecessary as table is included
+#ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + situation + lighting + glasses + visorhat)
 
@@
 ```{r GoogleRegression, fig.cap = "Google Regression\\label{fig:GoogleRegression}"}
-ALLmetaIMGnamedFaces %>% filter(type=="Manual" | type=="Google") %>%
+aminFaces %>% filter(type=="Manual" | type=="Google") %>%
   mutate(isplayer = ifelse(detect=="Player", 1, 0)) -> players

### 2017-09-01 Report06-12.Rmd
Latex table

@@
 
-\begin{table}[]
+\begin{table}[h]
+\parbox{.5\linewidth}{
 \centering
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|l|l|}
+\begin{tabular}{ccc}
 \hline  
-434 & 1861 \\ \hline
-527 & 787 \\ \hline
-\end{tabular}%
+Manual & Face & No Face\\ [0.5ex] 
+%heading
+\hline 
+Face & 434 & 1861 \\
+NoFace &527 & 787 \\ \hline
+\end{tabular}
+\caption{Animetrics}
 }
-\caption{My caption}
-\label{my-label}
+\hfill
+\parbox{.5\linewidth}{
+\centering
+\begin{tabular}{ccc}
+\hline  
+Manual & Face & No Face\\ [0.5ex] 
+%heading
+\hline
+Face & 1319 & 976 \\
+NoFace &638 & 676 \\ \hline
+\end{tabular}
+\caption{Google}
+}
 \end{table}
 
-```{r tableAMt, reaults='asis', fig.width=1}
-knitr::kable(AM, booktabs = TRUE, longtable=F, format="latex")
+\begin{table}[h]
+\parbox{.5\linewidth}{
+\centering
+\begin{tabular}{ccc}
+\hline
+Manual & Face & No Face\\ [0.5ex] 
+%heading
+\hline
+Face & 565 & 1730 \\
+NoFace &505 & 809 \\ \hline
+\end{tabular}
+\caption{Microsoft}
+}
+\hfill
+\parbox{.5\linewidth}{
+\centering
+\begin{tabular}{ccc}
+\hline  
+Manual & Face & No Face\\ [0.5ex] 
+%heading
+\hline 
+Face & 493 & 1802 \\
+NoFace &512 & 802 \\ \hline
+\end{tabular}
+\caption{Skybiometry}
+}
+\end{table}
+
+Each table above considers the individual faces found in the set.
+The upper left quadrany of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
+Table 4, the comparison of Skybiometry and Manually annotated faces gives the lowest amount in this regard. Table 5, Google, found the largest amount of faces that matched those manually annotated.
+
+Visual inspection showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table 5, that were found by Google but not found manually were actually faces, however they were not all of players.
+Some of these crowd members were beyond what would be expected of an emotion recognition application for detecting faces of tennis players during a match.
+These were deemed unlikely to be necessary when attempting to find faces of players during tennis matches, and neglected during manual annotation.
+
+Comparatively, visual inspection of the `r amin %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were actually very unusual results.
+
+```{r FaceUpSet, fig.cap = "\\label{fig:FaceUpset} Faces Per API Combination.
+The Bar Chart shows the faces that were recognised by multiple API or found manually.
+The largest group, with 809 faces, is faces only found by Manual annotations.
+The following group were the 716 faces recognized both Manually and by the Google API.
+These combinations may give some indication as to the circumstances when some APIs perform better than others."}
+createUpSet(aminFaces)
 ```
 
-```{r tableGMt, reaults='asis', fig.width=1}
-knitr::kable(GM, booktabs = TRUE, longtable=F, format="latex")
-```
-
-```{r tableMMt, reaults='asis'}
-knitr::kable(MM, booktabs = TRUE, longtable=F, format="latex")
-```
-
-```{r tableSMt, reaults='asis'}
-knitr::kable(SM, booktabs = TRUE, longtable=F, format="latex")
-```
-
-Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:TypeMatchesManual), that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd members were beyond what would be expected of an emotion recognition application for tennis players.
-These were deemed unlikely to be necessary when attempting to find faces of players during tennis matches, and neglected during manual annotation.
-
-Table \@ref(tab:TypeMatchesManual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces.
-Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were actually very unusual results.
+Figure \@ref(fig:FaceUpset) helps to understand faces that were found by a combination of APIs, and the manual annotations.
+The black bubbles  the bars show the API combination that detected all the faces counted in the bar above.
 
 ## False Discoveries
- are some examples of when faces were only found by one of the APIs, and how the APIs produced unusual false discoveries.
+Examples are included of faces only found by one of the APIs, as other than Google, the APIs produced several unusual false discoveries.
 These highlight the potential differences in the detection methods used by each of the APIs.
@@
 \\label{fig:UnusualImages}" }
-i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE)
-i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE)
-i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE)
-i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE)
+i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure a.")
+i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure b.")
+i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure c.")
+i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure d.")
 
@@
 ```
+
+Figure \@ref(fig:UnusualImages) depicts four images that contained unusual results of faces.
+Figure a highlights a very large area, most interesting about this is the face of the ball boy captured within this area.
+Figure b also shows unusual faces, the KIA logo was returned by Animetrics many times as a face.
+This discredits the ability of the API to distinguish actual faces from tricks of lights and colours in the complex setting of colourful tennis matches.
+
+Examples of tricks of colours are shown in Figure c, where logos on the shirts were eturned as faces.
 
@@
 ```{r Image-Characteristics-Table, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
-ImageCharacteristics <- ALLmetaIMGnamed %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
+ImageCharacteristics <- amin %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
 ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
@@
 
-We then considered that there would be an uneven amount of faces with certain image attributes. This is considered in the mosaics  in Figure \@ref(fig:Mosaic).
+We then considered that there would be an uneven amount of faces with certain image attributes. This is considered in the mosaics in Figure \@ref(fig:MosaicShotangle) and Figure \@ref(fig:MosaicSit).
 

### 2017-09-01 Report06-12.Rmd
acknowledgements progress

@@
 
-Google: @Google
+Google: @Google Refers to the Google Cloud Vision API
 
@@
 
-Skybiometry: @Skybiometry
+Skybiometry: @Skybiometry References the spin off detection and recognition software of Neurotechnology.
 
@@
 
-ManualClassifiedFaces.csv resulted from the use of the Manual Classification Program, it has information about each face identified manually.
+ManualClassifiedFaces.csv resulted from the use of the Manual Annotation Application, it contains information about each face identified manually.
 ManualClassifiedScenes.csv also resulted from the use of the app, it contains information about each image.
 
+Each script that was automated for POST requests created a classified faces csv.
+
 ## Packages
-The R package ggplot2 [@ggplot2] was used to make the plots.
+The R packages were used to create the following:
+
+* bookdown [@bookdown] and knitr [@knitr] created the pdf output
+* ggplot2 [@ggplot2] was used to make the plots 
+* pander [@pander] printed tables
+* knitcitations [@knitcitations] and RefManager [@RefManager] allowed for references to be integrated
+
+bookdown
+knitr
+RefManageR
+readr
+grid
+tidyverse
+kfigr
+UpSetR
+descr
+xtable
+gtable
+ggthemes
+EBImage
+gridExtra
+ggmosaic
 

### 2017-09-05 Report06-12.Rmd
Chunk cleaning

@@
 library(grid)
-library(tidyverse)
 library(kfigr)
@@
 library(ggmosaic)
+library(tidyverse)
+library(purrr)
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=FALSE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)
 
@@
 }
+
 ggplotProportion <- function(dataset, factorVar){
@@
 ```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
-knitr::kable(FaceAttributes, format = "latex", longtable=TRUE, booktabs = TRUE, caption = "This table lists the possible face descriptions that were appropriate for each individual face.
+knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "This table lists the possible face descriptions that were appropriate for each individual face.
 The most appropriate descrition for each face was built by selecting one option from each list describing a particular attribute of the face that was selected.
@@
 
-```{r timeTable, results='asis', fig.cap="System time taken by the four APIs to finish searching individual images, plotted against number of faces discovered.
-Skybiometry is the fastest, and Microsoft is the slowest.
-The largest variability is when no faces are found.\\label{tab:timeTable}"}
-
+```{r timeData}
 times <- amin %>% 
@@
   group_by(file, type) %>% 
-  mutate(n=dplyr::n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))
+  mutate(n=n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))  
+```
+
+```{r timeTable, results='asis', fig.cap="System time taken by the four APIs to finish searching individual images, plotted against number of faces discovered.
+Skybiometry is the fastest, and Microsoft is the slowest.
+The largest variability is when no faces are found.\\label{tab:timeTable}"}
 
@@
 
-```{r RegressionFunctions}
+```{r RegressionFunctions, cache=FALSE}
 # Prepare data
-library(purrr)
-library(tidyverse)
-library(gridExtra)
-library(dplyr)
-library(ggplot2)
-
 hitmiss <- function(x){
@@
     dplyr::rename(variable = rowname)
-}
-
-GlmModelEstimates <- function(model, data = GlmModelCreation(model)){
-  glmSummary <- data %>% 
-    map(~ ConvertModel2Table(.))
-
-  glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary))) 
-  return(glmPlot)
 }
@@
 
-drop1(mod1, test="Chisq")
-
+#drop1(mod1, test="Chisq")
+#summary(mod1)
 # currently same model as earlier, give two?
@@
 ```
+
 When forcing no intercept, all variables are significant at the 0 level, and obscured is only significant at the 0.001 level.
@@
 Each table above considers the individual faces found in the set.
-The upper left quadrany of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
+The upper left quadrant of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
 Table 4, the comparison of Skybiometry and Manually annotated faces gives the lowest amount in this regard. Table 5, Google, found the largest amount of faces that matched those manually annotated.
@@
 \\label{fig:UnusualImages}" }
-i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure a.")
-i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure b.")
-i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure c.")
-i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Figure d.")
+i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image a.")
+i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image b.")
+i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image c.")
+i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image d.")
 
@@
 ```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}"}
-
 aminFaces$situation <- factor(aminFaces$situation, levels = c("Court close−up not player",

### 2017-09-05 Report06-12.Rmd
Plot changes

@@
 ```{r MosaicShotangle, fig.cap = "\\label{fig:Mosaic}"}
-library(ggmosaic)
-#dev tools version has scale_y_productlist but cannot use it yet
-#aminFaces$shotangle 
-aminFaces$shotangle <- factor(aminFaces$shotangle, levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))
+aminFaces$shotangle <- factor(aminFaces$shotangle, 
+                              levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))
 
-MosaicShotangle<- ggplot(data=aminFaces) + 
+MosaicShotangle <- ggplot(data=aminFaces) + 
   geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
@@
   guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
-  labs(caption="") + coord_flip() +
+  labs(caption="") + 
+  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
+                            "Upward Angle"="Upward \nAngle",
+                            "Player Shoulder Height" =
+                            "Player \nShoulder \nHeight")) + coord_flip() +
   ylab("Proportion of faces") + xlab("Angle the face was captured from ") + theme(legend.position = "none") +
-  ggtitle("Plot a. Proportion of faces captured at each angle")
+  ggtitle("Plot a. Proportion of faces captured \nat each angle") 
 ```
@@
   guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
-  labs(caption="") + coord_flip() +
+  labs(caption="") + 
+  scale_x_productlist(labels=c("Court close−up not player"="Court \nclose−up \nnot player",
+          "Court in play"="Court \nin play",
+          "Off court close up of player"="Off court \nclose up \nof player",
+          "Crowd"="Crowd",
+          "Court player close−up"="Court \nplayer \nclose−up")) +
+  coord_flip() +
   ylab("Proportion of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")  +
-  ggtitle("Plot b. Proportion of faces captured in each situation")
+  ggtitle("Plot b. Proportion of faces captured \nin each situation")
 ```
@@
             na.rm=TRUE) + 
+  scale_x_discrete(labels=c("Birds Eye"="Birds \nEye",
+                            "Upward Angle"="Upward \nAngle",
+                            "Player Shoulder Height" =
+                            "Player \nShoulder \nHeight"))+
   coord_flip() +
@@
   ylab("Amount of faces") + xlab("Angle the face was captured from") + theme(legend.position = "none") +
-  ggtitle("Plot c. Proportion of faces captured at each angle \nwith various backgrounds")
+  ggtitle("Plot c. Proportion of faces captured\nat with each background given the angle")
 
@@
             na.rm=TRUE) +
+  scale_x_discrete(labels=c("Court close−up not player"="Court \nclose−up \nnot player",
+          "Court in play"="Court \nin play",
+          "Off court close up of player"="Off court \nclose up \nof player",
+          "Crowd"="Crowd",
+          "Court player close−up"="Court \nplayer \nclose−up")) +
   coord_flip() +
@@
   ylab("Amount of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none") +
-  ggtitle("Plot d. Proportion of faces captured in each situation \nwith various backgrounds")
+  ggtitle("Plot d. Proportion of faces captured\n with each background given the situation")
 ```
@@
 
-```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "These plots indicate the proportion or amount of faces with certain attributes, or attribute combinations.\\label{fig:ICFigs}"}
+```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually.
+The stacked bar charts show the amount of faces captured at certain angles, or situation, .\\label{fig:ICFigs}"}
 
-grid.arrange(MosaicShotangle, MosaicSit, sbbgshot, sbbgsit,
+plots <- arrangeGrob(MosaicShotangle, MosaicSit, sbbgshot, sbbgsit,
              nrow=2, ncol=2)
+
+g <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
+legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
+lheight <- sum(legend$height)
+
+grid.arrange(plots, legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight))
 ```
@@
 
-## Miscellaneous
+```{r glasses, fig.cap = "This cross table compares the amounts and percentages of faces captured and whether the person was wearing glasses.
+The first row is the faces that were tagged as not wearing glasses, the second row is faces that were.
+For the API to not have been affected by the prescence of glasses, the proportion should be similar to that found manually.
+Animetrics had the highest proportio difference, 93.31% of the faces it found did not have glasses.
+Google is the closest proportion, 88.62% of the faces it found were wearing glasses.\\label{tab:glasses}"}
 
-#### Challenges
-It is understandable that there would be many more faces to recognize in these shots than in shots where there is only a player, and therefore many more faces recognized.
-This provides many faces to sort through to find emotions of a player.
+aminFaces %>%
+  #filter(type=="Manual" | type=="Google") %>%
+  droplevels(.) %>%
+  CrossTable(data=., table(.$glasses, .$type), 
+               prop.chisq = FALSE, 
+               digits=2,
+               expected = FALSE,
+           prop.r = FALSE, prop.c = TRUE, prop.t = FALSE,
+           drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
+           dnn = c("Glasses","Headwear")) -> mgct
 
-We faced the challenge of accessing usable images of players, and specifically their faces.
-- Availability of software
-- Using the software
-- Time constraints
-
-Method, automated the process to reduce data cleaning and help group characteristics
-
-Pricing
-
-Employ the Google Vision API, which would allow the use of still images, or video (TEST VIDEO) files, reducing the need for stills.
-This product - cost in relation
-Ease of access - API calling
+pander(mgct, caption = "")
+```
 

### 2017-09-07 Report06-12.Rmd
Abstract draft

@@
 
+#Abstract
+
+This report aims to analyse the application of facial detection APIs to broadcasted video of Australian Open tennis matches to find a suitable API for face detection of players throughout a match.
+Four APIs are contrasted based on the amount of faces returned, and whether these faces matched those found manually.
+Considerations of whether using a broadcast video of a sport is approporiate is based on the characteristics of the images in the sample.
+The characteristics of the scenes captured and the features associated with individual faces casts light on what would be most appropriate for accurate and high volume facial detection to occur.
+Situations where certain APIs are less capable are highlighted, should applications require reliable results in these situations the shortcomings in time taken and performance under less than optimal conditions would present certain APIs as inapplicable.
+
 #Introduction
@@
 By statistically analyzing the faces and expressions of players during a match there is a hope that insight may be gained into the effects of the mental state on the outcome of a match.
-Facial expressions during competition provide the most direct insight into a player's thoughts.
+Facial expressions during competition may provide an insight into a player's thoughts.
 The aim of this project is to begin to develop methods to collect accurate information about the facial expressions of elite tennis athletes during match play.
@@
 While it is impossible to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through results produced by a recognition software.
-As opposed to the approach of previous studies that have used Player's recollections after a game to determine their emotions.
+This approach opposes the previous studies that have used player's recollections after a game to determine their emotions.
 
-Making use of the recognition software's currently available presents a challenge as high performance sports are not the intended uses of such software's.
-Their capabilities are often limited to their intended security and surveillance uses.
+Making use of the recognition software's currently available presents a challenge as high performance sports are not the intended use.
+Their capabilities are often limited to their intended security and surveillance purposes.
 @Boston addresses the 'lack of robustness of current tools in unstructured environments' that this paper faces and applies to a sports environment.
-This report aims to analyse the application of these software's to a broadcast to find a suitable software and API to use to analyse a previously recorded tennis broadcast file.
 
-##Project Aim
-The aims of the present study were to determine the feasibility of using currently available facial recognition algorithms for extracting facial information from players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
-This limited selection was based on accessible APIs that we believed would produce appropriate and useful facial recognition.
-The performance of the evaluated software was compared against manual classification obtained notation tool developed by the authors.
-In addition to looking at the overall performance, we also evaluated image factors that influences the performance of each service.
+The aims of the present study were to determine the feasibility of using currently available APIs for extracting facial information of players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
+This limited selection was based on accessible APIs believed to produce appropriate and useful facial recognition.
+The performance of the evaluated software was compared against manual classifications obtained by an annotation tool developed by the authors.
+In addition to looking at the overall performance, image factors that influences the performance of each service were also investigated.
 
@@
 
-```{r ModelEstimates, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
-GlmModelEstimates(model = hit ~ 0 + 
+```{r ModelEstimates, fig.cap ="\\label{tab:ModelEstimates}"}
+
+TypeModel <- hit ~ 0 + 
               shotangle + 
@@
               glasses + 
-              visorhat) -> ModelEstimates
+              visorhat
+
+TypeGlms <- GlmModelCreation(model=TypeModel)
+ModelEstimates <- GlmModelEstimates(data=TypeGlms)
+
 #Create estimates columns
@@
 ModelEstimatesTable <- as.data.frame(cbind(ModelEstimatesTypes, ModelEstimatesSign[,2:5])) %>%
-  unite(Animetrics, A.e, A.s, sep="") %>% 
-  unite(Google, G.e, G.s, sep="") %>% 
-  unite(Microsoft, M.e, M.s, sep="") %>% 
-  unite(Skybiometry, S.e, S.s, sep="")
+mutate(A = ifelse(A.s=="   ", "-", A.e),
+       G = ifelse(G.s=="   ", "-", G.e),
+       M = ifelse(M.s=="   ", "-", M.e),
+       S = ifelse(S.s=="   ", "-", S.e))%>% 
+  # unite(Animetrics, A, A.s, sep="") %>% 
+  # unite(Google, G, G.s, sep="") %>% 
+  # unite(Microsoft, M, M.s, sep="") %>% 
+  # unite(Skybiometry, S, S.s, sep="") %>%
+  # select(variable, Animetrics, Google, Microsoft, Skybiometry)
+  mutate(` ` = A.s,
+         `  ` = G.s,
+         `   ` = M.s,
+         `    ` = S.s) %>%
+   select(variable, A, ` `,
+          G, `  `, 
+          M, `   `,
+          S, `    `)
 
-knitr::kable(ModelEstimatesTable, align=c("l", "r", "r", "r", "r"),
-             booktabs = TRUE, longtable=TRUE, caption="", format = "latex")
+knitr::kable(ModelEstimatesTable, align=c("l", 
+                                          "r", "l",
+                                          "r", "l",
+                                          "r", "l",
+                                          "r", "l"),
+             booktabs = TRUE, longtable=TRUE, caption="The table of regression coefficients denotes the significant variables, and levels, for the four API types.
+The dashes represent coefficient that were not significant.
+The symbols to the right of the regression coefficients denote the significance level associated with each coefficient.
+The background variable, and levels of the interaction between shot angle and background were only significant for Google.", format = "latex")
 ```
 
-The variables were kept if they were significant.
+```{r UnlikelyFace, fig.cap = "The face captured manually in this image was not captured by any API.
+The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}"}
+
+predSet <-
+aminFaces %>% select(file,glasses, headangle, lighting, obscured, shotangle, situation, visorhat, bg) %>%
+  filter(headangle=="Profile" &
+         situation=="Court in play" &
+         lighting=="Shaded" &
+         shotangle=="Upward Angle" &
+         bg=="Crowd" &
+         obscured=="Yes" &
+         visorhat=="Yes")
+
+overlayGgplot(predSet$file)
+```
+
+The variables were kept if they were significant for any level of the variable for any type.
+Given the significant coefficients above it can be seen that the largest decrease in probability of a face being found by the APIs was the face profile being captured.
 
@@
 The upper left quadrant of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
-Table 4, the comparison of Skybiometry and Manually annotated faces gives the lowest amount in this regard. Table 5, Google, found the largest amount of faces that matched those manually annotated.
+Table 4, the comparison of Animetrics and Manually annotated faces, gives the lowest amount in this regard. Table 5, Google, found the largest amount of faces that matched those manually annotated.
 
@@
 The black bubbles  the bars show the API combination that detected all the faces counted in the bar above.
+Faces common to all four API and manual annotations were the fourth largest group, it was obvious that relevant faces were captured more commonly by Google and manually.
+The fifth group was the most suprising, this captured a lot of faces that were false discoveries.
 
@@
 
-Examples of tricks of colours are shown in Figure c, where logos on the shirts were eturned as faces.
+Examples of tricks of colours are shown in Figure c, where logos on the shirts were returned as faces.
+These discoveries discredit the use of Animetrics for facial detection applications during sports matches.
 
@@
 
-We then considered that there would be an uneven amount of faces with certain image attributes. This is considered in the mosaics in Figure \@ref(fig:MosaicShotangle) and Figure \@ref(fig:MosaicSit).
-
-The images were all considered manually. The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
+We then considered that there would be an uneven amount of faces with certain image attributes.
+These relationships can be explored in mosaics for the images that were all considered manually.
+The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
 This showed that crowd members faces were often recognized, this is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
-It also allowed for an increase in understanding how attributes of a face impact on the APIs detetion capabilities.
+It also allowed for an increase in understanding how attributes of a face or image impact on the API detection.
 
@@
 The most common faces in our set were those captured at Player Shoulder Height and found manually and by an APIs.
-
-```{r ShotangleCompare, eval=FALSE, fig.cap=".\\label{fig:ShotangleCompare}"}
-# CompShot <- aminFaces %>% 
-#   filter(shotangle=="Player Shoulder Height", 
-#          bg=="Logo wall", 
-#          situation=="Court player close−up",
-#          type=="Google" | type=="Manual",
-#          player2=="AMurray", player2:"AMurray")
-
-#mylist<-as.list(CompShot$file)
-#6,7,8,
-#View(CompShot)
-#lapply(mylist[1:5], overlayGgplot)
-#overlayGgplot(mylist)
-#decide on a comparison, one where images had faces both recognised manually, only one recognised by a software
-```
 
@@
 
-The use of accessories, glasses and headwear, visors or hats, was considered as the Australian Open takes place on both indoor and outdoor courts. 
+The use of accessories like glasses and headwear, visors or hats, was considered as the Australian Open takes place on both indoor and outdoor courts. 
 It was assumed that outdoor courts would lead to the use of these accessories and these accessories may contribute to the performance of a recognition software.
-There are many more faces recognized, by both the Google recognition's and manual annotations, that do not have Glasses.
-This disproportionate sample of faces with Glasses means that we considered it proportionally rather than as a total.
 
-```{r accessories, fig.cap = "\\label{tab:accessories}"}
+```{r accessories, fig.cap = "There are many more faces manually tagged as wearing glasses, and shows there was a more even split between those wearing headwear and those that were not.\\label{tab:accessories}"}
 
@@
 
-```{r glasses, fig.cap = "This cross table compares the amounts and percentages of faces captured and whether the person was wearing glasses.
-The first row is the faces that were tagged as not wearing glasses, the second row is faces that were.
-For the API to not have been affected by the prescence of glasses, the proportion should be similar to that found manually.
-Animetrics had the highest proportio difference, 93.31% of the faces it found did not have glasses.
-Google is the closest proportion, 88.62% of the faces it found were wearing glasses.\\label{tab:glasses}"}
+```{r glasses, fig.cap = "\\label{tab:glasses}"}
 
@@
 
-pander(mgct, caption = "")
+pander(mgct, caption = "This cross table compares the amounts and percentages of faces captured and whether the person was wearing glasses.
+The first row is the faces that were tagged as not wearing glasses, the second row is faces that were.
+For the API to not have been affected by the prescence of glasses, the proportion should be similar to that found manually.
+Animetrics had the highest proportio difference, 93.31% of the faces it found did not have glasses.
+Google is the closest proportion, 88.62% of the faces it found were wearing glasses.")
 ```
@@
 
+The APIs, the scripts used to access them and the resulting data set are contained in the supplementary materials.
+
 ## APIs
@@
 
-* bookdown [@bookdown] and knitr [@knitr] created the pdf output
-* ggplot2 [@ggplot2] was used to make the plots 
-* pander [@pander] printed tables
-* knitcitations [@knitcitations] and RefManager [@RefManager] allowed for references to be integrated
-
-bookdown
-knitr
-RefManageR
-readr
-grid
-tidyverse
-kfigr
-UpSetR
-descr
-xtable
-gtable
-ggthemes
-EBImage
-gridExtra
-ggmosaic
+* bookdown [@bookdown] 
+* descr [@descr]
+* EBImage [@EBImage]
+* ggthemes [@ggthemes]
+* ggmosaic [@ggmosaic]
+* grid [@grid]
+* gridExtra [@gridExtra]
+* gtable [@gtable]
+* kfigr [@kfigr]
+* knitcitations [@knitcitations]
+* knitr [@knitr] 
+* pander [@pander]
+* readr [@readr]
+* RefManager [@RefManager]
+* tidyverse [@tidyverse]
+* UpSetR [@UpSetR]
+* xtable [@xtable]
 

### 2017-09-11 Report06-12.Rmd
Converted data dense graphics to png with dpi 300

@@
 library(purrr)
-
 knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=FALSE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)
@@
 ```{r Trial-Image, fig.cap = "This image of Bernard Tomic was chosen as a trial image to be presented to each of the software before they were included in the research.
-It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE}
+It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE, dev="png", dpi=300}
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
@@
 Skybiometry is the fastest, and Microsoft is the slowest.
-The largest variability is when no faces are found.\\label{tab:timeTable}"}
+The largest variability is when no faces are found.\\label{tab:timeTable}", dev="png", dpi=300}
 
@@
 ```{r UnlikelyFace, fig.cap = "The face captured manually in this image was not captured by any API.
-The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}"}
+The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}", dev="png", dpi=300}
 
@@
 Animetrics found a fist to the right on the centre that it considered a potential face.
-\\label{fig:UnusualImages}" }
+\\label{fig:UnusualImages}", dev="png", dpi=300}
 i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image a.")

### 2017-09-11 Report06-12.Rmd
Converted plots with images to jpg for further size compression

@@
 ```{r Trial-Image, fig.cap = "This image of Bernard Tomic was chosen as a trial image to be presented to each of the software before they were included in the research.
-It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE, dev="png", dpi=300}
+It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE, dev="jpeg", dpi=300}
 imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
@@
 ```{r UnlikelyFace, fig.cap = "The face captured manually in this image was not captured by any API.
-The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}", dev="png", dpi=300}
+The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}", dev="jpeg", dpi=300}
 
@@
 Animetrics found a fist to the right on the centre that it considered a potential face.
-\\label{fig:UnusualImages}", dev="png", dpi=300}
+\\label{fig:UnusualImages}", dev="jpeg", dpi=300}
 i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image a.")

### 2017-09-12 Report06-12.Rmd
Proportion table

@@
 library(purrr)
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=FALSE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)
 
@@
                prop.chisq = FALSE, 
-               digits=2,
+               digits=max(2, getOption("digits")-2),
                expected = FALSE,
@@
            drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
-           dnn = c("Glasses","Headwear"))
+           dnn = c("Glasses","Type"))
 
@@
 
-```{r glasses, fig.cap = "\\label{tab:glasses}"}
+```{r glasses, fig.cap = "\\label{tab:glasses}", digit=3}
 
 aminFaces %>%
-  #filter(type=="Manual" | type=="Google") %>%
-  droplevels(.) %>%
-  CrossTable(data=., table(.$glasses, .$type), 
-               prop.chisq = FALSE, 
-               digits=2,
-               expected = FALSE,
-           prop.r = FALSE, prop.c = TRUE, prop.t = FALSE,
-           drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
-           dnn = c("Glasses","Headwear")) -> mgct
+  filter(type=="Manual") %>% 
+  select(glasses) %>%
+  table -> ManGlasses
 
-pander(mgct, caption = "This cross table compares the amounts and percentages of faces captured and whether the person was wearing glasses.
-The first row is the faces that were tagged as not wearing glasses, the second row is faces that were.
-For the API to not have been affected by the prescence of glasses, the proportion should be similar to that found manually.
-Animetrics had the highest proportio difference, 93.31% of the faces it found did not have glasses.
-Google is the closest proportion, 88.62% of the faces it found were wearing glasses.")
+aminFaces %>% filter(matchesManual) -> afm
+
+table(afm$glasses, afm$type) %>% as.matrix() -> glassesTab
+
+glassesdf <- rbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
+c("No", 
+  round(glassesTab[1,2]/glassesTab[1,1],2),
+  round(glassesTab[1,3]/glassesTab[1,1],2),
+  round(glassesTab[1,4]/glassesTab[1,1],2),
+  round(glassesTab[1,5]/glassesTab[1,1],2)),
+c("Yes", 
+  round(glassesTab[2,2]/glassesTab[2,1],2),
+  round(glassesTab[2,3]/glassesTab[2,1],2),
+  round(glassesTab[2,4]/glassesTab[2,1],2),
+  round(glassesTab[2,5]/glassesTab[2,1],2)))
+
+pander(glassesdf, caption = "This cross table contrasts the proportion of faces captured and whether the person was wearing glasses.
+The first row is the faces that were manually tagged as not wearing glasses, the second row is faces that were.
+For an API to not have been affected by the prescence of glasses, the proportions for both categorys should be similar.
+Animetrics had the highest proportion difference,  of the faces it found did not have glasses.
+Google is the closest proportion,  of the faces it found were wearing glasses.")
 ```

### 2017-09-12 Report06-12.Rmd
tweaking paper

@@
 
-This report aims to analyse the application of facial detection APIs to broadcasted video of Australian Open tennis matches to find a suitable API for face detection of players throughout a match.
-Four APIs are contrasted based on the amount of faces returned, and whether these faces matched those found manually.
-Considerations of whether using a broadcast video of a sport is approporiate is based on the characteristics of the images in the sample.
-The characteristics of the scenes captured and the features associated with individual faces casts light on what would be most appropriate for accurate and high volume facial detection to occur.
-Situations where certain APIs are less capable are highlighted, should applications require reliable results in these situations the shortcomings in time taken and performance under less than optimal conditions would present certain APIs as inapplicable.
+This paper examines the effectiveness of facial detection APIs on broadcast video stills of Australian Open tennis matches.
+The goal is determine the best API to use for face detection of players throughout a match.
+For training purposes faces were manually tagged in 6406 images, and the APIs were evaluated on their success rate at detecting these faces.
+The manual tagging also created data recording the scene characteristics and features of individual faces such as whether a visor or cap or sunglasses were being worn.
+This enables the performance to be assessed based on conditions.
 
@@
 t1 <- ggplot(times) +  
-  geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) + 
+  geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm") + 
   xlab("Number of faces detected") + ylab("System time (sec)") +  
@@
   ylim(c(0, 0.1)) +  
-  geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) + 
+  #geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) + 
   xlab("Number of faces detected") +  
@@
 ImageCharacteristics<-ImageCharacteristics[1:5,]
-knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="This table outlines the combinations of image attibutes that are most common in the image set.
+knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, format.args=list(width=8), caption="This table outlines the combinations of image attibutes that are most common in the image set.
 The combination of the Logo Wall background and the Player Shoulder Height angle are shared by three of the five image combinations.", format = "latex")
@@
                               levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))
+aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
 
@@
   #geom_text(aes(label="test", x=1, y=0.6)) +
+  scale_fill_brewer(palette="Dark2") +
   guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
@@
                             "Player \nShoulder \nHeight")) + coord_flip() +
-  ylab("Proportion of faces") + xlab("Angle the face was captured from ") + theme(legend.position = "none") +
-  ggtitle("Plot a. Proportion of faces captured \nat each angle") 
+  ylab("Proportion of faces") + xlab("Angle of face capture") + 
+  theme(legend.position = "none") + 
+  ggtitle("(a)") 
 ```
@@
 ```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}"}
-aminFaces$situation <- factor(aminFaces$situation, levels = c("Court close−up not player",
+aminFaces$situation <- factor(aminFaces$situation, levels = c("Court close-up not player",
           "Court in play",
@@
           "Crowd",
-          "Court player close−up"))
+          "Court player close-up"))
+aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
 
-MosaicSit<- ggplot(data=aminFaces) + 
+MosaicSit <- ggplot(data=aminFaces) + 
   geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
+  scale_fill_brewer(palette="Dark2") +
   guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
   labs(caption="") + 
-  scale_x_productlist(labels=c("Court close−up not player"="Court \nclose−up \nnot player",
-          "Court in play"="Court \nin play",
+  scale_x_productlist(labels=c("Court close-up not player"="Court \nclose−up \nnot player",
+          "Court in play"="Court in play",
           "Off court close up of player"="Off court \nclose up \nof player",
           "Crowd"="Crowd",
-          "Court player close−up"="Court \nplayer \nclose−up")) +
+          "Court player close-up"="Court \nplayer \nclose−up")) +
   coord_flip() +
-  ylab("Proportion of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")  +
-  ggtitle("Plot b. Proportion of faces captured \nin each situation")
+  ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none")  +
+  ggtitle("(b)")
 ```
@@
 sbbgshot <- ggplot(data=aminFaces) +
-   geom_bar(aes(x=shotangle, fill = bg), 
-            position = position_stack(reverse = TRUE), 
-            na.rm=TRUE) + 
-  scale_x_discrete(labels=c("Birds Eye"="Birds \nEye",
+   geom_mosaic(aes(x=product(shotangle), fill = bg)) +#, 
+            #position = position_fill(reverse = TRUE), 
+            #na.rm=TRUE) + 
+  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
                             "Upward Angle"="Upward \nAngle",
@@
   labs(caption="") +
-  ylab("Amount of faces") + xlab("Angle the face was captured from") + theme(legend.position = "none") +
-  ggtitle("Plot c. Proportion of faces captured\nat with each background given the angle")
+  ylab("Proportion of faces") + xlab("Angle of face capture") + theme(legend.position = "none") +
+  ggtitle("(c)")
 
@@
 sbbgsit <- ggplot(data=aminFaces) +
-   geom_bar(aes(x=situation, fill = bg), 
-            position = position_stack(reverse = TRUE), 
-            na.rm=TRUE) +
-  scale_x_discrete(labels=c("Court close−up not player"="Court \nclose−up \nnot player",
-          "Court in play"="Court \nin play",
+   geom_mosaic(aes(x=product(situation), fill = bg)) + #, 
+            #position = position_fill(reverse = TRUE), 
+            #na.rm=TRUE) +
+   scale_x_productlist(labels=c("Court close-up not player"="Court \nclose−up \nnot player",
+          "Court in play"="Court in play",
           "Off court close up of player"="Off court \nclose up \nof player",
           "Crowd"="Crowd",
-          "Court player close−up"="Court \nplayer \nclose−up")) +
+          "Court player close-up"="Court \nplayer \nclose−up")) +
   coord_flip() +
@@
   labs(caption="") +
-  ylab("Amount of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none") +
-  ggtitle("Plot d. Proportion of faces captured\n with each background given the situation")
+  ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none") +
+  ggtitle("(d)")
 ```
@@
 ```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually.
-The stacked bar charts show the amount of faces captured at certain angles, or situation, .\\label{fig:ICFigs}"}
+The stacked bar charts show the amount of faces captured at certain angles, or situation.\\label{fig:ICFigs}"}
 
@@
 
-The APIs, the scripts used to access them and the resulting data set are contained in the supplementary materials.
+The authors wish to thank Tennis Australia for access to the data.
+The analysis was conducted using R, and the following packages: bookdown[@bookdown], descr[@descr], EBImage [@EBImage], ggthemes [@ggthemes], ggmosaic [@ggmosaic], grid [@grid], gridExtra [@gridExtra], gtable [@gtable], kfigr [@kfigr], knitcitations [@knitcitations], knitr [@knitr] , pander [@pander], readr [@readr], RefManager [@RefManager], tidyverse [@tidyverse], UpSetR [@UpSetR], xtable [@xtable].
 
-## APIs
-Animetrics: This name used throughout the paper refers to the Animetrics Face Recognition API, FaceR API by @Animetrics.
+# Supplementary material
 
-Google: @Google Refers to the Google Cloud Vision API
+The APIs, the scripts used to access them, and the resulting data set are contained in the supplementary materials, available at [https://github.com/mvparrot/face-recognition](https://github.com/mvparrot/face-recognition).
+The APIs evaluated were:
 
-Microsoft: This has been used to refer to the Microsoft Azure Cognitive Services Face API, published by @Microsoft.
+- Animetrics: This name used throughout the paper refers to the Animetrics Face Recognition API, FaceR API by @Animetrics.
 
-Skybiometry: @Skybiometry References the spin off detection and recognition software of Neurotechnology.
+- Google: @Google Refers to the Google Cloud Vision API
 
-## Data Files
+- Microsoft: This has been used to refer to the Microsoft Azure Cognitive Services Face API, published by @Microsoft.
 
-All data files used are available on the github page.
+- Skybiometry: @Skybiometry References the spin off detection and recognition software of Neurotechnology.
 
-ManualClassifiedFaces.csv resulted from the use of the Manual Annotation Application, it contains information about each face identified manually.
-ManualClassifiedScenes.csv also resulted from the use of the app, it contains information about each image.
+Data files provided are:
 
-Each script that was automated for POST requests created a classified faces csv.
-
-## Packages
-The R packages were used to create the following:
-
-* bookdown [@bookdown] 
-* descr [@descr]
-* EBImage [@EBImage]
-* ggthemes [@ggthemes]
-* ggmosaic [@ggmosaic]
-* grid [@grid]
-* gridExtra [@gridExtra]
-* gtable [@gtable]
-* kfigr [@kfigr]
-* knitcitations [@knitcitations]
-* knitr [@knitr] 
-* pander [@pander]
-* readr [@readr]
-* RefManager [@RefManager]
-* tidyverse [@tidyverse]
-* UpSetR [@UpSetR]
-* xtable [@xtable]
+- ManualClassifiedFaces.csv resulted from the use of the Manual Annotation Application, it contains information about each face identified manually.
+- ManualClassifiedScenes.csv also resulted from the use of the app, it contains information about each image.
 

### 2017-09-18 Report06-12.Rmd
Changed section headings to sentence case

@@
 output: bookdown::pdf_document2
+number_sections: false
+toc: false
 fig_caption: yes
@@
 
-## Manual Annotations
+## Manual annotations
 
@@
 
-##Software Interaction
+##Software interaction
 The software choices allowed for POST requests to be sent via the internet.
@@
 
-##Data Processing
+##Data processing
+
 The data needed for our analysis was spread across six files.
@@
 
-### Modeling Face Detection Probabiity
+### Modeling face detection probabiity
 
@@
 
-Regression analysis showed that the situation variable had significant differences between intercept level of "Court Close-Up Not Player" and the categories of "Court in Play" and "Court Player Close Up".
-This would mean that the probability of all the APIs finding the face that had been found manually was significantly less if the situation depicted was "Court in Play" and "Court Player Close Up" rather than a "Court Close-Up Not Player".
+Regression analysis showed that the situation variable had significant differences between intercept level of "Not player" and the categories of "Match play" and "Court Player Close Up".
+This would mean that the probability of all the APIs finding the face that had been found manually was significantly less if the situation depicted was "Match play" and "Court Player Close Up" rather than a "Not player".
 
 The bar charts of the situations show that the situation is important in influencing the detection of a face.
-When the face is accessorised with them, all APIs have a significantly increased chance of finding the face in comparison to the base rate category of the "Court in Play".
+When the face is accessorised with them, all APIs have a significantly increased chance of finding the face in comparison to the base rate category of the "Match play".
 While the image being a Graphic had a large impact it was not significant, this is likely because of the small number of images with this attribute.
@@
 
-## Amount of Faces
+## Amount of faces
 
@@
 
-## Comparing Faces Found
+## Comparing faces found
 
@@
 
-## False Discoveries
+## False discoveries
 Examples are included of faces only found by one of the APIs, as other than Google, the APIs produced several unusual false discoveries.
@@
 
-## Image Characteristics
+## Image characteristics
 

### 2017-09-18 Report06-12.Rmd
Changed names of factor levels

@@
 
-A 'face' is considered to be any area designated manually or by an API as a location that encloses a human face. These may or may not be actual faces.
+A 'face' is considered to be any area designated manually or by an API as an area that encloses a human face. These may or may not be actual faces.
 
@@
   filter(headangle=="Profile" &
-         situation=="Court in play" &
+         situation=="Match play" &
          lighting=="Shaded" &
-         shotangle=="Upward Angle" &
+         shotangle=="Upward" &
          bg=="Crowd" &
@@
 \\label{fig:UnusualImages}", dev="jpeg", dpi=300}
-i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image a.")
-i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image b.")
-i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image c.")
-i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image d.")
+i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(a)")
+i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(b)")
+i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(c)")
+i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(d)")
 
@@
 aminFaces$shotangle <- factor(aminFaces$shotangle, 
-                              levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))
+                              levels = c("Birds Eye","Upward","Level"))
 aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
@@
   scale_fill_brewer(palette="Dark2") +
-  guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
+  guides(fill = guide_legend(title="API matches manual"))  +
   labs(caption="") + 
   scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
-                            "Upward Angle"="Upward \nAngle",
-                            "Player Shoulder Height" =
-                            "Player \nShoulder \nHeight")) + coord_flip() +
+                            "Upward"="Upward \nAngle",
+                            "Level" =
+                            "Level")) + coord_flip() +
   ylab("Proportion of faces") + xlab("Angle of face capture") + 
@@
 
-The colours in the mosaic in Figure \@ref(fig:ICFigs) Plot a.
-show the amount of faces that matched those found manually given the angle the faces were captured from.
-There is a greater amount of API faces that matched the faces found manually than those that did not match.
-However given the face was captured from a birds eye angle there were less faces that matched those found manually.
-The most common faces in our set were those captured at Player Shoulder Height and found manually and by an APIs.
+The colours in the mosaic (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
+There is a greater proprtion of API faces that matched the faces found manually than those that did not match.
+However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually.
+The most common faces in the set were those captured Level to player's faces, these faces were often recognised by the APIs as well.
 
 ```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}"}
-aminFaces$situation <- factor(aminFaces$situation, levels = c("Court close-up not player",
-          "Court in play",
-          "Off court close up of player",
+aminFaces$situation <- factor(aminFaces$situation, levels = c("Not player",
+          "Match play",
+          "Off court",
           "Crowd",
-          "Court player close-up"))
+          "Close-up"))
 aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
@@
   scale_fill_brewer(palette="Dark2") +
-  guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
+  guides(fill = guide_legend(title="API match manual"))  +
   labs(caption="") + 
-  scale_x_productlist(labels=c("Court close-up not player"="Court \nclose−up \nnot player",
-          "Court in play"="Court in play",
-          "Off court close up of player"="Off court \nclose up \nof player",
+  scale_x_productlist(labels=c("Not player"="Not player",
+          "Match play"="Match play",
+          "Off court"="Off court",
           "Crowd"="Crowd",
-          "Court player close-up"="Court \nplayer \nclose−up")) +
+          "Close-up"="Close-up")) +
   coord_flip() +
@@
 
-The mosaic in \@ref(fig:ICFigs), Plot b shows the number of Faces captured during each possible situation.
-It contrasts how many of the images captured in situations either did or did not match the faces annotated manually using the colour pink for potential faces that did not match, and blue for those that did.
-It can be seen that the largest portion of the faces were captured in a close up situation while the players were on court.
+The mosaic (b) in \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
+It contrasts the proportion of the images captured in each situation that either did or did not match the faces annotated manually.
+It can be seen that the largest portion of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
+This porportion is steady across most situations, from this we learn the situation may not be influencing the APIs rate of detection.
 
@@
   scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
-                            "Upward Angle"="Upward \nAngle",
-                            "Player Shoulder Height" =
-                            "Player \nShoulder \nHeight"))+
+                            "Upward"="Upward",
+                            "Level" =
+                            "Level"))+
   coord_flip() +
@@
             #na.rm=TRUE) +
-   scale_x_productlist(labels=c("Court close-up not player"="Court \nclose−up \nnot player",
-          "Court in play"="Court in play",
-          "Off court close up of player"="Off court \nclose up \nof player",
+   scale_x_productlist(labels=c("Not player"="Not player",
+          "Match play"="Match play",
+          "Off court"="Off court",
           "Crowd"="Crowd",
-          "Court player close-up"="Court \nplayer \nclose−up")) +
+          "Close-up"="Close-up")) +
   coord_flip() +

### 2017-09-18 Report06-12.Rmd
Edited plots and explanations

@@
 This stacked bar chart, Figure \@ref(fig:ICFigs) Plot c, allows consideration of the interaction between two image attributes.
-We are able to see that the background being the Logo Wall and the angle of Player Shoulder Height is common to the highest amount of faces.
+We are able to see that the background being the Logo Wall and the angle of Level is common to the highest amount of faces.
 There are also no images that were taken at an upward angle with the background of the court.
@@
 
-plots <- arrangeGrob(MosaicShotangle, MosaicSit, sbbgshot, sbbgsit,
-             nrow=2, ncol=2)
+g1 <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
+legend1 <- g1[[which(sapply(g1, function(x) x$name) == "guide-box")]]
+lheight1 <- sum(legend1$height)
 
-g <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
-legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
-lheight <- sum(legend$height)
+plots1 <- arrangeGrob(sbbgshot, sbbgsit, ncol=2)
+plots1 <- arrangeGrob(plots1, legend1, nrow=2, heights = unit.c(unit(1, "npc") - lheight1, lheight1))
 
-grid.arrange(plots, legend,
-        ncol = 1,
-        heights = unit.c(unit(1, "npc") - lheight, lheight))
+g2 <- ggplotGrob(MosaicShotangle + theme(legend.position="bottom"))$grobs
+legend2 <- g2[[which(sapply(g2, function(x) x$name) == "guide-box")]]
+lheight2 <- sum(legend2$height)
+
+plots2 <- arrangeGrob(MosaicShotangle, MosaicSit, ncol=2)
+plots2 <- arrangeGrob(plots2, legend2, nrow=2, heights = unit.c(unit(1, "npc") - lheight2, lheight2))
+
+grid.arrange(plots1, plots2, nrow=2)
+
 ```
@@
 
-aminFaces %>%
-  filter(type=="Manual") %>% 
-  select(glasses) %>%
-  table -> ManGlasses
+ManFaces %>% count(glasses) %>%
+  tally() -> ManGlasses
 
-aminFaces %>% filter(matchesManual) -> afm
+aminFaces %>% filter(matchesManual==TRUE) -> afm
 

### 2017-09-19 Report06-12.Rmd
Remove numbers from some sections

@@
 output: bookdown::pdf_document2
-number_sections: false
 toc: false
 fig_caption: yes
+number_sections: false
 fontsize: 11pt
@@
 
-#Abstract
+#Abstract {-}
 
@@
 
-##Software Selection
+##Software selection
+
 The choice of the initial software considered for this research was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.' [@Survey]
@@
 
-##Manual Annotation
 To record the details of attributes for each face and scene a Shiny [@shiny] App was created.
@@
 knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, format.args=list(width=8), caption="This table outlines the combinations of image attibutes that are most common in the image set.
-The combination of the Logo Wall background and the Player Shoulder Height angle are shared by three of the five image combinations.", format = "latex")
+The combination of the Logo Wall background and the Level angle are shared by three of the five image combinations.", format = "latex")
 ```
@@
 
-# Acknowledgements
+# Acknowledgements {-}
 
@@
 
-# Supplementary material
+# Supplementary material{-}
 

### 2017-09-19 R/mergeData.R

@@ -151,12 +151,12 @@ ALLmetaIMG<-read_csv("data/ALLmetaIMG.csv", col_types = cols(type = col_factor(l
 
 #Factor Names 
 ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
-ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
-ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
+ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No person", "Person"))
+ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Match play", "Close up", "Not player", "Crowd", "Off court", "Transition"))
 ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
-ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
+ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Level", "Birds Eye", "Upward"))
 
-ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:2, labels = c("Player", "Other staff on court", "Fan"))
+ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:2, labels = c("Player", "Staff", "Fan"))
 ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
 ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 1:2, labels = c("Shaded", "Partially shaded"))
 ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))

### 2017-09-20 Report06-12.Rmd
lots of formatting tweaks and data file shift

@@
 ---
-title: "Detecting Facial Expressions in Professional Tennis Matches"
+title: "Detecting Facial Expressions in Video Stills from Professional Tennis Matches"
 author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "This table lists the possible image descriptions that are associated with the attributes of each image.
-The most appropriate descrition from each list was selected.
-There are more options for more complex attributes, there were five expected situations the image may depict.")
-```
+knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Image descriptions that are associated with the attributes of each image.")
+```
+
+<!--
+\begin{table}[htp]
+\label{tab:Scene-Attributes-Table}
+\caption{Image descriptions that are associated with the attributes of each image. }
+\centering
+\begin{tabular}{lp{12cm}} \hline
+Attribute & Choices \\\hline
+Graphic & Live Image, 2D Graphic \\
+Background & Crowd, Court, Logo Wall, Not Applicable \\
+Person & Yes, No \\
+Shot Angle & Level, Birds Eye, Upward \\
+Situation & Match play, Close up, Not player, Crowd, Off court, Transition\\\hline
+\end{tabular}
+\end{table}
+-->
 
@@
 ```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
-knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "This table lists the possible face descriptions that were appropriate for each individual face.
-The most appropriate descrition for each face was built by selecting one option from each list describing a particular attribute of the face that was selected.
-Most of these categories selections were made obvious in the image, Obscured and Head Angle were more difficult to choose for some faces.")
+knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Possible face descriptions for each individual face.
+Most of the selections were obvious for each image, with the exception of obscured and head angle.")
 ```
@@
 
-knitr::kable(ModelEstimatesTable, align=c("l", 
+knitr::kable(ModelEstimatesTable, format = "latex", align=c("l", 
                                           "r", "l",
@@
                                           "r", "l"),
-             booktabs = TRUE, longtable=TRUE, caption="The table of regression coefficients denotes the significant variables, and levels, for the four API types.
+             booktabs = TRUE, longtable=FALSE, caption="The table of regression coefficients denotes the significant variables, and levels, for the four API types.
 The dashes represent coefficient that were not significant.
 The symbols to the right of the regression coefficients denote the significance level associated with each coefficient.
-The background variable, and levels of the interaction between shot angle and background were only significant for Google.", format = "latex")
+The background variable, and levels of the interaction between shot angle and background were only significant for Google.")
 ```
@@
 
-## Image characteristics
-
-We then considered the characteristics of the images that the API found Potential Faces in.
-
 ```{r Image-Characteristics-Table, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
@@
 ImageCharacteristics<-ImageCharacteristics[1:5,]
-knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, format.args=list(width=8), caption="This table outlines the combinations of image attibutes that are most common in the image set.
+knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=FALSE, format.args=list(width=8), caption="Combinations of image attibutes that are most common in the image set.
 The combination of the Logo Wall background and the Level angle are shared by three of the five image combinations.", format = "latex")
@@
 
-We then considered that there would be an uneven amount of faces with certain image attributes.
-These relationships can be explored in mosaics for the images that were all considered manually.
-The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
-This showed that crowd members faces were often recognized, this is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
-It also allowed for an increase in understanding how attributes of a face or image impact on the API detection.
-
-```{r MosaicShotangle, fig.cap = "\\label{fig:Mosaic}"}
+```{r MosaicShotangle, fig.cap = "\\label{fig:Mosaic}", eval=FALSE}
 aminFaces$shotangle <- factor(aminFaces$shotangle, 
@@
 
-The colours in the mosaic (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
-There is a greater proprtion of API faces that matched the faces found manually than those that did not match.
-However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually.
-The most common faces in the set were those captured Level to player's faces, these faces were often recognised by the APIs as well.
-
-```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}"}
+```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}", eval=FALSE}
 aminFaces$situation <- factor(aminFaces$situation, levels = c("Not player",
@@
 
-The mosaic (b) in \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
-It contrasts the proportion of the images captured in each situation that either did or did not match the faces annotated manually.
-It can be seen that the largest portion of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
-This porportion is steady across most situations, from this we learn the situation may not be influencing the APIs rate of detection.
-
-```{r sbbgshot, fig.cap = "\\label{fig:sbbgshot}"}
+```{r sbbgshot, fig.cap = "\\label{fig:sbbgshot}", eval=FALSE}
 
@@
 
-This stacked bar chart, Figure \@ref(fig:ICFigs) Plot c, allows consideration of the interaction between two image attributes.
-We are able to see that the background being the Logo Wall and the angle of Level is common to the highest amount of faces.
-There are also no images that were taken at an upward angle with the background of the court.
-
-```{r sbbgsit, fig.cap = "\\label{fig:sbbgsit}"}
+```{r sbbgsit, fig.cap = "\\label{fig:sbbgsit}", eval=FALSE}
 
@@
 
+```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually.
+The stacked bar charts show the amount of faces captured at certain angles, or situation.\\label{fig:ICFigs}"}
+
+aminFaces$shotangle <- factor(aminFaces$shotangle, 
+                              levels = c("Birds Eye","Upward","Level"))
+aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
+
+MosaicShotangle <- ggplot(data=aminFaces) + 
+  geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
+  #geom_text(aes(label="test", x=1, y=0.6)) +
+  scale_fill_brewer(palette="Dark2") +
+  guides(fill = guide_legend(title="API matches manual"))  +
+  labs(caption="") + 
+  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
+                            "Upward"="Upward \nAngle",
+                            "Level" =
+                            "Level")) + coord_flip() +
+  ylab("Proportion of faces") + xlab("Angle of face capture") + 
+  theme(legend.position = "none") + 
+  ggtitle("(a)") 
+aminFaces$situation <- factor(aminFaces$situation, levels = c("Not player",
+          "Match play",
+          "Off court",
+          "Crowd",
+          "Close-up"))
+aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
+
+MosaicSit <- ggplot(data=aminFaces) + 
+  geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
+  scale_fill_brewer(palette="Dark2") +
+  guides(fill = guide_legend(title="API match manual"))  +
+  labs(caption="") + 
+  scale_x_productlist(labels=c("Not player"="Not player",
+          "Match play"="Match play",
+          "Off court"="Off court",
+          "Crowd"="Crowd",
+          "Close-up"="Close-up")) +
+  coord_flip() +
+  ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none")  +
+  ggtitle("(b)")
+
+sbbgshot <- ggplot(data=aminFaces) +
+   geom_mosaic(aes(x=product(shotangle), fill = bg)) +#, 
+            #position = position_fill(reverse = TRUE), 
+            #na.rm=TRUE) + 
+  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
+                            "Upward"="Upward",
+                            "Level" =
+                            "Level"))+
+  coord_flip() +
+  guides(fill = guide_legend(title="Background")) +
+  labs(caption="") +
+  ylab("Proportion of faces") + xlab("Angle of face capture") + theme(legend.position = "none") +
+  ggtitle("(c)")
+
+sbbgsit <- ggplot(data=aminFaces) +
+   geom_mosaic(aes(x=product(situation), fill = bg)) + #, 
+            #position = position_fill(reverse = TRUE), 
+            #na.rm=TRUE) +
+   scale_x_productlist(labels=c("Not player"="Not player",
+          "Match play"="Match play",
+          "Off court"="Off court",
+          "Crowd"="Crowd",
+          "Close-up"="Close-up")) +
+  coord_flip() +
+  guides(fill = guide_legend(title="Background")) +
+  labs(caption="") +
+  ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none") +
+  ggtitle("(d)")
+
+g1 <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
+legend1 <- g1[[which(sapply(g1, function(x) x$name) == "guide-box")]]
+lheight1 <- sum(legend1$height)
+
+plots1 <- arrangeGrob(sbbgshot, sbbgsit, ncol=2)
+plots1 <- arrangeGrob(plots1, legend1, nrow=2, heights = unit.c(unit(1, "npc") - lheight1, lheight1))
+
+g2 <- ggplotGrob(MosaicShotangle + theme(legend.position="bottom"))$grobs
+legend2 <- g2[[which(sapply(g2, function(x) x$name) == "guide-box")]]
+lheight2 <- sum(legend2$height)
+
+plots2 <- arrangeGrob(MosaicShotangle, MosaicSit, ncol=2)
+plots2 <- arrangeGrob(plots2, legend2, nrow=2, heights = unit.c(unit(1, "npc") - lheight2, lheight2))
+
+grid.arrange(plots1, plots2, nrow=2)
+
+```
+
+## Image characteristics
+
+We then considered the characteristics of the images that the API found Potential Faces in.
+
+We then considered that there would be an uneven amount of faces with certain image attributes.
+These relationships can be explored in mosaics for the images that were all considered manually.
+The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
+
+This showed that crowd members faces were often recognized, this is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
+It also allowed for an increase in understanding how attributes of a face or image impact on the API detection.
+
+The colours in the mosaic (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
+There is a greater proprtion of API faces that matched the faces found manually than those that did not match.
+However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually.
+The most common faces in the set were those captured Level to player's faces, these faces were often recognised by the APIs as well.
+
+The mosaic (b) in \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
+It contrasts the proportion of the images captured in each situation that either did or did not match the faces annotated manually.
+It can be seen that the largest portion of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
+This porportion is steady across most situations, from this we learn the situation may not be influencing the APIs rate of detection.
+
+This stacked bar chart, Figure \@ref(fig:ICFigs) Plot c, allows consideration of the interaction between two image attributes.
+We are able to see that the background being the Logo Wall and the angle of Level is common to the highest amount of faces.
+There are also no images that were taken at an upward angle with the background of the court.
+
 This stacked bar chart, Figure \@ref(fig:ICFigs) Plot d, allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
@@
 The court is the background of an image only when players are captured, this occurs during close ups and while the court is in play.
-
-```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually.
-The stacked bar charts show the amount of faces captured at certain angles, or situation.\\label{fig:ICFigs}"}
-
-g1 <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
-legend1 <- g1[[which(sapply(g1, function(x) x$name) == "guide-box")]]
-lheight1 <- sum(legend1$height)
-
-plots1 <- arrangeGrob(sbbgshot, sbbgsit, ncol=2)
-plots1 <- arrangeGrob(plots1, legend1, nrow=2, heights = unit.c(unit(1, "npc") - lheight1, lheight1))
-
-g2 <- ggplotGrob(MosaicShotangle + theme(legend.position="bottom"))$grobs
-legend2 <- g2[[which(sapply(g2, function(x) x$name) == "guide-box")]]
-lheight2 <- sum(legend2$height)
-
-plots2 <- arrangeGrob(MosaicShotangle, MosaicSit, ncol=2)
-plots2 <- arrangeGrob(plots2, legend2, nrow=2, heights = unit.c(unit(1, "npc") - lheight2, lheight2))
-
-grid.arrange(plots1, plots2, nrow=2)
-
-```
 
@@
            drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
-           dnn = c("Glasses","Type"))
-
-pander(ct, caption = "This cross table compares the amount of faces that were captured wearing accessories.")
+           dnn = c("Glasses","Visor/hat"))
+
+pander(ct, caption = "Contingency table comparing the amount of captured faces of players that were wearing accessories.")
 ```
@@
 
-pander(glassesdf, caption = "This cross table contrasts the proportion of faces captured and whether the person was wearing glasses.
-The first row is the faces that were manually tagged as not wearing glasses, the second row is faces that were.
-For an API to not have been affected by the prescence of glasses, the proportions for both categorys should be similar.
-Animetrics had the highest proportion difference,  of the faces it found did not have glasses.
-Google is the closest proportion,  of the faces it found were wearing glasses.")
+pander(glassesdf, caption = "Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces.
+API's unaffected glasses will have similar proportions for both categories.
+Animetrics had the biggest proportion difference, and thus, most affected.
+Google is the least affected.")
 ```

### 2017-09-20 Internship/R/CreateFacesSet.R
unnecessary folder

@@ -1,31 +1,0 @@
-
-library(magick)
-ALLmetaIMGnamed<-read.csv("ALLmetaIMGnamed.csv")
-
-
-ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
-  filter(matchesManual) %>% 
-  dplyr::select(-ID, -facecounter)%>%
-  mutate(fileID = as.numeric(factor(file))) %>%
-  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
-  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))
-
-
-GoogleFaces<-ALLmetaIMGnamedFaces %>% subset(type=="Google")
-
-#create data set of just faces
-data<-GoogleFaces
-
-
-#CreateFaceSet
-for(n in 1:NROW(GoogleFaces)){
-SubImage <- image_read(paste0("images/", data$file[n]))
-
-cropValue<-paste0(data$maxX[n]-data$minX[n]+20, "x",data$maxY[n]-data$minY[n]+20,"+", data$minX[n]-10,"+", data$minY[n]-10, collapse = ", ")
-Cropped<-image_crop(SubImage, cropValue)
-
-image_write(Cropped, path=(paste0("Faces/","face-", data$FaceID[n], ".png", collapse = ", ")))
-}
-
-write.csv(GoogleFaces, "GoogleFaces.csv", row.names = FALSE)
-

### 2017-09-20 Internship/R/EmotionsAnalysis.R

@@ -1,213 +1,0 @@
-##Emotions Analysis
-
-library(tidyverse)
-library(readr)
-library(GGally)
-
-#EmoM <-read_csv("data/EmotionsMerged.csv")
-ME <- read_csv("data/MicrosoftEmotions.csv")
-SB<-read_csv("data/SkybiometryEmotions.csv")
-GE<- read_csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
-GoogleFaces <- read_csv("data/GoogleFaces.csv")
-ALLmetaIMGnamed <- read.csv("ALLmetaIMGnamed.csv")
-
-ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
-  filter(matchesManual)%>%
-  dplyr::select(-ID, -facecounter)%>%
-  mutate(fileID = as.numeric(factor(file))) %>%
-  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
-  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-")) %>%
-  mutate(FileName=paste("face-", FaceID, ".png", sep=""))
-
-
-#EmotionsMerged<-left_join(by="FileName", MicrosoftEmotions, ALLmetaIMGnamedFaces)
-#EmotionsMerged<-write.csv(EmotionsMerged, "EmotionsMerged.csv", row.names = FALSE)
-
-
-#EmotionsMerged<-EmotionsMerged %>% mutate(s = sum(anger, contempt, disgust, fear, happiness, neutral, sadness, surprise, na.rm=TRUE))
-
-# Connect face id to original Google set
-
-GE <- GE %>% 
-  rowwise() %>%
-  mutate(minX = min(boundingPoly.x1, boundingPoly.x4), maxX = min(boundingPoly.x2, boundingPoly.x3),
-         minY = min(boundingPoly.y1, boundingPoly.y2), maxY = min(boundingPoly.y3, boundingPoly.y4)) %>%
-  ungroup() %>%
-  mutate(minX = ifelse(is.na(minX), 0, minX), minY = ifelse(is.na(minY), 0, minY))
-
-
-# add meta data to Emotion results
-GF1<-GoogleFaces[,c(1, 35, 18:21, 2:14)]
-GE1<-GE[,c(1, 10:13, 135:138)]
-GE <- left_join(GF1, GE1, by = c("file","minX","maxX","minY","maxY")) 
-
-
[…]

### 2017-09-20 paper/paper.Rmd
created paper folder

--- 2017-09-20 Report06-12.Rmd
@@
   filter(!duplicates)
-SceneAttributes<-read_csv("figures/SceneAttributes.csv")
-FaceAttributes<-read_csv("figures/FaceAttributes.csv")
-SolutionSpecs<-read_csv("figures/SolutionSpecifications.csv")
+SceneAttributes<-read_csv("data/SceneAttributes.csv")
+FaceAttributes<-read_csv("data/FaceAttributes.csv")
+SolutionSpecs<-read_csv("data/SolutionSpecifications.csv")
 
@@
 
-\begin{table}[h]
-\parbox{.5\linewidth}{
+\begin{table}[htp]
+%\parbox{.5\linewidth}{
+\caption{Counts of captures of different APIs against manually tagged faces.}
+\label{tab:facecounts}
 \centering
-\begin{tabular}{ccc}
-\hline  
-Manual & Face & No Face\\ [0.5ex] 
+\begin{tabular}{ccccccc}
+\cline{1-3}\cline{5-7} 
+\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
+Manual & Face & No Face & & Manual & Face & No Face\\ 
 %heading
-\hline 
-Face & 434 & 1861 \\
-NoFace &527 & 787 \\ \hline
+\cline{1-3}\cline{5-7} 
+Face & 434 & 1861 & & Face & 1319 & 976\\
+NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
 \end{tabular}
-\caption{Animetrics}
-}
-\hfill
-\parbox{.5\linewidth}{
-\centering
-\begin{tabular}{ccc}
-\hline  
-Manual & Face & No Face\\ [0.5ex] 
+\\[1.5ex]
+\begin{tabular}{ccccccc}
+\cline{1-3}\cline{5-7} 
+\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
+Manual & Face & No Face & & Manual & Face & No Face\\ 
 %heading
-\hline
-Face & 1319 & 976 \\
-NoFace &638 & 676 \\ \hline
+\cline{1-3}\cline{5-7} 
+Face & 434 & 1861 & & Face & 1319 & 976\\
+NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
 \end{tabular}
-\caption{Google}
-}
 \end{table}
@@
 The upper left quadrant of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
-Table 4, the comparison of Animetrics and Manually annotated faces, gives the lowest amount in this regard. Table 5, Google, found the largest amount of faces that matched those manually annotated.
+Table \@ref(tab:facecounts), the comparison of Animetrics and Manually annotated faces, gives the lowest amount in this regard.
+Table 5, Google, found the largest amount of faces that matched those manually annotated.
 

### 2017-09-20 ct.tex

%latex.default(ct)%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{rrrrrrrrrrrrrrrrrrrrlrrrrrlrrrllrrllllllllllllrrrr}
\hline\hline
\multicolumn{1}{c}{tab Animetrics}&\multicolumn{1}{c}{tab Google}&\multicolumn{1}{c}{tab Microsoft}&\multicolumn{1}{c}{tab Skybiometry}&\multicolumn{1}{c}{prop.row Animetrics}&\multicolumn{1}{c}{prop.row Google}&\multicolumn{1}{c}{prop.row Microsoft}&\multicolumn{1}{c}{prop.row Skybiometry}&\multicolumn{1}{c}{prop.col Animetrics}&\multicolumn{1}{c}{prop.col Google}&\multicolumn{1}{c}{prop.col Microsoft}&\multicolumn{1}{c}{prop.col Skybiometry}&\multicolumn{1}{c}{prop.tbl Animetrics}&\multicolumn{1}{c}{prop.tbl Google}&\multicolumn{1}{c}{prop.tbl Microsoft}&\multicolumn{1}{c}{prop.tbl Skybiometry}&\multicolumn{1}{c}{gt}&\multicolumn{1}{c}{rs}&\multicolumn{1}{c}{cs}&\multicolumn{1}{c}{total.n}&\multicolumn{1}{c}{chisq}&\multicolumn{1}{c}{CST}&\multicolumn{1}{c}{chisq.corr}&\multicolumn{1}{c}{fisher.ts}&\multicolumn{1}{c}{fisher.lt}&\multicolumn{1}{c}{fisher.gt}&\multicolumn{1}{c}{print.mcnemar}&\multicolumn{1}{c}{mcnemar}&\multicolumn{1}{c}{mcnemar.corr}&\multicolumn{1}{c}{asr}&\multicolumn{1}{c}{RowData}&\multicolumn{1}{c}{ColData}&\multicolumn{1}{c}{digits}&\multicolumn{1}{c}{max.width}&\multicolumn{1}{c}{vector.x}&\multicolumn{1}{c}{expected}&\multicolumn{1}{c}{prop.chisq}&\multicolumn{1}{c}{resid}&\multicolumn{1}{c}{sresid}&\multicolumn{1}{c}{asresid}&\multicolumn{1}{c}{format}&\multicolumn{1}{c}{cell.layout}&\multicolumn{1}{c}{row.labels}&\multicolumn{1}{c}{percent}&\multicolumn{1}{c}{total.r}&\multicolumn{1}{c}{total.c}&\multicolumn{1}{c}{t Animetrics}&\multicolumn{1}{c}{t Google}&\multicolumn{1}{c}{t Microsoft}&\multicolumn{1}{c}{t Skybiometry}\tabularnewline
\hline
$528$&$ 638$&$505$&$512$&$0.241868987631700$&$0.292258360054970$&$0.231333027943197$&$0.234539624370133$&$0.547717842323652$&$0.325344212136665$&$0.47196261682243$&$0.509452736318408$&$0.1056$&$0.1276$&$0.101$&$0.1024$&$5000$&$2183$&$ 964$&$5000$&FALSE&$$&$$&$$&$$&$$&FALSE&$$&$$&$$&&&$4$&$$&FALSE&FALSE&FALSE&FALSE&FALSE&FALSE&SPSS&FALSE&TRUE&FALSE&TRUE&TRUE&$528$&$ 638$&$505$&$512$\tabularnewline
$436$&$1323$&$565$&$493$&$0.154774582889599$&$0.469648562300319$&$0.200567980120696$&$0.175008874689386$&$0.452282157676349$&$0.674655787863335$&$0.52803738317757$&$0.490547263681592$&$0.0872$&$0.2646$&$0.113$&$0.0986$&$5000$&$2817$&$1961$&$5000$&FALSE&$$&$$&$$&$$&$$&FALSE&$$&$$&$$&&&$4$&$$&FALSE&FALSE&FALSE&FALSE&FALSE&FALSE&SPSS&FALSE&TRUE&FALSE&TRUE&TRUE&$436$&$1323$&$565$&$493$\tabularnewline
\hline
\end{tabular}\end{center}
\end{table}

### 2017-09-20 paper/paper.Rmd

@@
 
-The APIs, the scripts used to access them, and the resulting data set are contained in the supplementary materials, available at [https://github.com/mvparrot/face-recognition](https://github.com/mvparrot/face-recognition).
+The APIs, the scripts used to access them, and the resulting data set are contained in the supplementary materials, available at [https://github.com/mvparrot/face-recognition/paper](https://github.com/mvparrot/face-recognition/paper).
 The APIs evaluated were:

### 2017-09-20 paper/paper.Rmd
Latex cross tables

@@
 author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
-date: "28 July 2017"
+date: "20 September 2017"
 output: bookdown::pdf_document2
@@
 \cline{1-3}\cline{5-7} 
-\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
+\multicolumn{3}{c}{Microsoft}&&\multicolumn{3}{c}{Skybiometry}\\\cline{1-3}\cline{5-7}
 Manual & Face & No Face & & Manual & Face & No Face\\ 
@@
 \cline{1-3}\cline{5-7} 
-Face & 434 & 1861 & & Face & 1319 & 976\\
-NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
+Face & 565 & 1730 & & Face & 493 & 1802\\
+No Face &505 & 809 & & No Face &512 & 802 \\\cline{1-3}\cline{5-7}
 \end{tabular}

### 2017-09-21 paper/paper.Rmd
added new latex table for accessories

@@
 \centering
-\begin{tabular}{ccccccc}
-\cline{1-3}\cline{5-7} 
+\begin{tabular}{ccccccc} \cline{1-3}\cline{5-7} 
 \multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
@@
 \\[1.5ex]
-\begin{tabular}{ccccccc}
+\begin{tabular}{ccccccc}\\\cline{1-3}\cline{5-7} 
+\multicolumn{3}{c}{Microsoft}&&\multicolumn{3}{c}{Skybiometry}\\
 \cline{1-3}\cline{5-7}
-\multicolumn{3}{c}{Microsoft}&&\multicolumn{3}{c}{Skybiometry}\\\cline{1-3}\cline{5-7}
 Manual & Face & No Face & & Manual & Face & No Face\\ 
@@
 
-\begin{table}[h]
-\parbox{.5\linewidth}{
-\centering
-\begin{tabular}{ccc}
-\hline
-Manual & Face & No Face\\ [0.5ex] 
-%heading
-\hline
-Face & 565 & 1730 \\
-NoFace &505 & 809 \\ \hline
-\end{tabular}
-\caption{Microsoft}
-}
-\hfill
-\parbox{.5\linewidth}{
-\centering
-\begin{tabular}{ccc}
-\hline  
-Manual & Face & No Face\\ [0.5ex] 
-%heading
-\hline 
-Face & 493 & 1802 \\
-NoFace &512 & 802 \\ \hline
-\end{tabular}
-\caption{Skybiometry}
-}
-\end{table}
-
 Each table above considers the individual faces found in the set.
@@
 Table \@ref(tab:facecounts), the comparison of Animetrics and Manually annotated faces, gives the lowest amount in this regard.
-Table 5, Google, found the largest amount of faces that matched those manually annotated.
-
-Visual inspection showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table 5, that were found by Google but not found manually were actually faces, however they were not all of players.
+Table \@ref(tab:facecounts), Google, found the largest amount of faces that matched those manually annotated.
+
+Visual inspection showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:facecounts), that were found by Google but not found manually were actually faces, however they were not all of players.
 Some of these crowd members were beyond what would be expected of an emotion recognition application for detecting faces of tennis players during a match.
@@
 
-```{r accessories, fig.cap = "There are many more faces manually tagged as wearing glasses, and shows there was a more even split between those wearing headwear and those that were not.\\label{tab:accessories}"}
+```{r accessories, eval=FALSE, fig.cap = "\\label{tab:accessories}"}
 
@@
 
-ct<-CrossTable(table(ManFaces$glasses, ManFaces$visorhat), 
-               prop.chisq = FALSE, 
-               digits=max(2, getOption("digits")-2),
-               expected = FALSE,
-           prop.r = FALSE, prop.c = FALSE, prop.t = TRUE,
-           drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
-           dnn = c("Glasses","Visor/hat"))
-
-pander(ct, caption = "Contingency table comparing the amount of captured faces of players that were wearing accessories.")
-```
+prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)
+```
+
+\begin{table}[ht]
+\centering
+%\parbox{.5\linewidth}{
+\caption{Proprotions of faces captured manually tagged as wearing headwear given they wore glasses, or did not.}
+\label{tab:accessories}
+\begin{tabular}{ccc}
+\hline 
+ & Headwear & No Headwear\\ 
+\hline
+Glasses & 0.50 & 0.50 \\
+No Glasses & 0.26 & 0.74 \\
+\hline
+\end{tabular}
+\end{table}
 

### 2017-09-27 paper/paper.Rmd
Minor text edits

@@
 FaceAttributes<-read_csv("data/FaceAttributes.csv")
-SolutionSpecs<-read_csv("data/SolutionSpecifications.csv")
 
@@
 This paper examines the effectiveness of facial detection APIs on broadcast video stills of Australian Open tennis matches.
-The goal is determine the best API to use for face detection of players throughout a match.
+The goal is to determine the best API to use for face detection of players throughout a match.
 For training purposes faces were manually tagged in 6406 images, and the APIs were evaluated on their success rate at detecting these faces.
-The manual tagging also created data recording the scene characteristics and features of individual faces such as whether a visor or cap or sunglasses were being worn.
+The manual tagging also created data recording the scene characteristics and features of individual faces, such as whether a visor or cap or sunglasses were being worn.
 This enables the performance to be assessed based on conditions.
@@
 
-Many tennis professionals believe that tennis is a game heavily affected by the mental states of the players.
+Many tennis professionals believe that tennis is a game heavily influenced by the mental states of the players.
 The opportunity for researching this "inner game" presents itself with the hope of improving the playing and coaching of tennis players by improving their "mental game".
@@
 In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcast videos of elite tennis matches.
-Using the broadcast videos gives an objective insight to emotions as the player progresses through a match.
-While it is impossible to know the thoughts and feelings of a player during a match, professionals may be able to infer this information through results produced by a recognition software.
-This approach opposes the previous studies that have used player's recollections after a game to determine their emotions.
+Using the broadcast videos gives an objective insight to emotions of a player as they progress through a match.
+While it is difficult to know the thoughts and feelings of a player during a match, professionals may be able to gain information through results produced by a recognition software.
+This approach to understanding players emotions during a match differs to previous studies that have used player's recollections after a game to understand their emotions.
 
@@
 The performance of the evaluated software was compared against manual classifications obtained by an annotation tool developed by the authors.
-In addition to looking at the overall performance, image factors that influences the performance of each service were also investigated.
+In addition to looking at the faces they detected, image factors that influences the performance of each service were also investigated.
 
 ##Sample and sampling approach
-The goal of the sample was to be representative of the video files that will be used for future facial recognition analysis.
+
+The images used were provided by Tennis Australia for this research, the goal of the sample was to be representative of the video files that will be used for future facial recognition analysis.
 
@@
 
-The sample consisted of a set of 6404 still images.
-To produce these images, a still shot of the frame was taken at every three seconds, for the length of each 5 minute segment.
-The stills were provided by Tennis Australia for use in this research, these segments were taken from 105 video files, which were the broadcast of the tennis Matches shown on the Seven Network during the Australian Open 2016.
+To produce the set of 6404 images, a still shot of the frame was taken at every three seconds, for the length of each 5 minute segment.
+These segments were taken from 105 video files, which were the broadcast of the tennis Matches shown on the Seven Network during the Australian Open 2016.
 The sample included an equal amount of singles tennis matches played between females and males.
@@
 
-The sample included images that contained the faces of many people, this included players, staff on the court and fans in the crowd.
+The sample included images that contained the faces of many people, such as players, staff on the court and fans in the crowd.
 These faces were included in the manual annotations as they were likely to be found by the software selected.
@@
 The process of software selection to determine which we would compare was based on several criteria.
-The results of the report, as it considered processing speed and feature selection techniques, as well as the ability to perform both still-to-video and video-to-video recognition.
-
-From the software analysed we considered availability for use within the time frame of the report.
-This led us to choose Animetrics FaceR.
-The report outlines that for Animetrics, 'one requirement is that image/face proportion should be at least 1:8 and that at least 64 pixels between eyes are required'.
+Considering the availability, speed, feature selection and whether images and/or videos could be preented for detection.
+The results of Gorodnichy's report, as it considered processing speed and feature selection techniques, as well as the ability to perform both still-to-video and video-to-video recognition.
+
+From the software analysed we considered availability for use within the time frame of the initial data collection stage.
+The report outlines that for Animetrics [@Animetrics], 'one requirement is that image/face proportion should be at least 1:8 and that at least 64 pixels between eyes are required'.
 We realize this could present challenges given the pixel sizes of faces in the image set.
+Other software considered in this survey were not chosen due to the time needed to initialise them, and the costs associated.
 It will also allow for an extension from detecting to recognizing people in the data set.
 
-After considering several other off-the-shelf products, we did not choose any other software's from those analysed as they were not as readily available as other products on the market.
-
-This led to SkyBiometry, an API that also allows for both detection and recognition. The cloud-based software as a service, is a 'spin-off of Neurotechnology', a software considered by the report.
-
-We then chose to consider companies who are expanding their API ranges.
-This resulted in the choice of Microsoft API, provided by Microsoft Cognitive Services.
-This detects faces and return a square area where the face was located, and predicts facial features.
-It also allows the possibility of video stream detection.
-
-The final software we chose to analyse was Google Vision API. Due to Google's expansion in many web based solutions we searched for a facial recognition software.
+This led to SkyBiometry [@Skybiometry], an API that also allows for both detection and recognition.
+The cloud-based software as a service, is a 'spin-off of Neurotechnology', a software considered by the report.
+
+Companies who have recently expanded their API ranges were considered.
+Microsoft API[@Microsoft], provided by Microsoft Cognitive Services detects faces and predicts facial features.
+The final software we chose to analyse was Google Vision API.
+Due to Google's expansion in many web based solutions including a facial recognition software.
 
@@
 ```{r Trial-Image, fig.cap = "This image of Bernard Tomic was chosen as a trial image to be presented to each of the software before they were included in the research.
+Each colour represents a different API source.
 It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE, dev="jpeg", dpi=300}
@@
 
-A 'face' is considered to be any area designated manually or by an API as an area that encloses a human face. These may or may not be actual faces.
+In this study any reference to a 'face' is considered to be an area designated manually or by an API as an area that encloses a human face. These may or may not be actual faces.
 
@@
 
-An annotation tool was constructed to allow image annotations that would capture the location of areas selected manually. We refer to the faces in these areas as Manual Face Classifications.
+An annotation tool was constructed to allow image annotations that would capture the location of areas selected manually.
 This tool also allowed selections of attributes of each face, and attributes describing the features of the Scenes.
@@
 
-The bar charts of the situations show that the situation is important in influencing the detection of a face.
-When the face is accessorised with them, all APIs have a significantly increased chance of finding the face in comparison to the base rate category of the "Match play".
-While the image being a Graphic had a large impact it was not significant, this is likely because of the small number of images with this attribute.
-It also shows that the shot angle is only significant for one or two APIs at each level.
-
 ```{r RegressionFunctions, cache=FALSE}
@@
 ```{r ModelEstimates, fig.cap ="\\label{tab:ModelEstimates}"}
-
 TypeModel <- hit ~ 0 + 
@@
 ```
+
+Table \@ref(tab:ModelEstimates) shows that for all of the APIs are significantly less likely to find a face accessorised with glasses or hats, or obscured by an object.
+All APIs are less likely to find a face if the face was not captured front on to the camera.
+The faces captured when the situation was match play siginifcantly decreased the likelihood of a hit for all APIs.
+
+Google was the only API that beneefitted from the interaction that was significant in increasing the likelihood of a hit when a face was captured at an angle level to the face, and had a background of the logo wall.
 
@@
 ```{r accessories, eval=FALSE, fig.cap = "\\label{tab:accessories}"}
-
 aminFaces %>%
@@
 prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)
+
 ```
@@
 
+Table \@ref(tab:accessories) of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without headwear.
+Of those without glasses only 26% wore headwear.
+This may be influenced by weather and sunlight on the court during Australian Ope nmatches.
+
 ```{r glasses, fig.cap = "\\label{tab:glasses}", digit=3}

### 2017-11-22 paper/paper.Rmd
Spelling and edits

@@
 bibliography: references.bib
-biblio-style: apalike
+biblio-style: harvard
 link-citations: true
@@
 The goal is to determine the best API to use for face detection of players throughout a match.
-For training purposes faces were manually tagged in 6406 images, and the APIs were evaluated on their success rate at detecting these faces.
-The manual tagging also created data recording the scene characteristics and features of individual faces, such as whether a visor or cap or sunglasses were being worn.
-This enables the performance to be assessed based on conditions.
+For training purposes faces were manually tagged in 6406 images, recording the scene characteristics and features of individual faces.
+This included information regarding accessories, such as headwear or sunglasses being worn.
+This enables the performance to be assessed based on conditions, and the APIs were evaluated on their success rate at detecting these faces.
+The practicality of usage was also assessed via time taken to complete detection within an image.
 
@@
 Many tennis professionals believe that tennis is a game heavily influenced by the mental states of the players.
-The opportunity for researching this "inner game" presents itself with the hope of improving the playing and coaching of tennis players by improving their "mental game".
-By statistically analyzing the faces and expressions of players during a match there is a hope that insight may be gained into the effects of the mental state on the outcome of a match.
-Facial expressions during competition may provide an insight into a player's thoughts.
-The aim of this project is to begin to develop methods to collect accurate information about the facial expressions of elite tennis athletes during match play.
-
-In this report, we investigate the performance of several popular facial recognition software's through their Application Programming Interfaces (APIs), and evaluate their performance when applied to the broadcast videos of elite tennis matches.
-Using the broadcast videos gives an objective insight to emotions of a player as they progress through a match.
-While it is difficult to know the thoughts and feelings of a player during a match, professionals may be able to gain information through results produced by a recognition software.
-This approach to understanding players emotions during a match differs to previous studies that have used player's recollections after a game to understand their emotions.
+The opportunity for researching this "inner game" presents itself with the hope of improving the performance, and coaching of, tennis players by improving their "mental game".
+By statistically analyzing the faces and expressions of players during a match insight may be gained into the effects of the mental state on the outcome of a match.
+The aim of this project is to develop methods to collect accurate information about the facial expressions of elite tennis athletes during match play.
+
+The performance of several popular facial recognition software's through their Application Programming Interfaces (APIs) is evaluated based on their performance on still images derived from broadcast videos of elite tennis matches.
+While it is difficult to know the thoughts and feelings of a player during a match, analysts may be able to gain information through results produced by recognition softwares.
+This approach to understanding player's emotions during a match differs to previous standards that have used player's recollections after a game to understand their emotions.
 
@@
 The aims of the present study were to determine the feasibility of using currently available APIs for extracting facial information of players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
-This limited selection was based on accessible APIs believed to produce appropriate and useful facial recognition.
-The performance of the evaluated software was compared against manual classifications obtained by an annotation tool developed by the authors.
-In addition to looking at the faces they detected, image factors that influences the performance of each service were also investigated.
+A limited selection of accessible APIs was chosen based on their ability to produce appropriate and useful facial recognition.
+The performance was evaluated against manual classifications obtained in an annotation tool developed by the authors.
+
+# Methodology
+
+In this study any reference to a 'face' is considered to be an area designated manually or by an API as an area that encloses a human face. These may or may not be actual faces.
 
@@
 
-The images used were provided by Tennis Australia for this research, the goal of the sample was to be representative of the video files that will be used for future facial recognition analysis.
-
-- 6406 Australian Open images (2.8GB)
-- 800x450px size frames from 105 match broadcast videos
-- Video frames taken every 3 seconds over a 5 minute segment
-
-To produce the set of 6404 images, a still shot of the frame was taken at every three seconds, for the length of each 5 minute segment.
-These segments were taken from 105 video files, which were the broadcast of the tennis Matches shown on the Seven Network during the Australian Open 2016.
-The sample included an equal amount of singles tennis matches played between females and males.
-The rounds of the competition vary as to not limit the pool of players to only those who progressed, though there was a higher chance of advancing players reappearing.
+Images from the Australian Open 2016 were provided by Tennis Australia, with goal being that the sample specified below is representative of the video files to be used for future facial recognition analysis:
+
+- 6406 images, 800x450px
+
+To produce the set of 6404 images, 5 minute segments were taken from 105 video files a still shot of the video was taken at every three seconds, for the length of each segment.
+The video file were the broadcast of the tennis Matches shown on the Seven Network during the Australian Open 2016.
+The sample included an equal amount of females and males singles tennis matches.
+The rounds of the competition vary so as to not limit the pool of players to only those who progressed, though there was a higher chance of advancing players reappearing.
 
 The sample included images that contained the faces of many people, such as players, staff on the court and fans in the crowd.
-These faces were included in the manual annotations as they were likely to be found by the software selected.
-We felt including these additional faces would not only increase the sample by which to judge the software's capabilities but also allow provision of information on how to differentiate between players and other people for further research.
+All of these faces were included in the manual annotations as they were likely to be found by the software selected.
+It was decided that including these additional faces would allow better evaluations of the software's capabilities, and provide information to differentiate between players and other faces captured.
 Therefore the sample was not filtered at this initial stage.
 
-There are many matches played during the Australian Open, and they are played on the range of courts available at Melbourne Olympic Park.
-Therefore the sample was selected to be representative of the seven courts that have the Hawk Eye technology enabled.
+Matches played during the Australian Open are played on a range of courts available at Melbourne Olympic Park.
+The sample was selected to be representative of the seven courts that have the Hawk Eye technology enabled.
 
@@
 
-The choice of the initial software considered for this research was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.' [@Survey]
-
-The process of software selection to determine which we would compare was based on several criteria.
-Considering the availability, speed, feature selection and whether images and/or videos could be preented for detection.
-The results of Gorodnichy's report, as it considered processing speed and feature selection techniques, as well as the ability to perform both still-to-video and video-to-video recognition.
-
-From the software analysed we considered availability for use within the time frame of the initial data collection stage.
-The report outlines that for Animetrics [@Animetrics], 'one requirement is that image/face proportion should be at least 1:8 and that at least 64 pixels between eyes are required'.
-We realize this could present challenges given the pixel sizes of faces in the image set.
-Other software considered in this survey were not chosen due to the time needed to initialise them, and the costs associated.
-It will also allow for an extension from detecting to recognizing people in the data set.
-
-This led to SkyBiometry [@Skybiometry], an API that also allows for both detection and recognition.
-The cloud-based software as a service, is a 'spin-off of Neurotechnology', a software considered by the report.
-
-Companies who have recently expanded their API ranges were considered.
-Microsoft API[@Microsoft], provided by Microsoft Cognitive Services detects faces and predicts facial features.
-The final software we chose to analyse was Google Vision API.
-Due to Google's expansion in many web based solutions including a facial recognition software.
-
-We were able to try the online demos to see whether these software were viable, we used the following Image displayed in Figure \@ref(fig:Trial-Image):
+The initial software to be considered was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications' [@Survey, pp.3].
+
+The selection criteria included the availability, speed, feature selection and whether images and/or videos could be presented for detection.
+The results of Gorodnichy, Granger and Radtke's [-@Survey] report considered processing speed, feature selection techniques, and the ability to perform both still-to-video and video-to-video recognition.
+
+The report outlined that Animetrics [@Animetrics] required an 'image/face proportion should be at least 1:8 and that at least 64 pixels between eyes are required'.
+
+SkyBiometry [@Skybiometry] is a 'spin-off of Neurotechnology' which was considered by Gorodnichy et al. an API that also allows for both detection and recognition.
+
+Companies who have recently expanded their API ranges were considered. Microsoft API[@Microsoft], provided by Microsoft Cognitive Services, and Google Vision API [@Google].
+
+Online demos were used to test viablity, Figure \@ref(fig:Trial-Image) depicts Bernard Tomic and the detected areas found.
 
@@
 ```
-
-# Methodology
-
-In this study any reference to a 'face' is considered to be an area designated manually or by an API as an area that encloses a human face. These may or may not be actual faces.
 
@@
 All APIs are less likely to find a face if the face was not captured front on to the camera.
-The faces captured when the situation was match play siginifcantly decreased the likelihood of a hit for all APIs.
-
-Google was the only API that beneefitted from the interaction that was significant in increasing the likelihood of a hit when a face was captured at an angle level to the face, and had a background of the logo wall.
+The faces captured when the situation was match play significantly decreased the likelihood of a hit for all APIs.
+
+Google was the only API that benefited from the interaction that was significant in increasing the likelihood of a hit when a face was captured at an angle level to the face, and had a background of the logo wall.
 
@@
 Faces common to all four API and manual annotations were the fourth largest group, it was obvious that relevant faces were captured more commonly by Google and manually.
-The fifth group was the most suprising, this captured a lot of faces that were false discoveries.
+The fifth group was the most surprising, this captured a lot of faces that were false discoveries.
 
@@
 The colours in the mosaic (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
-There is a greater proprtion of API faces that matched the faces found manually than those that did not match.
+There is a greater proportion of API faces that matched the faces found manually than those that did not match.
 However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually.
@@
 It can be seen that the largest portion of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
-This porportion is steady across most situations, from this we learn the situation may not be influencing the APIs rate of detection.
+This proportion is steady across most situations, from this we learn the situation may not be influencing the APIs rate of detection.
 
@@
 %\parbox{.5\linewidth}{
-\caption{Proprotions of faces captured manually tagged as wearing headwear given they wore glasses, or did not.} 
+\caption{Proportions of faces captured manually tagged as wearing headwear given they wore glasses, or did not.} 
 \label{tab:accessories}
@@
 \hline 
- & Headwear & No Headwear\\ 
+ & Head wear & No Head wear\\ 
 \hline
@@
 Of those without glasses only 26% wore headwear.
-This may be influenced by weather and sunlight on the court during Australian Ope nmatches.
+This may be influenced by weather and sunlight on the court during Australian Ope n matches.
 
@@
 # Future Work
-The Long Term goal of this research is to better understand how the emotion's felt by a player during a match affect player performance.
+The long term goal is to better understand how the emotion's felt by a player during a match affect player performance.
 Ultimately we would aim to create a program that automated the collection of player emotion data from throughout a match.
@@
 Considering the images used during our study were stills derived from Broadcast video files, it would be useful to extend further research to deal with the video files directly.
-The Google Vision API used in this research which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.
+The Google Vision API which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.
 
@@
 # References
+
+<div id="refs"></div>

### 2017-11-22 paper/paper.Rmd
Editing

@@
 
-An annotation tool was constructed to allow image annotations that would capture the location of areas selected manually.
-This tool also allowed selections of attributes of each face, and attributes describing the features of the Scenes.
+A web based annotation tool was developed to allow image annotations that would capture the location of areas selected manually, and annotation of attributes for each face, and scene.
 
@@
 
-The aim was to collect specific information on each different face within the scene.
-To determine which of the sometimes many faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
+Specific information for each face within each scene was collected.
+To determine which of the, sometimes many, faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
 
 The faces of players were recorded if it showed their face at a minimum of 20 by 20 pixels.
-The back of the head was not detected as a face by any software, these faces were classified manually but reclassified as other.
-Crowd shots provided difficultly in determining which faces were reasonable to classify.
-These faces were not the intended targets of the recognition however these faces contributed to our understanding of the software.
-The same face size standard applied to crowd members, but focus was placed on the most prominent faces. For each of these faces, we collected information on the following attributes:
+The back of the head was not detected as a face by any software, these areas were classified manually but reclassified as other.
+Crowd faces were not the intended targets of the recognition however these faces contributed to our understanding of the software.
+The same face size standard applied to crowd members, but focus was placed on the most prominent faces.
+For each of these faces, information was collected regarding the attributes in Table \@ref(tab:Face-Attribute-Tables).
 
@@
 
-To record the details of attributes for each face and scene a Shiny [@shiny] App was created.
-We called this Application our ManualClassificationProgram.
-This helped to provide information for all attributes quickly and consistently.
+The web app was created using Shiny [@shiny]. This has been expanded into an R package called taipan. A tool for annotating images in preparation for analysis.
 
 If there was a face in the image the annotator was able to highlight a section of the image to create a square 'Face Box'.
-This changed the display and presented a set of Attributes with radio buttons, this allowed information to be recorded for the face in the specific 'Face Box'.
-This recorded the x and y coordinates of the corner points of a box drawn by the mouse, and when the save button was hit it saved all the radio button selections and the 'Face Box' coordinates to a CSV file.
-
-When a face was not selected, the radio buttons showed the Scene attributes and the radio buttons with the possible selections the annotated was able to choose from.
-When in this display, selecting the save button would then save the Scene selections to a specific CSV file.
-
-If there were issues, the CSV files were able to be edited, this was reserved for extreme circumstances.
-As a lot of care was taken to ensure the first selections were correctly submitted and applied to the correct Faces and Scenes.
+This selection presented a set of Attributes questions to answer, and allowed information to be recorded for the face in the specific 'Face Box'.
+This recorded the x and y coordinates of the box drawn, and saved all the selections and the 'Face Box' coordinates to a CSV file.
+
+When a face was not visible in the scene only the scene attributes applied for that image.
 
 All the annotations for this sample were completed by one author.
-This was chosen to provide consistency across the sample of faces annotated manually.
-However the initial choices of what would be reasonably detected were made by several of the authors.
+This provided consistency across the sample of faces annotated manually.
+The choices of what would be reasonably detected was made by several of the authors.
 
 ##Software interaction
+
 The software choices allowed for POST requests to be sent via the internet.
@@
 
-Given that certain Scene attribute combinations produced more facial recognition than other combinations we should consider limiting the sample of images sent to Google Vision API.
+Given that certain scene attribute combinations produced more facial recognition than other combinations we should consider limiting the sample of images sent to Google Vision API.
 This would not only reduce cost but also provide a greater level of detail of the emotions felt by a player during a match.
 To provide a greater level of information at all points in a match it would be beneficial to derive images from a single camera feed.
-This feed should match the Scene attributes that provided the most Google faces.
+This feed should match the scene attributes that provided the most Google faces.
 

### 2017-12-04 paper/paper.Rmd
Software usage edits, level plot added

@@
 library(purrr)
+library(lvplot)
+
 knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)
@@
 
-All the annotations for this sample were completed by one author.
-This provided consistency across the sample of faces annotated manually.
-The choices of what would be reasonably detected was made by several of the authors.
-
-##Software interaction
-
-The software choices allowed for POST requests to be sent via the internet.
-To access the APIs through R we enlisted the httr package, using functions from this package a script was written for Google, Animetrics, Microsoft and Skybiometry.
-These scripts contained loops that would move through the images, individually posting a request for each image to be analysed.
-These scripts included retrieving the information provided and converting it into a usable format for our analysis.
-One interesting anomaly was found when using the Skybiometry software as it limited the amount of requests per minute.
-We accounted for this by stalling the posts for the amount of waiting time the software notified, and checking until the time lapsed and the script could continue looping.
-
-The amount of time taken for each software to process facial detection on the individual images is presented in the histogram :
+All the annotations for this sample were completed by one annotator to provide a consistent sample of faces annotated manually.
+The initial decisions of what would be reasonably detected was made by several people.
+
+##Software usage
+
+The face recognition software allowed for access through a R [@R] script, calling the APIs using the httr[@httr] package.
+The scripts looped through the images, individually posting a request to retrieve information provided and convert it into an appropriate format for analysis.
+
+Special handling was required due to the limits on requests per minute of Skybiometry and Microsoft, time-controlling the requests was incorporated for these APIs.
+
+Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image.
 
@@
 
-```{r timeTable, results='asis', fig.cap="System time taken by the four APIs to finish searching individual images, plotted against number of faces discovered.
+```{r timeFigure, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered.
 Skybiometry is the fastest, and Microsoft is the slowest.
-The largest variability is when no faces are found.\\label{tab:timeTable}", dev="png", dpi=300}
-
-t1 <- ggplot(times) +  
-  geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm") + 
-  xlab("Number of faces detected") + ylab("System time (sec)") +  
-  scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")
-
-t2 <- ggplot(times) +  
-  geom_jitter(aes(x=n, y=time.sys.self, colour=type), alpha=0.2, width=0.3, height=0.01) +  
+When there are few faces found there is more variable time taken per image.\\label{fig:timeFigure}"}
+# 
+# t1 <- ggplot(times) +  
+#   geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm") + 
+#   xlab("Number of faces detected") + ylab("System time (sec)") +  
+#   scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")
+
+# t2 <- ggplot(times) +
+#   geom_jitter(aes(x=n, y=time.sys.self, colour=type), alpha=0.2, width=0.3, height=0.01) +
+#   facet_wrap(~type) +
+#   ylim(c(0, 0.1)) +
+#   #geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) +
+#   xlab("Number of faces detected") +
+#   scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")
+
+#grid.arrange(t1,t2,nrow=1)
+
+# letter value plots
+t2 <- ggplot(times, aes(as.factor(n), time.sys.self)) + 
+  geom_lv(aes(fill = ..LV..)) +
+  ylim(c(0, 0.1)) + 
   facet_wrap(~type) +
-  ylim(c(0, 0.1)) +  
-  #geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) + 
-  xlab("Number of faces detected") +  
-  scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")
-
-grid.arrange(t1,t2,nrow=1)
+  xlab("Number of faces detected")
+
+t2
 ```
@@
 It would depend on the amount of frames sampled.
-This also does not account for the time taken to manipulate and save the information returned.
+This also does not account for the time taken to process the information returned.
 

### 2017-12-04 paper/paper.Rmd
Data processing section edits

@@
 
-The data needed for our analysis was spread across six files.
-For each software we had the information on the location of the Facial Bounding Boxes, as well as the time taken for the software to find the information.
-Some of the software also provided a more detailed level of information.
-
-The collation of the results from the Manual Recognition Program created
-two CSVs.
-
-A single data set was created to combine all necessary information in the previously mentioned files for our analysis.
-The information in the data set, was carefully considered.
-It considers the identify of each face, and all relative face attributes, as well as the image file the face was found in, from this information each face was able to be uniquely identified.
-Also included was information on the software that found it, and the time it took the software to identify the face.
-It also has a record of how many faces had been identified in the image by counting each additional recognized face.
-To do so, we gathered the name of the file the face was found in and the API that found it.
-The automatically determined time values were also included.
-The minimum and maximum x and y values were drawn from different values in each software's CSV files.
-This required some processing to align the differing values to be comparable.
-
-To find whether the software were recognizing the same faces a function was created.
-As the location and size of the boxes around the faces were recorded, these values were used to see if a particular identified face box matched a manually identified face, or a region found by another software.
-This function uses the information of each face and compares the intersecting regions of the polygons created by the x,y coordinates of Manual Faces and other software's faces, to determine if the same face was recognized.
-We determined the ratio of intersecting area to total area must be greater than 0.1 to be considered the same face.
-This allowed us to compare the identification areas, as well as contrast the identified faces of each software.
-This contributed another variable, boxID, to the data set.
+The data needed for our analysis was organised by source, separate files for each of the four APIs.
+They contained the information on the location of the faces found in the images and the time taken to find them.
+Some APIs also provided detailed information such as the estimated head angle, and locations of specific facial features.
+
+The manual tagging app resulted in two files, one containing information about the image, and the faces.
 

### 2017-12-04 paper/paper.Rmd
Results section edits

@@
 
-##Analysis
+##Results
 
-Using the data set of the combined API and manual results, we were able to compare the performance of the software.
-Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(fig:FaceData).
+The manual tagging helped to provide a benchamark for faces found by APIs. The
+face detection rate indicated what attributes of an image or face were associated with face detection by an API. 
+Faces that were found by multiply APIs indicated the industry expectations for face presentation.
+This application allowed for a broader range of angles, backgrounds and accessories that may have impacted detection.
+False discoveries were the instances of faces found by APIs that did not intersect with manually tagged faces.
+Some of these may actually have been faces or reveal sensitivities in the algorithms of the APIs.
+The analysis of image characteristics and accessories indicates whether the APIs were viable choices for detecting faces in sports environments.
 
-However, individual faces are not beneficial if they do not correspond to the faces manually annotated.
-Figure \@ref(fig:FaceUpset) was created by defining groups depending on the API that recognized each particular face.
-The UpSetR [-@UpSetR] package helps visualise set intersections.
-Where in this circumstance faces boxes may overlap on the same face, each bar shows the number of individual faces that have boxes resulting from each of the APIs highlighted below the bar.
+### Face detection rate modelled in characteristics
 
-### Modeling face detection probabiity
+A logistic regression model was used to assess the characteristics of the face and scene affecting detection.
 
-This shows how influential certain attributes are in determining whether a face will be detected, a hit, or not, a miss.
-
-A step wise method was used to determine the best regression model for predicting a hit or miss.
-The regression model that provided the best AIC, included the scene attributes: Shot Angle, Background, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
-It also included the lighting on the particular face, and whether the specific face was accessorised with glasses and headwear, a visor or hat.
-
-Regression analysis showed that the situation variable had significant differences between intercept level of "Not player" and the categories of "Match play" and "Court Player Close Up".
-This would mean that the probability of all the APIs finding the face that had been found manually was significantly less if the situation depicted was "Match play" and "Court Player Close Up" rather than a "Not player".
+A step wise method was used to determine the best regression model.
 
@@
                                           "r", "l"),
-             booktabs = TRUE, longtable=FALSE, caption="The table of regression coefficients denotes the significant variables, and levels, for the four API types.
-The dashes represent coefficient that were not significant.
-The symbols to the right of the regression coefficients denote the significance level associated with each coefficient.
-The background variable, and levels of the interaction between shot angle and background were only significant for Google.")
+             booktabs = TRUE, longtable=FALSE, caption="Evaluation of factors affecting face recognition by API.
+(** 0.01 * 0.05 .
+0.01 - NS) Coefficients from logitics regression models shown.
+Glasses, visorhat, headangle lighting, shotangle and situation all contribute significantly to face detection.")
 ```
 
-Table \@ref(tab:ModelEstimates) shows that for all of the APIs are significantly less likely to find a face accessorised with glasses or hats, or obscured by an object.
-All APIs are less likely to find a face if the face was not captured front on to the camera.
-The faces captured when the situation was match play significantly decreased the likelihood of a hit for all APIs.
-
-Google was the only API that benefited from the interaction that was significant in increasing the likelihood of a hit when a face was captured at an angle level to the face, and had a background of the logo wall.
+For the most part, the APIs were all affected by the same factors.
+The factors that negatively affected all APIs were glasses, visor or hat. Background only negatively affected Google. Situation had different effects on each API.
+Results for Google were most interestng in the shotangle had differing effects on the detection.
 
@@
 ```
-
-The variables were kept if they were significant for any level of the variable for any type.
-Given the significant coefficients above it can be seen that the largest decrease in probability of a face being found by the APIs was the face profile being captured.
 
@@
 
-# Results
-
-## Amount of faces
+### Detection rates
 
@@
 
-To evaluate the performance in terms of the overall accuracy of each algorithm we considered the amount of faces they classified that matched faces that were selected manually.
-This sample contains all the manually annotated faces and all the faces recognized by the four APIs.
+Figure \@ref(fig:FaceData) shows a bar chart of faces per API. Manual tagging produced the most faces, more than the four APIs. Google has the highest detection rate, almost twice that of other APIs.
 
-Figure \@ref(fig:FaceData), the bar chart of faces per API shows Google produces the most detections.
-Having a high volume of detected faces returned is valuable for the future use where faces of the player must be captured over time during sports matches.
+### API intersection
 
-## Comparing faces found
+The faces in Figure  \@ref(fig:FaceData) and Table \@ref(tab:facecounts) found by APIs and manually tagged are compared.
 
-The individual faces, the specified area of the image, found by each API are compared to those found manually and by the other APIs.
-
+Figure \@ref(fig:FaceUpset) illustrates the intersection between software over all of the images. Constructed using the UpSetR [@UpSetR] package it shows the faces found by Google 
 ```{r table}
@@
 %\parbox{.5\linewidth}{
-\caption{Counts of captures of different APIs against manually tagged faces.}
+\caption{Contingency tables of eaach API capture against manual tagging. Interestingly all APIs reported faces that would not be considered relevant faces by manual inspection}
 \label{tab:facecounts}

### 2017-12-12 paper/paper.Rmd
editing system time section

@@
 
-Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image.
+Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a letter value plot (*** add in reference to Heik'e paper).
+A letter value plot is like a boxplot, but more suited to skewed data like this.
+(Both Microsoft and Google have a few eimages each where they have taken a long time to complete and these were removed from this plot.) The times are quite variable between APIs, with Skybiometry being the most consistently fast.
+Microsoft and Animetrics are quite variable regardless of the number of faces found.
+Google is variable in time taken when there are few faces present, and then takes a little longer on average to find faces as the number of them in the image increases.
 
@@
 
-```{r timeFigure, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered.
-Skybiometry is the fastest, and Microsoft is the slowest.
-When there are few faces found there is more variable time taken per image.\\label{fig:timeFigure}"}
+```{r timeFigure, fig.height=6, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered, displayed as a letter value plot.
+Skybiometry is the most consistently fast.\\label{fig:timeFigure}"}
 # 
@@
   geom_lv(aes(fill = ..LV..)) +
-  ylim(c(0, 0.1)) + 
+  #ylim(c(0, 0.1)) + 
   facet_wrap(~type) +
+  scale_y_continuous("System time (ms)", 
+    breaks=seq(0, .08, .02), limits=c(0, 0.08)) +
+  # somethings funky when try to change axis labels
   xlab("Number of faces detected")
@@
 
-```{r accessories, eval=FALSE, fig.cap = "\\label{tab:accessories}"}
+```{r accessories, eval=TRUE, fig.cap = "\\label{tab:accessories}"}
 aminFaces %>%

### 2017-12-12 paper/paper.Rmd
making lots of changes

@@
 
+*** (1) Check caption sentences finish with "." (2) Check spelling (3) Check no referring to tables and figures in the text like "the table below ..." or the "figure above ..." (4) Check all the writing is in third person, remove "We then ..." (5) One sentence paragraphs should be very rarely used, and I suspect there are too many in the current draft.
+Check if the orphan sentence better belongs with the prior or after paragraph.
+
 #Introduction
@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Image descriptions that are associated with the attributes of each image.")
+knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics recorded for each image.")
 ```
@@
 ```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
-knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Possible face descriptions for each individual face.
-Most of the selections were obvious for each image, with the exception of obscured and head angle.")
+knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics recorded for each  face.
+Most were easy to assess for each face, with the exception of obscured and head angle.")
 ```
@@
 
-### Face detection rate modelled in characteristics
+### Modeling detection rate
 
-A logistic regression model was used to assess the characteristics of the face and scene affecting detection.
-
-A step wise method was used to determine the best regression model.
+A logistic regression model was used to assess the characteristics of the face and scene affecting detection, with stepwise variable selection.
+The binary response was whether the face was detected or not, using the manually tagged data as the benchmark, and characteristics included the setting, angle of shot and player, background, lighting and player adornments.
+(*** Any other variables considered but not selected for any model?)
+A separate model was fit for each API.
 
@@
                                           "r", "l"),
-             booktabs = TRUE, longtable=FALSE, caption="Evaluation of factors affecting face recognition by API.
-(** 0.01 * 0.05 .
-0.01 - NS) Coefficients from logitics regression models shown.
-Glasses, visorhat, headangle lighting, shotangle and situation all contribute significantly to face detection.")
+             booktabs = TRUE, longtable=FALSE, caption="Evaluation of factors affecting face recognition for API, as assessed by logistic regression model.
+Coefficients from the four models shown (significance: ** 0.01 * 0.05 .
+0.01 - NS).
+Most APIs wre affected by similar factors, with glasses, visor or hat, head angle, lighting, shot angle and situation all contributing significantly to face detection.")
 ```
 
+*** The number of digits should be consistent, e.g. "-1" should be "-1.00". I don't know how to force this with the kable printing, but one way or another we have to.
+
 For the most part, the APIs were all affected by the same factors.
-The factors that negatively affected all APIs were glasses, visor or hat. Background only negatively affected Google. Situation had different effects on each API.
+Those that negatively affected all APIs were glasses, visor or hat.
+Background only negatively affected Google's detection rate.
+Situation had different effects on each API.
 Results for Google were most interestng in the shotangle had differing effects on the detection.

### 2017-12-12 paper/paper.Rmd
up to 2.8

@@
 
-Each API returned areas that indicated the potential location of a face.
-These areas are defined using the four points returned by the APIs.
-The Google Vision API detected a large amount of faces, much more than Microsoft, Skybiometry or Animetrics.
-This can be seen in Figure \@ref(fig:FaceData).
+Each API returned areas in the image that indicated the face location.
+These are defined using the four points, marking the four corners of a rectangle.
+Figure \@ref(fig:FaceData) shows a barchart of the number of faces detected by each API.
+The Google Vision API detected largest number of faces, much more than the other three APIs, and most closely matched the number recorded by manual tagging.
 
-```{r FaceData, fig.cap = "\\label{fig:FaceData}   Face Boxes Per API: The bar chart shows the number of  Face Boxes produced by each API, comparing the height of the bars indicates that Google's Facial Recognition API recognized almost 1000 more faces than the next best API, Microsoft."}
+```{r FaceData, fig.cap = "\\label{fig:FaceData}  The bar chart of the number of faces detected by each API.
+Google's Facial Recognition API recognized almost 1000 more faces than the next best API, Microsoft."}
 
@@
 
-Figure \@ref(fig:FaceData) shows a bar chart of faces per API. Manual tagging produced the most faces, more than the four APIs. Google has the highest detection rate, almost twice that of other APIs.
+### API comparison
 
-### API intersection
+Table \@ref(tab:facecounts) cross-tabulates the faces found by each API relative to the manually tagged faces.
+For a perfect match with the manually tagged faces, the off-diagonal elements should be zero.
+Google has the closest match to the manual tagging, and Skybiometry, which was the fastest to run, performed very badly.
+It is interesting to see the high proportion of faces detected by the APIs that were not considered to be faces by manual tagging.
 
-The faces in Figure  \@ref(fig:FaceData) and Table \@ref(tab:facecounts) found by APIs and manually tagged are compared.
+The mismatches were manually examined, and showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces found by Google but not tagged manually were actually faces, but were crowd members.
+They would need to be used, for the long term purpose of the study, to detect and tag players' emotions during a match.
 
-Figure \@ref(fig:FaceUpset) illustrates the intersection between software over all of the images. Constructed using the UpSetR [@UpSetR] package it shows the faces found by Google 
+Comparatively, visual inspection of the `r amin %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were actually very unusual results, which are discussed later.
+
 ```{r table}
@@
 %\parbox{.5\linewidth}{
-\caption{Contingency tables of eaach API capture against manual tagging. Interestingly all APIs reported faces that would not be considered relevant faces by manual inspection}
+\caption{Contingency tables of each API capture against manual tagging. Interestingly all APIs reported faces that would not be considered faces by manual inspection.}
 \label{tab:facecounts}
@@
 
-Each table above considers the individual faces found in the set.
-The upper left quadrant of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
-Table \@ref(tab:facecounts), the comparison of Animetrics and Manually annotated faces, gives the lowest amount in this regard.
-Table \@ref(tab:facecounts), Google, found the largest amount of faces that matched those manually annotated.
-
-Visual inspection showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:facecounts), that were found by Google but not found manually were actually faces, however they were not all of players.
-Some of these crowd members were beyond what would be expected of an emotion recognition application for detecting faces of tennis players during a match.
-These were deemed unlikely to be necessary when attempting to find faces of players during tennis matches, and neglected during manual annotation.
-
-Comparatively, visual inspection of the `r amin %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were actually very unusual results.
+*** I've decided that these should be proportions.
 
@@
 
-Figure \@ref(fig:FaceUpset) helps to understand faces that were found by a combination of APIs, and the manual annotations.
-The black bubbles  the bars show the API combination that detected all the faces counted in the bar above.
-Faces common to all four API and manual annotations were the fourth largest group, it was obvious that relevant faces were captured more commonly by Google and manually.
-The fifth group was the most surprising, this captured a lot of faces that were false discoveries.
+Figure \@ref(fig:FaceUpset) is a set visualisation to examine the intersection of the APIs, and the manual annotations.
+This is produced with the UpSetR [@UpSetR] package.
+The black bubbles below the bars indicate the API combination that corresponds to the bar count.
+The largest count comes from manual tagging, followed by Google and manual tagging, and then Google.
+Faces detected by all four API and manual annotations were the fourth largest count.
+This says that the APIs agreed on about a quarter of the faces from the manually tagged collection.
+The fifth group was the most surprising -- these were faces captured by Animetrics alone, that were false discoveries.
 
 ## False discoveries
-Examples are included of faces only found by one of the APIs, as other than Google, the APIs produced several unusual false discoveries.
-These highlight the potential differences in the detection methods used by each of the APIs.
-This would need to be taken under consideration to prevent time wasted on sorting actual faces from false discoveries in future applications.
 
-```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual.
-The top left image presents a potential faces that actually defines an area containing a player's back and a ball boy's torso.
-The top right shows two potential faces that are actually the KIA logo on the net.
-The bottom left image was very interesting as the player's face was found, but the shirts of both the player and ball boy were deemed potential faces.
-The bottom right image had a lot more faces that usually recognised.
-Animetrics found a fist to the right on the centre that it considered a potential face.
+Animetrics provided many surprises. Figure \@ref(fig:UnusualImages) shows four images and the captures where non-faces were detected as faces. In image (a) the player's back is detected as a face.
+In image (b) the KIA logo was reported as a face. 
+In image (c), where logos on the player's and ballboy's shirts were returned as faces.
+In image (d) where there are a lot of crowd faces, if you look closely one of the detections is actully a fist (to the right on the center).
+
+The other APIs also returned some non-faces, but the most egregious mistakes came from Animetrics.
+
+```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual: (a) one of the detected face is a player's back, (b) the KIA logo on the net is detected as a face, (c) is very interesting as the player's face was found, but the shirts of both the player and ball boy were reported as faces, (d) had a lot more faces than many images but Animetrics also found a fist (to the right on the center) that it considered a face.
 \\label{fig:UnusualImages}", dev="jpeg", dpi=300}
@@
 ```
-
-Figure \@ref(fig:UnusualImages) depicts four images that contained unusual results of faces.
-Figure a highlights a very large area, most interesting about this is the face of the ball boy captured within this area.
-Figure b also shows unusual faces, the KIA logo was returned by Animetrics many times as a face.
-This discredits the ability of the API to distinguish actual faces from tricks of lights and colours in the complex setting of colourful tennis matches.
-
-Examples of tricks of colours are shown in Figure c, where logos on the shirts were returned as faces.
-These discoveries discredit the use of Animetrics for facial detection applications during sports matches.
 

### 2017-12-12 paper/paper.Rmd
Spelling, paragraph, and third person corrections

@@
 The performance of several popular facial recognition software's through their Application Programming Interfaces (APIs) is evaluated based on their performance on still images derived from broadcast videos of elite tennis matches.
-While it is difficult to know the thoughts and feelings of a player during a match, analysts may be able to gain information through results produced by recognition softwares.
+While it is difficult to know the thoughts and feelings of a player during a match, analysts may be able to gain information through results produced by recognition software.
 This approach to understanding player's emotions during a match differs to previous standards that have used player's recollections after a game to understand their emotions.
@@
 
-Images from the Australian Open 2016 were provided by Tennis Australia, with goal being that the sample specified below is representative of the video files to be used for future facial recognition analysis:
+Images from the Australian Open 2016 were provided by Tennis Australia, with goal being that the sample is representative of the video files to be used for future facial recognition analysis:
 
@@
 
-Online demos were used to test viablity, Figure \@ref(fig:Trial-Image) depicts Bernard Tomic and the detected areas found.
+Online demos were used to test viability, Figure \@ref(fig:Trial-Image) depicts Bernard Tomic and the detected areas found.
 
@@
 Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a letter value plot (*** add in reference to Heik'e paper).
-A letter value plot is like a boxplot, but more suited to skewed data like this.
-(Both Microsoft and Google have a few eimages each where they have taken a long time to complete and these were removed from this plot.) The times are quite variable between APIs, with Skybiometry being the most consistently fast.
+A letter value plot is like a box plot, but more suited to skewed data like this.
+(Both Microsoft and Google have a few images each where they have taken a long time to complete and these were removed from this plot.) The times are quite variable between APIs, with Skybiometry being the most consistently fast.
 Microsoft and Animetrics are quite variable regardless of the number of faces found.
@@
 Most of the images take less than one second to process.
-Google had the highest maximum time of 4.936", format = "latex") #%>%
+Google had the highest maximum time of 4.936.", format = "latex") #%>%
  # add_header_above(c(" " = 1, "Group 1" = 5, "Group 2" = 5))
@@
 
-The manual tagging helped to provide a benchamark for faces found by APIs. The
+The manual tagging helped to provide a benchmark for faces found by APIs. The
 face detection rate indicated what attributes of an image or face were associated with face detection by an API. 
@@
 
-A logistic regression model was used to assess the characteristics of the face and scene affecting detection, with stepwise variable selection.
+A logistic regression model was used to assess the characteristics of the face and scene affecting detection, with step wise variable selection.
 The binary response was whether the face was detected or not, using the manually tagged data as the benchmark, and characteristics included the setting, angle of shot and player, background, lighting and player adornments.
@@
 
-*** The number of digits should be consistent, e.g. "-1" should be "-1.00". I don't know how to force this with the kable printing, but one way or another we have to.
+*** The number of digits should be consistent, e.g. "-1" should be "-1.00". I don't know how to force this with the kale printing, but one way or another we have to.
 
@@
 Situation had different effects on each API.
-Results for Google were most interestng in the shotangle had differing effects on the detection.
+Results for Google were most interesting in the shot angle had differing effects on the detection.
 
@@
 These are defined using the four points, marking the four corners of a rectangle.
-Figure \@ref(fig:FaceData) shows a barchart of the number of faces detected by each API.
+Figure \@ref(fig:FaceData) shows a bar chart of the number of faces detected by each API.
 The Google Vision API detected largest number of faces, much more than the other three APIs, and most closely matched the number recorded by manual tagging.
@@
 Face & 434 & 1861 & & Face & 1319 & 976\\
-NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
+No Face &527 & 787 & & No Face &638 & 676 \\\cline{1-3}\cline{5-7}
 \end{tabular}
@@
 
-Figure \@ref(fig:FaceUpset) is a set visualisation to examine the intersection of the APIs, and the manual annotations.
+Figure \@ref(fig:FaceUpset) is a set visualization to examine the intersection of the APIs, and the manual annotations.
 This is produced with the UpSetR [@UpSetR] package.
@@
 In image (b) the KIA logo was reported as a face. 
-In image (c), where logos on the player's and ballboy's shirts were returned as faces.
-In image (d) where there are a lot of crowd faces, if you look closely one of the detections is actully a fist (to the right on the center).
+In image (c), where logos on the player's and ball boy's shirts were returned as faces.
+In image (d) where there are a lot of crowd faces, if you look closely one of the detections is actually a fist (to the right on the center).
 
@@
 
-We then considered the characteristics of the images that the API found Potential Faces in.
-
-We then considered that there would be an uneven amount of faces with certain image attributes.
+The characteristics of the images that the API found Potential Faces in were considered.
+For example, there would is an uneven amount of faces with certain image attributes.
 These relationships can be explored in mosaics for the images that were all considered manually.
@@
 It can be seen that the largest portion of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
-This proportion is steady across most situations, from this we learn the situation may not be influencing the APIs rate of detection.
+This proportion is steady across most situations, from this it can be inferred the situation may not be influencing the APIs rate of detection.
 
-This stacked bar chart, Figure \@ref(fig:ICFigs) Plot c, allows consideration of the interaction between two image attributes.
-We are able to see that the background being the Logo Wall and the angle of Level is common to the highest amount of faces.
+Figure \@ref(fig:ICFigs) Plot c contains a stacked bar chart which allows consideration of the interaction between two image attributes.
+It can be seen that the background being the Logo Wall and the angle of Level is common to the highest amount of faces.
 There are also no images that were taken at an upward angle with the background of the court.
@@
 The long term goal is to better understand how the emotion's felt by a player during a match affect player performance.
-Ultimately we would aim to create a program that automated the collection of player emotion data from throughout a match.
+A long term aim would be to create a program that automated the collection of player emotion data from throughout a match.
 This information would be presented in a timeline that allowed match performance, in the form of points won, to be aligned with the emotions felt at certain times throughout.
@@
 
-Given that Google found many faces that did not match manually annotated face, we considered that we should check for manual errors.
-There is the possibility that we could create another app that shows the Facial Bounding Boxes identified by each program, this would allow the annotator to confirm manually whether or not these are faces.
+Given that Google found many faces that did not match manually annotated face,  manual errors were a possibility.
+To search for these Taipan could be extended to allow the face identified to be displayed and confirmed this would allow the annotator to confirm manually whether or not these are faces.
 

### 2017-12-12 paper/paper.Rmd
Mitch paper edit suggestions

@@
 This enables the performance to be assessed based on conditions, and the APIs were evaluated on their success rate at detecting these faces.
-The practicality of usage was also assessed via time taken to complete detection within an image.
+The possible obstacles of real time implementation were also assessed via the time taken to complete detection within an image.
 
@@
 The opportunity for researching this "inner game" presents itself with the hope of improving the performance, and coaching of, tennis players by improving their "mental game".
-By statistically analyzing the faces and expressions of players during a match insight may be gained into the effects of the mental state on the outcome of a match.
+By statistically analyzing the faces and expressions of players during a match, insight may be gained about the mental state of a player and the effects changes in the mental state have on the outcome of a match.
 The aim of this project is to develop methods to collect accurate information about the facial expressions of elite tennis athletes during match play.
 
-The performance of several popular facial recognition software's through their Application Programming Interfaces (APIs) is evaluated based on their performance on still images derived from broadcast videos of elite tennis matches.
+Application Programming Interfaces (APIs) have been used to evaluated the performance of several popular facial recognition software, on the still images derived from broadcast videos of elite tennis matches.
 While it is difficult to know the thoughts and feelings of a player during a match, analysts may be able to gain information through results produced by recognition software.
@@
 
-Making use of the recognition software's currently available presents a challenge as high performance sports are not the intended use.
-Their capabilities are often limited to their intended security and surveillance purposes.
-@Boston addresses the 'lack of robustness of current tools in unstructured environments' that this paper faces and applies to a sports environment.
+Most facial recoginiton software began with the intention of security applications. There are others, such as Facebook which links images of people with their profiles.
+This means the recognition software currently available was not intended to be used in fast paced, elite sport environment.
+It was believed that the capabilities of the software could be limited by their intended security and surveillance purposes.
+@Boston addresses the 'lack of robustness of current tools in unstructured environments' and this survey explores how detection performance is affected by situations that arise in elite tennis matches.
 
@@
 
-- 6406 images, 800x450px
+- 6406 images, 800 $\times$ 450px
 
-To produce the set of 6404 images, 5 minute segments were taken from 105 video files a still shot of the video was taken at every three seconds, for the length of each segment.
-The video file were the broadcast of the tennis Matches shown on the Seven Network during the Australian Open 2016.
+To produce the set of 6406 images, 5 minute segments were taken from 105 video files a still shot of the video was taken at every three seconds, for the length of each segment.
+The video files used were the broadcasts of the tennis matches shown on the Seven Network during the Australian Open 2016.
 The sample included an equal amount of females and males singles tennis matches.
@@
 The initial software to be considered was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications' [@Survey, pp.3].
-
 The selection criteria included the availability, speed, feature selection and whether images and/or videos could be presented for detection.
@@
 The report outlined that Animetrics [@Animetrics] required an 'image/face proportion should be at least 1:8 and that at least 64 pixels between eyes are required'. 
-
-SkyBiometry [@Skybiometry] is a 'spin-off of Neurotechnology' which was considered by Gorodnichy et al. an API that also allows for both detection and recognition.
-
-Companies who have recently expanded their API ranges were considered. Microsoft API[@Microsoft], provided by Microsoft Cognitive Services, and Google Vision API [@Google].
-
+SkyBiometry [@Skybiometry] is a 'spin-off of Neurotechnology' which was considered by Gorodnichy et al. [-@Survey].
+Companies who have recently expanded their API ranges were also considered.
+This search produced two of the software, Microsoft API [@Microsoft], provided by Microsoft Cognitive Services, and Google Vision API [@Google].
 Online demos were used to test viability, Figure \@ref(fig:Trial-Image) depicts Bernard Tomic and the detected areas found.
@@
 ```{r Trial-Image, fig.cap = "This image of Bernard Tomic was chosen as a trial image to be presented to each of the software before they were included in the research.
-Each colour represents a different API source.
+Each colour represents a different detection source.
 It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE, dev="jpeg", dpi=300}
@@
 ## Manual annotations
-
-A web based annotation tool was developed to allow image annotations that would capture the location of areas selected manually, and annotation of attributes for each face, and scene.
 
@@
 
+A web based annotation tool was developed to allow image annotations that would capture the location of areas selected manually, and annotation of attributes for each face, and scene.
 Specific information for each face within each scene was collected.
 To determine which of the, sometimes many, faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
-
 The faces of players were recorded if it showed their face at a minimum of 20 by 20 pixels.
@@
 
-The web app was created using Shiny [@shiny]. This has been expanded into an R package called taipan. A tool for annotating images in preparation for analysis.
-
-If there was a face in the image the annotator was able to highlight a section of the image to create a square 'Face Box'.
-This selection presented a set of Attributes questions to answer, and allowed information to be recorded for the face in the specific 'Face Box'.
-This recorded the x and y coordinates of the box drawn, and saved all the selections and the 'Face Box' coordinates to a CSV file.
-
-When a face was not visible in the scene only the scene attributes applied for that image.
-
-All the annotations for this sample were completed by one annotator to provide a consistent sample of faces annotated manually.
+The web app was created using the Shiny package for R [@shiny] and has been developed into an R package called taipan, as it is a Tool for Annotating Images in Preparation for ANalysis.
+If there was a face in the image the annotator was able to highlight that section of the image to contain the face.
+This selection activated a set of attributes questions for the annotator to answer, and allowed information to be recorded for the face.
+The records included the location of the box in the image, and all appropriate answers.
+When a face was not visible in the image only the scene attributes were applicable for that image.
+All of the annotations for this sample were completed by one annotator to provide a consistent sample of faces annotated manually.
 The initial decisions of what would be reasonably detected was made by several people.
@@
 
-The face recognition software allowed for access through a R [@R] script, calling the APIs using the httr[@httr] package.
+The face recognition software APIs were accessed via a R [@R] script, calling the APIs relied on the httr [@httr] package.
 The scripts looped through the images, individually posting a request to retrieve information provided and convert it into an appropriate format for analysis.
+Special handling was required due to the limits on requests per minute of Skybiometry and Microsoft, time-controlling and error management of the requests was incorporated for these APIs.
 
-Special handling was required due to the limits on requests per minute of Skybiometry and Microsoft, time-controlling the requests was incorporated for these APIs.
-
-Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a letter value plot (*** add in reference to Heik'e paper).
+Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a letter value plot [@letterValue].
 A letter value plot is like a box plot, but more suited to skewed data like this.
@@
 Some APIs also provided detailed information such as the estimated head angle, and locations of specific facial features.
-
-The manual tagging app resulted in two files, one containing information about the image, and the faces.
+The manual tagging app resulted in two files, one containing information about the scene, and the other contained information regarding the faces.
 
@@
 face detection rate indicated what attributes of an image or face were associated with face detection by an API. 
-Faces that were found by multiply APIs indicated the industry expectations for face presentation.
+Faces that were found by multiple APIs indicated either obvious facial features were visible or the APIs may be using similar criteria to detect faces.
 This application allowed for a broader range of angles, backgrounds and accessories that may have impacted detection.
@@
 
-A logistic regression model was used to assess the characteristics of the face and scene affecting detection, with step wise variable selection.
+A logistic regression model was used to assess the characteristics of the face and scene that may have affected the detection likelihood of the face.
+A step-wise variable selection method was used to find variables of significance for any of the APIs.
 The binary response was whether the face was detected or not, using the manually tagged data as the benchmark, and characteristics included the setting, angle of shot and player, background, lighting and player adornments.
-(*** Any other variables considered but not selected for any model?)
-A separate model was fit for each API.
+Variables that were not included denoted whether there was a graphic or live shot visible, the role of the person whose face was captured and whether or not there was a person in the image.
+detect
+A separate model was fit using the faces for each API.
 
@@
 
-Given that certain scene attribute combinations produced more facial recognition than other combinations we should consider limiting the sample of images sent to Google Vision API.
+Given that certain scene attribute combinations produced more facial recognition than other combinations a limit should be implemented for the sample of images sent to Google Vision API.
 This would not only reduce cost but also provide a greater level of detail of the emotions felt by a player during a match.
@@
 
-To undertake sentiment analysis, we would take the boxes of faces found in this set of images.
-Allowing each face a border of pixels, we would crop the images and produce an individual face image that would form the data set for emotion recognition.
-We also feel that incorporating audio information from the microphones worn by players may assist in sentiment analysis.
-By including this information we would be able to define differences between certain emotions that may not be able to be found by facial features only.
+To undertake sentiment analysis, the faces found in this set of images could be used.
+Allowing each face a border of pixels, images could be cropped and produce an individual face image that would form the data set for emotion recognition.
+Incorporating audio information from the microphones worn by players may assist in sentiment analysis.
+By including this information differences between certain emotions that may not be able to be found by facial features only.
 

### 2017-12-12 paper/paper.Rmd
working on image characteristics

@@
 
-```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually.
-The stacked bar charts show the amount of faces captured at certain angles, or situation.\\label{fig:ICFigs}"}
+```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (a) Angle of face capture, (b) court situation, (c) angle of capture by background, and (d) situtation of capture by background.
+Most face captures occurred at a level angle, and this produces slightly better detection.
+Most situtation face captures are close up, but the detection rate is identical regardless of situation.
+Most level angles had the logo wall in the background, while most birds-eye had the court as background, as we would expect.
+Close ups were mostly against the logo wall.
+\\label{fig:ICFigs}"}
 
@@
 
-grid.arrange(plots1, plots2, nrow=2)
+grid.arrange(plots2, plots1, nrow=2)
 
@@
 ## Image characteristics
+
+There were several characteristics of the image recorded during manual tagging, as listed in Table \@ref(tab:Scene-Attributes-Table).
+This section examines the prevalence of these characteristics in the data collection.
 

### 2017-12-14 paper/paper.Rmd
small change to image char
Latex table edits

--- 2017-12-12 paper/paper.Rmd
@@
 
-*** (1) Check caption sentences finish with "." (2) Check spelling (3) Check no referring to tables and figures in the text like "the table below ..." or the "figure above ..." (4) Check all the writing is in third person, remove "We then ..." (5) One sentence paragraphs should be very rarely used, and I suspect there are too many in the current draft.
-Check if the orphan sentence better belongs with the prior or after paragraph.
-
 #Introduction
@@
   facet_wrap(~type) +
-  scale_y_continuous("System time (ms)", 
+  scale_y_continuous("System time (seconds)", 
     breaks=seq(0, .08, .02), limits=c(0, 0.08)) +
@@
 
-AM <- table(FacesAPI$Manual, FacesAPI$Animetrics, dnn = c("Manual", "Animetrics"))
-GM <- table(FacesAPI$Manual, FacesAPI$Google, dnn = c("Manual", "Google"))
-MM <- table(FacesAPI$Manual, FacesAPI$Microsoft, dnn = c("Manual", "Microsoft"))
-SM <- table(FacesAPI$Manual, FacesAPI$Skybiometry, dnn = c("Manual", "Skybiometry"))
+GM <- CrossTable(FacesAPI$Manual, FacesAPI$Google)
+MM <- CrossTable(FacesAPI$Manual, FacesAPI$Microsoft)
+SM <- CrossTable(FacesAPI$Manual, FacesAPI$Skybiometry)
+AM <- CrossTable(FacesAPI$Manual, FacesAPI$Animetrics)
 ```
@@
 \begin{table}[htp]
-%\parbox{.5\linewidth}{
-\caption{Contingency tables of each API capture against manual tagging. Interestingly all APIs reported faces that would not be considered faces by manual inspection.}
+\centering
+\caption{Table of the amount and proportion of faces each API captured, by manual tagging.}
 \label{tab:facecounts}
-\centering
-\begin{tabular}{ccccccc} \cline{1-3}\cline{5-7} 
-\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
-Manual & Face & No Face & & Manual & Face & No Face\\ 
-%heading
-\cline{1-3}\cline{5-7} 
-Face & 434 & 1861 & & Face & 1319 & 976\\
-No Face &527 & 787 & & No Face &638 & 676 \\\cline{1-3}\cline{5-7}
-\end{tabular}
-\\[1.5ex]
-\begin{tabular}{ccccccc}\\\cline{1-3}\cline{5-7} 
-\multicolumn{3}{c}{Microsoft}&&\multicolumn{3}{c}{Skybiometry}\\
-\cline{1-3}\cline{5-7}
-Manual & Face & No Face & & Manual & Face & No Face\\ 
-%heading
-\cline{1-3}\cline{5-7} 
-Face & 565 & 1730 & & Face & 493 & 1802\\
-No Face &505 & 809 & & No Face &512 & 802 \\\cline{1-3}\cline{5-7}
+\begin{tabular}{lllll}\\\cline{1-5}
+            & \multicolumn{2}{l}{Faces found} & \multicolumn{2}{l}{Non-faces detected as faces} \\\cline{1-5}
+
+            & Count        & Proportion       & Count                & Proportion               \\\cline{1-5}
+Google      & 1319         & 0.57             & 638                  & 0.49                     \\
+Microsoft   & 565          & 0.24             & 505                  & 0.38                     \\
+Skybiometry & 493          & 0.22             & 512                  & 0.39                     \\
+Animetrics  & 434          & 0.19             & 527                  & 0.40\\ \cline{1-5}
 \end{tabular}
 \end{table}
-
-*** I've decided that these should be proportions.
 
@@
 
-prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)
-
+#prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)
 ```
@@
   round(glassesTab[2,5]/glassesTab[2,1],2)))
+```
 
-pander(glassesdf, caption = "Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces.
+\begin{table}[ht]
+\centering
+%\parbox{.5\linewidth}{
+\caption{Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces.
 API's unaffected glasses will have similar proportions for both categories.
 Animetrics had the biggest proportion difference, and thus, most affected.
-Google is the least affected.")
-```
+Google is the least affected.}
+\label{tab:glasses}
+\begin{tabular}{ccccc}
+\hline 
+ & Animetrics & Google & Microsoft & Skybiometry\\ 
+\hline
+Glasses & 0.08 & 0.43 & 0.14 & 0.12 \\
+No Glasses & 0.21 & 0.60 & 0.26 & 0.23\\
+\hline
+\end{tabular}
+\end{table}
 

### 2017-12-14 paper/paper.Rmd
Removed face count bar chart

@@
 
-Each API returned areas in the image that indicated the face location.
-These are defined using the four points, marking the four corners of a rectangle.
-Figure \@ref(fig:FaceData) shows a bar chart of the number of faces detected by each API.
-The Google Vision API detected largest number of faces, much more than the other three APIs, and most closely matched the number recorded by manual tagging.
-
-```{r FaceData, fig.cap = "\\label{fig:FaceData}  The bar chart of the number of faces detected by each API.
-Google's Facial Recognition API recognized almost 1000 more faces than the next best API, Microsoft."}
-
-ggplot(amin, aes(x = type, fill=type)) + 
-  geom_bar(position="dodge") +
-  xlab("Facial Recognition APIs") +
-  scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +
-  ylab("Number of Faces") + 
-  guides(fill=FALSE) +
-  labs(caption="") + scale_fill_manual(values=type.colours)
-```
-
-### API comparison
-
-Table \@ref(tab:facecounts) cross-tabulates the faces found by each API relative to the manually tagged faces.
+Table \@ref(tab:facecounts) shows the amount of faces found by each API relative to the manually tagged faces.
 For a perfect match with the manually tagged faces, the off-diagonal elements should be zero.

### 2017-12-14 paper/paper.Rmd
Spell check

@@
 
-Most facial recoginiton software began with the intention of security applications. There are others, such as Facebook which links images of people with their profiles.
+Most facial recognition software began with the intention of security applications. There are others, such as Facebook which links images of people with their profiles.
 This means the recognition software currently available was not intended to be used in fast paced, elite sport environment.
@@
 Of those without glasses only 26% wore headwear.
-This may be influenced by weather and sunlight on the court during Australian Ope n matches.
+This may be influenced by weather and sunlight on the court during Australian Open matches.
 

### 2017-12-14 paper/paper.Rmd
Upset caption altered

@@
 The Bar Chart shows the faces that were recognised by multiple API or found manually.
-The largest group, with 809 faces, is faces only found by Manual annotations.
+The largest group, with 946 faces, is faces only found by Manual annotations.
 The following group were the 716 faces recognized both Manually and by the Google API.
-These combinations may give some indication as to the circumstances when some APIs perform better than others."}
+These combinations give insight to the algorithm specifications as some APIs certain faces when others do not."}
 createUpSet(aminFaces)

### 2017-12-14 paper/paper.Rmd
Detection rates edits

@@
 
-Table \@ref(tab:facecounts) shows the amount of faces found by each API relative to the manually tagged faces.
-For a perfect match with the manually tagged faces, the off-diagonal elements should be zero.
-Google has the closest match to the manual tagging, and Skybiometry, which was the fastest to run, performed very badly.
+Table \@ref(tab:facecounts) shows the amount of faces found by each API relative to whether or not the faces were tagged manually.
+Google has the closest match to the manual tagging.
 It is interesting to see the high proportion of faces detected by the APIs that were not considered to be faces by manual tagging.
-
-The mismatches were manually examined, and showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces found by Google but not tagged manually were actually faces, but were crowd members.
-They would need to be used, for the long term purpose of the study, to detect and tag players' emotions during a match.
-
-Comparatively, visual inspection of the `r amin %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were actually very unusual results, which are discussed later.
 
@@
 \end{table}
+
+The mismatches were manually examined, and showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces found by Google but not tagged manually were actually faces, but were crowd members.
+They would need to be used, for the long term purpose of the study, to detect and tag players' emotions during a match.
+
+Comparatively, visual inspection of the `r amin %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were unusual areas to be considered faces, this is discussed in the false discoveries section.
 

### 2017-12-14 paper/paper.Rmd
caption edits

@@
 
-```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual: (a) one of the detected face is a player's back, (b) the KIA logo on the net is detected as a face, (c) is very interesting as the player's face was found, but the shirts of both the player and ball boy were reported as faces, (d) had a lot more faces than many images but Animetrics also found a fist (to the right on the center) that it considered a face.
-\\label{fig:UnusualImages}", dev="jpeg", dpi=300}
+```{r UnusualImages, fig.cap = "Four images in which Animetrics located unusual faces. \\label{fig:UnusualImages}", dev="jpeg", dpi=300}
 i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(a)")

### 2017-12-14 paper/paper.Rmd
Mosaic figure

@@
 
-```{r MosaicShotangle, fig.cap = "\\label{fig:Mosaic}", eval=FALSE}
+```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually.\\label{fig:ICFigs}"}
+
 aminFaces$shotangle <- factor(aminFaces$shotangle, 
@@
 
-MosaicShotangle <- ggplot(data=aminFaces) + 
+MosSaMm <- ggplot(data=aminFaces) + 
   geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
@@
   ggtitle("(a)")
-```
 
-```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}", eval=FALSE}
 aminFaces$situation <- factor(aminFaces$situation, levels = c("Not player",
@@
 
-MosaicSit <- ggplot(data=aminFaces) + 
+MosSitMm <- ggplot(data=aminFaces) + 
   geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
@@
   ggtitle("(b)")
-```
 
-```{r sbbgshot, fig.cap = "\\label{fig:sbbgshot}", eval=FALSE}
-
-sbbgshot <- ggplot(data=aminFaces) +
+MosSaBg <- ggplot(data=aminFaces) +
    geom_mosaic(aes(x=product(shotangle), fill = bg)) +#, 
@@
 
-```
-
-```{r sbbgsit, fig.cap = "\\label{fig:sbbgsit}", eval=FALSE}
-
-sbbgsit <- ggplot(data=aminFaces) +
-   geom_mosaic(aes(x=product(situation), fill = bg)) + #, 
-            #position = position_fill(reverse = TRUE), 
-            #na.rm=TRUE) +
-   scale_x_productlist(labels=c("Not player"="Not player",
-          "Match play"="Match play",
-          "Off court"="Off court",
-          "Crowd"="Crowd",
-          "Close-up"="Close-up")) +
-  coord_flip() +
-  guides(fill = guide_legend(title="Background")) +
-  labs(caption="") +
-  ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none") +
-  ggtitle("(d)")
-```
-
-```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually.
-The stacked bar charts show the amount of faces captured at certain angles, or situation.\\label{fig:ICFigs}"}
-
-aminFaces$shotangle <- factor(aminFaces$shotangle, 
-                              levels = c("Birds Eye","Upward","Level"))
-aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
-
-MosaicShotangle <- ggplot(data=aminFaces) + 
-  geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
-  #geom_text(aes(label="test", x=1, y=0.6)) +
-  scale_fill_brewer(palette="Dark2") +
-  guides(fill = guide_legend(title="API matches manual"))  +
-  labs(caption="") + 
-  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
-                            "Upward"="Upward \nAngle",
-                            "Level" =
-                            "Level")) + coord_flip() +
-  ylab("Proportion of faces") + xlab("Angle of face capture") + 
-  theme(legend.position = "none") + 
-  ggtitle("(a)") 
-aminFaces$situation <- factor(aminFaces$situation, levels = c("Not player",
-          "Match play",
-          "Off court",
-          "Crowd",
-          "Close-up"))
-aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
-
-MosaicSit <- ggplot(data=aminFaces) + 
-  geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
-  scale_fill_brewer(palette="Dark2") +
-  guides(fill = guide_legend(title="API match manual"))  +
-  labs(caption="") + 
-  scale_x_productlist(labels=c("Not player"="Not player",
-          "Match play"="Match play",
-          "Off court"="Off court",
-          "Crowd"="Crowd",
-          "Close-up"="Close-up")) +
-  coord_flip() +
-  ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none")  +
-  ggtitle("(b)")
-
-sbbgshot <- ggplot(data=aminFaces) +
-   geom_mosaic(aes(x=product(shotangle), fill = bg)) +#, 
-            #position = position_fill(reverse = TRUE), 
-            #na.rm=TRUE) + 
-  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
-                            "Upward"="Upward",
-                            "Level" =
-                            "Level"))+
-  coord_flip() +
-  guides(fill = guide_legend(title="Background")) +
-  labs(caption="") +
-  ylab("Proportion of faces") + xlab("Angle of face capture") + theme(legend.position = "none") +
-  ggtitle("(c)")
-
-sbbgsit <- ggplot(data=aminFaces) +
+MosSitBg <- ggplot(data=aminFaces) +
    geom_mosaic(aes(x=product(situation), fill = bg)) + #, 
@@
 
-g1 <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
+g1 <- ggplotGrob(MosSaMm + theme(legend.position="bottom"))$grobs
 legend1 <- g1[[which(sapply(g1, function(x) x$name) == "guide-box")]]
@@
 
-plots1 <- arrangeGrob(sbbgshot, sbbgsit, ncol=2)
+plots1 <- arrangeGrob(MosSaMm, MosSitMm, ncol=2)
 plots1 <- arrangeGrob(plots1, legend1, nrow=2, heights = unit.c(unit(1, "npc") - lheight1, lheight1))
 
-g2 <- ggplotGrob(MosaicShotangle + theme(legend.position="bottom"))$grobs
+g2 <- ggplotGrob(MosSaBg + theme(legend.position="bottom"))$grobs
 legend2 <- g2[[which(sapply(g2, function(x) x$name) == "guide-box")]]
@@
 
-plots2 <- arrangeGrob(MosaicShotangle, MosaicSit, ncol=2)
+plots2 <- arrangeGrob(MosSaBg, MosSitBg, ncol=2)
 plots2 <- arrangeGrob(plots2, legend2, nrow=2, heights = unit.c(unit(1, "npc") - lheight2, lheight2))
@@
 
-The characteristics of the images that the API found Potential Faces in were considered.
-For example, there would is an uneven amount of faces with certain image attributes.
+The characteristics of the images were recorded in the manual tagging process and there are uneven amounts of faces with certain image attributes.
 These relationships can be explored in mosaics for the images that were all considered manually.
-The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
+The scene information was tallied and the combinations of these features were compared to how many potential faces were found with the combination of scene attributes.
 
-This showed that crowd members faces were often recognized, this is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
+This showed that crowd members faces were often recognized which is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
 It also allowed for an increase in understanding how attributes of a face or image impact on the API detection.
 
-The colours in the mosaic (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
+The colours in the mosaic \@ref(fig:ICFigs) (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
 There is a greater proportion of API faces that matched the faces found manually than those that did not match.
 However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually.
-The most common faces in the set were those captured Level to player's faces, these faces were often recognised by the APIs as well.
+The most common faces in the set were those captured level to player's faces, these faces were often recognised by the APIs as well.
 
-The mosaic (b) in \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
+The mosaic \@ref(fig:ICFigs) (b) in Figure \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
 It contrasts the proportion of the images captured in each situation that either did or did not match the faces annotated manually.
-It can be seen that the largest portion of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
-This proportion is steady across most situations, from this it can be inferred the situation may not be influencing the APIs rate of detection.
+It can be seen that the largest amount of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
+This proportion is steady across most situations, it can be inferred the situation may not be influencing the APIs rate of detection.
 
-Figure \@ref(fig:ICFigs) Plot c contains a stacked bar chart which allows consideration of the interaction between two image attributes.
-It can be seen that the background being the Logo Wall and the angle of Level is common to the highest amount of faces.
+Figure \@ref(fig:ICFigs) Plot c contains a mosaic which allows consideration of the interaction between two image attributes.
+It can be seen that the background being the logo wall and the angle of level is common to the highest amount of faces.
 There are also no images that were taken at an upward angle with the background of the court.
 
-This stacked bar chart, Figure \@ref(fig:ICFigs) Plot d, allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
+This mosiac, Figure \@ref(fig:ICFigs) Plot d, allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
 As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd.

### 2017-12-14 paper/paper.Rmd
Grammar edits

@@
 
-Figure \@ref(fig:ICFigs) Plot c contains a mosaic which allows consideration of the interaction between two image attributes.
+Figure \@ref(fig:ICFigs) (c) contains a mosaic which allows consideration of the interaction between two image attributes.
 It can be seen that the background being the logo wall and the angle of level is common to the highest amount of faces.
@@
 
-This mosiac, Figure \@ref(fig:ICFigs) Plot d, allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
+This mosiac, Figure \@ref(fig:ICFigs) (d), allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
 As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd.
@@
 
-Considering the images used during our study were stills derived from Broadcast video files, it would be useful to extend further research to deal with the video files directly.
+Considering the images used during our study were stills derived from broadcast video files, it would be useful to extend further research to deal with the video files directly.
 The Google Vision API which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.
@@
 
-Given that Google found many faces that did not match manually annotated face,  manual errors were a possibility.
+Google found many faces that did not match manually annotated faces, this showed manual errors were a possibility.
 To search for these Taipan could be extended to allow the face identified to be displayed and confirmed this would allow the annotator to confirm manually whether or not these are faces.
 
-Given that certain scene attribute combinations produced more facial recognition than other combinations a limit should be implemented for the sample of images sent to Google Vision API.
-This would not only reduce cost but also provide a greater level of detail of the emotions felt by a player during a match.
+Given that certain scene attribute combinations produced more successful facial recognition than other combinations, a limit should be implemented for the sample of images sent to Google Vision API.
+This would not help to reduce cost.
 To provide a greater level of information at all points in a match it would be beneficial to derive images from a single camera feed.
-This feed should match the scene attributes that provided the most Google faces.
+This feed should match the scene attributes that provided was most successful for Google to return faces.
 
@@
 
-- Animetrics: This name used throughout the paper refers to the Animetrics Face Recognition API, FaceR API by @Animetrics.
+- Animetrics: Animetrics Face Recognition API, FaceR API by @Animetrics.
 
-- Google: @Google Refers to the Google Cloud Vision API
+- Google: Google Cloud Vision API [-@Google]
 
-- Microsoft: This has been used to refer to the Microsoft Azure Cognitive Services Face API, published by @Microsoft.
+- Microsoft: Microsoft Azure Cognitive Services Face API, published by @Microsoft.
 
-- Skybiometry: @Skybiometry References the spin off detection and recognition software of Neurotechnology.
+- Skybiometry: @Skybiometry the spin off detection and recognition software of Neurotechnology.
 

### 2017-12-14 paper/paper.Rmd
Face ID allocation by intersecting area explained

@@
 The data needed for our analysis was organised by source, separate files for each of the four APIs.
-They contained the information on the location of the faces found in the images and the time taken to find them.
+They contained the information on the location of the faces found in the images, and the time taken to find them.
 Some APIs also provided detailed information such as the estimated head angle, and locations of specific facial features.
 The manual tagging app resulted in two files, one containing information about the scene, and the other contained information regarding the faces.
+
+The location and size of the boxes around the faces were recorded, these values were used to see if a particular identified face box matched a manually identified face, or a region found by another software.
+Every face found in an image manually, or by any API was compared.
+From their locations the intersecting area between them was found.
+When the ratio of this intersecting area to total area was greater than 0.1 the IDs were altered to reflect the two faces would be considered the same face.
+This allowed comparison of the identification areas on the same face, as well as contrast the identified faces of each software.
 

### 2017-12-14 paper/paper.Rmd
Image characteristics section

@@
 
-```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually.\\label{fig:ICFigs}"}
+```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (a) Angle of face capture, (b) court situation, (c) angle of capture by background, and (d) situtation of capture by background.
+Most face captures occurred at a level angle, and this produces slightly better detection.
+Most situtation face captures are close up, but the detection rate is identical regardless of situation.
+Most level angles had the logo wall in the background, while most birds-eye had the court as background, as we would expect.
+Close ups were mostly against the logo wall.
+\\label{fig:ICFigs}"}
 
@@
 ## Image characteristics
+
+There were several characteristics of the image recorded during manual tagging, as listed in Table \@ref(tab:Scene-Attributes-Table).
+This section examines the prevalence of these characteristics in the data collection.
+Figure \@ref(fig:ICFigs) shows the relationships of a subset of characteristics, using mosaic plots.
 

### 2017-12-15 paper/paper.Rmd
lots of changes by Di

@@
 }
+
 ```
@@
 The possible obstacles of real time implementation were also assessed via the time taken to complete detection within an image.
+
+*** (1) Check caption sentences finish with "." (2) Check spelling (3) Check no referring to tables and figures in the text like "the table below ..." or the "figure above ..." (4) Check all the writing is in third person, remove "We then ..." (5) One sentence paragraphs should be very rarely used, and I suspect there are too many in the current draft.
+Check if the orphan sentence better belongs with the prior or after paragraph.
 
@@
 
-Most facial recognition software began with the intention of security applications. There are others, such as Facebook which links images of people with their profiles.
+Most facial recoginiton software began with the intention of security applications. There are others, such as Facebook which links images of people with their profiles.
 This means the recognition software currently available was not intended to be used in fast paced, elite sport environment.
@@
   facet_wrap(~type) +
-  scale_y_continuous("System time (seconds)", 
+  scale_y_continuous("System time (ms)", 
     breaks=seq(0, .08, .02), limits=c(0, 0.08)) +
@@
 The data needed for our analysis was organised by source, separate files for each of the four APIs.
-They contained the information on the location of the faces found in the images, and the time taken to find them.
+They contained the information on the location of the faces found in the images and the time taken to find them.
 Some APIs also provided detailed information such as the estimated head angle, and locations of specific facial features.
 The manual tagging app resulted in two files, one containing information about the scene, and the other contained information regarding the faces.
-
-The location and size of the boxes around the faces were recorded, these values were used to see if a particular identified face box matched a manually identified face, or a region found by another software.
-Every face found in an image manually, or by any API was compared.
-From their locations the intersecting area between them was found.
-When the ratio of this intersecting area to total area was greater than 0.1 the IDs were altered to reflect the two faces would be considered the same face.
-This allowed comparison of the identification areas on the same face, as well as contrast the identified faces of each software.
 
@@
 
-### Detection rates
+### Detection rates and API comparison
 
-Table \@ref(tab:facecounts) shows the amount of faces found by each API relative to whether or not the faces were tagged manually.
-Google has the closest match to the manual tagging.
-It is interesting to see the high proportion of faces detected by the APIs that were not considered to be faces by manual tagging.
+Each API returned areas in the image that indicated the face location. These are defined using the four points, marking the four corners of a rectangle.
+
+```{r FaceData, eval=FALSE, fig.cap = "\\label{fig:FaceData}  The bar chart of the number of faces detected by each API.
+Google's Facial Recognition API recognized almost 1000 more faces than the next best API, Microsoft."}
+
+ggplot(amin, aes(x = type, fill=type)) + 
+  geom_bar(position="dodge") +
+  xlab("Facial Recognition APIs") +
+  scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +
+  ylab("Number of Faces") + 
+  guides(fill=FALSE) +
+  labs(caption="") + scale_fill_manual(values=type.colours)
+```
+
+Table \@ref(tab:facecounts) displays the proportion of the manually tagged faces that the APIs detected.
+Google had by far the best detection rate.
+In addition, the APIs also detected non-faces, in images that produced no manually tagged faces.
+Google had the highest of these, and the detections were for the most part helpful, primarily of tiny faces in the crowd, that were ignored by manual tagging.
+They would not be needed for the long term purpose of the study, to detect and tag players' emotions during a match.
+
+In comparison, examining the `r amin %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` images in which Animetrics detected faces, not reported manually, revealed surprising results, which are discussed in more detail later.
 
@@
 
-GM <- CrossTable(FacesAPI$Manual, FacesAPI$Google)
-MM <- CrossTable(FacesAPI$Manual, FacesAPI$Microsoft)
-SM <- CrossTable(FacesAPI$Manual, FacesAPI$Skybiometry)
-AM <- CrossTable(FacesAPI$Manual, FacesAPI$Animetrics)
+AM <- table(FacesAPI$Manual, FacesAPI$Animetrics, dnn = c("Manual", "Animetrics"))
+GM <- table(FacesAPI$Manual, FacesAPI$Google, dnn = c("Manual", "Google"))
+MM <- table(FacesAPI$Manual, FacesAPI$Microsoft, dnn = c("Manual", "Microsoft"))
+SM <- table(FacesAPI$Manual, FacesAPI$Skybiometry, dnn = c("Manual", "Skybiometry"))
 ```
@@
 \begin{table}[htp]
+%\parbox{.5\linewidth}{
+\caption{Proportion of API matches with the 2295 manually tagged faces, and faces detected in the 1314 images with no manually tagged faces.}
+\bigskip
+\label{tab:facecounts}
 \centering
-\caption{Table of the amount and proportion of faces each API captured, by manual tagging.}
-\label{tab:facecounts}
-\begin{tabular}{lllll}\\\cline{1-5}
-            & \multicolumn{2}{l}{Faces found} & \multicolumn{2}{l}{Non-faces detected as faces} \\\cline{1-5}
-
-            & Count        & Proportion       & Count                & Proportion               \\\cline{1-5}
+\begin{tabular}{|l|rr|rr|}  \hline
+& \multicolumn{2}{r|}{Faces found}&\multicolumn{2}{r|}{Non-faces found}\\\cline{2-5}
+API & Count & Prop & Count & Prop \\\hline
 Google & 1319 & 0.57 & 638 & 0.49 \\
-Microsoft   & 565          & 0.24             & 505                  & 0.38                     \\
-Skybiometry & 493          & 0.22             & 512                  & 0.39                     \\
-Animetrics  & 434          & 0.19             & 527                  & 0.40\\ \cline{1-5}
+Microsoft & 565 & 0.25 & 505 & 0.38 \\
+Skybiometry & 493 & 0.21 & 512 & 0.39 \\
+Animetrics & 434 & 0.19 & 527 & 0.40 \\\hline
 \end{tabular}
@@
 
-The mismatches were manually examined, and showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces found by Google but not tagged manually were actually faces, but were crowd members.
-They would need to be used, for the long term purpose of the study, to detect and tag players' emotions during a match.
+```{r FaceUpSet, fig.cap = "\\label{fig:FaceUpset} Set visualization, to examine intersections between API and manual face detections:  bar charts show counts, by API (lower left) and for combinations (main part of plot), and dot display (bottom) indicates the group intersections.
+All five way intersections are examined, but only the first few have large counts.
+The largest group is the manual tagging with 946 faces uniquely identified.
+The intersection between manual tagging and Google is 716 faces.
+The intersection of all four APIs and manual tagging is fourth highest, at 342."}
+setdata <- aminFaces %>% 
+  mutate(count = 1) %>%
+  select(type, FaceID, count) %>%
+  separate(FaceID, c("id1", "id2", "API")) %>%
+  unite(id, c("id1", "id2")) %>%
+  spread(API, count, fill=0) %>% 
+  arrange(id) %>% 
+  group_by(id) %>%
+  summarise(Animetrics=as.integer(sum(An)), 
+            Google=as.integer(sum(Go)), 
+            Manual=as.integer(sum(Ma)),
+            Microsoft=as.integer(sum(Mi)), 
+            Skybiometry=as.integer(sum(Sk)))
 
-Comparatively, visual inspection of the `r amin %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were unusual areas to be considered faces, this is discussed in the false discoveries section.
+setdata <- setdata %>% mutate(id=factor(id)) 
+setdata <- as.data.frame(setdata)
 
-```{r FaceUpSet, fig.cap = "\\label{fig:FaceUpset} Faces Per API Combination.
-The Bar Chart shows the faces that were recognised by multiple API or found manually.
-The largest group, with 946 faces, is faces only found by Manual annotations.
-The following group were the 716 faces recognized both Manually and by the Google API.
-These combinations give insight to the algorithm specifications as some APIs certain faces when others do not."}
-createUpSet(aminFaces)
+upset(setdata, order.by="freq")
+# colsum <- apply(setdata[,-1], 2, sum)
+# rowsum <- apply(setdata[,-1], 1, sum)
+# onlyone <- setdata[rowsum==1,] 
+# apply(onlyone[,-1], 2, sum)
 ```
@@
 
-```{r UnusualImages, fig.cap = "Four images in which Animetrics located unusual faces. \\label{fig:UnusualImages}", dev="jpeg", dpi=300}
+```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual: (a) one of the detected face is a player's back, (b) the KIA logo on the net is detected as a face, (c) is very interesting as the player's face was found, but the shirts of both the player and ball boy were reported as faces, (d) had a lot more faces than many images but Animetrics also found a fist (to the right on the center) that it considered a face.
+\\label{fig:UnusualImages}", dev="jpeg", dpi=300}
 i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(a)")
@@
 
-```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (a) Angle of face capture, (b) court situation, (c) angle of capture by background, and (d) situtation of capture by background.
-Most face captures occurred at a level angle, and this produces slightly better detection.
-Most situtation face captures are close up, but the detection rate is identical regardless of situation.
-Most level angles had the logo wall in the background, while most birds-eye had the court as background, as we would expect.
-Close ups were mostly against the logo wall.
-\\label{fig:ICFigs}"}
-
+```{r MosaicShotangle, fig.cap = "\\label{fig:Mosaic}", eval=FALSE}
 aminFaces$shotangle <- factor(aminFaces$shotangle, 
@@
 
-MosSaMm <- ggplot(data=aminFaces) + 
+MosaicShotangle <- ggplot(data=aminFaces) + 
   geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
@@
   ggtitle("(a)") 
+```
 
+```{r MosaicSit, fig.cap = "\\label{fig:MosaicSit}", eval=FALSE}
 aminFaces$situation <- factor(aminFaces$situation, levels = c("Not player",
@@
 
-MosSitMm <- ggplot(data=aminFaces) + 
+MosaicSit <- ggplot(data=aminFaces) + 
+  geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
+  scale_fill_brewer(palette="Dark2") +
+  guides(fill = guide_legend(title="API match manual"))  +
+  labs(caption="") + 
+  scale_x_productlist(labels=c("Not player"="Not player",
+          "Match play"="Match play",
+          "Off court"="Off court",
+          "Crowd"="Crowd",
+          "Close-up"="Close-up")) +
+  coord_flip() +
+  ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none")  +
+  ggtitle("(b)")
+```
+
+```{r sbbgshot, fig.cap = "\\label{fig:sbbgshot}", eval=FALSE}
+
+sbbgshot <- ggplot(data=aminFaces) +
+   geom_mosaic(aes(x=product(shotangle), fill = bg)) +#, 
+            #position = position_fill(reverse = TRUE), 
+            #na.rm=TRUE) + 
+  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
+                            "Upward"="Upward",
+                            "Level" =
+                            "Level"))+
+  coord_flip() +
+  guides(fill = guide_legend(title="Background")) +
+  labs(caption="") +
+  ylab("Proportion of faces") + xlab("Angle of face capture") + theme(legend.position = "none") +
+  ggtitle("(c)")
+
+```
+
+```{r sbbgsit, fig.cap = "\\label{fig:sbbgsit}", eval=FALSE}
+
+sbbgsit <- ggplot(data=aminFaces) +
+   geom_mosaic(aes(x=product(situation), fill = bg)) + #, 
+            #position = position_fill(reverse = TRUE), 
+            #na.rm=TRUE) +
+   scale_x_productlist(labels=c("Not player"="Not player",
+          "Match play"="Match play",
+          "Off court"="Off court",
+          "Crowd"="Crowd",
+          "Close-up"="Close-up")) +
+  coord_flip() +
+  guides(fill = guide_legend(title="Background")) +
+  labs(caption="") +
+  ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none") +
+  ggtitle("(d)")
+```
+
+```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (a) Angle of face capture, (b) court situation, (c) angle of capture by background, and (d) situtation of capture by background.
+Most face captures occurred at a level angle, and this produces slightly better detection.
+Most situtation face captures are close up, but the detection rate is identical regardless of situation.
+Most level angles had the logo wall in the background, while most birds-eye had the court as background, as we would expect.
+Close ups were mostly against the logo wall.
+\\label{fig:ICFigs}"}
+
+aminFaces$shotangle <- factor(aminFaces$shotangle, 
+                              levels = c("Birds Eye","Upward","Level"))
+aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
+
+MosaicShotangle <- ggplot(data=aminFaces) + 
+  geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
+  #geom_text(aes(label="test", x=1, y=0.6)) +
+  scale_fill_brewer(palette="Dark2") +
+  guides(fill = guide_legend(title="API matches manual"))  +
+  labs(caption="") + 
+  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
+                            "Upward"="Upward \nAngle",
+                            "Level" =
+                            "Level")) + coord_flip() +
+  ylab("Proportion of faces") + xlab("Angle of face capture") + 
+  theme(legend.position = "none") + 
+  ggtitle("(a)") 
+aminFaces$situation <- factor(aminFaces$situation, levels = c("Not player",
+          "Match play",
+          "Off court",
+          "Crowd",
+          "Close-up"))
+aminFaces$matchesManual <- factor(aminFaces$matchesManual, levels=c(TRUE, FALSE))
+
+MosaicSit <- ggplot(data=aminFaces) + 
   geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
@@
 
-MosSaBg <- ggplot(data=aminFaces) +
+sbbgshot <- ggplot(data=aminFaces) +
    geom_mosaic(aes(x=product(shotangle), fill = bg)) +#, 
@@
 
-MosSitBg <- ggplot(data=aminFaces) +
+sbbgsit <- ggplot(data=aminFaces) +
    geom_mosaic(aes(x=product(situation), fill = bg)) + #, 
@@
 
-g1 <- ggplotGrob(MosSaMm + theme(legend.position="bottom"))$grobs
+g1 <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
 legend1 <- g1[[which(sapply(g1, function(x) x$name) == "guide-box")]]
@@
 
-plots1 <- arrangeGrob(MosSaMm, MosSitMm, ncol=2)
+plots1 <- arrangeGrob(sbbgshot, sbbgsit, ncol=2)
 plots1 <- arrangeGrob(plots1, legend1, nrow=2, heights = unit.c(unit(1, "npc") - lheight1, lheight1))
 
-g2 <- ggplotGrob(MosSaBg + theme(legend.position="bottom"))$grobs
+g2 <- ggplotGrob(MosaicShotangle + theme(legend.position="bottom"))$grobs
 legend2 <- g2[[which(sapply(g2, function(x) x$name) == "guide-box")]]
@@
 
-plots2 <- arrangeGrob(MosSaBg, MosSitBg, ncol=2)
+plots2 <- arrangeGrob(MosaicShotangle, MosaicSit, ncol=2)
 plots2 <- arrangeGrob(plots2, legend2, nrow=2, heights = unit.c(unit(1, "npc") - lheight2, lheight2))
 
-grid.arrange(plots1, plots2, nrow=2)
+grid.arrange(plots2, plots1, nrow=2)
 
@@
 
-The characteristics of the images were recorded in the manual tagging process and there are uneven amounts of faces with certain image attributes.
+The characteristics of the images that the API found Potential Faces in were considered.
+For example, there would is an uneven amount of faces with certain image attributes.
 These relationships can be explored in mosaics for the images that were all considered manually.
-The scene information was tallied and the combinations of these features were compared to how many potential faces were found with the combination of scene attributes.
+The scene information was recorded and the combinations were shown to find how many potential faces were found with the combination of scene attributes.
 
-This showed that crowd members faces were often recognized which is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
+This showed that crowd members faces were often recognized, this is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
 It also allowed for an increase in understanding how attributes of a face or image impact on the API detection.
 
-The colours in the mosaic \@ref(fig:ICFigs) (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
+The colours in the mosaic (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
 There is a greater proportion of API faces that matched the faces found manually than those that did not match.
 However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually.
-The most common faces in the set were those captured level to player's faces, these faces were often recognised by the APIs as well.
+The most common faces in the set were those captured Level to player's faces, these faces were often recognised by the APIs as well.
 
-The mosaic \@ref(fig:ICFigs) (b) in Figure \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
+The mosaic (b) in \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
 It contrasts the proportion of the images captured in each situation that either did or did not match the faces annotated manually.
-It can be seen that the largest amount of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
-This proportion is steady across most situations, it can be inferred the situation may not be influencing the APIs rate of detection.
+It can be seen that the largest portion of the faces were captured in a close up situation and there were more of these faces that were found by the APIs that did match manually derived faces.
+This proportion is steady across most situations, from this it can be inferred the situation may not be influencing the APIs rate of detection.
 
-Figure \@ref(fig:ICFigs) (c) contains a mosaic which allows consideration of the interaction between two image attributes.
-It can be seen that the background being the logo wall and the angle of level is common to the highest amount of faces.
+Figure \@ref(fig:ICFigs) Plot c contains a stacked bar chart which allows consideration of the interaction between two image attributes.
+It can be seen that the background being the Logo Wall and the angle of Level is common to the highest amount of faces.
 There are also no images that were taken at an upward angle with the background of the court.
 
-This mosiac, Figure \@ref(fig:ICFigs) (d), allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
+This stacked bar chart, Figure \@ref(fig:ICFigs) Plot d, allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
 As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd.
@@
 
-#prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)
+prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)
+
 ```
@@
 Of those without glasses only 26% wore headwear.
-This may be influenced by weather and sunlight on the court during Australian Open matches.
+This may be influenced by weather and sunlight on the court during Australian Ope n matches.
 
@@
   round(glassesTab[2,5]/glassesTab[2,1],2)))
-```
 
-\begin{table}[ht]
-\centering
-%\parbox{.5\linewidth}{
-\caption{Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces.
+pander(glassesdf, caption = "Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces.
 API's unaffected glasses will have similar proportions for both categories.
 Animetrics had the biggest proportion difference, and thus, most affected.
-Google is the least affected.}
-\label{tab:glasses}
-\begin{tabular}{ccccc}
-\hline 
- & Animetrics & Google & Microsoft & Skybiometry\\ 
-\hline
-Glasses & 0.08 & 0.43 & 0.14 & 0.12 \\
-No Glasses & 0.21 & 0.60 & 0.26 & 0.23\\
-\hline
-\end{tabular}
-\end{table}
+Google is the least affected.")
+```
 
@@
 
-Considering the images used during our study were stills derived from broadcast video files, it would be useful to extend further research to deal with the video files directly.
+Considering the images used during our study were stills derived from Broadcast video files, it would be useful to extend further research to deal with the video files directly.
 The Google Vision API which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.
@@
 
-Google found many faces that did not match manually annotated faces, this showed manual errors were a possibility.
+Given that Google found many faces that did not match manually annotated face,  manual errors were a possibility.
 To search for these Taipan could be extended to allow the face identified to be displayed and confirmed this would allow the annotator to confirm manually whether or not these are faces.
 
-Given that certain scene attribute combinations produced more successful facial recognition than other combinations, a limit should be implemented for the sample of images sent to Google Vision API.
-This would not help to reduce cost.
+Given that certain scene attribute combinations produced more facial recognition than other combinations a limit should be implemented for the sample of images sent to Google Vision API.
+This would not only reduce cost but also provide a greater level of detail of the emotions felt by a player during a match.
 To provide a greater level of information at all points in a match it would be beneficial to derive images from a single camera feed.
-This feed should match the scene attributes that provided was most successful for Google to return faces.
+This feed should match the scene attributes that provided the most Google faces.
 
@@
 
-- Animetrics: Animetrics Face Recognition API, FaceR API by @Animetrics.
+- Animetrics: This name used throughout the paper refers to the Animetrics Face Recognition API, FaceR API by @Animetrics.
 
-- Google: Google Cloud Vision API [-@Google]
+- Google: @Google Refers to the Google Cloud Vision API
 
-- Microsoft: Microsoft Azure Cognitive Services Face API, published by @Microsoft.
+- Microsoft: This has been used to refer to the Microsoft Azure Cognitive Services Face API, published by @Microsoft.
 
-- Skybiometry: @Skybiometry the spin off detection and recognition software of Neurotechnology.
+- Skybiometry: @Skybiometry References the spin off detection and recognition software of Neurotechnology.
 

### 2017-12-15 paper/paper.Rmd

--- 2017-12-14 paper/paper.Rmd
@@
 For training purposes faces were manually tagged in 6406 images, recording the scene characteristics and features of individual faces.
-This included information regarding accessories, such as headwear or sunglasses being worn.
+This included information regarding accessories, such as head wear or sunglasses being worn.
 This enables the performance to be assessed based on conditions, and the APIs were evaluated on their success rate at detecting these faces.
@@
 
-The colours in the mosaic \@ref(fig:ICFigs) (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
+The colors in the mosaic \@ref(fig:ICFigs) (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
 There is a greater proportion of API faces that matched the faces found manually than those that did not match.
 However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually.
-The most common faces in the set were those captured level to player's faces, these faces were often recognised by the APIs as well.
+The most common faces in the set were those captured level to player's faces, these faces were often recognized by the APIs as well.
 
@@
 
-This mosiac, Figure \@ref(fig:ICFigs) (d), allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
+This mosaic, Figure \@ref(fig:ICFigs) (d), allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
 As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd.
@@
 
-The use of accessories like glasses and headwear, visors or hats, was considered as the Australian Open takes place on both indoor and outdoor courts. 
+The use of accessories like glasses and head wear, visors or hats, was considered as the Australian Open takes place on both indoor and outdoor courts. 
 It was assumed that outdoor courts would lead to the use of these accessories and these accessories may contribute to the performance of a recognition software.
@@
 %\parbox{.5\linewidth}{
-\caption{Proportions of faces captured manually tagged as wearing headwear given they wore glasses, or did not.} 
+\caption{Proportions of faces captured manually tagged as wearing headgear given they wore glasses, or did not.} 
 \label{tab:accessories}
@@
 
-Table \@ref(tab:accessories) of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without headwear.
-Of those without glasses only 26% wore headwear.
+Table \@ref(tab:accessories) of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without head wear.
+Of those without glasses only 26% wore head wear.
 This may be influenced by weather and sunlight on the court during Australian Open matches.

### 2017-12-17 paper/paper.Rmd
done with image characteristics

@@
 ImageCharacteristics<-ImageCharacteristics[1:5,]
-knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=FALSE, format.args=list(width=8), caption="Combinations of image attibutes that are most common in the image set.
-The combination of the Logo Wall background and the Level angle are shared by three of the five image combinations.", format = "latex")
+knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=FALSE, format.args=list(width=8), caption="Top five most frequent image attribute combinations.", format = "latex")
 ```
@@
 
-There were several characteristics of the image recorded during manual tagging, as listed in Table \@ref(tab:Scene-Attributes-Table).
-This section examines the prevalence of these characteristics in the data collection.
-Figure \@ref(fig:ICFigs) shows the relationships of a subset of characteristics, using mosaic plots.
+Image characteristics (Table \@ref(tab:Scene-Attributes-Table)) were constructed during manual tagging.
+The scene information was tallied and the most common combinations of these features shown in Table \@ref(tab:Image-Characteristics-Table).
 
-The characteristics of the images were recorded in the manual tagging process and there are uneven amounts of faces with certain image attributes.
-These relationships can be explored in mosaics for the images that were all considered manually.
-The scene information was tallied and the combinations of these features were compared to how many potential faces were found with the combination of scene attributes.
-
-This showed that crowd members faces were often recognized which is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research.
-It also allowed for an increase in understanding how attributes of a face or image impact on the API detection.
-
-The colors in the mosaic \@ref(fig:ICFigs) (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from.
-There is a greater proportion of API faces that matched the faces found manually than those that did not match.
-However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually.
-The most common faces in the set were those captured level to player's faces, these faces were often recognized by the APIs as well.
+Figure \@ref(fig:ICFigs) examines the relationships between several of the image characteristics, and face detection by the Google API, using mosaic plots.
+Plot (a) compares the angle of capture by detection rate.
+Colour is mapped to detection.
+Most images were taken at a level angle.
+The highest capture rate occurred when the angle was level, and least with a bird's eye, as might be expected.
+Plot (b) compares the situation with face detection.
+Close-up was the most common situation.
+The detection rate was the same across situations.
 
@@
 
-Figure \@ref(fig:ICFigs) (c) contains a mosaic which allows consideration of the interaction between two image attributes.
-It can be seen that the background being the logo wall and the angle of level is common to the highest amount of faces.
-There are also no images that were taken at an upward angle with the background of the court.
+Plots (c) and (d) show the three way relationship between capture angle, situation, background and face detection.
+In the level capture angle most faces were detected against the logo wall, but with bird's eye most were captured against the court.
+In close-ups the most faces were detected against the logo wall.
 
-This mosaic, Figure \@ref(fig:ICFigs) (d), allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring.
-As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd.
-The court is the background of an image only when players are captured, this occurs during close ups and while the court is in play.
-
-## Accessories
+## Player accessories
 

### 2017-12-17 paper/paper.Rmd
hear wear and glasses

@@
 
-The use of accessories like glasses and head wear, visors or hats, was considered as the Australian Open takes place on both indoor and outdoor courts. 
-It was assumed that outdoor courts would lead to the use of these accessories and these accessories may contribute to the performance of a recognition software.
+The use of accessories like glasses and head wear, visors or hats, is common during the Australian Open as play is mostly outdoors during daytime.
+Table \@ref(tab:accessories) shows player use of head wear and glasses, as tagged manually.
+
+of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without head wear.
+Of those without glasses only 26% wore head wear.
+This may be influenced by weather and sunlight on the court during Australian Open matches.
 
@@
 %\parbox{.5\linewidth}{
-\caption{Proportions of faces captured manually tagged as wearing headgear given they wore glasses, or did not.} 
+\caption{Usage of head wear and glasses by players. Most players did not wear glasses, and roughly half had hats or visors. } 
 \label{tab:accessories}
-\begin{tabular}{ccc}
+\begin{tabular}{|l|rr|r|}
 \hline 
- & Head wear & No Head wear\\ 
+ & No head wear & Head wear & Total\\ 
 \hline
-Glasses & 0.50 & 0.50 \\
-No Glasses & 0.26 & 0.74 \\
+Glasses & 92 & 260 & 352\\
+No glasses & 981 & 962 & 1943\\\hline
+Total & 1073 & 1222 & 2295 \\
 \hline
@@
 \end{table}
-
-Table \@ref(tab:accessories) of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without head wear.
-Of those without glasses only 26% wore head wear.
-This may be influenced by weather and sunlight on the court during Australian Open matches.
 
@@
 \label{tab:glasses}
-\begin{tabular}{ccccc}
+\begin{tabular}{|l|rrrr|}
 \hline 

### 2018-01-09 paper/paper.Rmd
Formatted digits in regression table to all have two decimal places

@@
 
-ModelEstimatesTable <- as.data.frame(cbind(ModelEstimatesTypes, ModelEstimatesSign[,2:5])) %>%
-mutate(A = ifelse(A.s=="   ", "-", A.e),
-       G = ifelse(G.s=="   ", "-", G.e),
-       M = ifelse(M.s=="   ", "-", M.e),
-       S = ifelse(S.s=="   ", "-", S.e))%>% 
-  # unite(Animetrics, A, A.s, sep="") %>% 
-  # unite(Google, G, G.s, sep="") %>% 
-  # unite(Microsoft, M, M.s, sep="") %>% 
-  # unite(Skybiometry, S, S.s, sep="") %>%
-  # select(variable, Animetrics, Google, Microsoft, Skybiometry)
-  mutate(` ` = A.s,
-         `  ` = G.s,
-         `   ` = M.s,
-         `    ` = S.s) %>%
-   select(variable, A, ` `,
-          G, `  `, 
-          M, `   `,
-          S, `    `)
+ModelEstimatesTable <- as.data.frame(cbind((ModelEstimatesTypes), ModelEstimatesSign[,2:5])) %>%
+mutate(A = ifelse(A.s=="   ", "-", format(round(A.e, 2), nsmall = 2)),
+       G = ifelse(G.s=="   ", "-", format(round(G.e, 2), nsmall = 2)),
+       M = ifelse(M.s=="   ", "-", format(round(M.e, 2), nsmall = 2)),
+       S = ifelse(S.s=="   ", "-", format(round(S.e, 2), nsmall = 2))) %>% 
+  select(variable, A, ` ` = A.s,
+         G, `  ` = G.s,
+         M, `   ` = M.s,
+         S, `    ` = S.s)
 
-knitr::kable(ModelEstimatesTable, format = "latex", align=c("l", 
-                                          "r", "l",
-                                          "r", "l",
-                                          "r", "l",
-                                          "r", "l"),
+knitr::kable(ModelEstimatesTable, format = "latex", align=c('l', 
+                                           'r', 'l',
+                                           'r', 'l',
+                                           'r', 'l',
+                                           'r', 'l'),
              booktabs = TRUE, longtable=FALSE, caption="Evaluation of factors affecting face recognition for API, as assessed by logistic regression model.
@@
 ```
-
-*** The number of digits should be consistent, e.g. "-1" should be "-1.00". I don't know how to force this with the kale printing, but one way or another we have to.
 

### 2018-01-16 paper/paper.Rmd
Violin time plot and explanation added.

@@
 
-Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a letter value plot [@letterValue].
-A letter value plot is like a box plot, but more suited to skewed data like this.
-(Both Microsoft and Google have a few images each where they have taken a long time to complete and these were removed from this plot.) The times are quite variable between APIs, with Skybiometry being the most consistently fast.
-Microsoft and Animetrics are quite variable regardless of the number of faces found.
-Google is variable in time taken when there are few faces present, and then takes a little longer on average to find faces as the number of them in the image increases.
+Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a violin plot.
+Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
+The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs.
+Microsoft and Google's times vary regardless of the number of faces found.
 
@@
 
-```{r timeFigure, fig.height=6, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered, displayed as a letter value plot.
-Skybiometry is the most consistently fast.\\label{fig:timeFigure}"}
-# 
-# t1 <- ggplot(times) +  
-#   geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm") + 
-#   xlab("Number of faces detected") + ylab("System time (sec)") +  
-#   scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")
+```{r timeFigure, fig.height=6, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered, displayed as violins.
+The width of the violin shows the most common times for the group of images.\\label{fig:timeFigure}"}
 
-# t2 <- ggplot(times) +
-#   geom_jitter(aes(x=n, y=time.sys.self, colour=type), alpha=0.2, width=0.3, height=0.01) +
-#   facet_wrap(~type) +
-#   ylim(c(0, 0.1)) +
-#   #geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) +
-#   xlab("Number of faces detected") +
-#   scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")
-
-#grid.arrange(t1,t2,nrow=1)
-
-# letter value plots
-t2 <- ggplot(times, aes(as.factor(n), time.sys.self)) + 
-  geom_lv(aes(fill = ..LV..)) +
-  #ylim(c(0, 0.1)) + 
-  facet_wrap(~type) +
-  scale_y_continuous("System time (seconds)", 
-    breaks=seq(0, .08, .02), limits=c(0, 0.08)) +
-  # somethings funky when try to change axis labels
-  xlab("Number of faces detected")
+# violin plot
+t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self)) +
+  geom_violin(scale = "width") + ylim(0,0.08) +
+  #geom_jitter(height = 0.005, width = 0.1, alpha=0.5) +
+  facet_wrap(~ type) +
+  xlab("Amount of faces found") +
+  ylab("Time taken per image (Seconds)")
 

### 2018-01-17 paper/paper.Rmd
violing plot tweaks

@@
 
-Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a violin plot.
+Figure \@ref(fig:timeFigure) displays the distribution of processing time required by the APIs for each image, as a violin plot (REF).
 Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
@@
 # violin plot
-t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self)) +
-  geom_violin(scale = "width") + ylim(0,0.08) +
+t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self, fill=type)) +
+  geom_violin(scale = "count", alpha=0.5, adjust=0.01) + ylim(0,0.08) +
   #geom_jitter(height = 0.005, width = 0.1, alpha=0.5) +
@@
   xlab("Amount of faces found") +
-  ylab("Time taken per image (Seconds)")
+  ylab("Time taken per image (Seconds)") + scale_fill_manual("", values=type.colours) +
+  geom_smooth(aes(x=n, time.sys.self), method="lm", se=F, colour="black") + 
+  scale_colour_manual("", values=type.colours)
 

### 2018-01-17 paper/paper.Rmd
violin

@@
 library(purrr)
-library(lvplot)
 
@@
   group_by(file, type) %>% 
-  mutate(n=n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))
+  mutate(n=n()) %>% 
+  distinct() %>% ungroup()
 ```
@@
 t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self, fill=type)) +
-  geom_violin(scale = "count", alpha=0.5, adjust=0.01) + ylim(0,0.08) +
+  geom_violin(scale = "width", alpha=0.5) + ylim(0,0.08) +
   #geom_jitter(height = 0.005, width = 0.1, alpha=0.5) +

### 2018-01-17 paper/paper.Rmd
accessory changes
Accessories tables reworked

@@
 
-Figure \@ref(fig:timeFigure) displays the distribution of processing time required by the APIs for each image, as a violin plot (REF).
+Figure \@ref(fig:timeFigure) displays the distribution of processing time required by the APIs for each image, as a violin plot [@Violin].
 Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
@@
 ```{r glasses, fig.cap = "\\label{tab:glasses}", digit=3}
-
-ManFaces %>% count(glasses) %>%
-  tally() -> ManGlasses
-
 aminFaces %>% filter(matchesManual==TRUE) -> afm
@@
 
-glassesdf <- rbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
+glassesdf <- cbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
+                   c("Yes", 
+  round(glassesTab[2,2]/glassesTab[2,1],2),
+  round(glassesTab[2,3]/glassesTab[2,1],2),
+  round(glassesTab[2,4]/glassesTab[2,1],2),
+  round(glassesTab[2,5]/glassesTab[2,1],2)),
 c("No", 
@@
   round(glassesTab[1,4]/glassesTab[1,1],2),
-  round(glassesTab[1,5]/glassesTab[1,1],2)),
+  round(glassesTab[1,5]/glassesTab[1,1],2))
+)
+
+# Headwear
+table(afm$visorhat, afm$type) %>% as.matrix() -> headwearTab
+
+headweardf <- cbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
                    c("Yes", 
-  round(glassesTab[2,2]/glassesTab[2,1],2),
-  round(glassesTab[2,3]/glassesTab[2,1],2),
-  round(glassesTab[2,4]/glassesTab[2,1],2),
-  round(glassesTab[2,5]/glassesTab[2,1],2)))
+  round(headwearTab[2,2]/headwearTab[2,1],2),
+  round(headwearTab[2,3]/headwearTab[2,1],2),
+  round(headwearTab[2,4]/headwearTab[2,1],2),
+  round(headwearTab[2,5]/headwearTab[2,1],2)),
+c("No", 
+  round(headwearTab[1,2]/headwearTab[1,1],2),
+  round(headwearTab[1,3]/headwearTab[1,1],2),
+  round(headwearTab[1,4]/headwearTab[1,1],2),
+  round(headwearTab[1,5]/headwearTab[1,1],2))
+)
 ```
 
-\begin{table}[ht]
-\centering
+\begin{table}[htp]
 %\parbox{.5\linewidth}{
-\caption{Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces.
-API's unaffected glasses will have similar proportions for both categories.
+\caption{Conditional proportions of faces of players wearing glassesor headwear or not, captured by the different software, as a proportion of the manually tagged faces.
+API's unaffected by glasses will have similar proportions for both categories.
 Animetrics had the biggest proportion difference, and thus, most affected.
 Google is the least affected.}
-\label{tab:glasses}
-\begin{tabular}{|l|rrrr|}
-\hline 
- & Animetrics & Google & Microsoft & Skybiometry\\ 
-\hline
-Glasses & 0.08 & 0.43 & 0.14 & 0.12 \\
-No Glasses & 0.21 & 0.60 & 0.26 & 0.23\\
-\hline
+\bigskip
+\label{tab:glassesheadwear}
+\centering
+\begin{tabular}{|l|rr|rr|}  \hline
+& \multicolumn{2}{r|}{Headwear}&\multicolumn{2}{r|}{Glasses}\\\cline{2-5}
+API & Yes & No & Yes & No \\\hline
+Google & 0.48 & 0.69 & 0.43 & 0.60 \\
+Microsoft & 0.19 & 0.32 & 0.14 & 0.26 \\
+Skybiometry & 0.16 & 0.28 & 0.12 & 0.23 \\
+Animetrics & 0.11 & 0.27 & 0.08 & 0.21 \\\hline
 \end{tabular}

### 2018-01-17 paper/paper.Rmd
Accessories table paragraph explanation

@@
 
-The use of accessories like glasses and head wear, visors or hats, is common during the Australian Open as play is mostly outdoors during daytime.
-Table \@ref(tab:accessories) shows player use of head wear and glasses, as tagged manually.
-
-of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without head wear.
-Of those without glasses only 26% wore head wear.
-This may be influenced by weather and sunlight on the court during Australian Open matches.
+The Australian Open conducts matches on a range of courts, as some of these courts are located outdoors it is common to see accessories worn by players.
+Glasses, visors, hats, sweatbands and other additional pieces are worn by players, especially during day matches played outside.
+Table \@ref(tab:accessories) shows the accessories associated with a manually tagged face.
+It can be seen that most faces captured were not wearing glasses, however there were a similar amount of faces captured with and without head wear.
 
@@
 
-\begin{table}[htp]
+\begin{table}[ht]
 %\parbox{.5\linewidth}{
-\caption{Conditional proportions of faces of players wearing glassesor headwear or not, captured by the different software, as a proportion of the manually tagged faces.
-API's unaffected by glasses will have similar proportions for both categories.
+\caption{Conditional proportions of faces of players wearing glasses or headwear or not, captured by the different software, as a proportion of the manually tagged faces.
+API's will have similar proportions for both categories if they are not affected by the presence of an accessory.
 Animetrics had the biggest proportion difference, and thus, most affected.
@@
 \end{table}
+
+The conditional proportions are interpretted as the proportion of faces found by the API, that were tagged manually and having the attributes that were tabulated.
+For example, the value in the first row and first column of table \@ref(tab:glassesheadwear) highlights that Google found 0.48, or 48%, of the faces found manually and tagged as wearing headwear.
+As the values in the row for Google are the largest amounts in each column, it found more of the manually tagged faces in any situation considered.
+The next best software, Microsoft, found less than half the amount of manually tagged faces that Google located.
+
+Animetrics may have been impeded by the use of accessories as it located only 0.08, or 8%, of the faces tagged manually as wearing a hat or visor, and 0.11, or 11%, of the faces tagged manually as wearing glasses.
+When acceories are not worn, the proportion of faces found are closer to the next best API, Skybiometry.
 

### 2018-01-17 paper/paper.Rmd
Violin plot explanation expanded, spell checks

@@
 Figure \@ref(fig:timeFigure) displays the distribution of processing time required by the APIs for each image, as a violin plot [@Violin].
-Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
+Both Microsoft and Google had few images which took a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
 The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs.
 Microsoft and Google's times vary regardless of the number of faces found.
+The lines overlaid in each plot represent the smoothed linear model of the amount of faces, it can be seen that all APIs take longer to complete detection of faces in an image when there are more faces.
+As all APIs had more images where only one or two faces were found it resulted in more variability in the amount of time taken.
 
@@
 
-The conditional proportions are interpretted as the proportion of faces found by the API, that were tagged manually and having the attributes that were tabulated.
+The conditional proportions are interpreted as the proportion of faces found by the API, that were tagged manually and having the attributes that were tabulated.
 For example, the value in the first row and first column of table \@ref(tab:glassesheadwear) highlights that Google found 0.48, or 48%, of the faces found manually and tagged as wearing headwear.
@@
 Animetrics may have been impeded by the use of accessories as it located only 0.08, or 8%, of the faces tagged manually as wearing a hat or visor, and 0.11, or 11%, of the faces tagged manually as wearing glasses.
-When acceories are not worn, the proportion of faces found are closer to the next best API, Skybiometry.
+When accessories are not worn, the proportion of faces found are closer to the next best API, Skybiometry.
 

### 2018-01-17 paper/paper.Rmd
Violin plot description

@@
 
-Figure \@ref(fig:timeFigure) displays the distribution of processing time required by the APIs for each image, as a violin plot [@Violin].
-Both Microsoft and Google had few images which took a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
+Figure \@ref(fig:timeFigure) shows the distribution of processing time required by the APIs for each image.
+The violin plot display created by @Violin 'combines the box plot and the density'.
+A categorical variable splits the data along the x axis, as would be seen in a box plot display.
+A density plot is then incorporated on the y axis.
+This is produced by manipulating a density display; switching the axes allows the continuous variable to increase along on the y axis, then the violin shape is created by mirroring the density.
+The width of the violin will now be twice the length that would be have been measured vertically in a density plot.
+
+As seen in the facets of Figure \@ref(fig:timeFigure), both Microsoft and Google had few images which took a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
 The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs.

### 2018-01-18 paper/paper.Rmd

@@
 
-The Australian Open conducts matches on a range of courts, as some of these courts are located outdoors it is common to see accessories worn by players.
-Glasses, visors, hats, sweatbands and other additional pieces are worn by players, especially during day matches played outside.
-Table \@ref(tab:accessories) shows the accessories associated with a manually tagged face.
-It can be seen that most faces captured were not wearing glasses, however there were a similar amount of faces captured with and without head wear.
+The use of accessories like glasses and head wear, visors or hats, is common during the Australian Open as play is mostly outdoors during daytime.
+Table \@ref(tab:accessories) shows player use of head wear and glasses, as tagged manually.
+Table \@ref(tab:glasses) compares the face capture rate of the different APIs for the player acessories.
+
+of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without head wear.
+Of those without glasses only 26% wore head wear.
+This may be influenced by weather and sunlight on the court during Australian Open matches.
 
@@
 
-table(afm$glasses, afm$type) %>% as.matrix() -> glassesTab
+table(afm$visorhat, afm$type) %>% as.matrix() -> glassesTab
 

### 2018-01-18 paper/paper.Rmd
player accessories

@@
 Table \@ref(tab:accessories) shows player use of head wear and glasses, as tagged manually.
-Table \@ref(tab:glasses) compares the face capture rate of the different APIs for the player acessories.
-
-of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without head wear.
-Of those without glasses only 26% wore head wear.
-This may be influenced by weather and sunlight on the court during Australian Open matches.
+Most players do not have glasses, but head wear, either visors or hats, are very common.
 
@@
 %\parbox{.5\linewidth}{
-\caption{Usage of head wear and glasses by players. Most players did not wear glasses, and roughly half had hats or visors. } 
+\caption{Usage of head wear and glasses by players, as manually tagged. Most players did not wear glasses, and roughly half had hats or visors. } 
 \label{tab:accessories}
@@
 %\parbox{.5\linewidth}{
-\caption{Conditional proportions of faces of players wearing glasses or headwear or not, captured by the different software, as a proportion of the manually tagged faces.
-API's will have similar proportions for both categories if they are not affected by the presence of an accessory.
-Animetrics had the biggest proportion difference, and thus, most affected.
-Google is the least affected.}
+\caption{Detection rates of the APIs for different accessories, as measured against the manual tagging.
+Rate is the proportion of detected with the accessory relative to without.
+Google has higher detection rates than the other APIs when a player is wearing head wear or glasses.
+}
 \bigskip
@@
 \centering
-\begin{tabular}{|l|rr|rr|}  \hline
-& \multicolumn{2}{r|}{Headwear}&\multicolumn{2}{r|}{Glasses}\\\cline{2-5}
-API & Yes & No & Yes & No \\\hline
-Google & 0.48 & 0.69 & 0.43 & 0.60 \\
-Microsoft & 0.19 & 0.32 & 0.14 & 0.26 \\
-Skybiometry & 0.16 & 0.28 & 0.12 & 0.23 \\
-Animetrics & 0.11 & 0.27 & 0.08 & 0.21 \\\hline
+\begin{tabular}{|l|rr|r|rr|r|}  \hline
+& \multicolumn{3}{c|}{Head wear}&\multicolumn{3}{c|}{Glasses}\\\cline{2-7}
+API & Yes & No & Rate &  Yes & No & Rate \\\hline
+Google & 0.48 & 0.69 & 0.70 & 0.43  & 0.60 & 0.72 \\
+Microsoft & 0.19 & 0.32 & 0.59 & 0.14  & 0.26 & 0.54 \\
+Skybiometry & 0.16  & 0.28 & 0.57  & 0.12 & 0.23 & 0.52 \\
+Animetrics & 0.11  & 0.27 & 0.41 & 0.08 & 0.21 & 0.38 \\\hline
 \end{tabular}
@@
 
-The conditional proportions are interpreted as the proportion of faces found by the API, that were tagged manually and having the attributes that were tabulated.
-For example, the value in the first row and first column of table \@ref(tab:glassesheadwear) highlights that Google found 0.48, or 48%, of the faces found manually and tagged as wearing headwear.
-As the values in the row for Google are the largest amounts in each column, it found more of the manually tagged faces in any situation considered.
-The next best software, Microsoft, found less than half the amount of manually tagged faces that Google located.
-
-Animetrics may have been impeded by the use of accessories as it located only 0.08, or 8%, of the faces tagged manually as wearing a hat or visor, and 0.11, or 11%, of the faces tagged manually as wearing glasses.
-When accessories are not worn, the proportion of faces found are closer to the next best API, Skybiometry.
+Table \@ref(tab:glassesheadwear) compares the face capture rate of the different APIs for the player accessories, as compared to the manually tagged face attributes.
+Conditional proportions are calculated two ways: (1) proportion of the manually tagged faces, (2) proportion detected with the accessory relative to without.
+From the former conditional probability it can be seen that Google detects more faces regardless of the accessory, with slightly higher proportion when the player has no head wear or glasses.
+From the latter calculation, Google has less difference between the accessory or not detection rate.
+Overall, Google detects a higher proportion of faces, but they also have better detection rates if faces of players wearing head wear and glasses.
+Animetrics performed the worst when a player was wearing head wear or glasses.
 

### 2018-01-19 paper/paper.Rmd
done with paper

@@
 
-Images from the Australian Open 2016 were provided by Tennis Australia, with goal being that the sample is representative of the video files to be used for future facial recognition analysis:
+Images from the Australian Open 2016 were provided by Tennis Australia, with goal being that the sample is representative of the video files to be used for future facial recognition analysis: 6406 images, 800 $\times$ 450px
 
-- 6406 images, 800 $\times$ 450px
-
-To produce the set of 6406 images, 5 minute segments were taken from 105 video files a still shot of the video was taken at every three seconds, for the length of each segment.
+To collect the images, 5 minute segments were taken from 105 video files, with a still shot stored every three seconds.
 The video files used were the broadcasts of the tennis matches shown on the Seven Network during the Australian Open 2016.
@@
 Specific information for each face within each scene was collected.
-To determine which of the, sometimes many, faces in the scene it would be reasonable for software to detect a standard was created for reasonable detection.
-The faces of players were recorded if it showed their face at a minimum of 20 by 20 pixels.
-The back of the head was not detected as a face by any software, these areas were classified manually but reclassified as other.
-Crowd faces were not the intended targets of the recognition however these faces contributed to our understanding of the software.
-The same face size standard applied to crowd members, but focus was placed on the most prominent faces.
-For each of these faces, information was collected regarding the attributes in Table \@ref(tab:Face-Attribute-Tables).
+To determine which of the, sometimes many, faces in the scene it would be reasonable for software to detect, and to minimize human labor, some rules were applied to the manual tagging:
+
+- The faces were recorded if it showed their face at a minimum of 20 by 20 pixels. 
+- The back of the head was not detected as a face by any software, these areas were classified manually but reclassified as other.
+- Crowd faces were not the intended targets of the recognition however these faces contributed to our understanding of the software. 
+- The same face size standard applied to crowd members, but focus was placed on the most prominent faces.
+
+Table \@ref(tab:Face-Attribute-Tables) summarises attribute information recorded for each face.
 
@@
 The web app was created using the Shiny package for R [@shiny] and has been developed into an R package called taipan, as it is a Tool for Annotating Images in Preparation for ANalysis.
-If there was a face in the image the annotator was able to highlight that section of the image to contain the face.
+The annotator was able to highlight the section of the image containing a face.
 This selection activated a set of attributes questions for the annotator to answer, and allowed information to be recorded for the face.
-The records included the location of the box in the image, and all appropriate answers.
-When a face was not visible in the image only the scene attributes were applicable for that image.
+The records included the location of the box in the image, and answers to the questions providing the attributes of the face.
+When a face was not visible in the image only the scene attributes were recorded for the image.
 All of the annotations for this sample were completed by one annotator to provide a consistent sample of faces annotated manually.
@@
 Plot (a) compares the angle of capture by detection rate.
-Colour is mapped to detection.
+Color is mapped to detection.
 Most images were taken at a level angle.
@@
 Rate is the proportion of detected with the accessory relative to without.
-Google has higher detection rates than the other APIs when a player is wearing head wear or glasses.
+Google has higher detection rates than the other APIs when a player has head wear or glasses.
 }
@@
 # Future Work
-The long term goal is to better understand how the emotion's felt by a player during a match affect player performance.
-A long term aim would be to create a program that automated the collection of player emotion data from throughout a match.
-This information would be presented in a timeline that allowed match performance, in the form of points won, to be aligned with the emotions felt at certain times throughout.
 
-Considering the images used during our study were stills derived from broadcast video files, it would be useful to extend further research to deal with the video files directly.
-The Google Vision API which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.
+This paper has described the results of a survey of commonly available software for face detection when applied to stills from tennis match video.
+A long term goal is to detect emotional state of the player, and track this through a match, to study the effect on performance.
+Several of the face recognition APIs also report an emotional state, but our analysis of this data suggests it is unreliable.
 
-It should also be considered that these are software focused on providing recognition in certain controlled scenarios.
-If the study was controlled to focus on certain camera angles that align with the facial angles these security programs are intended to recognize faces in.
+One of the problems encountered with the emotion reporting, was that individual player's faces were repeatedly tagged with one emotional state, which looked more related to the basic facial features of the player.
+To accurately detect an individual player's emotions would require getting something like a baseline measurement on what their face looks like in a neutral emotional state, and then measuring differences from that.
+To study emotions and performance, we would recommend creating a training data set similar to the face recognition data, where emotional state is manually tagged.
+It would also be important to take comprehensive video footage, to track a player throughout the tournament, rather than isolated images.
 
-Google found many faces that did not match manually annotated faces, this showed manual errors were a possibility.
-To search for these Taipan could be extended to allow the face identified to be displayed and confirmed this would allow the annotator to confirm manually whether or not these are faces.
-
-Given that certain scene attribute combinations produced more successful facial recognition than other combinations, a limit should be implemented for the sample of images sent to Google Vision API.
-This would not help to reduce cost.
-To provide a greater level of information at all points in a match it would be beneficial to derive images from a single camera feed.
-This feed should match the scene attributes that provided was most successful for Google to return faces.
-
-To undertake sentiment analysis, the faces found in this set of images could be used.
-Allowing each face a border of pixels, images could be cropped and produce an individual face image that would form the data set for emotion recognition.
-Incorporating audio information from the microphones worn by players may assist in sentiment analysis.
-By including this information differences between certain emotions that may not be able to be found by facial features only.
+The result of the face recognition survey clearly points to a winner: Google's API. It detected a higher proportion of faces under different conditions and with different accessories.
 
@@
 The authors wish to thank Tennis Australia for access to the data.
-The analysis was conducted using R, and the following packages: bookdown[@bookdown], descr[@descr], EBImage [@EBImage], ggthemes [@ggthemes], ggmosaic [@ggmosaic], grid [@grid], gridExtra [@gridExtra], gtable [@gtable], kfigr [@kfigr], knitcitations [@knitcitations], knitr [@knitr] , pander [@pander], readr [@readr], RefManager [@RefManager], tidyverse [@tidyverse], UpSetR [@UpSetR], xtable [@xtable].
+The analysis was conducted using R[@R], and the following packages: bookdown [@bookdown], descr [@descr], EBImage [@EBImage], ggthemes [@ggthemes], ggmosaic [@ggmosaic], grid [@R], gridExtra [@gridExtra], gtable [@gtable], kfigr [@kfigr], knitcitations [@knitcitations], knitr [@knitr], pander [@pander], readr [@readr], RefManager [@RefManager], tidyverse [@tidyverse], UpSetR [@UpSetR], xtable [@xtable].
 
@@
 
-- ManualClassifiedFaces.csv resulted from the use of the Manual Annotation Application, it contains information about each face identified manually.
-- ManualClassifiedScenes.csv also resulted from the use of the app, it contains information about each image.
+- ManualClassifiedFaces.csv contains the data collected on each face by manual tagging.
+- ManualClassifiedScenes.csv contains scene information about each image.
+
+The web app for manual tagging, called taipan, is available from https://github.com/srkob1/taipan. It can be installed using the devtools [@devtools] package function `install_github'.
 

### 2018-01-22 paper/paper.Rmd
Formatted for Journal submission

@@
 documentclass: article
+geometry: margin=1in
+header-includes:
+    - \usepackage{setspace}\doublespacing
 bibliography: references.bib
-biblio-style: harvard
+biblio-style: chicago
 link-citations: true
@@
 
-Animetrics provided many surprises. Figure \@ref(fig:UnusualImages) shows four images and the captures where non-faces were detected as faces. In image (a) the player's back is detected as a face.
-In image (b) the KIA logo was reported as a face. 
-In image (c), where logos on the player's and ball boy's shirts were returned as faces.
-In image (d) where there are a lot of crowd faces, if you look closely one of the detections is actually a fist (to the right on the center).
+Animetrics provided many surprises. Figure \@ref(fig:UnusualImages) shows four images and the captures where non-faces were detected as faces. In image (A) the player's back is detected as a face.
+In image (B) the KIA logo was reported as a face. 
+In image (C), where logos on the player's and ball boy's shirts were returned as faces.
+In image (D) where there are a lot of crowd faces, if you look closely one of the detections is actually a fist (to the right on the center).
 
@@
 ```{r UnusualImages, fig.cap = "Four images in which Animetrics located unusual faces. \\label{fig:UnusualImages}", dev="jpeg", dpi=300}
-i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(a)")
-i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(b)")
-i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(c)")
-i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(d)")
+i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(A)")
+i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(B)")
+i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(C)")
+i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("(D)")
 
@@
 
-```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (a) Angle of face capture, (b) court situation, (c) angle of capture by background, and (d) situtation of capture by background.
+```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (A) Angle of face capture, (B) court situation, (C) angle of capture by background, and (D) situtation of capture by background.
 Most face captures occurred at a level angle, and this produces slightly better detection.
@@
   theme(legend.position = "none") + 
-  ggtitle("(a)")
+  ggtitle("(A)")
 
@@
   ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none")  +
-  ggtitle("(b)")
+  ggtitle("(B)")
 
@@
   ylab("Proportion of faces") + xlab("Angle of face capture") + theme(legend.position = "none") +
-  ggtitle("(c)")
+  ggtitle("(C)")
 
@@
   ylab("Proportion of faces") + xlab("Situation") + theme(legend.position = "none") +
-  ggtitle("(d)")
+  ggtitle("(D)")
 
@@
 Figure \@ref(fig:ICFigs) examines the relationships between several of the image characteristics, and face detection by the Google API, using mosaic plots.
-Plot (a) compares the angle of capture by detection rate.
+Plot (A) compares the angle of capture by detection rate.
 Color is mapped to detection.
@@
 The highest capture rate occurred when the angle was level, and least with a bird's eye, as might be expected.
-Plot (b) compares the situation with face detection.
+Plot (B) compares the situation with face detection.
 Close-up was the most common situation.
@@
 
-The mosaic \@ref(fig:ICFigs) (b) in Figure \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
+The mosaic \@ref(fig:ICFigs) (B) in Figure \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
 It contrasts the proportion of the images captured in each situation that either did or did not match the faces annotated manually.
@@
 
-Plots (c) and (d) show the three way relationship between capture angle, situation, background and face detection.
+Plots (C) and (D) show the three way relationship between capture angle, situation, background and face detection.
 In the level capture angle most faces were detected against the logo wall, but with bird's eye most were captured against the court.

### 2018-01-22 paper/paper.Rmd
Table of counts and proportions

@@
 
-GM <- CrossTable(FacesAPI$Manual, FacesAPI$Google)
-MM <- CrossTable(FacesAPI$Manual, FacesAPI$Microsoft)
-SM <- CrossTable(FacesAPI$Manual, FacesAPI$Skybiometry)
-AM <- CrossTable(FacesAPI$Manual, FacesAPI$Animetrics)
+GM <- CrossTable(FacesAPI$Manual, FacesAPI$Google, prop.c = F, prop.t = F, prop.chisq = F)
+MM <- CrossTable(FacesAPI$Manual, FacesAPI$Microsoft, prop.c = F, prop.t = F, prop.chisq = F)
+SM <- CrossTable(FacesAPI$Manual, FacesAPI$Skybiometry, prop.c = F, prop.t = F, prop.chisq = F)
+AM <- CrossTable(FacesAPI$Manual, FacesAPI$Animetrics, prop.c = F, prop.t = F, prop.chisq = F)
 ```
@@
 %\parbox{.5\linewidth}{
-\caption{Proportion of API matches with the 2295 manually tagged faces, and faces detected in the 1314 images with no manually tagged faces.}
+\caption{Capture rates of the APIs relative to manually tagged faces.
+Google tagged twice as many of the manual faces found than the next best API.
+It also had a larger proportion of Non-faces found, all of these faces were actual faces, usually of crowd members.
+However many of the faces found by other APIs were not actually faces, instead areas contained the net, clothing and logos.}
 \bigskip

### 2018-01-22 paper/paper.Rmd
Characteristics tables captions

@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics recorded for each image.")
+knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics of the scene occuring when the still shot was taken, one option for each category was selected for each image.")
 ```
-
-<!--
-\begin{table}[htp]
-\label{tab:Scene-Attributes-Table}
-\caption{Image descriptions that are associated with the attributes of each image. }
-\centering
-\begin{tabular}{lp{12cm}} \hline
-Attribute & Choices \\\hline
-Graphic & Live Image, 2D Graphic \\
-Background & Crowd, Court, Logo Wall, Not Applicable \\
-Person & Yes, No \\
-Shot Angle & Level, Birds Eye, Upward \\
-Situation & Match play, Close up, Not player, Crowd, Off court, Transition\\\hline
-\end{tabular}
-\end{table}
--->
 
@@
 ```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
-knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics recorded for each  face.
-Most were easy to assess for each face, with the exception of obscured and head angle.")
+knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics of the faces captured, one option for each category was selected for each face manually tagged.")
 ```

### 2018-01-29 paper/paper.Rmd
ASA style

@@
 ---
-title: "Detecting Facial Expressions in Video Stills from Professional Tennis Matches"
-author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
-date: "20 September 2017"
-output: bookdown::pdf_document2
+title: "Performance Comparison of Common Face Detection APIs in Video Stills from Professional Tennis Matches"
+authors: 
+- name: Stephanie Kobakian
+  affiliation: Monash University 
+- name: Mitchell O'Hara-Wild
+  affiliation: Monash University
+- name: Dianne Cook
+  affiliation: Monash University
+- name: Stephanie Kovalchik
+  affiliation: Victoria University and Tennis Australia
+output: rticles::asa_article
 toc: false

### 2018-01-29 paper/test/test.Rmd
ASA style

---
title: "Performance Comparison of Common Face Detection APIs using Video Stills from Professional Tennis Matches"

# to produce blinded version set to 1
blinded: 0

authors: 
- name: Stephanie Kobakian
  thanks: The authors gratefully acknowledge ...
  affiliation: Monash University

- name: Mitchell O'Hara-Wild
  affiliation: Monash University

- name: Dianne Cook
  affiliation: Monash University

- name: Stephanie Kovalchik
  affiliation: Victoria University and Tennis Australia

keywords:
- data science
- sports analytics
- shiny
- R

abstract: |
  This paper examines the effectiveness of facial detection APIs on broadcast video stills of Australian Open tennis matches. The goal is to determine the best API to use for face detection of players throughout a match. For training purposes, faces were manually tagged in 6406 images, using a specially constructed web application, recording the scene characteristics and features of individual faces, such as head wear or sunglasses. API performance was evaluated on their success rate at detecting the tagged faces, and also relative face and scene attributes.

bibliography: references.bib
biblio-style: chicago
output: rticles::asa_article
---

# Introduction

This template demonstrates some of the basic latex you'll need to know to create a ASA article.

\section{Verifications}
\label{sec:verify}
This section will be just long enough to illustrate what a full page of
text looks like, for margins and spacing.

@Campbell02 @Schubert13 [@Chi81]

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
__With this spacing we have 30 lines per page.__

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

### 2018-01-29 paper/test/test.tex
ASA style

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\begin{document}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Performance Comparison of Common Face Detection APIs using Video Stills
from Professional Tennis Matches}

  \author{
        Stephanie Kobakian \thanks{The authors gratefully acknowledge \ldots{}} \\
    Monash University\\
     and \\     Mitchell O'Hara-Wild \\
    Monash University\\
     and \\     Dianne Cook \\
    Monash University\\
     and \\     Stephanie Kovalchik \\
    Victoria University and Tennis Australia\\
      }
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Performance Comparison of Common Face Detection APIs using Video Stills
from Professional Tennis Matches}
  \end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
This paper examines the effectiveness of facial detection APIs on
broadcast video stills of Australian Open tennis matches. The goal is to
determine the best API to use for face detection of players throughout a
match. For training purposes, faces were manually tagged in 6406 images,
using a specially constructed web application, recording the scene
characteristics and features of individual faces, such as head wear or
sunglasses. API performance was evaluated on their success rate at
detecting the tagged faces, and also relative face and scene attributes.
\end{abstract}

\noindent%
{\it Keywords:} data science, sports analytics, shiny, R
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!

\section{Introduction}\label{introduction}

This template demonstrates some of the basic latex you'll need to know
to create a ASA article.

\section{Verifications}
\label{sec:verify}

This section will be just long enough to illustrate what a full page of
text looks like, for margins and spacing.

\citet{Campbell02} \citeauthor{Schubert13}
\citetext{\citeyear{Schubert13}; \citealp{Chi81}}

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. \textbf{With this spacing we
have 30 lines per page.}

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog. The quick brown fox jumped
over the lazy dog. The quick brown fox jumped over the lazy dog. The
quick brown fox jumped over the lazy dog.

\bibliographystyle{agsm}
\bibliography{references.bib}

\end{document}

### 2018-01-30 paper/paper.Rmd
rticles implementation, referencing and additional information

--- 2018-01-22 paper/paper.Rmd
@@
 ---
-title: "Detecting Facial Expressions in Video Stills from Professional Tennis Matches"
-author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
-date: "20 September 2017"
-output: bookdown::pdf_document2
+title: "Performance Comparison of Common Face Detection APIs using Video Stills from Professional Tennis Matches"
+
+# to produce blinded version set to 1
+blinded: 0
+
+authors: 
+- name: Stephanie Kobakian
+  thanks: The authors gratefully acknowledge Tennis Australia.
+  affiliation: Monash University
+
+- name: Mitchell O'Hara-Wild
+  affiliation: Monash University
+
+- name: Dianne Cook
+  affiliation: Monash University
+
+- name: Stephanie Kovalchik
+  affiliation: Victoria University and Tennis Australia
+
+keywords:
+- data science
+- sports analytics
+- shiny
+- R
+
+abstract: |
+  This paper examines the effectiveness of facial detection APIs on broadcast video stills of Australian Open tennis matches.
+The goal is to determine the best API to use for face detection of players throughout a match.
+For training purposes, faces were manually tagged in 6406 images, using a specially constructed web application, recording the scene characteristics and features of individual faces, such as head wear or sunglasses.
+API performance was evaluated on their success rate at detecting the tagged faces, and also relative face and scene attributes.
+
 toc: false
@@
 fontsize: 11pt
-documentclass: article
-geometry: margin=1in
 header-includes:
-    - \usepackage{setspace}\doublespacing
+    - \usepackage{booktabs}
+    - \usepackage{longtable}
 bibliography: references.bib
 biblio-style: chicago
+output: rticles::asa_article
 link-citations: true
@@
 library(purrr)
+library(rticles)
 
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)
+knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE)
 
-options("citation_format" = "pandoc")
+options("citation_format" = "pandoc",knitr.table.format = "latex")
 
-BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
+BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic', longnamesfirst=T)
 
 #csv files:
-amin<-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry")))) %>% 
+amin <-read_csv("data/ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry")))) %>% 
   filter(!duplicates)
@@
 This search produced two of the software, Microsoft API [@Microsoft], provided by Microsoft Cognitive Services, and Google Vision API [@Google].
-Online demos were used to test viability, Figure \@ref(fig:Trial-Image) depicts Bernard Tomic and the detected areas found.
+Online demos were used to test viability, Figure \ref{fig:Trial-Image} depicts Bernard Tomic and the detected areas found.
 
@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics of the scene occuring when the still shot was taken, one option for each category was selected for each image.")
+kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics of the scene occuring when the still shot was taken, one option for each category was selected for each image.")
 ```
@@
 
-Table \@ref(tab:Face-Attribute-Tables) summarises attribute information recorded for each face.
+Table \ref{tab:Face-Attribute-Tables} summarises attribute information recorded for each face.
 
 ```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
-knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics of the faces captured, one option for each category was selected for each face manually tagged.")
+kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics of the faces captured, one option for each category was selected for each face manually tagged.")
 ```
@@
 
-Figure \@ref(fig:timeFigure) shows the distribution of processing time required by the APIs for each image.
+Figure \ref{fig:timeFigure} shows the distribution of processing time required by the APIs for each image.
 The violin plot display created by @Violin 'combines the box plot and the density'.
@@
 
-As seen in the facets of Figure \@ref(fig:timeFigure), both Microsoft and Google had few images which took a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
+As seen in the facets of Figure \ref{fig:timeFigure}, both Microsoft and Google had few images which took a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
 The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs.
@@
 
-```{r timeFigure, fig.height=6, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered, displayed as violins.
+```{r timeFigure, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered, displayed as violins.
 The width of the violin shows the most common times for the group of images.\\label{fig:timeFigure}"}
@@
 
-knitr::kable(timetable, booktabs = TRUE, longtable=TRUE, caption="This table allows comparisons to be made between the  amount of time taken for each API took to detect faces in each image.
+kable(timetable, booktabs = TRUE, longtable=TRUE, caption="This table allows comparisons to be made between the  amount of time taken for each API took to detect faces in each image.
 Most of the images take less than one second to process.
@@
 
-knitr::kable(ModelEstimatesTable, format = "latex", align=c('l', 
+kable(ModelEstimatesTable, format = "latex", align=c('l', 
                                            'r', 'l',
@@
 
-Table \@ref(tab:facecounts) displays the proportion of the manually tagged faces that the APIs detected.
+Table \ref{tab:facecounts} displays the proportion of the manually tagged faces that the APIs detected.
 Google had by far the best detection rate.
@@
 
-Figure \@ref(fig:FaceUpset) is a set visualization to examine the intersection of the APIs, and the manual annotations.
+Figure \ref{fig:FaceUpset} is a set visualization to examine the intersection of the APIs, and the manual annotations.
 This is produced with the UpSetR [@UpSetR] package.
@@
 
-Animetrics provided many surprises. Figure \@ref(fig:UnusualImages) shows four images and the captures where non-faces were detected as faces. In image (A) the player's back is detected as a face.
+Animetrics provided many surprises. Figure \ref{fig:UnusualImages} shows four images and the captures where non-faces were detected as faces. In image (A) the player's back is detected as a face.
 In image (B) the KIA logo was reported as a face. 
@@
 ImageCharacteristics<-ImageCharacteristics[1:5,]
-knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=FALSE, format.args=list(width=8), caption="Top five most frequent image attribute combinations.", format = "latex")
+kable(ImageCharacteristics, booktabs = TRUE, longtable=FALSE, format.args=list(width=8), caption="Top five most frequent image attribute combinations.", format = "latex")
 ```
 
-```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (A) Angle of face capture, (B) court situation, (C) angle of capture by background, and (D) situtation of capture by background.
+```{r ICFigs, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (A) Angle of face capture, (B) court situation, (C) angle of capture by background, and (D) situtation of capture by background.
 Most face captures occurred at a level angle, and this produces slightly better detection.
@@
 
-Image characteristics (Table \@ref(tab:Scene-Attributes-Table)) were constructed during manual tagging.
-The scene information was tallied and the most common combinations of these features shown in Table \@ref(tab:Image-Characteristics-Table).
+Image characteristics (Table \ref{tab:Scene-Attributes-Table}) were constructed during manual tagging.
+The scene information was tallied and the most common combinations of these features shown in Table \ref{tab:Image-Characteristics-Table}.
 
-Figure \@ref(fig:ICFigs) examines the relationships between several of the image characteristics, and face detection by the Google API, using mosaic plots.
+Figure \ref{fig:ICFigs} examines the relationships between several of the image characteristics, and face detection by the Google API, using mosaic plots.
 Plot (A) compares the angle of capture by detection rate.
@@
 
-The mosaic \@ref(fig:ICFigs) (B) in Figure \@ref(fig:ICFigs), shows the amount of Faces captured during each possible situation.
+The mosaic \ref{fig:ICFigs} (B) in Figure \ref{fig:ICFigs}, shows the amount of Faces captured during each possible situation.
 It contrasts the proportion of the images captured in each situation that either did or did not match the faces annotated manually.
@@
 The use of accessories like glasses and head wear, visors or hats, is common during the Australian Open as play is mostly outdoors during daytime.
-Table \@ref(tab:accessories) shows player use of head wear and glasses, as tagged manually.
+Table \ref{tab:accessories} shows player use of head wear and glasses, as tagged manually.
 Most players do not have glasses, but head wear, either visors or hats, are very common.
@@
 
-Table \@ref(tab:glassesheadwear) compares the face capture rate of the different APIs for the player accessories, as compared to the manually tagged face attributes.
+Table \ref{tab:glassesheadwear} compares the face capture rate of the different APIs for the player accessories, as compared to the manually tagged face attributes.
 Conditional proportions are calculated two ways: (1) proportion of the manually tagged faces, (2) proportion detected with the accessory relative to without.

### 2018-01-31 paper/paper.Rmd
ackowledgement language
added keywords

@@
 - name: Stephanie Kobakian
-  thanks: The authors gratefully acknowledge Tennis Australia.
+  thanks: The authors gratefully acknowledge Tennis Australia providing data for this project.
   affiliation: Monash University
@@
 - R
+- statistics
+- glm
+- data visualization
 

### 2018-02-06 paper/paper.Rmd
trying to get rid of pandoc errors

@@
 fontsize: 11pt
-header-includes:
-    - \usepackage{booktabs}
-    - \usepackage{longtable}
 bibliography: references.bib
@@
 
-- The faces were recorded if it showed their face at a minimum of 20 by 20 pixels. 
-- The back of the head was not detected as a face by any software, these areas were classified manually but reclassified as other.
-- Crowd faces were not the intended targets of the recognition however these faces contributed to our understanding of the software. 
-- The same face size standard applied to crowd members, but focus was placed on the most prominent faces.
+\begin{itemize}
+\item The faces were recorded if it showed their face at a minimum of 20 by 20 pixels. 
+\item The back of the head was not detected as a face by any software, these areas were classified manually but reclassified as other.
+\item Crowd faces were not the intended targets of the recognition however these faces contributed to our understanding of the software. 
+\item The same face size standard applied to crowd members, but focus was placed on the most prominent faces. 
+\end{itemize}
 
@@
 grid.arrange(plots1, plots2, nrow=2)
-
 ```
@@
 
-- Animetrics: Animetrics Face Recognition API, FaceR API by @Animetrics.
-
-- Google: Google Cloud Vision API [-@Google]
-
-- Microsoft: Microsoft Azure Cognitive Services Face API, published by @Microsoft.
-
-- Skybiometry: @Skybiometry the spin off detection and recognition software of Neurotechnology.
+\begin{itemize}
+\item Animetrics: Animetrics Face Recognition API, FaceR API by @Animetrics.
+\item Google: Google Cloud Vision API [-@Google]
+\item Microsoft: Microsoft Azure Cognitive Services Face API, published by @Microsoft.
+\item Skybiometry: @Skybiometry the spin off detection and recognition software of Neurotechnology. 
+\end{itemize}
 
@@
 
-- ManualClassifiedFaces.csv contains the data collected on each face by manual tagging.
-- ManualClassifiedScenes.csv contains scene information about each image.
+\begin{itemize}
+\item ManualClassifiedFaces.csv contains the data collected on each face by manual tagging.
+\item ManualClassifiedScenes.csv contains scene information about each image.
+\end{itemize}
 

### 2018-02-07 paper/paper.Rmd
Blinded pdf

--- 2018-01-31 paper/paper.Rmd
@@
 # to produce blinded version set to 1
-blinded: 0
+blinded: 1
 
@@
 - R
-- statistics
-- glm
-- data visualization
 
@@
 
-```{r ICFigs, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (A) Angle of face capture, (B) court situation, (C) angle of capture by background, and (D) situtation of capture by background.
+```{r ICFigs, fig.height=7, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (A) Angle of face capture, (B) court situation, (C) angle of capture by background, and (D) situtation of capture by background.
 Most face captures occurred at a level angle, and this produces slightly better detection.

### 2018-02-07 paper/paper.Rmd
Paper section arrangement

@@
 ```
-
-#Abstract {-}
-
-This paper examines the effectiveness of facial detection APIs on broadcast video stills of Australian Open tennis matches.
-The goal is to determine the best API to use for face detection of players throughout a match.
-For training purposes faces were manually tagged in 6406 images, recording the scene characteristics and features of individual faces.
-This included information regarding accessories, such as head wear or sunglasses being worn.
-This enables the performance to be assessed based on conditions, and the APIs were evaluated on their success rate at detecting these faces.
-The possible obstacles of real time implementation were also assessed via the time taken to complete detection within an image.
 
@@
 
-# References
-
 <div id="refs"></div>

### 2018-02-12 paper/paper.Rmd
Expand Introduction

@@
 
-Many tennis professionals believe that tennis is a game heavily influenced by the mental states of the players.
-The opportunity for researching this "inner game" presents itself with the hope of improving the performance, and coaching of, tennis players by improving their "mental game".
-By statistically analyzing the faces and expressions of players during a match, insight may be gained about the mental state of a player and the effects changes in the mental state have on the outcome of a match.
-The aim of this project is to develop methods to collect accurate information about the facial expressions of elite tennis athletes during match play.
+The presence of emotions during professional tennis matches and the influence they have on athletes is often discussed in commentary, by players and coaches alike.
+However there is little quantitative evidence to support the theories and suggestions that the presence of emotions improves or impedes the performance of players. 
+As many tennis professionals believe it is a game heavily influenced by the mental states of the players there is an opportunity to analyse this "inner game", with the hope of improving the performance, and coaching of, tennis players.
+By statistically analyzing the faces and expressions of players during a match, insights may be gained about the mental state of a player and the effects changes in the mental state have on the outcome of a match.
+The aim of this study is to develop methods to collect accurate information about the facial expressions of elite tennis athletes during match play.
 
@@
 
-The aims of the present study were to determine the feasibility of using currently available APIs for extracting facial information of players during broadcasts of professional matches by comparing the performance of several popular facial recognition APIs.
+The aims of the present study were to determine the feasibility of using currently available APIs for extracting facial information of players during broadcasts of professional matches, by comparing the performance of several popular facial recognition APIs.
 A limited selection of accessible APIs was chosen based on their ability to produce appropriate and useful facial recognition.

### 2018-02-14 paper/paper.Rmd
Sample section edits

@@
 
-Images from the Australian Open 2016 were provided by Tennis Australia, with goal being that the sample is representative of the video files to be used for future facial recognition analysis: 6406 images, 800 $\times$ 450px
+Images from the Australian Open 2016 were provided by Tennis Australia, with the following specs: 6406 images, 800 $\times$ 450px
 
-To collect the images, 5 minute segments were taken from 105 video files, with a still shot stored every three seconds.
+Images were derived from, 5 minute segments taken from 105 video files, with a still shot stored every three seconds.
 The video files used were the broadcasts of the tennis matches shown on the Seven Network during the Australian Open 2016.
 The sample included an equal amount of females and males singles tennis matches.
-The rounds of the competition vary so as to not limit the pool of players to only those who progressed, though there was a higher chance of advancing players reappearing.
-
-The sample included images that contained the faces of many people, such as players, staff on the court and fans in the crowd.
-All of these faces were included in the manual annotations as they were likely to be found by the software selected.
-It was decided that including these additional faces would allow better evaluations of the software's capabilities, and provide information to differentiate between players and other faces captured.
-Therefore the sample was not filtered at this initial stage.
-
+Images contained the faces of many people, such as players, staff on the court and fans in the crowd. The sample was not filtered at this initial stage.
 Matches played during the Australian Open are played on a range of courts available at Melbourne Olympic Park.
@@
 ```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
-kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics of the scene occuring when the still shot was taken, one option for each category was selected for each image.")
+kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Summary of extracted scene information for match images.")
 ```
@@
 ```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
-kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics of the faces captured, one option for each category was selected for each face manually tagged.")
+kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Summary of extracted face information for match images")
 ```

### 2018-02-16 paper/paper.Rmd
Sample and software section edits

@@
 
-##Sample and sampling approach
+## Sample and sampling approach
 
-Images from the Australian Open 2016 were provided by Tennis Australia, with the following specs: 6406 images, 800 $\times$ 450px
-
-Images were derived from, 5 minute segments taken from 105 video files, with a still shot stored every three seconds.
+Images from the Australian Open 2016 were provided by Tennis Australia. There were 6406 images, 800 $\times$ 450px.
+The images were derived from 5 minute segments taken from 105 video files, with a still shot stored every three seconds.
 The video files used were the broadcasts of the tennis matches shown on the Seven Network during the Australian Open 2016.
 The sample included an equal amount of females and males singles tennis matches.
-Images contained the faces of many people, such as players, staff on the court and fans in the crowd. The sample was not filtered at this initial stage.
-Matches played during the Australian Open are played on a range of courts available at Melbourne Olympic Park.
-The sample was selected to be representative of the seven courts that have the Hawk Eye technology enabled.
+Images contained the faces of many people, such as players, staff on the court and fans in the crowd.
 
-##Software selection
+## Software selection
 
@@
 
-##Software usage
+##Software Processing Time
 
 The face recognition software APIs were accessed via a R [@R] script, calling the APIs relied on the httr [@httr] package.
-The scripts looped through the images, individually posting a request to retrieve information provided and convert it into an appropriate format for analysis.
 Special handling was required due to the limits on requests per minute of Skybiometry and Microsoft, time-controlling and error management of the requests was incorporated for these APIs.
@@
 The width of the violin will now be twice the length that would be have been measured vertically in a density plot.
+The lines overlaid in each plot represent the smoothed linear model of the amount of faces, it can be seen that all APIs take longer to complete detection of faces in an image when there are more faces.
 
-As seen in the facets of Figure \ref{fig:timeFigure}, both Microsoft and Google had few images which took a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network.
-The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs.
+As seen in the facets of Figure \ref{fig:timeFigure} times taken to search are varied between APIs, but Skybiometry consistently spent less time than other APIs.
 Microsoft and Google's times vary regardless of the number of faces found.
-The lines overlaid in each plot represent the smoothed linear model of the amount of faces, it can be seen that all APIs take longer to complete detection of faces in an image when there are more faces.
-As all APIs had more images where only one or two faces were found it resulted in more variability in the amount of time taken.
 

### 2018-02-16 paper/paper.Rmd
Validation and resultsection included

@@
 
-##Results
+##  Validation
 
-The manual tagging helped to provide a benchmark for faces found by APIs. The
-face detection rate indicated what attributes of an image or face were associated with face detection by an API. 
+Descriptive statistics were used to discern differences in the performance of the four APIs. These are presented in tables and plots and discussed in the results section.
+A logistic regression was used to study the effect of conditions and accessories on the detection performance of the APIs.
+
+## Regression Analysis
+
+A logistic regression model was used to assess the characteristics of the face and scene that may have affected the detection likelihood of the face.
+A step-wise variable selection method was used to find variables of significance for any of the APIs.
+The binary response was whether the face was detected or not, using the manually tagged data as the benchmark, and characteristics included the setting, angle of shot and player, background, lighting and player adornments.
+Variables that were not included denoted whether there was a graphic or live shot visible, the role of the person whose face was captured and whether or not there was a person in the image.
+A separate model was fit using the faces for each API.
+
+# Results
+
+The manual tagging helped to provide a benchmark for faces found by APIs. The face detection rate indicated what attributes of an image or face were associated with face detection by an API. 
 Faces that were found by multiple APIs indicated either obvious facial features were visible or the APIs may be using similar criteria to detect faces.
@@
 
-### Modeling detection rate
-
-A logistic regression model was used to assess the characteristics of the face and scene that may have affected the detection likelihood of the face.
-A step-wise variable selection method was used to find variables of significance for any of the APIs.
-The binary response was whether the face was detected or not, using the manually tagged data as the benchmark, and characteristics included the setting, angle of shot and player, background, lighting and player adornments.
-Variables that were not included denoted whether there was a graphic or live shot visible, the role of the person whose face was captured and whether or not there was a person in the image.
-detect
-A separate model was fit using the faces for each API.
+## Modeling detection rate
 
@@
 For the most part, the APIs were all affected by the same factors.
-Those that negatively affected all APIs were glasses, visor or hat.
-Background only negatively affected Google's detection rate.
-Situation had different effects on each API.
-Results for Google were most interesting in the shot angle had differing effects on the detection.
+The factors that negatively affected all APIs were glasses, visor or hat. Background only negatively affected Google's detection rate. Situation had different effects on each API.
+When the shot angle was considered in conjunction with the background the results for Google showed there was a positive effect on detection rate of faces in all circumstances.
+There was no significant impact on the other APIs.
 
 ```{r UnlikelyFace, fig.cap = "The face captured manually in this image was not captured by any API.
-The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}", dev="jpeg", dpi=300}
+The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match are all associated with lower rates of detection.\\label{fig:UnlikelyFace}", dev="jpeg", dpi=300}
 
@@
 
-When forcing no intercept, all variables are significant at the 0 level, and obscured is only significant at the 0.001 level.
+When forcing no intercept, all variables are significant at the 0 level, and obscured was significant for all four up to the 0.01 level.
 
-### Detection rates and API comparison
+## Detection rates and API comparison
 

### 2018-04-23 paper/paper.Rmd
Extended on abstract, validation, discussion

@@
   This paper examines the effectiveness of facial detection APIs on broadcast video stills of Australian Open tennis matches.
-The goal is to determine the best API to use for face detection of players throughout a match.
+The aim was to evaluate the performance of several APIs to determine the best API to use for face detection of players throughout a match.
 For training purposes, faces were manually tagged in 6406 images, using a specially constructed web application, recording the scene characteristics and features of individual faces, such as head wear or sunglasses.
 API performance was evaluated on their success rate at detecting the tagged faces, and also relative face and scene attributes.
+Google found 1319 faces, this amount is 0.57 of the manually tagged faces, it also found an additional 638 relevant faces that were not tagged manually.
+A logistic regression was used to determine the effects of the scene characteristics and features of individual faces on the likelihood of an API detecting the face.
+It showed all APIs were significantly affected by features of individual faces, and not all were significantly impacted by scene attributes.
+It would be expected that, in future, utilising cameras with a focus on the player's faces would be necessary to improve detection of faces and minimise impacts of features of individual faces.
 
@@
 
-Descriptive statistics were used to discern differences in the performance of the four APIs. These are presented in tables and plots and discussed in the results section.
+Descriptive statistics were used to discern differences in the performance of the four APIs.
+These are presented in tables and plots and discussed in the results section.
 A logistic regression was used to study the effect of conditions and accessories on the detection performance of the APIs.
+The estimates shown indicate the magnitude of the impact on the detection rate, and the symbols shown indicate the significance, or reliability, of the estimated impact.
+Proportions were used a simplistic comparison to indicate the amount of the total faces that were detected by the software.
+Faces were grouped by the softwares that detected them, these groups and the attributes of the faces within them show the common features that contributed to a face being detected.
+Mosaic plots also examine faces that posessed a combination of features. Two way feature intersections show the common intersections of manually tagged faces.
+Some examples of intersections across four variables are displayed in a table format, only the most common feature combinations were displayed.
 
@@
 
-# SignificancePlot <- function(model, data = GlmModelEstimates(model)) {
-#   data %>%
-#   mutate(significant = `Pr(>|z|)` < 0.05) %>%
-#   ggplot(aes(x=type, y=`Pr(>|z|)`)) +
-#   geom_col(aes(fill=significant)) + 
-#   facet_wrap(~ variable) +
-#   coord_flip()
-# }
-
 EstimatesPlot <- function(model, data = GlmModelEstimates(model)) {
@@
   ep<-EstimatesPlot(model, data)
-  #sp<- SignificancePlot(model, data) 
-  grid.arrange(ep)#, sp)
+  grid.arrange(ep)
 }
@@
 TypeGlms <- GlmModelCreation(model=TypeModel)
+
+#modSummaries <- map(TypeGlms, broom::glance)
+
 ModelEstimates <- GlmModelEstimates(data=TypeGlms)
@@
 0.01 - NS).
-Most APIs wre affected by similar factors, with glasses, visor or hat, head angle, lighting, shot angle and situation all contributing significantly to face detection.")
+Most APIs were affected by similar factors, with glasses, visor or hat, head angle, lighting, shot angle and situation all contributing significantly to face detection.")
 ```
@@
 
-# Future Work
+# Discussion
 
-This paper has described the results of a survey of commonly available software for face detection when applied to stills from tennis match video.
+This paper has compiled results from applying commonly available software for face detection to a set of stills from tennis match video.
+The set of detected faces from each software were able to be contrasted against manually tagged faces and those found by other software.
+This combined set has allowed the performance of the software to be analysed under a range of circumstances.
+The varying accessories, camera angles and scene attributes noted for each manually tagged face allow a reference point to determine how the detection rates of the software are influenced.
+If an image set shows similar features to those exhibited in the Australian Open broadcast stills this will highlight the impacts the features will have on the software's ability to produce relevant detections.
+
+If an image set utilised a camera angle that captured a person's profile, using Animetrics, Microsoft or Skybiometry would significantly reduce the rate of detection.
+The logistic regression contributed to understanding the impacts of face and scene features in a measurable way.
+For each software it utilised the set of manually tagged faces to analyse impacts on detection.
+This analysis showed
+
 A long term goal is to detect emotional state of the player, and track this through a match, to study the effect on performance.
